### 2022-10-09 paper/Paper.tex
fix to typo in citations committing updated paper.tex with LNCS format

\documentclass[runningheads]{llncs}

%KYR: need to ensure included packages don't interfere with LNCS style
%\usepackage[utf8]{inputenc}
%\usepackage{amsthm, amsmath, amssymb}
\usepackage{amsfonts} %mathbb
\usepackage{amsmath} %hdots
\usepackage{mathabx} %vDash
\usepackage{mathrsfs} %mathscr
\usepackage{blkarray} %for blockarray
%\usepackage{textcomp}
%\usepackage{xcolor}
%\usepackage{soul}
%\usepackage{ dsfont }
\usepackage{hyperref}
\usepackage{cancel} %for \cancel
\usepackage{algorithm} %for algorithm environment
\usepackage{algcompatible}
\usepackage[noend]{algpseudocode}
%\usepackage{changepage}%http://ctan.org/pkg/changepage
\usepackage{graphicx} %for includegraphics
\usepackage{tikz}
\usepackage{lscape} %for landscape orientation
%\usepackage{float} %for figures
\usetikzlibrary{shapes.misc, positioning}
\usetikzlibrary{arrows.meta}
\tikzset{>={Latex[width=2mm,length=2mm]}}

%% \hypersetup{
%%     colorlinks=true,
%%     linkcolor=blue,
%%     filecolor=magenta,
%%     urlcolor=red,
%%     citecolor=teal
%% }

%LNCS:
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Spacing Magic
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{pslatex} % DON'T REMOVE!  BUYS US HALF A PAGE OR MORE!!!!!
%Use only in case of emergencies: \linespread{0.98} %KYR: make lines spaces .99 instead of 1 to save space
\usepackage{times} %KYR: substitute for pslatex that does not mess up math :)

\usepackage{enumitem}
\setlist[itemize]{noitemsep, nolistsep, topsep=0pt, partopsep={0pt}}

%CAUTION: dirty trick; questionably allowed... use ONLY in case of emergencies!
% \linespread{0.99}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure Magic
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{epsfig}
\usepackage{float} % put figure in minipage
%\usepackage{framed}
%\usepackage{subfigure}

% diagonal line in the table
%\usepackage{diagbox}

\usepackage{enumitem}
\newlist{Properties}{enumerate}{2}
\setlist[Properties]{label=Property \arabic*.,itemindent=*}

%\usepackage{tikz}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%            \node[shape=circle,draw,inner sep=0.5pt] (char) {#1};}}
%
%\newcommand{\VarPhiSequence}{\ensuremath{\langle T_{\varphi} \rangle}\xspace}
%\newcommand{\ExSeq}[1]{\ensuremath{\langle T_{#1} \rangle}\xspace}
%\newcommand{\ExSeqElement}[2]{\ensuremath{\langle T^{#1}_{#2} \rangle}\xspace}
%\newcommand{\IN}{\mathbb{N}}

% draw box around text
\usepackage{tcolorbox}

\renewcommand{\topfraction}{.99} %figures can take up at most 99% of the page before being alone
\renewcommand{\bottomfraction}{.99} %figures can take up at most 99% of the page before being alone
\renewcommand{\textfraction}{.01} %at most this % of page will be text before making figure-only page
\addtolength{\textfloatsep}{-5mm}
\addtolength{\floatsep}{-5mm}
\addtolength{\intextsep}{-5mm}
\addtolength{\abovecaptionskip}{-3mm}
\addtolength{\belowcaptionskip}{-2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\phi}{\varphi}

%\theoremstyle{definition}
%\newtheorem{proposition}{Proposition}
%\newtheorem{remark}{Remark}
%\newtheorem{example}{Example}
%\newtheorem{definition}{Definition}
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}

\def\nuXmv{{\sf nuXmv}\xspace}

\begin{document}
%
%\title{Contribution Title\thanks{Supported by organization x.}}
\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [ommitted for blind review]}}
%
\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%\author{Jenna Elwing\thanks{University of Michigan, Ann Arbor} \and Laura Gamboa Guzmán\thanks{Iowa State University} \and Jeremy Sorkin\thanks{The Ohio State University} \and Chiara Travesset\thanks{Purdue University} \and Zili Wang\thanks{University of California, Berkeley} \and Kristin Y. Rozier\footnotemark[2]}
%
%\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
%\institute{Princeton University, Princeton NJ 08544, USA \and
%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
%\email{lncs@springer.com}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
%\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%

\begin{abstract}
        \noindent Mission-time Linear Temporal Logic (MLTL) is an extension of propositional logic that allows temporal quantifiers over finite discrete intervals. A computation is a finite sequence of truth assignments. In this paper, we use regular expressions to describe the structure of the computations that satisfy a given MLTL formula. We prove soundness and completeness of our structure. We also give an implemented algorithm (the WEST program) and analyze its complexity both theoretically and experimentally. Finally, we generate a test suite using control flow diagrams to robustly test the code.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}

\section{Introduction}

System specifications, such as aerospace operational concepts, often utilize timelines to express critical requirements. We can cite examples of this from NASA's Automated Airspace Concept \cite{EH10}, the U.~S.~Navy's Aircraft Carrier Deck Scheduler \cite{RCRBS11}, the JAXA-NASA Global Precipitation Measurement (GPM) Observatory \cite{GPM}, and many others. Formal methods provide continuously-advancing tools and techniques to rigourously analyze timelines expressed in the form of temporal logic requirements, from early design-time model checking and theorem proving to on-board runtime verification. The U.~S.~Federal Aviation Administration (FAA) even advocates the use of formal methods for flight certification of these critical systems \cite{DO-178C,DO-254,DO-333}. Yet, a significant hurdle to the use of formal methods remains: how to convincingly demonstrate to the humans in the loop, from system designers to certifiers, that the analyzed formulas truly represent the system requirements \cite{Roz16}. We creatively address this validation question using regular expressions and truth tables.

NASA, for example, has developed several tools that operate over temporal logic requirements, such as FRET\cite{GMRPSS20}, R2U2\cite{RS17}, and a PVS library \cite{CTGPD22} for the logic MLTL (Mission-time Linear Temporal Logic) \cite{RRS14,LVR22}. MLTL was the logic used recently in NASA's Robonaut2 verification project \cite{KZJZR20} and is being used currently for both design-time and runtime verification of the NASA Lunar Gateway Vehicle System Manager \cite{DBR21}. Other recent verification %verification-for-certification
efforts involving MLTL include a JAXA autonomous satellite \cite{JAXA}, a UAS Traffic Management (UTM) system involving Collins and Mosaic Aerospace \cite{HCHJR21}, a sounding rocket \cite{HLR21}, and multiple small satellites \cite{LLR21,LJBHCLR22,AJR22}. However, all of these successful verificaiton efforts were carried out by groups specializing in formal methods research. To enable broader application of formal verification, and adoption across larger projects, we critically need better validation, e.g., so that analysis over MLTL-specified requirements can tranparently contribute to flight certification.

Many specifications from case studies, in logics such as MTL \cite{AH90} and STL \cite{MN04} fall within the MLTL fragments of these logics. 
Variations on Metric Temporal Logic (MTL) such as MLTL grow increasingly popular, in part due to their comparatively tractable complexity-to-expressibility trade-offs \cite{OW08}.
The model checker {\sf nuXmv} encodes a popular subset of MLTL for use in symbolic model checking \cite{nuXmv-v1.1.0}.%, where the $\Box$ and $\Diamond$ operators of an \texttt{LTLSPEC} can have integer bounds \cite{nuXmv-v1.1.0}, though bounds cannot be placed on the $\U$ or $\V$ (the Release operator of \nuxmv) operators.

We show that our contributions not only fill a critical gap in temporal logic valiation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C code from temporal logic behavior descriptions.

%% Mission-time Linear Temporal Logic (MLTL) extends propositional logic by including temporal operators over finite discrete intervals. It is useful for writing specifications for spacecraft, rovers, aircraft, and other robotic missions \cite{LVR22}. In standard propositional logic, a convenient way to check that a formula captures a specification correctly is to write out its truth table and check that the formula behaves in the desired manner. The same strategy can be employed for MLTL, but the truth tables increase in size at a much faster rate, making them too large to be useful. For instance, an MLTL formula with just two propositional variables and 10 time steps would require $\left(2^{10}\right)^2 = 2^{20}$ rows. This is often called the ``State Explosion Problem" \cite{stateexp}.

%% In this paper, we offer a remedy to the state explosion problem by using regular expressions to describe the set of all computations satisfying a MLTL formula, which significantly reduces the space needed to express the computations. We implement these regular expressions into the WEST program, which allows the user to input a MLTL formula and obtain the satisfying computations. The WEST program can be found on its \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{Github} repository.

The structure of the paper is as follows. In section \ref{prereq}, we build on the semantics of MLTL to define a computation, and its bit string representation. % of a computation that is used throughout the paper and the WEST program. Finally, we describe negation normal form (NNF), a standardized way to express MLTL formulas. By writing the MLTL formulas in NNF, the WEST program is able to run much more efficiently.
%
In section \ref{regex}, we recursively define regular expressions encapsulating the satisfying computations of MLTL formulas and prove that our new translation algorithm is both sound and complete. In addition, we provide a calculation for the minimum computation length required to describe all the satisfying computations of a MLTL formula that slightly improves upon existing calculations in the literature. Finally, we show an application of the regular expressions of the satisfying computations by using them to prove an MLTL theorem. In particular, we show that $\alpha\mathcal{U}_{[a,b]}(\alpha\mathcal{U}_{[0,c]}\beta) = \alpha\mathcal{U}_{[a,b+c]}\beta$ and $\alpha\mathcal{R}_{[a,b]}(\alpha\mathcal{R}_{[0,c]}\beta) = \alpha\mathcal{R}_{[a,b+c]}\beta$.
%
We introduce a new tool, called WEST, that implements automated validation in section \ref{specs} %, we give the WEST code specifications. In particular, we describe the grammar that the program follows and give an overview of the important functions in the program.
%
calculate its space and time complexity, both theoretically and experimentally, in section \ref{complex}. We show that the theoretical worst-case complexity for both space and time is doubly exponential, but that the average case fares far better.
%
Section \ref{test} proves correctness of the algorithms and provides a test suite to show correctness of implementation with high confidence. Intelligent fuzzing techniques contribute to test suite construction from a state diagram representing the control flow of the algorithm. We also verify the correctness of outputs of the WEST program against a naive brute force implementation.
%
Section \ref{simpsection}, provides a combinatorial theorem for simplifying certain outputs of the WEST program. Formulas of the form $\alpha \equiv \beta$ to check for equivalence between two expressions can lead to outputs that are non-trivial to simplify. Section \ref{Conclusion} discusses impacts and future work.

\section{Mission-time LTL and Regular Expressions} \label{prereq}
\subsection{Mission-time Linear Temporal Logic}
Mission-time Linear Temporal Logic (MLTL) \cite{LVR22} is a finite variation of Linear Temporal Logic (LTL) \cite{bmc} over bounded discrete intervals. Instead of taking the LTL operators over an infinite time line, we restrict the operators to a finite time line, taking each temporal operator over a closed interval $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$. The syntax of an MLTL formula over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:
$$\alpha := \top \ | \ \bot \ | \ p \ | \ \neg \alpha \ | \ \alpha \land \alpha \ | \ \alpha \lor \alpha \ | \ \mathcal{F}_{[a,b]} \alpha \ | \ \mathcal{G}_{[a,b]} \alpha \ | \ \alpha \mathcal{U}_{[a,b]} \alpha \ | \ \alpha \mathcal{R}_{[a,b]} \alpha \footnote{For simplicity, we do not include parentheses in the grammar, but they may used as needed. The WEST program uses parentheses (see section \ref{specs} for more details).}$$

\begin{definition}[\emph{Computation}]
A computation of length $m$ is a sequence $\{\pi[i]\}_{i = 0}^{m-1}$ of sets of propositional variables, $\pi[i] \subseteq \mathcal{AP}$, where the $i$th set holds the propositional variables that are satisfied at the $i$th time step. That is, a propositional variable $p$ is true at time step $i$ if and only if $p \in \pi[i]$. We denote the suffix of $\pi$ starting at $i$ (including $i$) by $\pi_i$. Note that $\pi_0 = \pi$.
\end{definition}

We use a bit string representation for our computations. This representation is easy to describe using regular expressions and is convenient to code.

\begin{definition}[\emph{Bit String Representation}]
Let $p_0, p_1, ..., p_{n-1}$ be propositional variables for a fixed $n \in \mathbb{N}$. We represent a (finite) computation $\pi$ of length $m \in \mathbb{N}$ using a bit string representation as follows:
\begin{itemize}
    \item We represent a true assignment to a propositional variable by $1$ and a false assignment by $0$.
    \item For each time step $j \in [0,1,\hdots,m-1]$, we have a bit string of length $n$ where the $k$-th bit represents the truth assignment of the proposition $p_{k-1}$.
    \item We separate each time step by a comma and order the time steps in chronological order.
\end{itemize}
\end{definition}

\noindent We write that a computation $\pi$ is equal to its bit string representation. An example is given below.

\begin{example}
Suppose $n=2$. The bit string representation $\pi = 10, 01$ means that $p_0$ is true in the first time step and false in the second one, and that $p_1$ is false in the first time step and true in the second one.
\end{example}

\subsubsection{Semantics}
We say a computation $\pi$ as satisfies a given MLTL formula $\alpha$, written $\pi \vDash \alpha$, when\footnote{In MLTL, we do not include the Next ($\chi$) operator since $\mathcal{G}_{[1,1]}$ is equivalent to it.}:
\begin{align}
    &\pi \vDash p \text{ iff } p \in \pi[0]\\
    &\pi \vDash \neg \alpha \text{ iff } \pi \nvDash \alpha\\
    &\pi \vDash \alpha \land \beta \text{ iff } \pi \vDash \alpha \text{ and } \pi \vDash \beta\\
    &\pi \vDash \alpha \lor \beta \text{ iff } \pi \vDash \alpha \text{ or } \pi \vDash \beta\\
    &\pi \vDash \mathcal{F}_{[a,b]}\alpha \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \alpha\\
    &\pi \vDash \mathcal{G}_{[a,b]}\alpha \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \alpha\\
    &\pi \vDash \alpha \ \mathcal{U}_{[a,b]} \beta \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \beta \text{ and }\\
    & \indent \forall j \in [a, i-1]\ \pi_j \vDash \alpha \nonumber \\
    &\pi \vDash \alpha \ \mathcal{R}_{[a,b]} \beta \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \beta \text{ or }\\
    & \indent \exists j \in [a,b-1] \text{ such that } \pi_j \vDash \alpha \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \beta \nonumber
\end{align}

The reader may observe that in this paper, we define Release independently from Until. 
It is not uncommon for Release instead to be defined as the dual of Until \cite{bmc} \cite{LVR22}. 
These two definitions are in fact equivalent, and the full proof is provided in Appendix \ref{duality appendix}.

\subsection{Negation Normal Form}
All MLTL formulas can be written in negation normal form (NNF) \cite{bmc}. We require MLTL formulas to be written in NNF to generate the satisfying computations using regular expressions. Without this requirement, generating the satisfying computations requires taking complements of the languages described by regular expressions, which is a very expensive operation.
\begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
An MLTL formula $\alpha$ is in \emph{negation normal form} if
\begin{itemize}
    \item Any negation symbols appear only in front of propositional variables.
    \item We allow only the operations $\top$, $\bot$, $\land$, and $\lor$ from propositional logic.
    \item We allow only the operations $\mathcal{U}$ and $\mathcal{R}$ from MLTL.
\end{itemize}
\end{definition}

In the literature, NNF does not include the Finally and Global operators, as $\bot \mathcal{R}_{[a,b]} \alpha = \mathcal{G}_{[a,b]} \alpha$ and $\top \mathcal{U}_{[a,b]} \alpha = \mathcal{F}_{[a,b]} \alpha$. In this paper, we stray from the literature and include Finally and Global as part of NNF, as this is far more natural for writing our regular expressions that describe the satisfying computations of a MLTL formula.

\subsection{Regular Expressions}
  We use regular expressions (regex) to describe the form of the satisfying computations. 
\begin{definition}[\emph{Regular Expression \cite{sipser}}]
A \emph{regular expression} is a string that describes the form of a language. 
Let $\Sigma$ denote a finite alphabet. The empty set $\emptyset$, the empty string $\epsilon = ``"$, and any character in $\Sigma$ are constants defined to be a regular expression. 
Beyond that, we define regular expressions recursively. 
Suppose $R$ and $T$ are regular expressions. 
Then the following operations generate regular expressions:
\begin{itemize}
    \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
    \item \emph{(Kleene Star)} Denoted $R^*$, this operation describes the set of all strings made by concatenating any finite number (including zero) of strings described by $R$ together.
    \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$.
\end{itemize}
\end{definition}

\noindent We provide an example of each operation.
\begin{example}
Let $R$ describe \{`$a$', `$b$'\} and $T$ describe \{ `$c$', `$d$' \}.
\begin{itemize}
    \item $RT$ describes the set \{ `$ac$', `$ad$', `$bc$', `$bd$' \}.
    \item $R | T$ describes the set \{`$a$', `$b$', `$c$', `$d$' \}.
    \item $R^*$ describes the set \{ $\epsilon$, `$a$', `$b$', `$aa$', `$bb$', `$ab$', `$ba$', `$aaa$', `$aba$',... \}.
    \item $R^2$ describes the set \{ `$aa$', `$bb$', `$ab$', `$ba$' \}.
\end{itemize}
\end{example}

\noindent We provide examples of different regex and possible combinations of the above operations.
\begin{example}
Let `$a$', `$b$', and `$c$' denote characters in a finite alphabet.
\begin{itemize}
    \item $ab^*$ describes the set \{ `$a$', `$ab$', `$abb$', `$abbb$', ... \}.
    \item $a^*|b$ describes the set \{ $\epsilon$, `$b$', `$a$', `$aa$', `$aaa$', ...\}.
    \item $a(b^*)c$ describes the set \{ `$ac$', `$abc$', `$abbc$', `$abbbc$', ... \}.
    \item $(a | b)^3$ describes the set \{ `$aaa$', `$aba$', `$aab$', `$abb$', `$bbb$', ... \}.
\end{itemize}
\end{example}

\section{MLTL Regular Expressions} \label{regex}
  We introduce the following additional notation for our regular expressions that describe the satisfying computations of a MLTL formula:
\begin{definition}[\emph{Additional Notation}]
Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$. Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula. We use the following operations in the next section to describe the form of satisfying computations of the formula in the bit string representation:
\begin{itemize}
    \item $R \lor T$ denotes alternation. We use this notation to match our notation for set intersection defined below.
    \item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length. Note that in the bit string representation, $(,S^n)$, denotes a time step in which the truth value of all $n$ propositional variables does not matter.
    \item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
    \item We do not use the Kleene star since our computations are a fixed finite length.
\end{itemize}
\end{definition}
An example of these operations follows.
\begin{example}
Let there be $n = 2$ propositional variables, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$). Clearly $T$ is the longer regex by one time step, so we concatenate $,S^2$ to the right of $R$. Thus $T =1S,1S | S1,S1$ and $R = S1,SS$. Now the regexes are the same length, so we can perform set intersection and alternation:
\begin{itemize}
    \item $R \land T = 11,1S | S1, S1$.
    \item $R \lor T = S1,SS | 1S,1S | S1,S1 = S1,SS | 1S,1S$.
\end{itemize}
\end{example}

For the purposes of describing the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{`$0$' , `$1$', `$,$'\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\alpha, \beta$ well-formed MLTL formulas in negation normal form. We define the regular expression of satisfying computations for an MLTL formula as follows:
 \begin{align}
     &\text{reg}(\top) = S^n\\
     &\text{reg}(\bot) = \emptyset \\
     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta) \\
    &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
 \end{align}

 \subsection{Minimum Computation Length}
 These regular expressions describe all the satisfying computations of an MLTL formula of length $\text{complen}(\alpha)$, which is defined recursively below:
\begin{align}
    &\text{complen}(p_k) = \text{complen}(\neg p_k) = 1\\
    &\text{complen}(\alpha \land \beta) = \text{complen}(\alpha \lor \beta) = \max(\text{complen}(\alpha), \text{complen}(\beta))\\
    &\text{complen}(\mathcal{G}_{[a,b]} \alpha) = \text{complen}(\mathcal{F}_{[a,b]} \alpha) = b + \text{complen}(\alpha)\\
    &\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta))
\end{align}

Intuitively, $\text{complen}(\alpha)$ is the minimum computation length required to ensure that none of the intervals in $\alpha$ are out of bounds.
Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature. In \cite{KZJZR20}, $$\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha), \text{complen}(\beta))$$

whereas our minimum computation length for Until and Release is 
$$\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\mathbf{\text{complen}(\alpha)-1}, \text{complen}(\beta)).$$
We provide the proof for the minimum computation length of Until and Release below.
\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]
    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\alpha, \beta$ be well-formed MLTL formulas in NNF. The minimum computation length of Until and Release is given by $\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta))$.
\end{theorem}

\begin{proof}
The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Global, And, and Or.\\
 Recall that $\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)$. Thus
 \begin{align*}
     \text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) &= \max_{a \leq i \leq b} \left( \text{complen}(\mathcal{G}_{[a, i-1]} \alpha \land \mathcal{G}_{[i,i]} \beta) \right)\\
     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{complen}(\alpha), i + \text{complen}(\beta))\right)\\
     &= \max_{a \leq i \leq b} \left(i + \max(\text{complen}(\alpha) - 1, \text{complen}(\beta))\right)\\
     &= b + \max(\text{complen}(\alpha) - 1, \text{complen}(\beta)).
 \end{align*}
 Now recall that $\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)$. Thus
 \begin{align*}
     \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) &= \max \left( \text{complen}(\mathcal{G}_{[a,b]} \beta), \text{complen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)  \right)\\
     &= \max\left( b + \text{complen}(\beta), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)\\
     &= \max \left( b + \text{complen}(\beta), \max_{a \leq i \leq b-1} \left(\max(i + \text{complen}(\beta), i + \text{complen}(\alpha))\right) \right)\\
     &= \max \left( b + \text{complen}(\beta), \max(b-1+\text{complen}(\alpha), b-1+\text{complen}(\beta))\right)\\
     &= \max(b + \text{complen}(\beta), b-1+\text{complen}(\alpha), b-1+\text{complen}(\beta))\\
     &= b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta)).
 \end{align*}
 This completes the proof.
 \end{proof}

 \noindent Intuitively, this optimization of the minimum computation length of Until and Release makes sense:
 \begin{itemize}
     \item At the final time-step for $\alpha \mathcal{U}_{[a,b]} \beta$, if $\beta$ has not yet been assigned to be true in the computation, it will be assigned true because $\alpha \mathcal{U}_{[a,b]} \beta$ is a strong operator. Semantically, the truth value of $\alpha$ at this time interval doesn't matter; whether $\alpha$ is true or false, the computation for $\alpha \mathcal{U}_{[a,b]} \beta$ is satisfied.
     \item Likewise, in the case for $\alpha \mathcal{R}_{[a,b]} \beta$, if $\beta$ is true from the first to the last time-step, the truth value of $\alpha$ at the final time-step doesn't matter - the computation satisfies $\alpha \mathcal{R}_{[a,b]} \beta$ regardless of whether $\alpha$ is true or false.
 \end{itemize}

\subsection{Soundness and Completeness}
 We write $\mathscr{L}(\text{reg}(\alpha))$ to denote the language of reg($\alpha$). That is, the set of computations represented by the regular expression $\text{reg}(\alpha)$.

 \begin{theorem}[\emph{Soundness and Completeness}]
 For any well formed MLTL formula $\alpha$ in negation normal form, a computation $\pi$ with $|\pi| = \text{complen}(\alpha)$ satisfies $\alpha$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\alpha))$.
 \end{theorem}
 \begin{proof}
 We proceed by induction on the length of the formula.\\

 \noindent \textbf{Base Cases.}\\
 \noindent\textbf{reg($\top$)}\\
 Any computation $\pi$ satisfies $\top$, and $\mathscr{L}(\text{reg}(\top))$ is the set of all computations of one time step. Padding conventions extends this to the set of all computations of any positive number of time steps, so we are done.\\

 \noindent\textbf{reg($\bot$)}\\
 There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\

 \noindent\textbf{reg($p_k$)}\\
 For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
 $$S^{k} 1 S^{n-k-1}$$
 which is precisely reg($p_k$).\\

 \noindent\textbf{reg($\neg p_k$)}\\
 If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
 $$S^{k} 0 S^{n-k-1}$$
 which is precisely reg($\neg p_k$).\\

 \noindent\textbf{Inductive Step.}\\
 Suppose the theorem holds for MLTL formulas $\varphi$ and $\psi$. We now show that it holds for $\varphi \land \psi$, $\varphi \lor \psi$, $\mathcal{F}_{[a,b]} \varphi$, $\mathcal{G}_{[a,b]} \varphi$, $\varphi \ \mathcal{U}_{[a,b]} \psi$, and $\varphi \mathcal{R}_{[a,b]} \psi$.\\

 \noindent \textbf{reg($\varphi \land \psi$)}\\
 We know that $\pi \vDash \varphi \land \psi \text{ iff } \pi \vDash \varphi \text{ and } \pi \vDash \psi$.\\
 By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
 \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
 $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$

 \noindent \textbf{reg($\varphi \lor \psi$)}\\
 We know that $\pi \vDash \varphi \lor \psi \text{ iff } \pi \vDash \varphi \text{ or } \pi \vDash \psi$.\\
 By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
 \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
 $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$

 \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
 We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
 If $|\pi| = \text{complen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$. Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{complen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
 By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
 $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$

 \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
 We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
 Since $|\pi| = \text{complen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{complen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
 By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
 $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$

 \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
  We have that 
  $$\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } (\pi_i \vDash \psi \text{ and } \forall a \leq j < i, \pi_j \vDash \varphi).$$
  As argued in the Finally case, the length condition is satisfied.\\
  By the inductive hypothesis, $\pi_i \vDash \psi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\psi))$, or equivalently, \\
  $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[i,i]} \psi))$. Also, $\pi_j \vDash \varphi$ if and only if $\pi_j \in \mathscr{L}(\text{reg}(\varphi))$.\\
  By the argument used in the Global case, we see that $\forall a \leq j < i, \ \pi_j \vDash \varphi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a, i-1]} \varphi))$.\\
  Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently, 
  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$

  \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
  We have that
  \begin{align*}
    &\pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or } \\ 
    &\exists j\in[a,b] \text{ such that }
    (\pi_j \vDash \varphi \text{ and } \forall a\leq k \leq j, \pi_k \vDash \psi).
  \end{align*}
  As argued in the Global case, the first option for satisfying the formula never occurs.\\
  By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case. the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)\right)$. Hence

  \begin{align*}
    \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)\right) \\
    &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)\right)\\
    &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
  \end{align*}

 \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
 \end{proof}
 \newpage
\subsection{Nested Until and Release Rewriting Theorem}
 We prove the following theorem using the regular expressions above. As detailed in section \ref{complex}, nested binary temporal operators create the worst case time and space complexity for the WEST program. Although the WEST program does not implement this theorem, we would expect an implementation of this theorem to improve runtime. On its own, this theorem can be used to simplify MLTL formulas, making them easier to interpret.

\begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}]  Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas. Let $\mathcal{B} = \mathcal{R} \text{ or } \mathcal{U}$. Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \alpha,   \beta$ \text{be well-formed MLTL formulas in NNF. Then,} $ \alpha \ \mathcal{B}_{[a,b+c]} \beta = \alpha \ \mathcal{B}_{[a,b]}(\alpha \ \mathcal{B}_{[0,c]} \beta)$. That is, $ \alpha \ \mathcal{U}_{[a,b+c]} \beta \equiv \alpha \ \mathcal{U}_{[a,b]}(\alpha \ \mathcal{U}_{[0,c]} \beta)$ and $ \alpha \ \mathcal{R}_{[a,b+c]} \beta \equiv \alpha \ \mathcal{R}_{[a,b]}(\alpha \ \mathcal{R}_{[0,c]} \beta)$.
\end{theorem}
\begin{proof}

\textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\

\noindent Let $\gamma = \alpha \ \mathcal{U}_{[0,c]} \beta$. Then, $\alpha \ \mathcal{U}_{[a,b]}(\alpha \ \mathcal{U}_{[0,c]} \beta) = \alpha \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha \land \mathcal{G}_{[j, j]}\beta\right).$ Thus

\begin{align*}
\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\beta\right) \right) \right).
\end{align*}
$\mathcal{G}_{[i, i]}$ distributes over $\land$ and $\lor$, so
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\beta\right) \right) \right) \\
&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
\mathcal{G}_{[j, j]}\beta \right) \right) \right).
\end{align*}
Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \alpha \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \alpha$, we have
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta \right) \right) \right) \\
&= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta \right).
\end{align*}
Since $\mathcal{G}_{[t_1,t_2-1]}\alpha \land \mathcal{G}_{[t_2,t_3]} \alpha \equiv \mathcal{G}_{[t_1,t_3]} \alpha$, we have
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta  \right)\\
&= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta  \right).
\end{align*}
Finally, let $k = i + j$. Thus
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\beta  \right) \\
&= \text{reg}\left(\alpha \ \mathcal{U}_{[a,b+c]} \beta\right).
\end{align*}
This shows that $\alpha \ \mathcal{U}_{[a,b]}(\alpha \ \mathcal{U}_{[0,c]} \beta) \equiv \alpha \ \mathcal{U}_{[a,b+c]} \beta$.\\

\noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,  \\
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\beta\right) &= \text{reg}\left(\neg\left(\neg\alpha \ \mathcal{U}_{[a,b]}\neg\beta\right)\right) \\
&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\alpha \land \mathcal{G}_{[i, i]}\neg\beta\right)\right).
\end{align*}
Global is the dual of Finally, so
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\beta\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\alpha \land \neg\mathcal{F}_{[i, i]}\beta\right)\right)\\
&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\beta\right)\right)\right)\\
&= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\beta\right)\right)\\
&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\beta\right).
\end{align*}
This completes the rewriting of the regex for Release. Now let $\gamma = \alpha \ \mathcal{R}_{[0,c]} \beta$. Then $\alpha \ \mathcal{R}_{[a,b]}(\alpha \ \mathcal{R}_{[0,c]} \beta) = \alpha \ \mathcal{R}_{[a,b]}\gamma$ and
$\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha \lor \mathcal{F}_{[j, j]}\beta\right)$. Thus
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\beta\right) \right) \right).
\end{align*}
$\mathcal{F}_{[i, i]} \equiv \mathcal{G}_{[i, i]}$, so this operation distributes over $\land$ and $\lor$. Thus
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\beta\right) \right) \right) \\
&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\beta \right) \right) \right).
\end{align*}
Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \alpha \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \alpha$, we have
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta \right) \right) \right) \\
&= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta \right).
\end{align*}
Since $\mathcal{F}_{[t_1,t_2-1]} \alpha \land \mathcal{F}_{[t_2,t_3]} \alpha \equiv \mathcal{F}_{[t_1, t_3]} \alpha$, we have
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta  \right) \\
&= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta  \right).
\end{align*}
Let $k = i + j$. Thus
\begin{align*}
\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\beta  \right) \\
&= \text{reg}\left(\alpha \ \mathcal{R}_{[a,b+c]} \beta\right).
\end{align*}
Thus  $\alpha \ \mathcal{R}_{[a,b]}(\alpha \ \mathcal{R}_{[0,c]} \beta) \equiv \alpha \ \mathcal{R}_{[a,b+c]} \beta$, so $\alpha \ \mathcal{B}_{[a,b+c]} \beta \equiv \alpha \ \mathcal{B}_{[a,b]}(\alpha \ \mathcal{B}_{[0,c]} \beta)$. This completes the proof.
\end{proof}

\section{WEST Code Specifications} \label{specs}
 The code for the WEST program can be found on its \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{Github} repository. The MLTL syntax for our program is given as the context free grammar below. In the alphabet, $T$ and $!$ refer to the propositional constants `true' and `false', respectively. $\&$, $v$, $=$, $>$ refer to propositional logic operators `and', `or, `equivalent', and `implies', respectively. Note that the last comma listed is not a typo and indeed part of the alphabet. \\
\textbf{Alphabet}: 
\begin{align*}
    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `>' ,}\\
    &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
\end{align*}

\begin{align*}
    \text{Digit} &\to 0 \,|\, 1 \,|\,2 \,|\,3 \,|\,4 \,|\,5 \,|\,6 \,|\,7 \,|\, 8 \,|\, 9 \\
    \text{Num} &\to \text{Digit} \; \text{Num} \,|\, \text{Digit} \\
    \text{Interval} &\to [ \; \text{Num} \; : \; \text{Num} \; ] \\
    \text{Prop\_cons} &\to \text{T} \;|\; ! \\
    \text{Prop\_var} &\to \text{p} \; \text{Num} \\
    \text{Unary\_Prop\_conn} &\to \hspace{1mm}\scriptstyle{\sim} \\
    \text{Binary\_Prop\_conn} &\to \text{v} \;|\; \& \;|\; = \;|\; > \\
    \text{Assoc\_Prop\_conn} &\to \text{v} \;|\; \& \;|\; = \\
    \text{Array\_entry} &\to \text{Wff} \; , \; \text{Array\_entry} \;|\; \text{Wff} \\
    \text{Unary\_Temp\_conn} &\to \text{F} \;|\; \text{G} \\
    \text{Binary\_Temp\_conn} &\to \text{U} \;|\; \text{R} \\
    \text{Wff} &\to \text{Prop\_cons} \;|\; \text{Prop\_var} \\
               &\hspace{5mm} \;|\; \text{Unary\_Prop\_conn} \;\; \text{Wff} \\
               &\hspace{5mm} \;|\; \text{Wff} \;\; \text{Binary\_Prop\_conn} \;\; \text{Wff}\\
               &\hspace{5mm} \;|\; ( \; \text{Assoc\_Prop\_conn} \; [ \; \text{Array\_entry} \; ] \; ) \\
               &\hspace{5mm} \;|\; \text{Unary\_Temp\_conn} \;\; \text{Interval} \;\; \text{Wff} \\
               &\hspace{5mm} \;|\; ( \; \text{Wff} \;\; \text{Binar\_Temp\_conn} \;\; \text{Interval} \;\; \text{Wff} \; )
\end{align*}

In the grammar, associative propositional connectives (\textit{Assoc\_Prop\_conn}) are included for the ease of the user. Given well-formed formulas $\alpha_1, \alpha_2, \alpha_3$, the following formula in prefix notation $(\lor[\alpha_1, \alpha_2, \alpha_3])$ is parsed into $((\alpha_1 \lor \alpha_2) \lor \alpha_3)$, which is in turn equivalent to $(\alpha_1 \lor \alpha_2 \lor \alpha_3)$. \\
\begin{remark}
For two propositional variables, the associative equivalence operator functions identically to the binary propositional connective equivalence operator. For formulas with 3 or more propositional variables, however , the associative equivalence operator does not mean that each propositional variable in the list is equivalent. Instead, it means that the equivalence of the first two propositional variables in the list is equivalent to the next propositional variable in the list, and the truth value for this expression is equivalent to the next propositional variable, and so on. For example, =[p1,p2,p3] is equivalent to (p1=p2)=p3 rather than p1=p2=p3.
\end{remark}

In Appendix \ref{pseudocode appendix}, we provide the full pseudocode of the WEST program. Below we summarize only the important points to provide analysis of time and space complexity in the next section. The regular expression $R = \{R_1 | R_2 | ... | R_k\}$, where for all $1 \leq i \leq k$, $R_i \in \{$`0', `1', `S', `,'$\}^*$, is represented as a vector $R = {R_1, R_2, ..., R_k}$.

In order to compute MLTL operations, we define functions for handling union and intersection of such vectors. 
The \textit{join} function performs simple concatenation of two vectors, while the \textit{set\_intersect} function calculates pairwise intersection of strings from two vectors.
The intersection of two strings is performed by \textit{bit\_wise\_and}, which computes intersection character by character.
For example, \textit{bit\_wise\_and}$(1s, 0s)$ is the empty string while \textit{bit\_wise\_and}$(s11, 0s1) = 011$.

The main focus is on the recursive function \textit{reg}, which is based on the structure of the grammar. It computes the propositional logic operators $>$ and  $=$ through formula rewriting in terms of And and Or. The four temporal operators in the grammar are computed according to the definitions of their regexes (See section \ref{regex}).

If the user would like to see the satisfying computations for all the subformulas in their original formula, \textit{reg} contains a boolean to enable this functionality.

It is often the case that a vector of regular expression strings contains many redundancies, and can be simplified to a smaller vector of regular expressions that improves space complexity and drastically enhances user readability. 
As such, the \textit{simplify} function performs this by iterating through pairs of strings from the vector to search for valid simplifications. 
If a pair of strings$(w, v)$ can be written in the form $w = w_1 c_w w_2$ and $v = v_1 c_v v_2$ such that $w_1 = v_1$ and $w_2 = v_2$, then they are combined into one string $w_1 (c_w | c_v) w_2$.

\section{Complexity} \label{complex}

\subsection{Theoretical Complexity}
 In order to reason about the complexity of our algorithms, we make a few reasonable assumptions about our inputs.
Suppose that the lower and upper intervals of temporal operators are bounded by some constant $d \in \mathbb{N}$, and that the difference between any bound is less than some constant $\delta \in \mathbb{N}$. 
We provide a summary of the complexity of each of the helper functions described for \textit{reg}. 
For any function $f(\alpha)$ taking a string argument $\alpha$, we use $|\alpha|$ to denote the number of characters in $\alpha$ and $S(f(\alpha))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\

\textbf{If $\alpha$ is a propositional constant or variable:}
%\begin{adjustwidth}{10mm}{3em}
    It's easy to see that $S(\text{\emph{reg}}(!)) = 0$ since only the empty vector is returned. \\
    By definition $\text{\emph{reg}}(T) = S^n$, so we have that $S(\text{\emph{reg}}(T)) = O(n)$. Similar to $\alpha = T$, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)$ both return strings of the same length and thus we also have $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)) = S(\text{\emph{reg}}(T)) = n$.\\
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} \lor \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we return $\textit{join}(\text{\emph{reg}}(\alpha_{1}), \text{\emph{reg}}(\alpha_{2}))$ \\
    Thus, our space complexity is:
    \[
    S(\text{\emph{reg}}(\alpha_{1} \lor \alpha_{2})) = S(\text{\emph{reg}}(\alpha_{1})) + S(\text{\emph{reg}}(\alpha_{2})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} \; \& \; \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we return $ \textit{set\_intersect}(\text{\emph{reg}}(\alpha_{1}), \text{\emph{reg}}(\alpha_{2}), n)$ \\
    In the worst case, \textit{set\_intersect}($A$, $B$, $n$) will return a vector of size $S(A) \cdot S(B)$.\\
    Thus, our space complexity is:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} \; \& \; \alpha_{2})) = S(\text{\emph{reg}}(\alpha_{1})) \cdot S(\text{\emph{reg}}(\alpha_{2})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} >  \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} > \alpha_{2}$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \lor \text{''} + \alpha_{2} + \text{``)''}.
    \]
    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
    So for space complexity, we have:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} > \alpha_{2})) = S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) + S(\text{\emph{reg}}(\alpha_{2})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} = \alpha_{2}$'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} = \alpha_{2}$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = 
    \text{``((''} + \alpha_{1} + \text{``} \& \text{''} + \alpha_{2} + \text{``)}
    \lor 
    \text{(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \& \text{''} +  \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2}) + \text{``))''}.
    \]
    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
    So for space complexity, we have:
    \[ 
    S(\text{\emph{reg}}(\alpha_{1} = \alpha_{2})) =
    S(\text{\emph{reg}}(\alpha_{1})) \cdot S(\text{\emph{reg}}(\alpha_{2})) \; + \;  
    S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) \cdot S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\lor$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $\lor [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \lor \alpha_{2}) \lor ... \alpha_{k})\text{''}.
    \]
Using the space complexity of $\lor$, we have that:
    \[
    S(\text{\emph{reg}}(\lor [\alpha_{1}, .., \alpha_{k}])) = 
    \sum_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$\&$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $\& [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \& \alpha_{2}) \& ... \alpha_{k})\text{''}.
    \]
Using the space complexity of $\&$, we have that:
    \[
    S(\text{\emph{reg}}(\& [\alpha_{1}, .., \alpha_{k}])) = 
    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
    \]
%\end{adjustwidth}

\textbf{If} $\alpha$ \textbf{is} ``$=$ [$\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:}
%\begin{adjustwidth}{10mm}{3em}
For this case in our \emph{reg} function, we first rewrite $= [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
    \[ 
    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} = \alpha_{2}) = ... \alpha_{k})\text{''}.
    \]
Based on the space complexities of $\&$ and $\lor$, this gives:
    \[
    S(\text{\emph{reg}}(= [\alpha_{1}, .., \alpha_{k}])) = 
    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i}))
    + \prod_{i=1}^{k} S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{i}))).
    \]
%\end{adjustwidth}

 \textbf{If} $\alpha \text{ is } ``\mathcal{G}_{[a,b]} \alpha_{1}$"\textbf{:}
% \begin{adjustwidth}{10mm}{3em}
 Recall that $\text{\emph{reg}}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\alpha) (,S^n)^{b-i}$.\\
 As shown in the \textit{Assoc\_Prop\_Conn} case, if $\alpha$ is ``$\&[\alpha_1, ... ,\alpha_k$]", then \\
 $\text{S(\emph{reg}}(\& [\alpha_{1}, .., \alpha_{k}])) = 
    \prod_{i=1}^{k} \text{S(\emph{reg}}(\alpha_{i}))$. We have that:
 \begin{align*}
     \text{S(\emph{reg}}(\alpha)) &= \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\alpha_{1}))\\
     &< \Bigl([(n+1)b+1] \cdot \text{S(\emph{reg}}(\alpha_1))\Bigl)^\delta \\
     &= \mathcal{C}_{G} \cdot \text{S(\emph{reg}}(\alpha_1)^\delta 
 \end{align*}
 where $\mathcal{C}_{G} = [(n+1)b+1]^{\delta}$.
 In the calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a vector of only length 1 strings. \\
% \end{adjustwidth}

 \textbf{If} $\alpha \text{ is } ``\mathcal{F}_{[a,b]} \alpha_{1}$"\textbf{:}
% \begin{adjustwidth}{10mm}{3em}
 Recall that $\text{\emph{reg}}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\alpha)(,S^n)^{b-i}$. \\
 As shown in the \textit{Assoc\_Prop\_Conn} case, if $\alpha$ is ``$\lor[\alpha_1, ... ,\alpha_k$]", then \\
 $S(\text{\emph{reg}}(\lor [\alpha_{1}, .., \alpha_{k}])) = 
    \sum_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i}))$. Thus with similar calculation to $\mathcal{G}$,
 \begin{align*}
     \text{S(\emph{reg}}(\alpha)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\alpha_{1})) \\
     &< \delta\Bigl(((n+1)b+1) \cdot \text{S(\emph{reg}}(\alpha_1))\Bigl) \\
     &= \mathcal{C}_{F} \cdot \text{S(\emph{reg}}(\alpha_1)
 \end{align*}
 where $\mathcal{C}_{F} = \delta[(n+1)b+1]$.
% \end{adjustwidth}

 \textbf{If $\alpha$ = $``\alpha_1 \mathcal{U}_{[a, b]} \alpha_2"$:}
% \begin{adjustwidth}{10mm}{3em}
    By our previous definitions, 
    $\text{\emph{reg}}(\alpha_1 \ \mathcal{U}_{[a,b]} \alpha_2) =  \bigvee_{i=a}^{b} \text{\emph{reg}}\left(\mathcal{G}_{[a,i-1]}\alpha_1 \land \mathcal{G}_{[i, i]} \alpha_2\right)$. \\
    We can bound $S(\text{\emph{reg}}(\mathcal{G}_{[i, i]} \alpha_2))$ by $(n+1) \cdot i \cdot S(\text{\emph{reg}}(\alpha_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
    Thus using our previous results for the $\mathcal{G}$, $\&$ and $\lor$ operators, we have that:
    \begin{align*}
        S(\text{\emph{reg}}(\alpha)) &= 
        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\text{\emph{reg}}(\alpha_1))]^\delta 
        [(n+1) \cdot i \cdot S(\text{\emph{reg}}(\alpha_2))] \\
        &< \delta [((n+1)(b-1) + 1) \cdot S(\text{\emph{reg}}(\alpha_1))]^\delta 
        [(n+1) \cdot b \cdot S(\text{\emph{reg}}(\alpha_2))] \\
        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\text{\emph{reg}}(\alpha_1))^\delta \cdot S(\text{\emph{reg}}(\alpha_2)) \\
        &= \mathcal{C}_U \cdot S(\text{\emph{reg}}(\alpha_1))^\delta \cdot S(\text{\emph{reg}}(\alpha_2))
    \end{align*}
    where $\mathcal{C}_U = \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d$.
%  \end{adjustwidth}

  \textbf{If $\alpha$ = $``\alpha_1 \mathcal{R}_{[a, b]} \alpha_2"$:}
%  \begin{adjustwidth}{10mm}{3em}
        By our previous definitions, $\text{\emph{reg}}(\alpha_1 \mathcal{R}_{[a,b]} \alpha_2) =  \text{\emph{reg}}\left(\mathcal{G}_{[a,b]}\alpha_2\right) \lor \bigvee_{i=a}^{b-1} \text{\emph{reg}}\left(\mathcal{G}_{[a,i]}\alpha_2 \land \mathcal{G}_{[i, i]} \alpha_1\right)$. Thus, a similar argument to the $\mathcal{U}$ case gives us that: 
        \begin{align*}
            S(\text{\emph{reg}}(\alpha)) &< 
            \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
            \delta + \sum_{i = a}^{b-1} [\mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
            \delta \cdot (n+1)\cdot i \cdot S(\text{\emph{reg}}(\alpha_2))] \\
            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
            \delta + \delta[\mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
            \delta \cdot (n+1)(b-1) \cdot S(\text{\emph{reg}}(\alpha_2))] \\
            &= \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
            \delta [1 + \delta(n+1)(b-1)S(\text{\emph{reg}}(\alpha_2))] \\
            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
            \delta (\delta(n+1)d \cdot S(\text{\emph{reg}}(\alpha_2))) \\
            &= \mathcal{C}_R \cdot S(\text{\emph{reg}}(\alpha_1))^\delta \cdot S(\text{\emph{reg}}(\alpha_2))
        \end{align*}
        where $\mathcal{C}_R = \mathcal{C}_G \cdot \delta (n+1)d$. \\
%  \end{adjustwidth}

\begin{theorem}[\emph{Space Complexity}]
Given a well formed MLTL formula $\alpha$, $\text{\emph{reg}}(\alpha)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\alpha$. 
\end{theorem}
\begin{proof}
    To analyze worst-case complexity, it's clear from the analysis above that $\mathcal{U}$ and $\mathcal{R}$ give the largest complexity. From the constants in their respective bounds, we can show that $\mathcal{C}_U = ((n+1)d - n)^\delta \cdot \mathcal{C}_R > \mathcal{C}_R$, and so we'll analyze only repeated nesting of the operator $\mathcal{U}$.

    However, notice that the structure of the parse tree is important. For example, formulas similar to $(a \mathcal{U} b) \mathcal{U} (c \mathcal{U} d)$ generate a balanced binary parse tree where the maximum depth of recursion is $O(\log \ell)$. However if the nesting is only from one side, such as formulas similar to $(((p_0 \mathcal{U} p_1) \mathcal{U} p_2) \mathcal{U} p_3)$, then the maximum depth of recursion is $O(\ell)$. Thus we'll focus on the formula $$\alpha = (((p_0 \mathcal{U}_{[a_1, b_1]} p_1) \mathcal{U}_{[a_2, b_2]} p_2) \mathcal{U}_{[a_3, b_3]}... \mathcal{U}_{[a_{\ell - 1}, b_{\ell - 1}]} p_{\ell - 1}) \mathcal{U}_{[a_\ell, b_\ell]} p_\ell$$ where there are $\ell$ logical connectives $\mathcal{U}$ and $n = \ell + 1$ propositional variables.

    We'll derive the complexity of $S(\text{\emph{reg}}(\alpha))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\text{\emph{reg}}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\text{\emph{reg}}(p_{k+1}))$. The recurrence relation captures an extra nesting of the $\mathcal{U}$ operator, based on the complexity of $\mathcal{U}$ defined above. We calculate $S(p_m) = n = \ell + 1$ for all $m$ such that $0 \leq m \leq \ell$, thus $s_1 = \mathcal{C}_U(\ell + 1)^{\delta + 1}$ and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot (\ell + 1)$.

    The explicit formula is given by $s_k = \mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}$. It's easy to check that the base case $k = 1$ holds, and we prove the claim by induction:
    \begin{align*}
        S_{k + 1} &= \mathcal{C}_U (\mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}) ^ \delta \cdot (\ell + 1) \\
        &= \mathcal{C}_U^{1 + \sum_{i = 0}^{k - 1} \delta^{i + 1}} \cdot (\ell + 1)^{1 + \sum_{i = 0}^{k} \delta^{i + 1}} \\
        &= \mathcal{C}_U^{\sum_{i = 0}^k \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k+1} \delta^i}.
    \end{align*}

    \noindent Thus we have that $S(\text{\emph{reg}}(\alpha)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.

 \end{proof}

For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity. In particular, the time complexities of $\alpha = p_k, \scriptstyle{\sim}\textstyle p_k, T, !$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{C}_U$ match their respective space complexities. Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.

One feature within our implementation of \textit{reg} is to apply the \textit{simplify} function to all intermediary vector calculations in order to decrease the output size. In the worst case if no simplification occurs, space complexity remains unchanged, but time complexity of \textit{simplify} is cubic in input size. In practice however, both time and space complexities are much more optimistic than worst-case estimates.

\subsection{Experimental Benchmarking}
 Along with theoretical space and time complexity, we provide some experimental benchmarking of these complexities using randomly generated MLTL formulas.
This was done on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
For each simulation, we generated 1000 MLTL formulas using the parameters DELTA, INTERVAL\_MAX, number of propositional variables, and number of iterations. DELTA is the maximum length we allow for any interval. INTERVAL\_MAX is the largest allowed upper bound for any interval. Number of iterations refers to the level of nesting in the generated formulas. For example, $\mathcal{G}_{[0,2]}p_0$ is a formula generated with one iteration, while $\mathcal{G}_{[0,2]}(p_0 \land p_1)$ is a formula generated with two iterations. We measure the number of characters in the output and the amount of time in milliseconds taken to run the program. Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.

\subsubsection{Simulation 1}
For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. Below are some examples of generated formulas:
\begin{itemize}
  \item $(p_4 \land p_0) \mathcal{U}_{[2,3]} (\neg p_1)$.
  \item $(\mathcal{G}_{[3,5]} p_3) \mathcal{R}_{[7,8]} (p_3 \rightarrow p_0)$.
  \item $\mathcal{F}_{[1,6]} (p_4 = p_3)$.
\end{itemize}
We obtain the following plots:
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim1Length.png}
    \caption{Input length in number of characters vs output length in number of characters for simulation 1. Input length counts all characters, including parentheses, of the inputted formulas. Output length counts all the characters outputted, including commas.}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim1Time.png}
    \caption{Input length in number of characters vs run time in milliseconds for simulation 1. Input length counts all characters, including parentheses, of the inputted formulas.}
\end{figure}
\noindent The extreme outlier seen in the output length plot corresponds to the formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$.\\
The three extreme outliers seen in the time plot correspond to the formulas 
\begin{itemize}
    \item $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ (same formula as the complexity outlier).
    \item $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$.
    \item $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$.
\end{itemize}

\subsubsection{Simulation 2}
For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Below are some examples of generated formulas:
\begin{itemize}
    \item $\mathcal{F}_{[10,17]} p_4$.
    \item $\neg p_6$.
    \item $p_6 \mathcal{U}_{[6,14]} p_8$.
\end{itemize}
We obtain the following plots:
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim2Length.png}
    \caption{Input length in number of characters vs output length in number of characters for simulation 2. Input length counts all characters, including parentheses, of the inputted formulas. Output length counts all the characters outputted, including commas.}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim2Time.png}
    \caption{Input length in number of characters vs run time in milliseconds for simulation 2. Input length counts all characters, including parentheses, of the inputted formulas.}
\end{figure}

\subsubsection{Simulation 3}
For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. Below are some examples of generated formulas:
\begin{itemize}
    \item $(p_5 \land p_0) = (p_8 \mathcal{U}_{[3,6]} p_8)$.
    \item $(\mathcal{G}_{[6,7]} p_4) \land (\mathcal{F}_{[5,7]} p_1)$.
    \item $\neg (p_0 \mathcal{U}_{[2,5]} p_7)$.
\end{itemize}
We obtain the following plots:
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim3Length.png}
    \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim3Time.png}
    \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
\end{figure}
The three outliers in the output length plot are the formulas 
\begin{itemize}
    \item $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$.
    \item $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$.
    \item $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
\end{itemize}
The former two are also the time complexity outliers.

\subsubsection{Simulation 4}
For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. Below are some examples of generated formulas:
\begin{itemize}
    \item $\neg p_1$.
    \item $p_1 \mathcal{R}_{[6,7]} p_3$.
    \item $\mathcal{F}_{[5,5]} p_3$.
\end{itemize}

We obtain the following plots:
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim4Length.png}
    \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
\end{figure}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.75]{images/Sim4Time.png}
    \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
\end{figure}

\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively sparse. We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators. As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in practical applications.

\section{Verification of Correctness} \label{test}
 The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program). 
On one hand, correctness of an algorithm is assured by mathematical analysis of the algorithm on all possible inputs and showing that it behaves as desired. 
However, assuring correctness of the program is a difficult task.
One naive approach is to test every possible input up to a certain size, and verify the output or behavior of the program.
This often times involves a test suite that is too large to be computationally feasible, and the test suite may be overtly redundant. 
For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program for any reasonable party.

We approach this problem more intelligently. In the following sections, we prove the correctness of our algorithm and also test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm. A control path can be thought of as a sequence of lines of code that are executed in one calculation of an input formula. Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST program.

\subsection{Theoretical Correctness of the WEST Algorithm}
 Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}.

The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.

\textit{Join} takes as input two vectors of computation strings $R$ and $T$, and simply returns a vector containing all strings in $R$ and $T$, which is equivalent to $R \cup T$.

\textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ... | r_a$ and $T$ represents $t_1 | ... | t_b$ such that each $r_i$ and $t_j$ are regular expressions over $\Sigma = \{`0', `1', `S', `,'\}$. Assume that all strings of regular expressions are right padded to equal length. We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that 
\begin{align*}
    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^a \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^b \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^a \bigcup_{j = 0}^b \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
\end{align*}

\textit{Set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.  Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. $\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$. Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.

The correctness for \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, \textit{reg\_R}, and \textit{reg} will be proven by induction on depth of recursion to \textit{reg}. 
The depth of recursion is exactly the depth of the parse tree of the input formula.

For the base case (depth $0$), \textit{reg\_prop\_var} and \textit{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.

Then assume \textit{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$. Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$. $\gamma$ must be of the form $\mathcal{G}_{[a,b]}\alpha$, $\mathcal{F}_{[a,b]}\alpha$, $\alpha \mathcal{U}_{[a,b]} \beta$, or $\alpha \mathcal{R}_{[a,b]} \beta$, such that $\alpha$ and $\beta$ are of depth at most $d$, and $a$, $b$ are positive integers. The proof for all four cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.

We give the explicit proof for the case $\gamma = \alpha \mathcal{U}_{[a,b]} \beta$ as an example.
In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_alpha} = \textit{reg}(\alpha)$ and $\textit{reg\_beta} = \textit{reg}(\beta)$, which, by the induction hypothesis, are correctly and recursively computed.
The regular expression for the Until operator may be rewritten as follows: 
\begin{align*}
   \text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) &=  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
   &= \text{reg}\left(\mathcal{G}_{[a,a-1]}\alpha \land \mathcal{G}_{[a, a]} \beta\right) \lor \bigvee_{i=a+1}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
   &= \text{reg}\left(\mathcal{G}_{[a, a]} \beta \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\alpha \land \mathcal{G}_{[i+1, i+1]} \beta\right)
\end{align*}

The last line follows from the semantics of the Global operator, which defines out of bound time step behavior to be vacuously true. In the pseudocode for $reg\_U$ (\ref{regU}), the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_beta}, and is the regular expression for $\mathcal{G}_[a, a] \beta$. Next, the Or block from $i = a + 1$ to $b - 1$ is iteratively computed using \textit{set\_intersect} for the inner expression, and added to \textit{comp} with the \textit{join} function, which are both proven correct above. This shows correctness of \textit{reg\_U}.
Continue in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.

\subsection{Correctness of WEST}
 Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; fuzz testing (also know as fuzzing) is a form of negative testing.
The earliest use of fuzzing by Miller \cite{Miller} was to discover bugs in Unix utilities by randomly generating command line inputs, and monitoring for unexpected crashes or security. This style of black box testing assumes no prior knowledge of the target program, and is centered on generating a large quantity of inputs. Miller describes his approach in \cite{Miller} as follows: \\

 \textit{``If we consider a program to
be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''} \\

Intelligent fuzzing (sometimes referred to as whitebox fuzzing) is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage. 
Borrowing the words of Miller, our approach to testing the WEST program can be thought of as walking all possible paths up to a certain depth of the state space of our algorithm. 
We first outline our overall approach to intelligent fuzzing: 
\begin{enumerate}
    \item Construct a state diagram of our algorithm, represented as a directed graph. 
    The edges of the graph capture control flow of our algorithm, and vertices represent the remaining blocks of the code without branching statements.  
    \item Construct a test suite that explores all possible paths in the digraph up to a certain depth. Run the WEST program on the test suite to produce a set of output files.
    \item Run a naive brute force generator of satisfying computations on the test suite and verify that both outputs match for all test cases.
\end{enumerate}

\subsubsection{State Diagram Construction}
 We choose to represent the states space of algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements. 
The core of the WEST program is executed in the recursive routine, \textit{reg}, which calls the $8$ different subroutines discussed earlier, as shown in the graph below:

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, star/.style={circle, draw=red!60, fill=red!5, very thick, minimum size=1mm}]

    %Nodes
    \node[bignode](reg){\textbf{Reg}};
    \node[node](prop_var)[left=2 cm of reg]{Prop\_Var};
    \node[node](prop_cons)[below=of prop_var]{Prop\_Cons};
    \node[star](unary_star)[below=2 cm of reg]{};
    \node[node](reg_f)[below=of unary_star]{Reg\_F};
    \node[node](reg_g)[left= of reg_f]{Reg\_G};
    \node[star](temp_binary_star1)[right=2 cm of unary_star]{};
    \node[star](temp_binary_star2)[below= of temp_binary_star1]{};
    \node[node](reg_u)[below=of temp_binary_star2]{Reg\_U};
    \node[node](reg_r)[right=of reg_u]{Reg\_R};
    \node[star](prop_binary_star1)[right= of reg]{};
    \node[star](prop_binary_star2)[right= of prop_binary_star1]{};
    \node[node](join)[right=of prop_binary_star2]{Join};
    \node[node](set_intersect)[below=of join]{Set\_Intersect};

    %Lines
    \draw[->] (reg.west) -- (prop_var.east);
    \draw[->] (reg.south) -- (prop_cons.north);
    \draw[->] (reg.south) -- (unary_star.north);
    \draw[->] (unary_star.south) -- (reg_f.north);
    \draw[->] (unary_star.south) -- (reg_g.north);
    \draw[->] (reg.south) -- (temp_binary_star1.north);
    \draw[->] (reg.east) -- (prop_binary_star1.west);
    \draw[->] (temp_binary_star1.south) -- (temp_binary_star2.north);
    \draw[->] (temp_binary_star2.south) -- (reg_r.north);
    \draw[->] (temp_binary_star2.south) -- (reg_u.north);
    \draw[->] (prop_binary_star1.east) -- (prop_binary_star2.west);
    \draw[->] (prop_binary_star2.east) -- (join.west);
    \draw[->] (prop_binary_star2.south) -- (set_intersect.north);
    \end{tikzpicture}

    \caption{Abstracted graph of the \textit{reg} main routine (refer to Appendix \ref{graphs appendix} for expanded graph and graphs of helper functions). Red nodes signal recursive calls to \textit{reg} on sub formulas of the input formula.}
    \label{fig:abstracted graph}
\end{figure}

In order to construct the intelligent fuzzing test suite, we make the design choice to abstract away the eight subroutines in the overall state space diagram, despite the fact that they may have different possible execution paths within them. Without this abstraction, attempting to explore all execution paths in this finer graph is infeasible due to the explosion in the number of paths \cite{Pham_2016}, some of which are provably impossible to construct a test input to explore.

Additionally, the astute reader may observe that analysis of the $>$, $=$, and \textit{assoc\_prop\_conn} operators are not included in the state diagram. 
These cases are handled in the algorithm through only formula rewriting to the core operators. This is done through simple string manipulation, which is relatively simple to guarantee and test correctness of through unit testing.

\subsubsection{Creating the Test Suite}
 We now give the procedure of how the intelligent fuzzing test suite is generated. 
Firstly, we count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
For $d = 0$, only the paths leading to \textit{prop\_var} and \textit{prop\_cons} can be explored, so $\phi(0) = 2$. For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \textit{reg\_G} and \textit{reg\_F} is counted in the linear term, and paths \textit{reg\_U}, \textit{reg\_R}, \textit{set\_intersect}, and \textit{join} is counted by the quadratic term. 
This gives $\phi(1) = 20$, $\phi(2) = 1640$, and $\phi(3) = 10761680$. 
$d = 3$ is computationally infeasible, and $d = 1$ doesn't give us assurance about operators interacting with each other through nesting. Thus $d = 2$ is a happy medium.

The full test suite is generated in a similar recursive manner. 
Firstly, the $d = 0$ test suite comprises of two formulas: a propositional variable or its negation, and a propositional constant. 
Then for any $d \geq 1$, the test suite is constructed by iterating through all formulas in the depth $d-1$ test suite for \textit{reg\_G} and \textit{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths. 
To ensure wider coverage, each of the propositional variables or their negation and propositional constants are randomly generated (full pseudocode description in Appendix \ref{pseudocode appendix}).

\subsubsection{Verifying against Naive Brute Force}
 A relatively straight forward approach to generating the set of all satisfying computations of a MLTL formula $\alpha$ over $n$ variables, such that $m = \text{complen}(\alpha)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings. 
The main work is done by an interpreter function that takes arguments of computation $\pi$ and MLTL formula $\alpha$ and determines if $\pi \vDash \alpha$ purely based on semantics that define MLTL.
Every first-order quantifier is easily translated to loops, and checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
The full implementation details can be found on the \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{GitHub} repository.

As expected for a brute force implementation, extensive run time poses a major limitation; the previously mentioned infeasibility of not abstracting away subroutines and running test suites for deeper depths is primarily caused by this stage of verification. 
On an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM, the brute force program took nearly nine hours to execute the depth two test suite of $1640$ formulas. 
For this test suite, the number of propositional variables was fixed at $n = 4$ and the largest computation length was $m = 5$, from formulas with doubly-nested temporal operators. 
In comparison, the WEST program executed the same test suite in under thirty minutes on the same machine. One thing to note is that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the `$S$' characters in the regular expressions. For instance, the regular expression ``$1SS0SS1$" yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.

It's important to state that although the full test suite matches between both implementations, absolute correctness on all inputs is not guaranteed for either program. However, the successful execution of the test suite gives us a much higher confidence in correctness of both the WEST program and the brute force program.

\section{Regular Expression Simplification Theorem} \label{simpsection}
 As a final result of our paper, we provide a regular expression simplification theorem. This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all `$S$'s. Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of `$S$'s when a formula holds true for every computation. We first define some vocabulary.

\begin{definition}[\emph{Arbitrary Computation}]
We say a regular expression composed entirely of `$S$'s and commas is an \emph{arbitrary computation}. For the purposes of the following theorem, we remove all commas from computations.
\end{definition}
\begin{definition}[\emph{Fixed Truth Value}]
We say `0' or a `1' in a regular expression is a \emph{fixed truth value}.
\end{definition}
\begin{definition}[\emph{Matrix}]
We overload the definition of a matrix and say that a \emph{matrix} is a representation of a union of regular expressions, where each row is a regular expression. This aids significantly in the description and proof of the theorem; note, however, that matrix algebra does not apply in this definition. 
\end{definition}

\begin{theorem}[\emph{Regular Expression Simplification Theorem}] \label{simp}
Let M be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length n with commas stripped. If each column has one `$1$', one `$0$', and $n-1$ `$S$'s, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.
\end{theorem}

\noindent \textbf{Example:}
\vspace{-0.05\textwidth}
\begin{center}
\[
    \begin{pmatrix} \label{example1}
    1 & S & S & S\\
    S & 1 & S & S\\
    S & S & 1 & S\\
    S & S & S & 1\\
    0 & 0 & 0 & 0
    \end{pmatrix} = SSSS.
\]
\end{center}

\noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\

Note that the theorem is a sufficient but not necessary condition for simplification to the arbitrary computation. One such example is the regular expression $101|S1S|1S0|0SS$, which fails the hypothesis of the simplification theorem but is still equivalent to $SSS$.

\subsection{Implementation Challenges of the Regular Expression Simplification Theorem}

\begin{example} \label{example1}
Consider the MLTL formula:
$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$
\end{example}
Our program outputs the following union of regular expressions to represent this formula:

\begin{center}
    $
    \begin{pmatrix}
    1 & S & S & S\\
    S & 1 & S & S\\
    S & S & 1 & S\\
    S & S & S & 1\\
    0 & 0 & 0 & 0
    \end{pmatrix}.
$
\end{center}

Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation. However, we foresee some challenges to the implementation of this algorithm.

First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence. A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof. For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.

Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end. Consider the following MLTL formula:
\begin{example} \label{example2}
$T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$
\end{example}
\noindent The WEST program generates the following union of regular expressions:
\begin{center}
$
    \begin{pmatrix}
    S & S & 1 & S\\
    S & S & S & 1\\
    S & S & 0 & 0
    \end{pmatrix}.
$
\end{center}

It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.

Furthermore, identical substrings may be interspersed throughout the set of regular expressions. Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up" by common substrings. Consider the following modification to the matrix generated by example \ref{example1}:
\begin{center}
$
\begin{pmatrix}
  0 & \mathbf{1} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
  0 & \mathbf{S} & \mathbf{1} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
  0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{1} & \mathbf{S} & 1\\
  0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{1} & 1\\
  0 & \mathbf{0} & \mathbf{0} & 1 & S & 0 & \mathbf{0} & \mathbf{0} & 1\\
    \end{pmatrix} \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
$
\end{center}

The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively. In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for. Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.

\section{Closing Remarks}
\label{Conclusion}
 One goal of this research project is to visually represent MLTL formulas as truth tables, similar to classical truth tables in propositional logic. 
The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safe critical systems, and the WEST program can aide in the debugging of such specifications. 
The WEST program accomplishes this: given MLTL formula $\alpha$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions. 
The tool itself has demonstratively reasonable run time. 
Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very sparse in practice.

We have also applied techniques in intelligent fuzzing to explore the state space of the algorithm in a structured way. 
For a reasonably complex program, a complete walk of the input space is infeasible. 
However, basing testing on a (manually constructed) graph of the algorithm provides a middle ground where some level of coverage is guaranteed. 
Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used in algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.

\subsection{Additional Research Directions}
\textbf{Describe all satisfying computations to LTL formulas using $\omega$-regular expressions.}

$\omega$-regular expression are defined to match only infinite words, and can be used to describe satisfying computations to LTL formulas (which has infinite time steps). 
Our original efforts were spent reasoning about the general LTL case before restricting to MLTL. Particular difficulties revolves around the need for the Kleene star operation, which leads to messy arithmetic of infinite unions and intersections of regular expressions. \\

\noindent \textbf{Simplifying unions of regular expressions to a minimal representation.}

Theorem \ref{simp} addresses a non-trivial situation in which a vector of regular expressions may be simplified. A natural question to ask is what is the minimum number of strings of regular expressions needed to represent a language of computations. However, such a minimal representation is not unique. For instance, $\mathscr{L}(S1|1S) = \mathscr{L}(S1|10) = \{01, 10, 11\}$. There may be other schemes needed to simplify any arbitrary union of regular expressions to their minimal representation.\\

\noindent \textbf{A more general application of intelligent fuzzing to recursive algorithms.}

A tool to systematically convert a recursive algorithm (perhaps written in some strictly defined pseudocode syntax) into a directed graph representation of the state space would be a helpful aid for generating test suites. 
Significant efforts were made to construct the graph of the WEST algorithm by hand, and an automated process would invaluable. 
Additional care should be put into allowing for varying levels of abstractions of execution due to concerns of the path explosion problem.

% FUTURE WORK:
% potentially recursive function implementation of Regular Expression Simplification Theorem

%% \subsubsection{Acknowledgements}

%% \hspace{\parindent} This work was done as part of Iowa State University's Research Experience for Undergraduates funded by NSF grant DMS-1950583. We would like to thank Iowa State University and the NSF for this research opportunity.

%% The assistance of our mentors Dr. Kristin Yvonne Rozier and Laura Gamboa Guzmán was invaluable and greatly appreciated. In addition, we thank Dr. Steve Butler and Dr. Bernard Lidický for their management of this program and organization of its funding.

%% Finally, we want to thank Brian Kempa for his guidance and suggestions on the intelligent fuzzing portion of our research, and Dr. Steve Butler for his intuition on the Regular Expression Simplification Theorem.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{Citations}

\newpage

\appendix
\section*{Appendix} \label{Appendix}
\renewcommand{\thesection}{\Roman{section}}

 \section{Until and Release Duality Lemma} \label{duality appendix}
 \begin{lemma}[\emph{Until and Release Duality}]\label{dual_proof}
 The definition of Release is equivalent to the dual of Until: 
 $\alpha \mathcal{R} \beta \equiv \neg (\neg \alpha \mathcal{U} \neg \beta)$. That is to say,
$\alpha \mathcal{R}_{[a,b]} \beta$ if and only if $|\pi| \le a \text{ or } \forall s \in [a,b] ,(\pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] , \pi_t \vDash \alpha)$.
 \end{lemma}

\begin{proof} $ $\newline
($\Rightarrow$):\\
\indent Suppose $\pi \vDash \alpha \mathcal{R}_{[a,b]} \beta$, so:
\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \pi_k \vDash \beta \text{)} \]

We proceed by cases to show that:
\[
|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)} \tag{A1}
\]
\indent Case 0: If $|\pi| \leq a$, then we are immediately done.

\indent Case 1: Suppose $\forall i \in [a,b] \text{, } \pi_i \vDash \beta$.\\
\indent Through re-labeling, we have $\forall s \in [a,b] \text{, } \pi_s \vDash \beta$. Then we clearly have:
\[
|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)} \tag{A1}
\]

\indent Case 2: Suppose $\exists i \in [a,b] \text{, } \pi_i \cancel{\vDash} \beta$.\\
\indent \indent Then we must have that:
\[ \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{1} \]
\indent \indent We want to show that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)}$.\\
\\
\indent \indent Suppose by contradiction that: 
\[ \exists s \in [a,b] \text{, (} \forall t \in [a, s-1] \text{, } \pi_t \cancel{\vDash} \alpha \text{)} \tag{2} \]
\indent \indent Since $s \in [a,b] \text{ and }  t \in [a, s-1]$, we have that $t \in [a,b-1]$.\\
\indent \indent Since $j \in [a,b-1]$ (from Line 1), we have that $\pi_j \cancel{\vDash} \alpha$ from Line 2.\\
\indent \indent However from Line 1 we have that $\pi_j \vDash \alpha$ and have thus derived a contradiction.\\
\indent \indent Thus, we now have that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)}$.\\ \indent \indent From this, we clearly have that:
\[
|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)} \tag{A1}
\]
$ $ \newline
\indent Since these $3$ cases exhaustively capture all cases fo the assumption, the ($\Rightarrow$) direction is proved.
$ $ \newline

\noindent ($\Leftarrow$):\\
\indent Suppose that $\pi \vDash \neg (\neg \alpha \mathcal{U} \neg \beta)$:
\[
|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{) \tag{1}}
\]
$ $ \newline
\indent We want to show $\pi \vDash \alpha R_{[a,b]} \beta$, that is:
\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{B1} \]

\indent Case 0: If $|\pi| \leq a$, again we are immediately done. \\
\indent Case 1: Suppose $\forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{)}$.\\ 
\indent \indent Relabeling $s$ to $i$, we now have that $\forall i \in [a, b] \text{, (}\pi_s \vDash \beta \text{)}$, which implies line B1. \\

\indent Case 2: Suppose $\exists s \in [a,b], \pi_s \cancel{\vDash} \beta$.\\
\indent \indent By re-labeling $s$ to $i$, we have that $\exists i \in [a,b], \pi_i \cancel{\vDash} \beta$.\\
\indent \indent Since $[a,b]$ is a finite-discrete interval, there must exist a first $i_1$ s.t. $\pi_{i_1} \cancel{\vDash} \beta$, that is:
\[ 
\exists i_1 \in [a,b]\text{, (}  \pi_{i_1} \cancel{\vDash} \beta  \text{ and }  \forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \beta \text{)}
\tag{2}\]

\indent \indent Since (line 2) $\exists i_1 \in [a,b], \pi_{i_1} \cancel{\vDash} \beta$, by Line 1 we have that: $\pi_{i_1} \vDash \beta \text{ or } \exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \alpha$.\\
\indent \indent Thus, we have that: 
\[
\exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \alpha \tag{3}
\]
\indent \indent Since  $[a, t] \subseteq [a, i_1 - 1]$ and $\forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \beta$, we have that:
\[ 
\forall k \in [a, t]\text{, } \pi_{k} \vDash \beta \tag{4}
\]

\indent \indent Since $[a,t] \subseteq [a, i_1 - 1] \subseteq [a,b-1]$, we have that $t \in [a,b-1]$, so let $j := t$.

\indent \indent Then from lines 3 and 4, we have that:
\[
\exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{5}
\]

\indent \indent From line 5, we now get:
\[ 
|\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{B1}
\]
\indent Again the 3 cases are exhaustive of all cases in the assumption, this we have the ($\Leftarrow$) direction.\\
\\
This finishes the proof.
\end{proof}

\section{Regular Expression Simplification Theorem} \label{simp appendix}
\begin{proof}[Proof of \ref{simp}]
Assume no row is the arbitrary computation, because then the union of the set of regular expressions would trivially simplify to the arbitrary computation.\\

We begin by showing that there must be at least one row in the matrix $M$ that is composed of one fixed truth value and $n-1$ `$S$'s. This will be of use later in the proof. Because there are $n$ columns and $2$ fixed truth values in each column, there are $2n$ fixed truth values. There are $n+1$ rows, so the average number of fixed truth values per row is strictly less than $2$ since $\frac{2n}{n+1} < \ 2$.
Thus, there must exist at least one row composed of one fixed truth value and $n-1$ `$S$'s. \\

\noindent We now proceed by induction on the length of computations, $n$. \\
\textbf{Base Cases:} $n=1$ and $n=2$. \\
The $n=1$ case holds by definition:
    $$\begin{bmatrix}
    1\\
    0
    \end{bmatrix}  \equiv S.$$
For $n=2$, we can manually verify that each possible matrix indeed satisfies the theorem. Note that because the union of regular expressions is commutative, any permutation of rows is equivalent:
        $$\begin{bmatrix}
    1 & S\\
    S & 1\\
    0 & 0
    \end{bmatrix}  \equiv \begin{bmatrix}
    0 & S\\
    S & 0\\
    1 & 1
    \end{bmatrix} \equiv \begin{bmatrix}
    1 & S\\
    S & 0\\
    0 & 1
    \end{bmatrix} \equiv \begin{bmatrix}
    0 & S\\
    S & 1\\
    1 & 0
    \end{bmatrix} \equiv SS.
        $$

\noindent \textbf{Inductive Hypothesis:}\\
Let $n\geq 2$. Assume that a matrix of regular expressions, $H$, with the following characteristics is equivalent to the arbitrary computation of length $n-1$: $n$ rows, $n-1$ columns, one `$1$' per column, one `$0$' per column, and $n-2$ `$S$'s per column.\\
\noindent \textbf{Inductive Step:}\\
Consider a matrix of regular expressions, $J$, with the following characteristics: $n+1$ rows, $n$ columns, one `$1$' per column, one `$0$' per column, and $n-1$ `$S$'s per column. We show $J$ is equivalent to the arbitrary computation of length $n$.\\

As aforementioned, there must exist at least one row composed of one fixed truth value and $n-1$ `$S$'s, and the union of regular expressions is commutative. Thus, WLOG, let the first row of $J$, $r_1$, be a row with one known truth value.
Suppose this known truth value is in column $k$, $c_k$, where $1 \leq k \leq n$.. Assume WLOG that this value is a 0. Matrix $J$ can be represented as follows:

\[
J = \begin{blockarray}{cccccccc}
\mathbf{c_1} & & \mathbf{c_{k-1}} & \mathbf{c_k} & \mathbf{c_{k+1}} & & \mathbf{c_n} \\
\begin{block}{(ccccccc)c}
    S & \hdots & S & 0 & S & \hdots & S & \mathbf{r_1}\\
     &  &  & S &  &  &  & \mathbf{r_2}\\
    &  &  & \vdots &  &  &  & \\
    &  & & S &  &  &  & \\
    & \vdots &  & 1 &  & \vdots &  & \\
    & &  & S &  & &  & \\
    &  &  & \vdots & &  &  & \\
    &  & & S & &  & & \mathbf{r_{n+1}}\\
\end{block}
\end{blockarray}
 \]

The first row of $J$ represents half of the regular expressions contained in the arbitrary computation. The other half would be represented by a regular expression of all `S's, except for a `1' at the $k$th position. Thus, if the rest of $J$, rows $r_2$ through $r_{n+1}$, represents the other half of the arbitrary computation, then the matrix - the union of the set of the regular expressions - represents the arbitrary computation of length $n$. We show that this is indeed the case:

Because the first row represents all the computations with `0' at the $k$th position, every `$S$' in $c_k$ can be replaced with a `1', to avoid redundancy; the case for which each `$S_k$' is `0' is a subset of $r_1$. Thus, matrix $J$ can be represented as follows:

\[
J = \begin{blockarray}{cccccccc}
\mathbf{c_1} & & \mathbf{c_{k-1}} & \mathbf{c_k} & \mathbf{c_{k+1}} & & \mathbf{c_n} \\
\begin{block}{(ccccccc)c}
    S & \hdots & S & 0 & S & \hdots & S & \mathbf{r_1}\\
     &  &  & 1 &  &  &  & \mathbf{r_2}\\
    &  \vdots &  & \vdots &  &  \vdots &  & \\
    &  &  &  &  & &  & \\
    & & & 1 & &  & & \mathbf{r_{n+1}}\\
\end{block}
\end{blockarray}
 \]

The problem reduces to showing that $J - r_1$, that is, $J$ with the row $r_1$ removed, represents the other half of the arbitrary computation. Thus, let $J' = J - r_1$:

\[
J' = \begin{blockarray}{cccccc}
\mathbf{c_1} &  & \mathbf{c_k} & & \mathbf{c_n} \\
\begin{block}{(ccccc)c}
     &   & 1 &   &  & \mathbf{r_2}\\
     \vdots & &  \vdots & & \vdots  & \\
    &   &   & &  & \\
    & & 1 &  & & \mathbf{r_{n+1}}\\
\end{block}
\end{blockarray}
 \]

Again, we want to show that $J'$ represents the other half of the arbitrary computation. Recall that we specify this to be the union of regular expressions of all $`S'$s except for a $`1'$ at the $k$th position. Because each row indeed contains a $`1'$ at the $k$th position, the problem reduces to showing that $r_2 - c_k$ through $r_{n+1} - c_k$ represents the arbitrary computation, where $r_j - c_k$ is the row $r_j$ with the $k$th entry removed. Thus, we remove $c_k$ from $J'$ and call this new matrix $J''$:
\[
 J'' = \begin{pmatrix}
    r_2 - c_k \\
    . \\
    . \\
    . \\
    r_{n+1} - c_k \\

  \end{pmatrix}
\]

Because $J''$ is the result removing one row and one column from $J$, $J''$ has $n$ rows and $n-1$ columns. In each column of $J''$, there remains one `$1$' and one `$0$'. Also, there are now $n-2$ `$S$'s in each column, because $r_1$ was removed. Thus, $J''$ is equivalent to $H$, and is therefore equivalent to the arbitrary computation by the inductive hypothesis.

Because $r_1$ is equivalent to half of the arbitrary computation and $J'$ is equivalent to the other half of the arbitrary computation, $J$ is equivalent to the arbitrary computation, as the union of $r_1$ and $J'$ is equivalent to $J$.

Therefore, by induction, the theorem holds.
\end{proof}

\section{Pseudocode for the WEST Algorithm Functions} \label{pseudocode appendix}

To compute the satisfying computations of an MLTL formula, many of the functions in the WEST program require the regular expressions of the satisfying computations of the subformulas as inputs. We denote these regexes by $R$ and $B$, where $R = R_1 | R_2 | ... | R_k$ is represented as a vector of strings $R = {R_1, R_2, ..., R_k}$, and $B = B_1 | B_2 | ... | B_\ell$ is represented as a vector of strings $B = {B_1, B_2, ..., B_\ell}$. Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.

\begin{algorithm}[H]
\caption{Pad a vector to elements of all equal length}
Input: Vector of strings that represents a regex, number of propositional variables \\
Output: Vector of strings padded to equal length
\begin{algorithmic}

\Procedure{Pad}{vector $R$, int $n$} 
    \State max\_Length $\leftarrow$ $max_{\{r \in R\}}$($r$.length()) \Comment{determines length to pad all strings to}
    \For{($r \in R$)}
        \State diff $\leftarrow$ (max\_length$- r$.length()) / $(n+1)$ 
        \Comment{determines how many $S^n$s to append}
        \State  $r \leftarrow r + (,S^n)^{\text{diff}}$
    \EndFor
    \State return $R$

\EndProcedure

\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Computes regex for propositional constant}
Input: String that is either ``T" or ``!", number of propositional variables\\
Output: Vector of strings that represents the appropriate satisfying computations
\begin{algorithmic}
\Procedure{reg\_prop\_cons}{string nnf, int $n$}
    \If {(nnf $=$ ``T" and $n \neq 0$)}
        \State return $\{S^n\}$ \Comment{regex of satisfying computations for ``T"}
    \Else 
        \State return $\{\}$ \Comment{regex of satisfying computations for ``!"}
    \EndIf
\EndProcedure

\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Output the vector of computation satisfying a propositional variable.}
Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
Output: Vector of strings that represents the appropriate satisfying computations
\begin{algorithmic}

\Procedure{reg\_prop\_var}{string nnf, int $n$}
    \If {(nnf $=$ ``p$k$", where $k$ is a nonnegative integer)}
        \State return $\{S^k1S^{n-k-1}\}$ \Comment{regex of satisfying computations for ``p$k$"}
    \EndIf 
    \If {(nnf $=$ ``$\scriptstyle{\sim}$p$k$", where $k$ is a nonnegative integer)}
        \State return $\{S^k0S^{n-k-1}\}$ \Comment{regex of satisfying computations for ``$\scriptstyle{\sim}$p$k$"}
    \EndIf
\EndProcedure

\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Combines two strings that differ only by one character into one}
Input: Two strings that represent regexes\\
Output: Single string that represents computations represented by both input strings or FAIL
\begin{algorithmic}

\Procedure{simplify\_string}{string $r$, string $b$}   
    \If{($r$.length() $\neq$ $b$.length())}
        \State exit \Comment{cannot compare strings if they differ in length}
        \EndIf
    \For{($0 \leq i < r$.length())}
        \State pre\_r $\leftarrow r[0, i-1]$ \Comment{stores string $r$ up to comparison character}
        \State char\_r $\leftarrow r[i]$ \Comment{stores character to compare in $r$}
        \State post\_r $\leftarrow r[i+1, r\text{.length()}-1]$ \Comment{stores remaining part of string $r$}
        \\
        \State pre\_b $\leftarrow b[0, i-1]$ \Comment{stores string $b$ up to comparison character}
        \State char\_b $\leftarrow b[i]$ \Comment{stores character to compare in $b$}
        \State post\_b $\leftarrow b[i+1, b\text{.length()}-1]$ \Comment{stores remaining part of string $b$}
        \\
        \If{(pre\_r $=$ pre\_b and post\_r $=$ post\_b)} \Comment{\parbox[t]{.4\linewidth}{checks that strings $r$ and $b$ match for all but one character}}
            \If{(char\_r $\neq$ char\_b)}
                \State return pre\_r +``$S$" + post\_r \Comment{\parbox[t]{.5\linewidth}{if the comparison characters differ, replace character with $``S"$}}
            \Else
                \State return $r$ \Comment{if the comparison character match, strings are identical}
            \EndIf
        \EndIf
    \EndFor
    \State return FAIL 
    \Comment{Indicates strings differed by more than one character}
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Simplifies a vector of strings using simplify\_string}
Input: Vector of strings representing a regex\\
Output: Vector of strings representing a regex simplified using simplify\_string
\begin{algorithmic}

\Procedure{simplify}{vector $R$}    
    \State Pad all strings in $R$ to the same length \Comment{ensures all inputs to simplify\_string are valid}
    \If{($R$.length() $\leq 1$)}
        \State return $R$ \Comment{insufficient strings in $R$ to use simplify\_string}
        \EndIf

    \State $i = R\text{.length} - 1$
    \State $j = i - 1$

    \State START
    \While{($i \geq 1$)}
        \While{($j \geq 0$)}
            \State simplified = simplify\_string($R[i]$, $R[j]$) \Comment{\parbox[t]{.4\linewidth}{for each combination of strings in $R$, apply simplify\_string}}
            \If{(simplified $\neq$ FAIL)}
                \State replace string at index $j$ with simplified \Comment{updating $R[j]$ to be combined string}
                \State remove string at index $i$ from $R$ \Comment{remove $R[i]$, as it's redundant}
                \State $i = R\text{.length()} - 1$
                \State $j = i - 1$
                \State goto START
                \EndIf

            \State -{}-$j$
            \EndWhile

        \State -{}-$i$
        \State $j = i - 1$
        \EndWhile

    \State return $R$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Takes the intersection of two computations}
Input: Two strings representing regexes\\
Output: Bitwise AND of the inputted strings
\begin{algorithmic}
\Procedure{bit\_wise\_and}{string $r$, string $b$}
    \State ret $\leftarrow$ ``" \Comment{initializing string to store bitwise AND}
    \For {(i $\in [0, \ r\text{.length()}]$)}
        \If{($r[i] \land$ $b[i] = ``"$)}
        \State return ``" \Comment{if bitwise AND is ever empty, entire string intersection is empty}
        \Else 
        \State ret $\leftarrow$ ret $+$ $r[i] \land b[i]$ \Comment{for each character, store bitwise AND}
        \EndIf
    \EndFor
    \State return ret
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Takes set intersection of the languages of two regexes}
Input: Vectors of strings that represent regexes, simplify boolean\\
Output: Vector of strings that represents set intersection of the languages of the inputted regexes
\begin{algorithmic}

\Procedure{set\_intersect}{vector $R$, vector $B$, bool simp}
    \State Pad $R$ and $B$ to the same length
    \State ret $\leftarrow \{\}$ \Comment{initializing a vector of strings to store set intersection}
    \For{($r \in R$)}
        \For{($b \in B$)} \Comment{take bitwise AND of every combination of strings from $R$ and $B$}
            \State add bit\_wise\_and($r, b$) to ret 
            \Comment{store results in ret}
        \EndFor
    \EndFor
    \If{(simp is true)}
    \State return simplify(ret) \Comment{if user requests simplified output, run ret through simplify}
    \Else
    \State return ret
    \EndIf
\EndProcedure

\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Takes union of two regexes (combines two vectors into one)}
Input: Vectors of strings that represent regexes, simplify boolean\\
Output: Vector of strings that represents union of inputted regexes
\begin{algorithmic}

\Procedure{join}{vector $R$, vector $B$, bool simp}
    \State ret $\leftarrow \{\}$ \Comment{initializing a vector of strings to store union}
    \For{($r \in R$)}
        \State add $r$ to ret \Comment{add all vectors in $R$ to ret}
    \EndFor
    \For{($b \in B$)}
        \State add $b$ to ret \Comment{add all vectors in $B$ to ret}
    \EndFor
    \If{(simp is true)}
    \State return simplify(ret) \Comment{if user requests simplified output, run ret through simplify}
    \Else
    \State return ret
    \EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Computes the regex for a MLTL formula G[a:b]$\alpha$}
Inputs: Vector of strings representing the regex for $\alpha$, interval bounds, number of propositional variables, simplify boolean\\
Output: Vector of strings that represents the appropriate satisfying computations
\begin{algorithmic}

\Procedure{reg\_G}{vector reg\_alpha, int $a$, int $b$, int $n$, bool simp} 
    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$ \Comment{before the start of the interval, computation is arbitrary}
    \State comp $\leftarrow$ reg\_alpha \Comment{\parbox[t]{.7\linewidth}{initializing vector of strings for outputted regex with subformula regex}}
    \If{$a > b$} \Comment{empty interval, Global is trivially true}
        \State return $\{S^n\}$
    \EndIf
    \For{($1 \leq i \leq b-a$)} \Comment{computing $\bigwedge_{i=1}^{b-a} (S^n,)^i \text{reg}(\alpha)$}
        \State temp\_alpha $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_alpha
        \State comp $\leftarrow$ set\_intersect(comp, temp\_alpha, simp)
    \EndFor
    \State return pre + comp \Comment{\parbox[t]{.6\linewidth}{prepending string pre to every string in comp; result is regex for Global defined in section \ref{regex}}}
\EndProcedure

\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Computes the regex for a MLTL formula F[a:b]$\alpha$}
Inputs: Vector of strings representing the regex for $\alpha$, interval bounds, number of propositional variables, simplify boolean\\
Output: Vector of strings that represents the appropriate satisfying computations 
\begin{algorithmic}

\Procedure{reg\_F}{vector reg\_alpha, int $a$, int $b$, int $n$, bool simp} 
    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$ \Comment{before the start of the interval, computation is arbitrary}
    \State comp $\leftarrow$ reg\_alpha \Comment{\parbox[t]{.7\linewidth}{initializing vector of strings for outputted regex with subformula regex}}
    \If{$a > b$} \Comment{empty interval, Finally is trivially false}
        \State return $\{\}$
    \EndIf
    \For{($1 \leq i \leq b-a$) } \Comment{computing $\bigvee_{i=1}^{b-a} (S^n,)^i \text{reg}(\alpha)$}
        \State temp\_alpha $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_alpha
        \State comp $\leftarrow$ join(comp, temp\_alpha, simp)
    \EndFor
    \State return pre + comp \Comment{\parbox[t]{.6\linewidth}{prepending string pre to every string in comp; result is regex for Finally defined in section \ref{regex}}}
\EndProcedure

\end{algorithmic}
\end{algorithm}

\label{regU}
\begin{algorithm}[H]
\caption{Computes the regex for a MLTL formula $\alpha$U[a:b]$\beta$} 
Inputs: Vectors of strings representing the regexes for $\alpha$ and $\beta$, interval bounds, number of propositional variables, simplify boolean\\
Output: Vector of strings that represents the appropriate satisfying computations 
\begin{algorithmic}

\Procedure{reg\_U}{vector reg\_alpha, vector reg\_beta int $a$, int $b$, int $n$, bool simp} 
    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ reg\_beta \Comment{\parbox[t]{.55\linewidth}{initializing vector of strings for outputted regex with regex for beta, prepended with $`S'$s up to start of interval}}
    \If{$a > b$}
        \State return $\{\}$ \Comment{empty interval, Until is trivially false}
    \EndIf
    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)$, loop ends at $b-1$ because comp is initialized to $i=a$ case and loop is reindexed}}\\
        \State{\parbox[t]{.9\linewidth}{temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_alpha, $a$, $i$, $n$), reg\_G(reg\_beta, $i+1$, $i+1$, $n$), $n$, simp)}}
        \State comp $\leftarrow$ join(comp, temp\_comp, simp)
    \EndFor

    \State return comp
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Computes the regex for a MLTL formula $\alpha$R[a:b]$\beta$}
Inputs: Vectors of strings representing the regexes for $\alpha$ and $\beta$, interval bounds, number of propositional variables, simplify boolean\\
Output: Vector of strings that represents the appropriate satisfying computations 
\begin{algorithmic}

\Procedure{reg\_R}{vector reg\_alpha, vector reg\_beta int $a$, int $b$, int $n$, bool simp} 
    \State comp $\leftarrow$ reg\_G(reg\_beta, $a$, $b$, $n$, simp)
    \Comment{\parbox[t]{.5\linewidth}{initializing vector of strings for output regex with regex for G[a:b]$\beta$}}
    \If{$a > b$}
        \State return $\{S^n\}$
        \Comment empty interval, Release is trivially true
    \EndIf
    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)$, first run through loop includes $\text{reg}\left(\mathcal{G}_{[a,b]}\beta\right)$}}\\
        \State temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_beta, $a$, $i$, $n$), reg\_G(reg\_alpha, $i$, $i$, $n$), $n$, simp)
        \State comp $\leftarrow$ join(comp, temp\_comp, simp)
    \EndFor

    \State return comp
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\caption{Computes the regex for an MLTL formula in NNF}
Inputs: MLTL formula in negation normal form, number of propositional variables, boolean sub for storing subformula computations in global variable FORMULAS, simplify boolean\\
Output: Vector of strings that represents the appropriate satisfying computations
\begin{algorithmic}

\Procedure{reg}{string nnf, int $n$, bool sub, bool simp} 
    \If{(nnf is a prop. var. or $\scriptstyle{\sim}$prop. var)}
        \If{(sub)}
            \State Run reg on formula and store formula with its regular expression
        \EndIf
        \State return reg\_prop\_var(nnf, $n$)
        \Comment call helper function for propositional variable
    \EndIf\\
    \If{(nnf is $T$ or $!$)}
        \If{(sub)}
            \State Run reg on formula and store formula with its regular expression
        \EndIf
        \State return reg\_prop\_cons(nnf, $n$)
        \Comment call helper function for propositional constant
    \EndIf
    \\
    \If{(nnf is of the form unary\_temp\_conn interval alpha)}
        \State unary\_temp\_conn $\leftarrow$ unary\_temp\_conn in nnf
        \Comment parse formula to find unary operator
        \State $a$ $\leftarrow$ start of interval
        \State $b$ $\leftarrow$ end of interval
        \State reg\_alpha $\leftarrow$ reg(alpha, $n$, sub, simp)
        \Comment recursive call to reg on subformula\\
        \If{(unary\_temp\_conn $=$ `F')}
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return reg\_F(reg\_alpha, $a$, $b$, $n$, simp)
            \Comment Call helper function for Finally operator
        \EndIf\\
        \If{(unary\_temp\_conn $=$ `G')}
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return reg\_G(reg\_alpha, $a$, $b$, $n$, simp)
            \Comment Call helper function for Global operator
        \EndIf
    \EndIf
    \\
    \If{(nnf is of the form ``(Assoc\_prop\_conn[nnf\_array])")}
    \Comment{Rewrite nnf in non-array form}
        \State assoc\_prop\_conn $\leftarrow$ assoc\_prop\_conn in nnf
        \State equiv\_formula $\leftarrow$ ``" 
        \Comment For instance, $\&[\alpha_1, \alpha_2, \alpha_3]$ is rewritten to $((\alpha_1 \& \alpha_2) \& \alpha_3)$
        \For{(array entry alpha in nnf\_array)}
            \If{(alpha is first entry)}
                \State equiv\_formula $\leftarrow$ alpha
                \Comment First entry doesn't need parentheses
            \Else
                \State equiv\_formula $=$ ``(" + equiv\_formula + assoc\_prop\_conn + alpha + ``)"
            \EndIf
        \EndFor
        \If{(sub)}
            \State Run reg on formula and store formula with its regular expression
        \EndIf
        \State return reg(equiv\_formula, $n$, sub, simp)
        \Comment recursively call reg on the rewritten formula
    \EndIf
    \algstore{myalg}
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
\begin{algorithmic}
\algrestore{myalg}
    \If{(nnf is of the form alpha binary\_prop\_conn beta)}
        \State binary\_prop\_conn $\leftarrow$ binary\_prop\_conn in nnf
        \Comment parse formula to find binary operator
        \State reg\_alpha $\leftarrow$ reg(alpha, $n$, sub, simp)
        \Comment recursive call to reg on subformula
        \State reg\_beta $\leftarrow$ reg(beta, $n$, sub, simp)
        \Comment recursive call to reg on subformula\\
        \If{(binary\_prop\_conn $=$ ``\&")}
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return set\_intersect(reg\_alpha, reg\_beta, $n$, simp)
            \Comment Call helper function for \& operator
        \EndIf\\
        \If{(binary\_prop\_conn $=$ ``$\lor$")}
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return join(reg\_alpha, reg\_beta, $n$, simp)
            \Comment Call helper function for $\lor$ operator
        \EndIf\\
        \If{(binary\_prop\_conn $=$ ``=")}
            \Comment{Rewrite in terms of OR, AND, and NOT}
            \State equiv\_formula $=$ ``((" + alpha + ``\&" + beta + ``)$\lor$(" + wff\_to\_nnf($\scriptstyle{\sim}$alpha) + 
            \State ``\&" + wff\_to\_nnf($\scriptstyle{\sim}$beta) + ``))"
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return reg(equiv\_formula, $n$, sub, simp)
            \Comment recursive call to reg on rewritten formula
        \EndIf\\
        \If{(binary\_prop\_conn $=$ ``\textgreater")}
            \Comment{Rewrite in terms of OR, AND, and NOT}
            \State equiv\_formula $=$ ``(" + wff\_to\_nnf($\scriptstyle{\sim}$alpha) + "$\lor$" + beta + ``)"
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return reg(equiv\_formula, $n$, sub, simp)
            \Comment recursive call to reg on rewritten formula
        \EndIf
    \EndIf\\
   \If{(nnf is of the form alpha binary\_temp\_conn interval beta)}
        \State binary\_temp\_conn $\leftarrow$ binary\_temp\_conn in nnf
        \Comment parse for binary operator
        \State $a$ $\leftarrow$ start of interval
        \State $b$ $\leftarrow$ end of interval
        \State reg\_alpha $\leftarrow$ reg(alpha, $n$, sub, simp)
        \Comment recursive call to reg on subformula
        \State reg\_beta $\leftarrow$ reg(beta, $n$, sub, simp)
        \Comment recursive call to reg on subformula
        \\
        \If{(binary\_temp\_conn $=$ `U')}
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return reg\_U(reg\_alpha, reg\_beta, $a$, $b$, $n$, simp)
            \Comment Call helper function for Until\\
        \ElsIf{(binary\_temp\_conn $=$ `R')}
            \If{(sub)}
                \State Run reg on formula and store formula with its regular expression
            \EndIf
            \State return reg\_R(reg\_alpha, reg\_beta, $a$, $b$, $n$, simp)
            \Comment Call helper function for Release
        \EndIf
    \EndIf\\
    \State Throw exception \Comment{\parbox[t]{.7\linewidth}{If none of the previous statements held, there's an error with the formula nnf}}
    \State return \{\}
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]
    \caption{Generates test suite template without propositional constants, propositional variables, or negations of propositional variables filled in}
    Inputs: Depth of desired test suite template to generate, interval bounds\\
    Output: Vector of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
    \begin{algorithmic}
        \Procedure{generate\_test\_template}{int depth, int $a$, int $b$}
        \If{(depth = 0)}
            \State return $\{p, q\}$
            \Comment{\parbox[t]{.54\linewidth}{$p$ represents a propositional variable or its negation, $q$ represents a propositional constant}}
        \EndIf

        \State template $\leftarrow \{\}$
        \Comment initialize variable to store final template
        \State $V \leftarrow$ generate\_test\_template(depth$- 1$, $a$, $b$)
        \Comment{\parbox[t]{.45\linewidth}{recursively generate all formulas of $1$ lower depth}}
        \For{(string $\alpha \in V$)}
            \State add ``G[a:b]" + $\alpha$ to template
            \State add ``F[a:b]" + $\alpha$ to template
            \Comment Add unary temporal operators to template
            \For{string $\beta \in V$}
                \State add $\alpha$ + ``U[a:b]" + $\beta$ to template
                \State add  $\alpha$ + ``R[a:b]" + $\beta$ to template
                \State add $\alpha$ + ``$\lor$" + $\beta$ to template
                \State add $\alpha$ + ``\&" + $\beta$ to template
                \Comment add binary operators to template
            \EndFor
        \EndFor
        \State return template
    \EndProcedure
    \end{algorithmic}

\end{algorithm}

\begin{algorithm}[H]
    \caption{Generates a complete test suite of MLTL formulas in negation normal form up to a certain depth}
    Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
    Output: Vector of MLTL formulas
    \begin{algorithmic}
        \Procedure{generate\_test}{int depth, int $a$, int $b$, int $n$}
        \State tests $\leftarrow$ generate\_test\_template(depth, $a$, $b$) 
        \For{string $t \in $ tests}
            \For{char ch $\in t$}
                \If{ch $ = p$}
                \Comment{\parbox[t]{.52\linewidth}{replace $a$ with a random propositional variable or the negation of a random propositional variable}}
                    \State $k \leftarrow \text{rand()} \% n$ 
                    \Comment assign $k$ as a random int between $0$ and $n - 1$
                    \If{rand() $\% 2 = 0$}
                    \Comment imitate randomness of a coin toss
                        \State replace ch with p$k$
                    \Else 
                        \State replace ch with $\scriptstyle{\sim}$p$k$
                    \EndIf
                \ElsIf{ch $= q$}
                \Comment Replace $q$ with a random propositional constant
                    \If{rand() $\% 2 = 0$}
                        \State replace ch with T
                    \Else 
                        \State replace ch with $!$
                    \EndIf
                \EndIf
            \EndFor
        \EndFor
    \State return tests
    \EndProcedure
    \end{algorithmic}
\end{algorithm}

\newpage
\section{State Diagram Graphs} \label{graphs appendix}
Below we provide the graphs of state diagrams of the critical functions examined in our intelligent fuzzing. In general, nodes in the graph represent portions of the code without control flow statements. As a result, a single node can represent large chunks of code. Directed edges represent branching of control flow, such as IF statements and loops. Each graph directly corresponds with the pseudocode of their corresponding function, with nodes and edges being labeled accordingly. Note that these graphs, the option to run the \textit{simplify} function has been omitted for clarity. For the graph of the \textit{reg} function, the option to store subformulas has been omitted as well.\\

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vector R, \# of propositional variables n};
    \node[node](length)[below=of inputs]{Run max\_length on R};
    \node[node](body)[below=of length]{pad r, update R};
    \node[emptynode](empty_vector)[rotate=-70, left=1cm of body]{R $=\{\}$};
    \node[emptynode](for_loop)[right=.75cm of body]{for r in R};
    \node[node](return)[below=of body]{return R};

    %Lines
    \draw[->] (inputs.south) -- (length.north);
    \draw[->] (length.south) -- (body.north);
    \draw[->] (body.south) -- (return.north);
    \draw[->] (inputs.west) .. controls +(left:1 cm) and +(down:1 cm) .. (return.west);
    \draw[->] (body.south) .. controls +(right:5 cm) and +(up:1.5 cm) .. (body.north);

    \end{tikzpicture}

    \caption{Pad Function}
    \label{fig:pad graph}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){strings r, b};
    \node[node](initialize)[below=of inputs]{Initialize string Ret};
    \node[node](loop_entry)[below=of initialize]{Loop Entry};
    \node[node](return)[below=2cm of loop_entry]{return Ret};
    \node[node](empty)[left=of return]{return ``"};
    \node[node](update)[right=of return]{Take bitwise AND, store in Ret};
    \node[emptynode](placeholder)[below=0.05cm of loop_entry]{};
    \node[emptynode](emptytext)[rotate=35, left=.75cm of placeholder]{\small{r$[i] \land$ b$[i] = ``"$}};
    \node[emptynode](placeholder2)[below=0.05cm of placeholder]{};
    \node[emptynode](else)[rotate=-23, right=1.9cm of placeholder2]{else};
    \node[emptynode](updatetext)[right=3cm of loop_entry]{for $0 \leq i \leq$ r.length};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (loop_entry.north);
    \draw[->] (loop_entry.south) -- (return.north);
    \draw[->] (loop_entry.south) -- (empty.north);
    \draw[->] (loop_entry.south) -- (update.north);
    \draw[->] (update.east) .. controls +(right:3 cm) and +(up:1.5 cm) .. (loop_entry.north);

    \end{tikzpicture}
    \caption{Bitwise\_And Function}
    \label{fig:bitwise_and graph}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vectors R, B};
    \node[node](initialize)[below=of inputs]{Initialize vector Ret};
    \node[node](add_r)[below=of initialize]{Add r to Ret};
    \node[node](add_t)[below=of add_r]{Add b to Ret};
    \node[node](return)[below=of add_t]{return Ret};
    \node[emptynode](rtext)[right=of add_r]{for string r$\in$R};
    \node[emptynode](ttext)[left=of add_t]{for string b$\in$B};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (add_r.north);
    \draw[->] (add_r.south) -- (add_t.north);
    \draw[->] (add_t.south) -- (return.north);
    \draw[->] (add_r.south) .. controls +(right:5 cm) and +(up:1.5 cm) .. (add_r.north);
    \draw[->] (add_t.south) .. controls +(left:5 cm) and +(up:1.5 cm) .. (add_t.north);

    \end{tikzpicture}
    \caption{Join Function}
    \label{fig:join graph}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vectors R,B};
    \node[node](initialize)[below=of inputs]{Pad R and B, Initialize vector Ret=\{\}};
    \node[node](outer_loop)[below=of initialize]{Outer Loop Entry};
    \node[node](inner_loop)[below=of outer_loop]{Update Ret};
    \node[node](outer_exit)[below=of inner_loop]{Outer Loop Exit};
    \node[node](return)[below=of outer_exit]{return Ret};
    \node[emptynode](inner_text)[right=1.25cm of inner_loop]{for b$\in$B};
    \node[emptynode](outer_text)[left=2.25 cm of inner_loop]{for r$\in$R};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (outer_loop.north);
    \draw[->] (outer_loop.south) -- (inner_loop.north);
    \draw[->] (inner_loop.south) -- (outer_exit.north);
    \draw[->] (outer_exit.south) -- (return.north);
    \draw[->] (inner_loop.south) .. controls +(right:5 cm) and +(up:2cm) .. (inner_loop.north);
    \draw[->] (outer_exit.west) .. controls +(left:5 cm) and +(up:3 cm) .. (outer_loop.north);

    \end{tikzpicture}
    \caption{Set\_Intersect Function}
    \label{fig:set_intersect graph}
\end{figure}
\newpage
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vector reg\_alpha, integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{\}};
    \node[node](return)[below=of loop]{return pre + Comp};
    \node[emptynode](loop_text)[right= of loop]{for $i \in [1, \text{b}-\text{a}]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (empty.north);
    \draw[->] (initialize.south) -- (loop.north);
    \draw[->] (loop.south) -- (return.north);
    \draw[->] (loop.south) .. controls +(right:5 cm) and +(up:1.5 cm) .. (loop.north);

    \end{tikzpicture}

    \caption{Reg\_F Function}
    \label{fig:reg_f graph}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vector reg\_alpha, integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{$S^n$\}};
    \node[node](return)[below=of loop]{return pre + Comp};
    \node[emptynode](loop_text)[right= of loop]{for $i \in [1, \text{b}-\text{a}]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (empty.north);
    \draw[->] (initialize.south) -- (loop.north);
    \draw[->] (loop.south) -- (return.north);
    \draw[->] (loop.south) .. controls +(right:5 cm) and +(up:1.5 cm) .. (loop.north);

    \end{tikzpicture}

    \caption{Reg\_G Function}
    \label{fig:reg_g graph}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vector reg\_alpha, reg\_beta and integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{$S^n$\}};
    \node[node](return)[below=of loop]{return Comp};
    \node[emptynode](loop_text)[right= of loop]{for $i \in [\text{a}, \text{b}-1]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (empty.north);
    \draw[->] (initialize.south) -- (loop.north);
    \draw[->] (loop.south) -- (return.north);
    \draw[->] (loop.south) .. controls +(right:5 cm) and +(up:1.5 cm) .. (loop.north);

    \end{tikzpicture}

    \caption{Reg\_R Function}
    \label{fig:reg_r graph}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]

    %Nodes
    \node[emptynode](inputs){vector reg\_alpha, reg\_beta and integers a, b, n};
    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
    \node[node](loop)[below=2cm of initialize]{Update Comp};
    \node[node](empty)[left=of loop]{return \{\}};
    \node[node](return)[below=of loop]{return Comp};
    \node[emptynode](loop_text)[right= of loop]{for $i \in [\text{a}, \text{b}-1]$};
    \node[emptynode](placeholder)[below=0.5cm of initialize]{};
    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};

    %Lines
    \draw[->] (inputs.south) -- (initialize.north);
    \draw[->] (initialize.south) -- (empty.north);
    \draw[->] (initialize.south) -- (loop.north);
    \draw[->] (loop.south) -- (return.north);
    \draw[->] (loop.south) .. controls +(right:5 cm) and +(up:1.5 cm) .. (loop.north);

    \end{tikzpicture}

    \caption{Reg\_U Function}
    \label{fig:reg_u graph}
\end{figure}

\begin{landscape}
\begin{figure}[htbp]
    \centering
    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, text width=3cm,text centered, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none,text width=3cm,text centered, very thick, minimum size=1mm}, rednode/.style={rounded rectangle, draw=red!60, fill=red!5, text width=3cm,text centered, very thick, minimum size=15mm}]

    %Nodes
    \node[emptynode](inputs){string nnf, integer n};
    \node[bignode](start)[below=of inputs]{\textbf{Start Reg}};

    \node[node](prop_var)[left=2cm of inputs]{return reg\_prop\_var};

    \node[node](prop_cons)[left=3cm of start]{return reg\_prop\_cons};

    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, alpha and call reg(alpha, n)};
    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F(alpha)};
    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G(alpha)};

    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, alpha, beta};
    \node[rednode](prop_alpha)[below=of parse_binary_prop]{reg\_alpha $\leftarrow$ reg(alpha,n)};
    \node[rednode](prop_beta)[below=of prop_alpha]{reg\_beta $\leftarrow$ reg(beta,n)};
    \node[rednode](equals)[left=0.5cm of prop_beta]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};
    \node[node](set_intersect)[below=of prop_beta]{return set\_intersect};
    \node[node](join)[left=of set_intersect]{return join};
    \node[rednode](implies)[right=of set_intersect]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};

    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, alpha, beta};
    \node[rednode](temp_alpha)[below=of parse_binary_temp]{reg\_alpha $\leftarrow$ reg(alpha,n)};
    \node[rednode](temp_beta)[below=of temp_alpha]{reg\_beta $\leftarrow$ reg(beta,n)};
    \node[node](until)[below=of temp_beta]{return reg\_U};
    \node[node](release)[right=of until]{return reg\_R};

    \node[node](parse_assoc)[right=2cm of inputs]{Parse for assoc prop conn, initialize string equiv\_formula};
    \node[node](rewrite_assoc)[right=of parse_binary_temp]{Update equiv\_formula};
    \node[rednode](assoc_return)[below=of rewrite_assoc]{return reg(equiv\_formula,n)};

    \node[emptynode](prop_cons_text)[left=0.01cm of start]{nnf is T or !$$~$$};
    \node[emptynode](prop_var_text)[rotate=-43, above=1.1cm of prop_cons_text]{nnf is p or $\scriptstyle{\sim}\textstyle$p};

    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] alpha}};
    \node[emptynode](reg_g_text)[above=0.2cm of reg_g]{X is G};
    \node[emptynode](reg_f_text)[right=1.5cm of reg_g_text]{X is F};

    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is alpha X[a,b] beta}};
    \node[emptynode](release_text)[above=0.2cm of release]{X is R};
    \node[emptynode](until_text)[left=1.75cm of release_text]{X is U};

    \node[emptynode](assoc_text)[rotate=45, above=1.1cm of binary_temp_text]{\footnotesize{nnf is X[nnf\_array]}};
    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for alpha in nnf\_array};

    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is alpha X beta};
    \node[emptynode](join_text)[above=0.2cm of join]{X is v};
    \node[emptynode](intersect_text)[right=1.75cm of join_text]{X is \&};
    \node[emptynode](implies_text)[right=-0.25cm of prop_beta]{X is $>$};
    \node[emptynode](equals_text)[right=-1.2cm of reg_f_text]{X is =};

    %Lines
    \draw[->] (inputs.south) -- (start.north);
    \draw[->] (start.west) -- (prop_var.east);
    \draw[->] (start.west) -- (prop_cons.east);
    \draw[->] (start.west) -- (parse_unary.east);
    \draw[->] (parse_unary.south) -- (reg_g.north);
    \draw[->] (parse_unary.south) -- (reg_f.north);
    \draw[->] (start.south) -- (parse_binary_prop.north);
    \draw[->] (parse_binary_prop.south) -- (prop_alpha.north);
    \draw[->] (prop_alpha.south) -- (prop_beta.north);
    \draw[->] (prop_beta.south) -- (set_intersect.north);
    \draw[->] (prop_beta.south) -- (join.north);
    \draw[->] (parse_binary_prop.east) .. controls +(down:2cm) .. (implies.north);
    \draw[->] (parse_binary_prop.west) .. controls +(down:2cm) .. (equals.north);
    \draw[->] (start.east) -- (parse_binary_temp.west);
    \draw[->] (parse_binary_temp.south) -- (temp_alpha.north);
    \draw[->] (temp_alpha.south) -- (temp_beta.north);
    \draw[->] (temp_beta.south) -- (until.north);
    \draw[->] (temp_beta.south) -- (release.north);
    \draw[->] (start.east) -- (parse_assoc.west);
    \draw[->] (parse_assoc.east) -- (rewrite_assoc.north);
    \draw[->] (rewrite_assoc.south) -- (assoc_return.north);
    \draw[->] (rewrite_assoc.east) .. controls +(right:1 cm) and +(up:1.5 cm) .. (rewrite_assoc.north);

    \end{tikzpicture}
    \caption{Control Flow of Reg. Red nodes indicate a recursive call to Reg.}
    \label{fig:big boy}
\end{figure}
\end{landscape}
\end{document}

### 2022-10-09 paper/Paper.tex
typo fixes

@@
 %
-We introduce a new tool, called WEST, that implements automated validation in section \ref{specs} %, we give the WEST code specifications.
+We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in section \ref{specs} %, we give the WEST code specifications.
 In particular, we describe the grammar that the program follows and give an overview of the important functions in the program.
 %
-calculate its space and time complexity, both theoretically and experimentally, in section \ref{complex}.
+and calculate its space and time complexity, both theoretically and experimentally, in section \ref{complex}.
 We show that the theoretical worst-case complexity for both space and time is doubly exponential, but that the average case fares far better.

### 2022-10-09 paper/Paper.tex
LaTeX updates (small)
some edits to section 2

@@
 
-The structure of the paper is as follows.
+We structure the paper around our contributions as follows.
 In section \ref{prereq}, we build on the semantics of MLTL to define a computation, and its bit string representation.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Mission-time LTL and Regular Expressions} \label{prereq}
-\subsection{Mission-time Linear Temporal Logic}
-Mission-time Linear Temporal Logic (MLTL) \cite{LVR22} is a finite variation of Linear Temporal Logic (LTL) \cite{bmc} over bounded discrete intervals.
-Instead of taking the LTL operators over an infinite time line, we restrict the operators to a finite time line, taking each temporal operator over a closed interval $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
+%\subsection{Mission-time Linear Temporal Logic}
+{\bf Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
 The syntax of an MLTL formula over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:
-$$\alpha := \top \ | \ \bot \ | \ p \ | \ \neg \alpha \ | \ \alpha \land \alpha \ | \ \alpha \lor \alpha \ | \ \mathcal{F}_{[a,b]} \alpha \ | \ \mathcal{G}_{[a,b]} \alpha \ | \ \alpha \mathcal{U}_{[a,b]} \alpha \ | \ \alpha \mathcal{R}_{[a,b]} \alpha \footnote{For simplicity, we do not include parentheses in the grammar, but they may used as needed.
-The WEST program uses parentheses (see section \ref{specs} for more details).}$$
+$$\alpha := \top \ | \ \bot \ | \ p \ | \ \neg \alpha \ | \ \alpha \land \alpha \ | \ \alpha \lor \alpha \ | \ \mathcal{F}_{[a,b]} \alpha \ | \ \mathcal{G}_{[a,b]} \alpha \ | \ \alpha \mathcal{U}_{[a,b]} \alpha \ | \ \alpha \mathcal{R}_{[a,b]} \alpha \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
+We encode the Release operator directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
 
@@
 
-\subsubsection{Semantics}
-We say a computation $\pi$ as satisfies a given MLTL formula $\alpha$, written $\pi \vDash \alpha$, when\footnote{In MLTL, we do not include the Next ($\chi$) operator since $\mathcal{G}_{[1,1]}$ is equivalent to it.}:
-\begin{align}
-    &\pi \vDash p \text{ iff } p \in \pi[0]\\
-    &\pi \vDash \neg \alpha \text{ iff } \pi \nvDash \alpha\\
-    &\pi \vDash \alpha \land \beta \text{ iff } \pi \vDash \alpha \text{ and } \pi \vDash \beta\\
-    &\pi \vDash \alpha \lor \beta \text{ iff } \pi \vDash \alpha \text{ or } \pi \vDash \beta\\
-    &\pi \vDash \mathcal{F}_{[a,b]}\alpha \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \alpha\\
-    &\pi \vDash \mathcal{G}_{[a,b]}\alpha \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \alpha\\
-    &\pi \vDash \alpha \ \mathcal{U}_{[a,b]} \beta \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \beta \text{ and }\\
-    & \indent \forall j \in [a, i-1]\ \pi_j \vDash \alpha \nonumber \\
-    &\pi \vDash \alpha \ \mathcal{R}_{[a,b]} \beta \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \beta \text{ or }\\
-    & \indent \exists j \in [a,b-1] \text{ such that } \pi_j \vDash \alpha \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \beta \nonumber
-\end{align}
-
-The reader may observe that in this paper, we define Release independently from Until. 
-It is not uncommon for Release instead to be defined as the dual of Until \cite{bmc} \cite{LVR22}. 
-These two definitions are in fact equivalent, and the full proof is provided in Appendix \ref{duality appendix}.
+%KYR: the following is very useful for a tech report, but in a space-constrained conference paper, we refer the reader to LVR22 instead.
+(Maybe if there's a journal version we can include semantics again.)
+%
+%% \subsubsection{Semantics}
+%% We say a computation $\pi$ as satisfies a given MLTL formula $\alpha$, written $\pi \vDash \alpha$, when\footnote{In MLTL, we do not include the Next ($\chi$) operator since $\mathcal{G}_{[1,1]}$ is equivalent to it.}:
+%% \begin{align}
+%%     &\pi \vDash p \text{ iff } p \in \pi[0]\\
+%%     &\pi \vDash \neg \alpha \text{ iff } \pi \nvDash \alpha\\
+%%     &\pi \vDash \alpha \land \beta \text{ iff } \pi \vDash \alpha \text{ and } \pi \vDash \beta\\
+%%     &\pi \vDash \alpha \lor \beta \text{ iff } \pi \vDash \alpha \text{ or } \pi \vDash \beta\\
+%%     &\pi \vDash \mathcal{F}_{[a,b]}\alpha \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \alpha\\
+%%     &\pi \vDash \mathcal{G}_{[a,b]}\alpha \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \alpha\\
+%%     &\pi \vDash \alpha \ \mathcal{U}_{[a,b]} \beta \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \beta \text{ and }\\
+%%     & \indent \forall j \in [a, i-1]\ \pi_j \vDash \alpha \nonumber \\
+%%     &\pi \vDash \alpha \ \mathcal{R}_{[a,b]} \beta \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \beta \text{ or }\\
+%%     & \indent \exists j \in [a,b-1] \text{ such that } \pi_j \vDash \alpha \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \beta \nonumber
+%% \end{align}
+
+%KYR: moved up to earlier footnote
+%% The reader may observe that in this paper, we define Release independently from Until. 
+%% It is not uncommon for Release instead to be defined as the dual of Until \cite{bmc} \cite{LVR22}. 
+%% These two definitions are in fact equivalent, and the full proof is provided in Appendix \ref{duality appendix}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{MLTL Regular Expressions} \label{regex}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{WEST Code Specifications} \label{specs}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Complexity} \label{complex}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Verification of Correctness} \label{test}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Regular Expression Simplification Theorem} \label{simpsection}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Closing Remarks}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \appendix
@@
 \renewcommand{\thesection}{\Roman{section}}
+Content in the appendix will appear online, on the paper's website, but appears here for now due to blind review.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Regular Expression Simplification Theorem} \label{simp appendix}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Pseudocode for the WEST Algorithm Functions} \label{pseudocode appendix}
@@
 \newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{State Diagram Graphs} \label{graphs appendix}

### 2022-10-10 paper/Paper.tex
pass over sections 1-2 is done; moving on to section 3...

@@
 \usepackage{times} %KYR: substitute for pslatex that does not mess up math :)
+%\usepackage{savetrees} %KYR: maybe also helps... if we can fix the text to enable this
 
@@
 %\title{Contribution Title\thanks{Supported by organization x.}}
-\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [ommitted for blind review]}}
+\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review]}}
 %
@@
 We can cite examples of this from NASA's Automated Airspace Concept \cite{EH10}, the U.~S.~Navy's Aircraft Carrier Deck Scheduler \cite{RCRBS11}, the JAXA-NASA Global Precipitation Measurement (GPM) Observatory \cite{GPM}, and many others.
-Formal methods provide continuously-advancing tools and techniques to rigourously analyze timelines expressed in the form of temporal logic requirements, from early design-time model checking and theorem proving to on-board runtime verification.
+Formal methods provide continuously-advancing tools and techniques to rigorously analyze timelines expressed in the form of temporal logic requirements, from early design-time model checking and theorem proving to on-board runtime verification.
 The U.~S.~Federal Aviation Administration (FAA) even advocates the use of formal methods for flight certification of these critical systems \cite{DO-178C,DO-254,DO-333}.
@@
 efforts involving MLTL include a JAXA autonomous satellite \cite{JAXA}, a UAS Traffic Management (UTM) system involving Collins and Mosaic Aerospace \cite{HCHJR21}, a sounding rocket \cite{HLR21}, and multiple small satellites \cite{LLR21,LJBHCLR22,AJR22}.
-However, all of these successful verificaiton efforts were carried out by groups specializing in formal methods research.
-To enable broader application of formal verification, and adoption across larger projects, we critically need better validation, e.g., so that analysis over MLTL-specified requirements can tranparently contribute to flight certification.
+However, all of these successful verification efforts were carried out by groups specializing in formal methods research.
+To enable broader application of formal verification, and adoption across larger projects, we critically need better validation, e.g., so that analysis over MLTL-specified requirements can transparently contribute to flight certification.
 
@@
 
-We show that our contributions not only fill a critical gap in temporal logic valiation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C code from temporal logic behavior descriptions.
+We show that our contributions not only fill a critical gap in temporal logic validation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C code from temporal logic behavior descriptions.
 
@@
 $$\alpha := \top \ | \ \bot \ | \ p \ | \ \neg \alpha \ | \ \alpha \land \alpha \ | \ \alpha \lor \alpha \ | \ \mathcal{F}_{[a,b]} \alpha \ | \ \mathcal{G}_{[a,b]} \alpha \ | \ \alpha \mathcal{U}_{[a,b]} \alpha \ | \ \alpha \mathcal{R}_{[a,b]} \alpha \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
-We encode the Release operator directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
+We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
 
 \begin{definition}[\emph{Computation}]
-A computation of length $m$ is a sequence $\{\pi[i]\}_{i = 0}^{m-1}$ of sets of propositional variables, $\pi[i] \subseteq \mathcal{AP}$, where the $i$th set holds the propositional variables that are satisfied at the $i$th time step.
+A computation $\pi$ of length $m$ is a sequence $\{\pi[i]\}_{i = 0}^{m-1}$ of sets of propositional variables, $\pi[i] \subseteq \mathcal{AP}$, where the $i^{th}$ set holds the propositional variables that are satisfied at the $i^{th}$ time step.
 That is, a propositional variable $p$ is true at time step $i$ if and only if $p \in \pi[i]$.
@@
 
-We use a bit string representation for our computations. This representation is easy to describe using regular expressions and is convenient to code.
-
-\begin{definition}[\emph{Bit String Representation}]
+%We use a bit string representation for our computations. This representation is easy to describe using regular expressions and is convenient to code.
+
+\begin{definition}[\emph{Bit String Representation of a Computation}]
 Let $p_0, p_1, ..., p_{n-1}$ be propositional variables for a fixed $n \in \mathbb{N}$.
@@
 \begin{itemize}
-    \item We represent a true assignment to a propositional variable by $1$ and a false assignment by $0$.
-    \item For each time step $j \in [0,1,\hdots,m-1]$, we have a bit string of length $n$ where the $k$-th bit represents the truth assignment of the proposition $p_{k-1}$.
-    \item We separate each time step by a comma and order the time steps in chronological order.
+%KYR: redundant    \item We represent a true assignment to a propositional variable by $1$ and a false assignment by $0$.
+    \item For each time step $j \in [0,1,\hdots,m-1]$, we have a bit string of length $n$ where the $k^{th}$ bit represents the truth assignment of the proposition $p_{k-1}$.
+    \item We separate each time step by a comma and order the time steps chronologically.
 \end{itemize}
@@
 
-\noindent We write that a computation $\pi$ is equal to its bit string representation. An example is given below.
+%\noindent We write that a computation $\pi$ is equal to its bit string representation. An example is given below.
 
@@
 
-\subsection{Negation Normal Form}
-All MLTL formulas can be written in negation normal form (NNF) \cite{bmc}.
+%\subsection{Negation Normal Form}
+
+%KYR: TODO: represent the following sentiment when introducing the translation instead:
+%All MLTL formulas can be written in negation normal form (NNF) \cite{bmc}.
 We require MLTL formulas to be written in NNF to generate the satisfying computations using regular expressions.
 Without this requirement, generating the satisfying computations requires taking complements of the languages described by regular expressions, which is a very expensive operation.
-\begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
-An MLTL formula $\alpha$ is in \emph{negation normal form} if
-\begin{itemize}
-    \item Any negation symbols appear only in front of propositional variables.
-    \item We allow only the operations $\top$, $\bot$, $\land$, and $\lor$ from propositional logic.
-    \item We allow only the operations $\mathcal{U}$ and $\mathcal{R}$ from MLTL.
-\end{itemize}
-\end{definition}
-
-In the literature, NNF does not include the Finally and Global operators, as $\bot \mathcal{R}_{[a,b]} \alpha = \mathcal{G}_{[a,b]} \alpha$ and $\top \mathcal{U}_{[a,b]} \alpha = \mathcal{F}_{[a,b]} \alpha$.
+
+%KYR: not necessary for TACAS; the audience alraedy knows this
+%% \begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
+%% An MLTL formula $\alpha$ is in \emph{negation normal form} if
+%% \begin{itemize}
+%%     \item Any negation symbols appear only in front of propositional variables.
+%%     \item We allow only the operations $\top$, $\bot$, $\land$, and $\lor$ from propositional logic.
+%%     \item We allow only the operations $\mathcal{U}$ and $\mathcal{R}$ from MLTL.
+%% \end{itemize}
+%% \end{definition}
+
+%% In the literature, NNF does not include the Finally and Global operators, as $\bot \mathcal{R}_{[a,b]} \alpha = \mathcal{G}_{[a,b]} \alpha$ and $\top \mathcal{U}_{[a,b]} \alpha = \mathcal{F}_{[a,b]} \alpha$.
 In this paper, we stray from the literature and include Finally and Global as part of NNF, as this is far more natural for writing our regular expressions that describe the satisfying computations of a MLTL formula.
 
-\subsection{Regular Expressions}
-  We use regular expressions (regex) to describe the form of the satisfying computations. 
-\begin{definition}[\emph{Regular Expression \cite{sipser}}]
-A \emph{regular expression} is a string that describes the form of a language. 
-Let $\Sigma$ denote a finite alphabet. The empty set $\emptyset$, the empty string $\epsilon = ``"$, and any character in $\Sigma$ are constants defined to be a regular expression. 
-Beyond that, we define regular expressions recursively. 
-Suppose $R$ and $T$ are regular expressions. 
-Then the following operations generate regular expressions:
-\begin{itemize}
-    \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
-    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
-    \item \emph{(Kleene Star)} Denoted $R^*$, this operation describes the set of all strings made by concatenating any finite number (including zero) of strings described by $R$ together.
-    \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$.
-\end{itemize}
-\end{definition}
-
-\noindent We provide an example of each operation.
-\begin{example}
-Let $R$ describe \{`$a$', `$b$'\} and $T$ describe \{ `$c$', `$d$' \}.
-\begin{itemize}
-    \item $RT$ describes the set \{ `$ac$', `$ad$', `$bc$', `$bd$' \}.
-    \item $R | T$ describes the set \{`$a$', `$b$', `$c$', `$d$' \}.
-    \item $R^*$ describes the set \{ $\epsilon$, `$a$', `$b$', `$aa$', `$bb$', `$ab$', `$ba$', `$aaa$', `$aba$',... \}.
-    \item $R^2$ describes the set \{ `$aa$', `$bb$', `$ab$', `$ba$' \}.
-\end{itemize}
-\end{example}
-
-\noindent We provide examples of different regex and possible combinations of the above operations.
-\begin{example}
-Let `$a$', `$b$', and `$c$' denote characters in a finite alphabet.
-\begin{itemize}
-    \item $ab^*$ describes the set \{ `$a$', `$ab$', `$abb$', `$abbb$', ... \}.
-    \item $a^*|b$ describes the set \{ $\epsilon$, `$b$', `$a$', `$aa$', `$aaa$', ...\}.
-    \item $a(b^*)c$ describes the set \{ `$ac$', `$abc$', `$abbc$', `$abbbc$', ... \}.
-    \item $(a | b)^3$ describes the set \{ `$aaa$', `$aba$', `$aab$', `$abb$', `$bbb$', ... \}.
-\end{itemize}
-\end{example}
+%\subsection{Regular Expressions}
+%  We use regular expressions (regex) to describe the form of the satisfying computations.
+
+%KYR: Take this out and replace it with a statement that we use the standard RE operators:...
+%% \begin{definition}[\emph{Regular Expression \cite{sipser}}]
+%% A \emph{regular expression} is a string that describes the form of a language. 
+%% Let $\Sigma$ denote a finite alphabet. The empty set $\emptyset$, the empty string $\epsilon = ``"$, and any character in $\Sigma$ are constants defined to be a regular expression. 
+%% Beyond that, we define regular expressions recursively. 
+%% Suppose $R$ and $T$ are regular expressions. 
+%% Then the following operations generate regular expressions:
+%% \begin{itemize}
+%%     \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
+%%     \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
+%%     \item \emph{(Kleene Star)} Denoted $R^*$, this operation describes the set of all strings made by concatenating any finite number (including zero) of strings described by $R$ together.
+%%     \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$.
+%% \end{itemize}
+%% \end{definition}
+%
+%KYR: Examples are super nice, but if we have them we should have them after the MLTL regex example
+%\noindent We provide an example of each operation.
+%% \begin{example}
+%% Let $R$ describe \{`$a$', `$b$'\} and $T$ describe \{ `$c$', `$d$' \}.
+%% \begin{itemize}
+%%     \item $RT$ describes the set \{ `$ac$', `$ad$', `$bc$', `$bd$' \}.
+%%     \item $R | T$ describes the set \{`$a$', `$b$', `$c$', `$d$' \}.
+%%     \item $R^*$ describes the set \{ $\epsilon$, `$a$', `$b$', `$aa$', `$bb$', `$ab$', `$ba$', `$aaa$', `$aba$',... \}.
+%%     \item $R^2$ describes the set \{ `$aa$', `$bb$', `$ab$', `$ba$' \}.
+%% \end{itemize}
+%% \end{example}
+
+%% %\noindent We provide examples of different regex and possible combinations of the above operations.
+%% \begin{example}
+%% Let `$a$', `$b$', and `$c$' denote characters in a finite alphabet.
+%% \begin{itemize}
+%%     \item $ab^*$ describes the set \{ `$a$', `$ab$', `$abb$', `$abbb$', ... \}.
+%%     \item $a^*|b$ describes the set \{ $\epsilon$, `$b$', `$a$', `$aa$', `$aaa$', ...\}.
+%%     \item $a(b^*)c$ describes the set \{ `$ac$', `$abc$', `$abbc$', `$abbbc$', ... \}.
+%%     \item $(a | b)^3$ describes the set \{ `$aaa$', `$aba$', `$aab$', `$abb$', `$bbb$', ... \}.
+%% \end{itemize}
+%% \end{example}
 
@@
 \section{MLTL Regular Expressions} \label{regex}
-  We introduce the following additional notation for our regular expressions that describe the satisfying computations of a MLTL formula:
-\begin{definition}[\emph{Additional Notation}]
+We add to the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of a MLTL formula.
+\begin{definition}[\emph{Temporal Regular Expression}]
 Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$.
 Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula.
-We use the following operations in the next section to describe the form of satisfying computations of the formula in the bit string representation:
+We use the following operations to describe the form of satisfying computations of the formula in the bit string representation:
 \begin{itemize}
+  \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
+%    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
     \item $R \lor T$ denotes alternation. We use this notation to match our notation for set intersection defined below.
@@
     \item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
+      \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$. %KYR: is this one relevant or should we take it out?
     \item We do not use the Kleene star since our computations are a fixed finite length.
@@
 The first row of $J$ represents half of the regular expressions contained in the arbitrary computation.
-The other half would be represented by a regular expression of all `S's, except for a `1' at the $k$th position.
+The other half would be represented by a regular expression of all `S's, except for a `1' at the $k^{th}$ position.
 Thus, if the rest of $J$, rows $r_2$ through $r_{n+1}$, represents the other half of the arbitrary computation, then the matrix - the union of the set of the regular expressions - represents the arbitrary computation of length $n$.
@@
 
-Because the first row represents all the computations with `0' at the $k$th position, every `$S$' in $c_k$ can be replaced with a `1', to avoid redundancy; the case for which each `$S_k$' is `0' is a subset of $r_1$.
+Because the first row represents all the computations with `0' at the $k^{th}$ position, every `$S$' in $c_k$ can be replaced with a `1', to avoid redundancy; the case for which each `$S_k$' is `0' is a subset of $r_1$.
 Thus, matrix $J$ can be represented as follows:
@@
 Again, we want to show that $J'$ represents the other half of the arbitrary computation.
-Recall that we specify this to be the union of regular expressions of all $`S'$s except for a $`1'$ at the $k$th position.
-Because each row indeed contains a $`1'$ at the $k$th position, the problem reduces to showing that $r_2 - c_k$ through $r_{n+1} - c_k$ represents the arbitrary computation, where $r_j - c_k$ is the row $r_j$ with the $k$th entry removed.
+Recall that we specify this to be the union of regular expressions of all $`S'$s except for a $`1'$ at the $k^{th}$ position.
+Because each row indeed contains a $`1'$ at the $k^{th}$ position, the problem reduces to showing that $r_2 - c_k$ through $r_{n+1} - c_k$ represents the arbitrary computation, where $r_j - c_k$ is the row $r_j$ with the $k^{th}$ entry removed.
 Thus, we remove $c_k$ from $J'$ and call this new matrix $J''$:

### 2022-10-10 paper/Paper.tex
small fix
complen -> cplen, other minor changes to section 3

@@
 
-%KYR: not necessary for TACAS; the audience alraedy knows this
+%KYR: not necessary for TACAS; the audience already knows this
 %% \begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
@@
 \begin{itemize}
-  \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
+  \item \emph{(Concatenation)} Denoted $RT$, this denotes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
 %    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
@@
 \end{definition}
-An example of these operations follows.
+%An example of these operations follows.
 \begin{example}
-Let there be $n = 2$ propositional variables, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
+Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
@@
 We define the regular expression of satisfying computations for an MLTL formula as follows:
+
+% ZILI: Failed attempt to get formulas side by side
+% \begin{minipage}{0.45 \textwidth}
+%     \begin{align}
+%     &\text{reg}(\top) = S^n\\
+%     &\text{reg}(\bot) = \emptyset \\
+%     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
+%     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
+%     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
+%     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta)
+%     \end{align}
+% \end{minipage}
+% \begin{minipage}{0.55 \textwidth}
+%     \begin{align}
+%     &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
+%     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
+%     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
+%     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
+%     \end{align}
+% \end{minipage}
+
 \begin{align}
@@
  \subsection{Minimum Computation Length}
- These regular expressions describe all the satisfying computations of an MLTL formula of length $\text{complen}(\alpha)$, which is defined recursively below:
+ These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\alpha)$, which is defined recursively below:
 \begin{align}
-    &\text{complen}(p_k) = \text{complen}(\neg p_k) = 1\\
-    &\text{complen}(\alpha \land \beta) = \text{complen}(\alpha \lor \beta) = \max(\text{complen}(\alpha), \text{complen}(\beta))\\
-    &\text{complen}(\mathcal{G}_{[a,b]} \alpha) = \text{complen}(\mathcal{F}_{[a,b]} \alpha) = b + \text{complen}(\alpha)\\
-    &\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta))
+    &\text{cplen}(p_k) = \text{cplen}(\neg p_k) = 1\\
+    &\text{cplen}(\alpha \land \beta) = \text{cplen}(\alpha \lor \beta) = \max(\text{cplen}(\alpha), \text{cplen}(\beta))\\
+    &\text{cplen}(\mathcal{G}_{[a,b]} \alpha) = \text{cplen}(\mathcal{F}_{[a,b]} \alpha) = b + \text{cplen}(\alpha)\\
+    &\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta))
 \end{align}
 
-Intuitively, $\text{complen}(\alpha)$ is the minimum computation length required to ensure that none of the intervals in $\alpha$ are out of bounds.
+Intuitively, $\text{cplen}(\alpha)$ is the minimum computation length required to ensure that none of the intervals in $\alpha$ are out of bounds.
 Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature.
-In \cite{KZJZR20}, $$\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha), \text{complen}(\beta))$$
+In \cite{KZJZR20}, $$\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha), \text{cplen}(\beta))$$
 
 whereas our minimum computation length for Until and Release is 
-$$\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\mathbf{\text{complen}(\alpha)-1}, \text{complen}(\beta)).$$
+$$\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\mathbf{\text{cplen}(\alpha)-1}, \text{cplen}(\beta)).$$
 We provide the proof for the minimum computation length of Until and Release below.
@@
     Let $0 \leq a\leq b \in \mathbb{N}$ and let $\alpha, \beta$ be well-formed MLTL formulas in NNF.
-The minimum computation length of Until and Release is given by $\text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta))$.
+The minimum computation length of Until and Release is given by $\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta))$.
 \end{theorem}
@@
  \begin{align*}
-     \text{complen}(\alpha \mathcal{U}_{[a,b]} \beta) &= \max_{a \leq i \leq b} \left( \text{complen}(\mathcal{G}_{[a, i-1]} \alpha \land \mathcal{G}_{[i,i]} \beta) \right)\\
-     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{complen}(\alpha), i + \text{complen}(\beta))\right)\\
-     &= \max_{a \leq i \leq b} \left(i + \max(\text{complen}(\alpha) - 1, \text{complen}(\beta))\right)\\
-     &= b + \max(\text{complen}(\alpha) - 1, \text{complen}(\beta)).
+     \text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \alpha \land \mathcal{G}_{[i,i]} \beta) \right)\\
+     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\alpha), i + \text{cplen}(\beta))\right)\\
+     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\alpha) - 1, \text{cplen}(\beta))\right)\\
+     &= b + \max(\text{cplen}(\alpha) - 1, \text{cplen}(\beta)).
  \end{align*}
@@
  \begin{align*}
-     \text{complen}(\alpha \mathcal{R}_{[a,b]} \beta) &= \max \left( \text{complen}(\mathcal{G}_{[a,b]} \beta), \text{complen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)  \right)\\
-     &= \max\left( b + \text{complen}(\beta), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)\\
-     &= \max \left( b + \text{complen}(\beta), \max_{a \leq i \leq b-1} \left(\max(i + \text{complen}(\beta), i + \text{complen}(\alpha))\right) \right)\\
-     &= \max \left( b + \text{complen}(\beta), \max(b-1+\text{complen}(\alpha), b-1+\text{complen}(\beta))\right)\\
-     &= \max(b + \text{complen}(\beta), b-1+\text{complen}(\alpha), b-1+\text{complen}(\beta))\\
-     &= b + \max(\text{complen}(\alpha)-1, \text{complen}(\beta)).
+     \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \beta), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)  \right)\\
+     &= \max\left( b + \text{cplen}(\beta), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)\\
+     &= \max \left( b + \text{cplen}(\beta), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\beta), i + \text{cplen}(\alpha))\right) \right)\\
+     &= \max \left( b + \text{cplen}(\beta), \max(b-1+\text{cplen}(\alpha), b-1+\text{cplen}(\beta))\right)\\
+     &= \max(b + \text{cplen}(\beta), b-1+\text{cplen}(\alpha), b-1+\text{cplen}(\beta))\\
+     &= b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta)).
  \end{align*}
@@
  \begin{theorem}[\emph{Soundness and Completeness}]
- For any well formed MLTL formula $\alpha$ in negation normal form, a computation $\pi$ with $|\pi| = \text{complen}(\alpha)$ satisfies $\alpha$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\alpha))$.
+ For any well formed MLTL formula $\alpha$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\alpha)$ satisfies $\alpha$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\alpha))$.
  \end{theorem}
@@
  We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
- If $|\pi| = \text{complen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
-Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{complen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
+ If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
+Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
@@
  We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
- Since $|\pi| = \text{complen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{complen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
+ Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
@@
 %\end{adjustwidth}
-
 \textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} = \alpha_{2}$'' \textbf{:}
@@
 %\end{adjustwidth}
-
 \textbf{If} $\alpha$ \textbf{is} ``$\lor$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
@@
 %\end{adjustwidth}
-
 \textbf{If} $\alpha$ \textbf{is} ``$\&$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
@@
 %\end{adjustwidth}
-
 \textbf{If} $\alpha$ \textbf{is} ``$=$ [$\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:}
@@
 %\end{adjustwidth}
-
  \textbf{If} $\alpha \text{ is } ``\mathcal{G}_{[a,b]} \alpha_{1}$"\textbf{:}
@@
 % \end{adjustwidth}
-
  \textbf{If} $\alpha \text{ is } ``\mathcal{F}_{[a,b]} \alpha_{1}$"\textbf{:}
@@
 %  \end{adjustwidth}
-
 \begin{theorem}[\emph{Space Complexity}]
@@
  \end{proof}
-
 For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
@@
 Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.
-
 One feature within our implementation of \textit{reg} is to apply the \textit{simplify} function to all intermediary vector calculations in order to decrease the output size.
@@
 Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.
-
 \subsubsection{Simulation 1}
@@
 \end{itemize}
-
 \subsubsection{Simulation 2}
@@
 \end{figure}
-
 \subsubsection{Simulation 3}
@@
 The former two are also the time complexity outliers.
-
 \subsubsection{Simulation 4}
@@
 \end{itemize}
-
 We obtain the following plots:
@@
 \end{figure}
-
 \noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively sparse.
@@
 As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in practical applications.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program for any reasonable party.
-
 We approach this problem more intelligently.
@@
 Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST program.
-
 \subsection{Theoretical Correctness of the WEST Algorithm}
  Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}.
-
 The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
-
 \textit{Join} takes as input two vectors of computation strings $R$ and $T$, and simply returns a vector containing all strings in $R$ and $T$, which is equivalent to $R \cup T$. 
-
 \textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ...
@@
 \end{align*}
-
 \textit{Set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
@@
 Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.
-
 The correctness for \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, \textit{reg\_R}, and \textit{reg} will be proven by induction on depth of recursion to \textit{reg}. 
 The depth of recursion is exactly the depth of the parse tree of the input formula.
-
 For the base case (depth $0$), \textit{reg\_prop\_var} and \textit{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.
-
 Then assume \textit{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$.
@@
 The proof for all four cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.
-
 We give the explicit proof for the case $\gamma = \alpha \mathcal{U}_{[a,b]} \beta$ as an example.
@@
 \end{align*}
-
 The last line follows from the semantics of the Global operator, which defines out of bound time step behavior to be vacuously true.
@@
 Continue in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.
-
 \subsection{Correctness of WEST}
@@
 Miller describes his approach in \cite{Miller} as follows: \\
-
  \textit{``If we consider a program to
 be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''} \\
-
 Intelligent fuzzing (sometimes referred to as whitebox fuzzing) is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
@@
 \end{enumerate}
-
 \subsubsection{State Diagram Construction}
@@
 The core of the WEST program is executed in the recursive routine, \textit{reg}, which calls the $8$ different subroutines discussed earlier, as shown in the graph below: 
-
 \begin{figure}[H]
@@
 \end{figure}
-
 In order to construct the intelligent fuzzing test suite, we make the design choice to abstract away the eight subroutines in the overall state space diagram, despite the fact that they may have different possible execution paths within them.
 Without this abstraction, attempting to explore all execution paths in this finer graph is infeasible due to the explosion in the number of paths \cite{Pham_2016}, some of which are provably impossible to construct a test input to explore.
-
 Additionally, the astute reader may observe that analysis of the $>$, $=$, and \textit{assoc\_prop\_conn} operators are not included in the state diagram. 
@@
 This is done through simple string manipulation, which is relatively simple to guarantee and test correctness of through unit testing.
-
 \subsubsection{Creating the Test Suite}
@@
 $d = 3$ is computationally infeasible, and $d = 1$ doesn't give us assurance about operators interacting with each other through nesting. Thus $d = 2$ is a happy medium. 
-
 The full test suite is generated in a similar recursive manner. 
@@
 To ensure wider coverage, each of the propositional variables or their negation and propositional constants are randomly generated (full pseudocode description in Appendix \ref{pseudocode appendix}).
-
 \subsubsection{Verifying against Naive Brute Force}
- A relatively straight forward approach to generating the set of all satisfying computations of a MLTL formula $\alpha$ over $n$ variables, such that $m = \text{complen}(\alpha)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
+ A relatively straight forward approach to generating the set of all satisfying computations of a MLTL formula $\alpha$ over $n$ variables, such that $m = \text{cplen}(\alpha)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
 The main work is done by an interpreter function that takes arguments of computation $\pi$ and MLTL formula $\alpha$ and determines if $\pi \vDash \alpha$ purely based on semantics that define MLTL.
@@
 The full implementation details can be found on the \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{GitHub} repository. 
-
 As expected for a brute force implementation, extensive run time poses a major limitation; the previously mentioned infeasibility of not abstracting away subroutines and running test suites for deeper depths is primarily caused by this stage of verification.
@@
 For instance, the regular expression ``$1SS0SS1$" yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
-
 It's important to state that although the full test suite matches between both implementations, absolute correctness on all inputs is not guaranteed for either program.
 However, the successful execution of the test suite gives us a much higher confidence in correctness of both the WEST program and the brute force program.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 We first define some vocabulary.
-
 \begin{definition}[\emph{Arbitrary Computation}]
@@
 \end{definition}
-
 \begin{theorem}[\emph{Regular Expression Simplification Theorem}] \label{simp}
@@
 \end{theorem}
-
 \noindent \textbf{Example:}
@@
 \end{center}
-
 \noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\
-
 Note that the theorem is a sufficient but not necessary condition for simplification to the arbitrary computation.
 One such example is the regular expression $101|S1S|1S0|0SS$, which fails the hypothesis of the simplification theorem but is still equivalent to $SSS$.
-
 \subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
-
 \begin{example} \label{example1}
@@
 Our program outputs the following union of regular expressions to represent this formula:
-
 \begin{center}
@@
 \end{center}
-
 Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation.
 However, we foresee some challenges to the implementation of this algorithm.
-
 First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
@@
 For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
-
 Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end. Consider the following MLTL formula:
@@
 \end{center}
-
 It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
-
 Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
@@
 \end{center}
-
 The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively.
@@
 Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very sparse in practice. 
-
 We have also applied techniques in intelligent fuzzing to explore the state space of the algorithm in a structured way. 
@@
 Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used in algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
-
 \subsection{Additional Research Directions}
 \textbf{Describe all satisfying computations to LTL formulas using $\omega$-regular expressions.}
-
 $\omega$-regular expression are defined to match only infinite words, and can be used to describe satisfying computations to LTL formulas (which has infinite time steps). 
@@
 \\
-
 \noindent \textbf{Simplifying unions of regular expressions to a minimal representation.}
-
 Theorem \ref{simp} addresses a non-trivial situation in which a vector of regular expressions may be simplified.
@@
 There may be other schemes needed to simplify any arbitrary union of regular expressions to their minimal representation.\\
-
 \noindent \textbf{A more general application of intelligent fuzzing to recursive algorithms.}
-
 A tool to systematically convert a recursive algorithm (perhaps written in some strictly defined pseudocode syntax) into a directed graph representation of the state space would be a helpful aid for generating test suites.
@@
 Additional care should be put into allowing for varying levels of abstractions of execution due to concerns of the path explosion problem. 
-
 % FUTURE WORK:
 % potentially recursive function implementation of Regular Expression Simplification Theorem
-
 %% \subsubsection{Acknowledgements}
-
 %% \hspace{\parindent} This work was done as part of Iowa State University's Research Experience for Undergraduates funded by NSF grant DMS-1950583.
 We would like to thank Iowa State University and the NSF for this research opportunity.
-
 %% The assistance of our mentors Dr.
@@
 Bernard Lidický for their management of this program and organization of its funding.
-
 %% Finally, we want to thank Brian Kempa for his guidance and suggestions on the intelligent fuzzing portion of our research, and Dr.
 Steve Butler for his intuition on the Regular Expression Simplification Theorem.
-
 %
@@
 \bibliography{Citations}
-
 \newpage
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \pi_k \vDash \beta \text{)} \]
-
 We proceed by cases to show that:
@@
 \indent Case 0: If $|\pi| \leq a$, then we are immediately done.
-
 \indent Case 1: Suppose $\forall i \in [a,b] \text{, } \pi_i \vDash \beta$.\\
@@
 \]
-
 \indent Case 2: Suppose $\exists i \in [a,b] \text{, } \pi_i \cancel{\vDash} \beta$.\\
@@
 $ $ \newline
-
 \noindent ($\Leftarrow$):\\
@@
 \[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{B1} \]
-
 \indent Case 0: If $|\pi| \leq a$, again we are immediately done. \\
@@
 \indent \indent Relabeling $s$ to $i$, we now have that $\forall i \in [a, b] \text{, (}\pi_s \vDash \beta \text{)}$, which implies line B1. \\
-
 \indent Case 2: Suppose $\exists s \in [a,b], \pi_s \cancel{\vDash} \beta$.\\
@@
 \tag{2}\]
-
 \indent \indent Since (line 2) $\exists i_1 \in [a,b], \pi_{i_1} \cancel{\vDash} \beta$, by Line 1 we have that: $\pi_{i_1} \vDash \beta \text{ or } \exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \alpha$.\\
@@
 \]
-
 \indent \indent Since $[a,t] \subseteq [a, i_1 - 1] \subseteq [a,b-1]$, we have that $t \in [a,b-1]$, so let $j := t$.
-
 \indent \indent Then from lines 3 and 4, we have that:
@@
 \]
-
 \indent \indent From line 5, we now get:
@@
 \end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Assume no row is the arbitrary computation, because then the union of the set of regular expressions would trivially simplify to the arbitrary computation.\\
-
 We begin by showing that there must be at least one row in the matrix $M$ that is composed of one fixed truth value and $n-1$ `$S$'s.
@@
 Thus, there must exist at least one row composed of one fixed truth value and $n-1$ `$S$'s. \\
-
 \noindent We now proceed by induction on the length of computations, $n$. \\
@@
         $$
-
 \noindent \textbf{Inductive Hypothesis:}\\
@@
 We show $J$ is equivalent to the arbitrary computation of length $n$.\\
-
 As aforementioned, there must exist at least one row composed of one fixed truth value and $n-1$ `$S$'s, and the union of regular expressions is commutative.
@@
 Suppose this known truth value is in column $k$, $c_k$, where $1 \leq k \leq n$.. Assume WLOG that this value is a 0. Matrix $J$ can be represented as follows:
-
 \[
@@
  \]
-
 The first row of $J$ represents half of the regular expressions contained in the arbitrary computation.
@@
 We show that this is indeed the case:
-
 Because the first row represents all the computations with `0' at the $k^{th}$ position, every `$S$' in $c_k$ can be replaced with a `1', to avoid redundancy; the case for which each `$S_k$' is `0' is a subset of $r_1$.
 Thus, matrix $J$ can be represented as follows:
-
 \[
@@
  \]
-
 The problem reduces to showing that $J - r_1$, that is, $J$ with the row $r_1$ removed, represents the other half of the arbitrary computation. Thus, let $J' = J - r_1$:
-
 \[
@@
  \]
-
 Again, we want to show that $J'$ represents the other half of the arbitrary computation.
@@
 \]
-
 Because $J''$ is the result removing one row and one column from $J$, $J''$ has $n$ rows and $n-1$ columns.
@@
 Thus, $J''$ is equivalent to $H$, and is therefore equivalent to the arbitrary computation by the inductive hypothesis.
-
 Because $r_1$ is equivalent to half of the arbitrary computation and $J'$ is equivalent to the other half of the arbitrary computation, $J$ is equivalent to the arbitrary computation, as the union of $r_1$ and $J'$ is equivalent to $J$.
-
 Therefore, by induction, the theorem holds.
 \end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.
-
 \begin{algorithm}[H]
@@
 \begin{algorithmic}
-
 \Procedure{Pad}{vector $R$, int $n$} 
@@
 \EndProcedure
-
 \end{algorithmic}
 \end{algorithm}
-
 \begin{algorithm}[H]
@@
 \begin{algorithmic}
-
 \Procedure{reg\_prop\_var}{string nnf, int $n$}
@@
 \begin{algorithmic}
-
 \Procedure{simplify\_string}{string $r$, string $b$}   
@@
 \begin{algorithmic}
-
 \Procedure{simplify}{vector $R$}    
@@
 \end{algorithm}
-
 \begin{algorithm}[H]
@@
 \begin{algorithmic}
-
 \Procedure{set\_intersect}{vector $R$, vector $B$, bool simp}
@@
 \begin{algorithmic}
-
 \Procedure{join}{vector $R$, vector $B$, bool simp}
@@
 \begin{algorithmic}
-
 \Procedure{reg\_G}{vector reg\_alpha, int $a$, int $b$, int $n$, bool simp} 
@@
 \EndProcedure
-
 \end{algorithmic}
@@
 \begin{algorithmic}
-
 \Procedure{reg\_F}{vector reg\_alpha, int $a$, int $b$, int $n$, bool simp} 
@@
 \EndProcedure
-
 \end{algorithmic}
 \end{algorithm}
-
 \label{regU}
@@
 \begin{algorithmic}
-
 \Procedure{reg\_U}{vector reg\_alpha, vector reg\_beta int $a$, int $b$, int $n$, bool simp} 
@@
 \begin{algorithmic}
-
 \Procedure{reg\_R}{vector reg\_alpha, vector reg\_beta int $a$, int $b$, int $n$, bool simp} 
@@
 \begin{algorithmic}
-
 \Procedure{reg}{string nnf, int $n$, bool sub, bool simp} 
@@
 \end{algorithm}
-
 \newpage
@@
 For the graph of the \textit{reg} function, the option to store subformulas has been omitted as well.\\
-
 \begin{figure}[H]
@@
 \end{figure}
-
 \begin{figure}[H]
@@
 \end{figure}
-
 \begin{landscape}

### 2022-10-10 paper/Paper.tex
put MLTL formulas side by side, included paragraph about NNF

@@
 \begin{itemize}
-  \item \emph{(Concatenation)} Denoted $RT$, this denotes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
+    \item \emph{(Concatenation)} $RT$ denotes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
 %    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
-    \item $R \lor T$ denotes alternation. We use this notation to match our notation for set intersection defined below.
+    \item \emph{(Alternation)} Denoted $R \lor T$ to match the notation for set intersection below.
     \item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
@@
 \begin{example}
-Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
+Let $n = 2$, and let $R = S1$ and $T = 1S,1S \lor S1,S1$.\\
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
 Clearly $T$ is the longer regex by one time step, so we concatenate $,S^2$ to the right of $R$.
-Thus $T =1S,1S | S1,S1$ and $R = S1,SS$.
+Thus $T =1S,1S \lor S1,S1$ and $R = S1,SS$.
 Now the regexes are the same length, so we can perform set intersection and alternation:
 \begin{itemize}
-    \item $R \land T = 11,1S | S1, S1$.
-    \item $R \lor T = S1,SS | 1S,1S | S1,S1 = S1,SS | 1S,1S$.
+    \item $R \land T = 11,1S \lor S1, S1$.
+    \item $R \lor T = S1,SS \lor 1S,1S \lor S1,S1 = S1,SS \lor 1S,1S$.
 \end{itemize}
@@
 Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\alpha, \beta$ well-formed MLTL formulas in negation normal form. 
-We define the regular expression of satisfying computations for an MLTL formula as follows:
-
-% ZILI: Failed attempt to get formulas side by side
-% \begin{minipage}{0.45 \textwidth}
+All MLTL formulas can be written in negation normal form (NNF) \cite{bmc}.
+We require MLTL formulas to be written in NNF to generate the satisfying computations using regular expressions.
+Without this requirement, generating the satisfying computations requires taking complements of the languages described by regular expressions, which is a very expensive operation.
+We now define the regular expression of satisfying computations for an MLTL formula as follows:
+
+% ZILI: Should we left align equations 9 and 10?
+\begin{minipage}{0.50 \textwidth}
+    \begin{align}
+    &\text{reg}(\top) = S^n\\
+    &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
+    &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
+    &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)
+    \end{align}
+\end{minipage}
+\begin{minipage}{0.50 \textwidth}
+    \begin{align}
+    &\text{reg}(\bot) = \emptyset \\
+    &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
+    &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta)\\
+    &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) 
+    \end{align}
+\end{minipage}
+\begin{align}
+    &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
+    &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
+\end{align}
+
+% ZILI: Reformatted for better space efficiency
 % \begin{align}
@@
 %      &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
-%     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta)
-%     \end{align}
-% \end{minipage}
-% \begin{minipage}{0.55 \textwidth}
-%     \begin{align}
+%      &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta) \\
 %      &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
@@
 % \end{align}
-% \end{minipage}
-
-\begin{align}
-     &\text{reg}(\top) = S^n\\
-     &\text{reg}(\bot) = \emptyset \\
-     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
-     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
-     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta) \\
-     &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
-     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
-     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
-     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
-\end{align}
 

### 2022-10-10 paper/Paper.tex
alpha -> phi beta -> psi

--- 2022-10-10 paper/Paper.tex
@@
 %\title{Contribution Title\thanks{Supported by organization x.}}
-\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review]}}
+\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}}
 %
@@
 
+\vspace{-0.1in}
 \begin{abstract}
@@
 Finally, we generate a test suite using control flow diagrams to robustly test the code.
-
+\vspace{-0.1in}
 \keywords{First keyword  \and Second keyword \and Another keyword.}
@@
 
+\vspace{-0.1in}
 \section{Introduction}
-
+\vspace{-0.1in}
 System specifications, such as aerospace operational concepts, often utilize timelines to express critical requirements.
@@
 Finally, we show an application of the regular expressions of the satisfying computations by using them to prove an MLTL theorem.
-In particular, we show that $\alpha\mathcal{U}_{[a,b]}(\alpha\mathcal{U}_{[0,c]}\beta) = \alpha\mathcal{U}_{[a,b+c]}\beta$ and $\alpha\mathcal{R}_{[a,b]}(\alpha\mathcal{R}_{[0,c]}\beta) = \alpha\mathcal{R}_{[a,b+c]}\beta$.
+In particular, we show that $\phi\mathcal{U}_{[a,b]}(\phi\mathcal{U}_{[0,c]}\psi) = \phi\mathcal{U}_{[a,b+c]}\psi$ and $\phi\mathcal{R}_{[a,b]}(\phi\mathcal{R}_{[0,c]}\psi) = \phi\mathcal{R}_{[a,b+c]}\psi$.
 %
@@
 Section \ref{simpsection}, provides a combinatorial theorem for simplifying certain outputs of the WEST program.
-Formulas of the form $\alpha \equiv \beta$ to check for equivalence between two expressions can lead to outputs that are non-trivial to simplify.
+Formulas of the form $\phi \equiv \psi$ to check for equivalence between two expressions can lead to outputs that are non-trivial to simplify.
 Section \ref{Conclusion} discusses impacts and future work.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Mission-time LTL and Regular Expressions} \label{prereq}
+\vspace{-0.1in}
+\section{Preliminaries: Mission-time LTL and Bit String Computations} \label{prereq}
+\vspace{-0.1in}
 %\subsection{Mission-time Linear Temporal Logic}
 {\bf Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
-The syntax of an MLTL formula over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:
-$$\alpha := \top \ | \ \bot \ | \ p \ | \ \neg \alpha \ | \ \alpha \land \alpha \ | \ \alpha \lor \alpha \ | \ \mathcal{F}_{[a,b]} \alpha \ | \ \mathcal{G}_{[a,b]} \alpha \ | \ \alpha \mathcal{U}_{[a,b]} \alpha \ | \ \alpha \mathcal{R}_{[a,b]} \alpha \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
+The syntax of an MLTL formula over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
+\vspace{-0.1in}
+$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \phi \ | \ \phi \land \phi \ | \ \phi \lor \phi \ | \ \mathcal{F}_{[a,b]} \phi \ | \ \mathcal{G}_{[a,b]} \phi \ | \ \phi \mathcal{U}_{[a,b]} \phi \ | \ \phi \mathcal{R}_{[a,b]} \phi \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
 We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
-
+\vspace{-0.1in}
+%
 \begin{definition}[\emph{Computation}]
@@
 %% \subsubsection{Semantics}
-%% We say a computation $\pi$ as satisfies a given MLTL formula $\alpha$, written $\pi \vDash \alpha$, when\footnote{In MLTL, we do not include the Next ($\chi$) operator since $\mathcal{G}_{[1,1]}$ is equivalent to it.}:
+%% We say a computation $\pi$ as satisfies a given MLTL formula $\phi$, written $\pi \vDash \phi$, when\footnote{In MLTL, we do not include the Next ($\chi$) operator since $\mathcal{G}_{[1,1]}$ is equivalent to it.}:
 %% \begin{align}
 %%     &\pi \vDash p \text{ iff } p \in \pi[0]\\
-%%     &\pi \vDash \neg \alpha \text{ iff } \pi \nvDash \alpha\\
-%%     &\pi \vDash \alpha \land \beta \text{ iff } \pi \vDash \alpha \text{ and } \pi \vDash \beta\\
-%%     &\pi \vDash \alpha \lor \beta \text{ iff } \pi \vDash \alpha \text{ or } \pi \vDash \beta\\
-%%     &\pi \vDash \mathcal{F}_{[a,b]}\alpha \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \alpha\\
-%%     &\pi \vDash \mathcal{G}_{[a,b]}\alpha \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \alpha\\
-%%     &\pi \vDash \alpha \ \mathcal{U}_{[a,b]} \beta \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \beta \text{ and }\\
-%%     & \indent \forall j \in [a, i-1]\ \pi_j \vDash \alpha \nonumber \\
-%%     &\pi \vDash \alpha \ \mathcal{R}_{[a,b]} \beta \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \beta \text{ or }\\
-%%     & \indent \exists j \in [a,b-1] \text{ such that } \pi_j \vDash \alpha \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \beta \nonumber
+%%     &\pi \vDash \neg \phi \text{ iff } \pi \nvDash \phi\\
+%%     &\pi \vDash \phi \land \psi \text{ iff } \pi \vDash \phi \text{ and } \pi \vDash \psi\\
+%%     &\pi \vDash \phi \lor \psi \text{ iff } \pi \vDash \phi \text{ or } \pi \vDash \psi\\
+%%     &\pi \vDash \mathcal{F}_{[a,b]}\phi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \phi\\
+%%     &\pi \vDash \mathcal{G}_{[a,b]}\phi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \phi\\
+%%     &\pi \vDash \phi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \psi \text{ and }\\
+%%     & \indent \forall j \in [a, i-1]\ \pi_j \vDash \phi \nonumber \\
+%%     &\pi \vDash \phi \ \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or }\\
+%%     & \indent \exists j \in [a,b-1] \text{ such that } \pi_j \vDash \phi \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \psi \nonumber
 %% \end{align}
@@
 %% \begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
-%% An MLTL formula $\alpha$ is in \emph{negation normal form} if
+%% An MLTL formula $\phi$ is in \emph{negation normal form} if
 %% \begin{itemize}
@@
 
-%% In the literature, NNF does not include the Finally and Global operators, as $\bot \mathcal{R}_{[a,b]} \alpha = \mathcal{G}_{[a,b]} \alpha$ and $\top \mathcal{U}_{[a,b]} \alpha = \mathcal{F}_{[a,b]} \alpha$.
+%% In the literature, NNF does not include the Finally and Global operators, as $\bot \mathcal{R}_{[a,b]} \phi = \mathcal{G}_{[a,b]} \phi$ and $\top \mathcal{U}_{[a,b]} \phi = \mathcal{F}_{[a,b]} \phi$.
 In this paper, we stray from the literature and include Finally and Global as part of NNF, as this is far more natural for writing our regular expressions that describe the satisfying computations of a MLTL formula.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{-0.1in}
 \section{MLTL Regular Expressions} \label{regex}
-We add to the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of a MLTL formula.
+\vspace{-0.1in}
+We extend the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of an MLTL formula.
 \begin{definition}[\emph{Temporal Regular Expression}]
@@
 \begin{itemize}
-  \item \emph{(Concatenation)} Denoted $RT$, this denotes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
-%    \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
-    \item $R \lor T$ denotes alternation. We use this notation to match our notation for set intersection defined below.
+  \item \emph{(Concatenation)} Denoted $RT$, describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
+ \item \emph{(Alternation)} Denoted $R \lor T$, describes the set union of the strings generated by $R$ and $T$.
     \item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
@@
 %An example of these operations follows.
-\begin{example}
+\begin{example} %KYR: NICE example!
 Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
-Clearly $T$ is the longer regex by one time step, so we concatenate $,S^2$ to the right of $R$.
+Since $T$ is the longer regex by one time step, we concatenate $,S^2$ to the right of $R$.
 Thus $T =1S,1S | S1,S1$ and $R = S1,SS$.
@@
 
-For the purposes of describing the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{`$0$' , `$1$', `$,$'\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
-Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\alpha, \beta$ well-formed MLTL formulas in negation normal form.
-We define the regular expression of satisfying computations for an MLTL formula as follows:
-
+To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{`$0$' , `$1$', `$,$'\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
+Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\phi, \psi$ well-formed MLTL formulas in negation normal form.
+We define the regular expression of satisfying computations for an MLTL formula as follows:\\
+%
+%
 % ZILI: Failed attempt to get formulas side by side
@@
 %     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-%     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
-%     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta)
+%     &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
+%     &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi)
 %     \end{align}
@@
 %     \begin{align}
-%     &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
-%     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
-%     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
-%     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
+%     &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi) \\
+%     &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)\\
+%     &\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
+%     &\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
 %     \end{align}
 % \end{minipage}
-
-\begin{align}
-     &\text{reg}(\top) = S^n\\
-     &\text{reg}(\bot) = \emptyset \\
-     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
-     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-     &\text{reg}(\alpha \lor \beta) =  \text{reg}(\alpha) \lor \text{reg}(\beta)\\
-     &\text{reg}(\alpha \land \beta) = \text{reg}(\alpha) \land \text{reg}(\beta) \\
-     &\text{reg}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha) \\
-     &\text{reg}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)\\
-     &\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
-     &\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \label{release}
-\end{align}
-
+%
+%ORIGINAL:
+%% \begin{align}
+%%      &\text{reg}(\top) = S^n\\
+%%      &\text{reg}(\bot) = \emptyset \\
+%%      &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
+%%      &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
+%%      &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
+%%      &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi) \\
+%%      &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi) \\
+%%      &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)\\
+%%      &\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
+%%      &\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
+%% \end{align}
+%%
+     $\text{reg}(\top) = S^n$ \hfill 
+     $\text{reg}(\bot) = \emptyset$ \\
+     $\text{reg}(p_k) = S^{k}1S^{n-k-1}$ \hfill
+     $\text{reg}(\neg p_k) = S^{k}0S^{n-k-1}$ \\
+     $\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)$\hfill
+     $\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi)$ \\
+     $\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)$ \hfill
+     $\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)$\\
+     $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$ \\
+     $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$ %\label{release} %KYR: I notice this label was not used...
+
+     \vspace{-0.1in}
      \subsection{Minimum Computation Length}
- These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\alpha)$, which is defined recursively below:
-\begin{align}
-    &\text{cplen}(p_k) = \text{cplen}(\neg p_k) = 1\\
-    &\text{cplen}(\alpha \land \beta) = \text{cplen}(\alpha \lor \beta) = \max(\text{cplen}(\alpha), \text{cplen}(\beta))\\
-    &\text{cplen}(\mathcal{G}_{[a,b]} \alpha) = \text{cplen}(\mathcal{F}_{[a,b]} \alpha) = b + \text{cplen}(\alpha)\\
-    &\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta))
-\end{align}
-
-Intuitively, $\text{cplen}(\alpha)$ is the minimum computation length required to ensure that none of the intervals in $\alpha$ are out of bounds.
+          \vspace{-0.1in}
+ %These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\phi)$, which is defined recursively below:
+We define computation length $\text{cplen}(\phi)$ of an MLTL formula recursively:\\
+          %\begin{align}
+\indent \qquad   $\text{cplen}(p_k) = \text{cplen}(\neg p_k) = 1$\\
+\indent \qquad   $\text{cplen}(\phi \land \psi) = \text{cplen}(\phi \lor \psi) = \max(\text{cplen}(\phi), \text{cplen}(\psi))$\\
+\indent \qquad   $\text{cplen}(\mathcal{G}_{[a,b]} \phi) = \text{cplen}(\mathcal{F}_{[a,b]} \phi) = b + \text{cplen}(\phi)$\\
+\indent \qquad   $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi))$
+%\end{align}
+
+Intuitively, $\text{cplen}(\phi)$ is the minimum computation length required to ensure that none of the intervals in $\phi$ are out of bounds.
 Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature.
-In \cite{KZJZR20}, $$\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha), \text{cplen}(\beta))$$
+In \cite{KZJZR20}, $$\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi), \text{cplen}(\psi))$$
 
 whereas our minimum computation length for Until and Release is 
-$$\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\mathbf{\text{cplen}(\alpha)-1}, \text{cplen}(\beta)).$$
+$$\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\mathbf{\text{cplen}(\phi)-1}, \text{cplen}(\psi)).$$
 We provide the proof for the minimum computation length of Until and Release below.
 \begin{theorem}[\emph{Minimum Computation Length of Until and Release}]
-    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\alpha, \beta$ be well-formed MLTL formulas in NNF.
-The minimum computation length of Until and Release is given by $\text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) = \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) = b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta))$.
+    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\phi, \psi$ be well-formed MLTL formulas in NNF.
+The minimum computation length of Until and Release is given by $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi))$.
 \end{theorem}
@@
 The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Global, And, and Or.\\
- Recall that $\text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)$. Thus
- \begin{align*}
-     \text{cplen}(\alpha \mathcal{U}_{[a,b]} \beta) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \alpha \land \mathcal{G}_{[i,i]} \beta) \right)\\
-     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\alpha), i + \text{cplen}(\beta))\right)\\
-     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\alpha) - 1, \text{cplen}(\beta))\right)\\
-     &= b + \max(\text{cplen}(\alpha) - 1, \text{cplen}(\beta)).
- \end{align*}
- Now recall that $\text{reg}(\alpha \mathcal{R}_{[a,b]} \beta) =  \text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)$.
+ Recall that $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$. Thus
+ \begin{align*}
+     \text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \phi \land \mathcal{G}_{[i,i]} \psi) \right)\\
+     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\phi), i + \text{cplen}(\psi))\right)\\
+     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi))\right)\\
+     &= b + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi)).
+ \end{align*}
+ Now recall that $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$.
 Thus
  \begin{align*}
-     \text{cplen}(\alpha \mathcal{R}_{[a,b]} \beta) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \beta), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)  \right)\\
-     &= \max\left( b + \text{cplen}(\beta), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right) \right)\\
-     &= \max \left( b + \text{cplen}(\beta), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\beta), i + \text{cplen}(\alpha))\right) \right)\\
-     &= \max \left( b + \text{cplen}(\beta), \max(b-1+\text{cplen}(\alpha), b-1+\text{cplen}(\beta))\right)\\
-     &= \max(b + \text{cplen}(\beta), b-1+\text{cplen}(\alpha), b-1+\text{cplen}(\beta))\\
-     &= b + \max(\text{cplen}(\alpha)-1, \text{cplen}(\beta)).
+     \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \psi), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)  \right)\\
+     &= \max\left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)\\
+     &= \max \left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\psi), i + \text{cplen}(\phi))\right) \right)\\
+     &= \max \left( b + \text{cplen}(\psi), \max(b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\right)\\
+     &= \max(b + \text{cplen}(\psi), b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\\
+     &= b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi)).
  \end{align*}
@@
  \begin{itemize}
-     \item At the final time-step for $\alpha \mathcal{U}_{[a,b]} \beta$, if $\beta$ has not yet been assigned to be true in the computation, it will be assigned true because $\alpha \mathcal{U}_{[a,b]} \beta$ is a strong operator.
-Semantically, the truth value of $\alpha$ at this time interval doesn't matter; whether $\alpha$ is true or false, the computation for $\alpha \mathcal{U}_{[a,b]} \beta$ is satisfied.
-     \item Likewise, in the case for $\alpha \mathcal{R}_{[a,b]} \beta$, if $\beta$ is true from the first to the last time-step, the truth value of $\alpha$ at the final time-step doesn't matter - the computation satisfies $\alpha \mathcal{R}_{[a,b]} \beta$ regardless of whether $\alpha$ is true or false.
+     \item At the final time-step for $\phi \mathcal{U}_{[a,b]} \psi$, if $\psi$ has not yet been assigned to be true in the computation, it will be assigned true because $\phi \mathcal{U}_{[a,b]} \psi$ is a strong operator.
+Semantically, the truth value of $\phi$ at this time interval doesn't matter; whether $\phi$ is true or false, the computation for $\phi \mathcal{U}_{[a,b]} \psi$ is satisfied.
+     \item Likewise, in the case for $\phi \mathcal{R}_{[a,b]} \psi$, if $\psi$ is true from the first to the last time-step, the truth value of $\phi$ at the final time-step doesn't matter - the computation satisfies $\phi \mathcal{R}_{[a,b]} \psi$ regardless of whether $\phi$ is true or false.
  \end{itemize}
@@
 \subsection{Soundness and Completeness}
- We write $\mathscr{L}(\text{reg}(\alpha))$ to denote the language of reg($\alpha$). That is, the set of computations represented by the regular expression $\text{reg}(\alpha)$.
+ We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
 
  \begin{theorem}[\emph{Soundness and Completeness}]
- For any well formed MLTL formula $\alpha$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\alpha)$ satisfies $\alpha$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\alpha))$.
+ For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
  \end{theorem}
@@
  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
- $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
+ $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
 
@@
  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
- $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\alpha)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
+ $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
 
@@
   Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently,
-  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
+  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
 
@@
   By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case.
-the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)\right)$.
+the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)$.
 Hence
@@
   \begin{align*}
-    \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)\right) \\
-    &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)\right)\\
+    \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right) \\
+    &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)\\
     &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
@@
 Let $\mathcal{B} = \mathcal{R} \text{ or } \mathcal{U}$.
-Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \alpha,   \beta$ \text{be well-formed MLTL formulas in NNF.
-Then,} $ \alpha \ \mathcal{B}_{[a,b+c]} \beta = \alpha \ \mathcal{B}_{[a,b]}(\alpha \ \mathcal{B}_{[0,c]} \beta)$.
-That is, $ \alpha \ \mathcal{U}_{[a,b+c]} \beta \equiv \alpha \ \mathcal{U}_{[a,b]}(\alpha \ \mathcal{U}_{[0,c]} \beta)$ and $ \alpha \ \mathcal{R}_{[a,b+c]} \beta \equiv \alpha \ \mathcal{R}_{[a,b]}(\alpha \ \mathcal{R}_{[0,c]} \beta)$.
+Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \phi,   \psi$ \text{be well-formed MLTL formulas in NNF.
+Then,} $ \phi \ \mathcal{B}_{[a,b+c]} \psi = \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
+That is, $ \phi \ \mathcal{U}_{[a,b+c]} \psi \equiv \phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi)$ and $ \phi \ \mathcal{R}_{[a,b+c]} \psi \equiv \phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi)$.
 \end{theorem}
@@
 
-\noindent Let $\gamma = \alpha \ \mathcal{U}_{[0,c]} \beta$.
-Then, $\alpha \ \mathcal{U}_{[a,b]}(\alpha \ \mathcal{U}_{[0,c]} \beta) = \alpha \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha \land \mathcal{G}_{[j, j]}\beta\right).$ Thus
-
-\begin{align*}
-\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\beta\right) \right) \right).
+\noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
+Then, $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
+
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
+&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right).
 \end{align*}
@@
 \begin{align*}
-\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\beta\right) \right) \right) \\
-&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\alpha\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
-\mathcal{G}_{[j, j]}\beta \right) \right) \right).
-\end{align*}
-Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \alpha \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \alpha$, we have
-\begin{align*}
-\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta \right) \right) \right) \\
-&= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta \right).
-\end{align*}
-Since $\mathcal{G}_{[t_1,t_2-1]}\alpha \land \mathcal{G}_{[t_2,t_3]} \alpha \equiv \mathcal{G}_{[t_1,t_3]} \alpha$, we have
-\begin{align*}
-\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta  \right)\\
-&= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\beta  \right).
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right) \\
+&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
+\mathcal{G}_{[j, j]}\psi \right) \right) \right).
+\end{align*}
+Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right) \right) \right) \\
+&= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right).
+\end{align*}
+Since $\mathcal{G}_{[t_1,t_2-1]}\phi \land \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1,t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right)\\
+&= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right).
 \end{align*}
@@
 \begin{align*}
-\text{reg}\left(\alpha \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\alpha\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\beta  \right) \\
-&= \text{reg}\left(\alpha \ \mathcal{U}_{[a,b+c]} \beta\right).
-\end{align*}
-This shows that $\alpha \ \mathcal{U}_{[a,b]}(\alpha \ \mathcal{U}_{[0,c]} \beta) \equiv \alpha \ \mathcal{U}_{[a,b+c]} \beta$.\\
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\psi  \right) \\
+&= \text{reg}\left(\phi \ \mathcal{U}_{[a,b+c]} \psi\right).
+\end{align*}
+This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
 
@@
 \begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\beta\right) &= \text{reg}\left(\neg\left(\neg\alpha \ \mathcal{U}_{[a,b]}\neg\beta\right)\right) \\
-&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\alpha \land \mathcal{G}_{[i, i]}\neg\beta\right)\right).
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \text{reg}\left(\neg\left(\neg\phi \ \mathcal{U}_{[a,b]}\neg\psi\right)\right) \\
+&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\phi \land \mathcal{G}_{[i, i]}\neg\psi\right)\right).
 \end{align*}
@@
 \begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\beta\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\alpha \land \neg\mathcal{F}_{[i, i]}\beta\right)\right)\\
-&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\beta\right)\right)\right)\\
-&= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\beta\right)\right)\\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\beta\right).
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\phi \land \neg\mathcal{F}_{[i, i]}\psi\right)\right)\\
+&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\right)\\
+&= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\\
+&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right).
 \end{align*}
 This completes the rewriting of the regex for Release.
-Now let $\gamma = \alpha \ \mathcal{R}_{[0,c]} \beta$.
-Then $\alpha \ \mathcal{R}_{[a,b]}(\alpha \ \mathcal{R}_{[0,c]} \beta) = \alpha \ \mathcal{R}_{[a,b]}\gamma$ and
-$\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha \lor \mathcal{F}_{[j, j]}\beta\right)$. Thus
-\begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\beta\right) \right) \right).
+Now let $\gamma = \phi \ \mathcal{R}_{[0,c]} \psi$.
+Then $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) = \phi \ \mathcal{R}_{[a,b]}\gamma$ and
+$\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi \lor \mathcal{F}_{[j, j]}\psi\right)$. Thus
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
+&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right).
 \end{align*}
@@
 \begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\beta\right) \right) \right) \\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\alpha\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\beta \right) \right) \right).
-\end{align*}
-Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \alpha \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \alpha$, we have
-\begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta \right) \right) \right) \\
-&= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\alpha\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta \right).
-\end{align*}
-Since $\mathcal{F}_{[t_1,t_2-1]} \alpha \land \mathcal{F}_{[t_2,t_3]} \alpha \equiv \mathcal{F}_{[t_1, t_3]} \alpha$, we have
-\begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta  \right) \\
-&= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\beta  \right).
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right) \\
+&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\psi \right) \right) \right).
+\end{align*}
+Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right) \right) \right) \\
+&= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right).
+\end{align*}
+Since $\mathcal{F}_{[t_1,t_2-1]} \phi \land \mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1, t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right) \\
+&= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right).
 \end{align*}
@@
 \begin{align*}
-\text{reg}\left(\alpha \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\alpha\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\beta  \right) \\
-&= \text{reg}\left(\alpha \ \mathcal{R}_{[a,b+c]} \beta\right).
-\end{align*}
-Thus  $\alpha \ \mathcal{R}_{[a,b]}(\alpha \ \mathcal{R}_{[0,c]} \beta) \equiv \alpha \ \mathcal{R}_{[a,b+c]} \beta$, so $\alpha \ \mathcal{B}_{[a,b+c]} \beta \equiv \alpha \ \mathcal{B}_{[a,b]}(\alpha \ \mathcal{B}_{[0,c]} \beta)$.
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\psi  \right) \\
+&= \text{reg}\left(\phi \ \mathcal{R}_{[a,b+c]} \psi\right).
+\end{align*}
+Thus  $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) \equiv \phi \ \mathcal{R}_{[a,b+c]} \psi$, so $\phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
 This completes the proof.
@@
 \section{WEST Code Specifications} \label{specs}
- The code for the WEST program can be found on its \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{Github} repository.
+The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
+{Github} repository.
 The MLTL syntax for our program is given as the context free grammar below.
@@
 In the grammar, associative propositional connectives (\textit{Assoc\_Prop\_conn}) are included for the ease of the user.
-Given well-formed formulas $\alpha_1, \alpha_2, \alpha_3$, the following formula in prefix notation $(\lor[\alpha_1, \alpha_2, \alpha_3])$ is parsed into $((\alpha_1 \lor \alpha_2) \lor \alpha_3)$, which is in turn equivalent to $(\alpha_1 \lor \alpha_2 \lor \alpha_3)$.
+Given well-formed formulas $\phi_1, \phi_2, \phi_3$, the following formula in prefix notation $(\lor[\phi_1, \phi_2, \phi_3])$ is parsed into $((\phi_1 \lor \phi_2) \lor \phi_3)$, which is in turn equivalent to $(\phi_1 \lor \phi_2 \lor \phi_3)$.
 \\
@@
 We provide a summary of the complexity of each of the helper functions described for \textit{reg}. 
-For any function $f(\alpha)$ taking a string argument $\alpha$, we use $|\alpha|$ to denote the number of characters in $\alpha$ and $S(f(\alpha))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
-
-\textbf{If $\alpha$ is a propositional constant or variable:}
+For any function $f(\phi)$ taking a string argument $\phi$, we use $|\phi|$ to denote the number of characters in $\phi$ and $S(f(\phi))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
+
+\textbf{If $\phi$ is a propositional constant or variable:}
 %\begin{adjustwidth}{10mm}{3em}
@@
     By definition $\text{\emph{reg}}(T) = S^n$, so we have that $S(\text{\emph{reg}}(T)) = O(n)$.
-Similar to $\alpha = T$, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)$ both return strings of the same length and thus we also have $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)) = S(\text{\emph{reg}}(T)) = n$.\\
+Similar to $\phi = T$, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)$ both return strings of the same length and thus we also have $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)) = S(\text{\emph{reg}}(T)) = n$.\\
 %\end{adjustwidth}
 
-\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} \lor \alpha_{2}$'' \textbf{:}
+\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} \lor \phi_{2}$'' \textbf{:}
 %\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we return $\textit{join}(\text{\emph{reg}}(\alpha_{1}), \text{\emph{reg}}(\alpha_{2}))$ \\
+    For this case in our \emph{reg} function, we return $\textit{join}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}))$ \\
     Thus, our space complexity is:
     \[
-    S(\text{\emph{reg}}(\alpha_{1} \lor \alpha_{2})) = S(\text{\emph{reg}}(\alpha_{1})) + S(\text{\emph{reg}}(\alpha_{2})).
+    S(\text{\emph{reg}}(\phi_{1} \lor \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).
     \]
@@
 
-\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} \; \& \; \alpha_{2}$'' \textbf{:}
+\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} \; \& \; \phi_{2}$'' \textbf{:}
 %\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we return $ \textit{set\_intersect}(\text{\emph{reg}}(\alpha_{1}), \text{\emph{reg}}(\alpha_{2}), n)$ \\
+    For this case in our \emph{reg} function, we return $ \textit{set\_intersect}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}), n)$ \\
     In the worst case, \textit{set\_intersect}($A$, $B$, $n$) will return a vector of size $S(A) \cdot S(B)$.\\
@@
     \[ 
-    S(\text{\emph{reg}}(\alpha_{1} \; \& \; \alpha_{2})) = S(\text{\emph{reg}}(\alpha_{1})) \cdot S(\text{\emph{reg}}(\alpha_{2})).
+    S(\text{\emph{reg}}(\phi_{1} \; \& \; \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})).
     \]
@@
 
-\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} >  \alpha_{2}$'' \textbf{:}
+\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} >  \phi_{2}$'' \textbf{:}
 %\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} > \alpha_{2}$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \lor \text{''} + \alpha_{2} + \text{``)''}.
+    For this case in our \emph{reg} function, we first rewrite $\phi_{1} > \phi_{2}$ to the equivalent formula:
+    \[ 
+    \textit{equiv\_formula} = \text{``(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1}) + \text{``} \lor \text{''} + \phi_{2} + \text{``)''}.
     \]
@@
     \[ 
-    S(\text{\emph{reg}}(\alpha_{1} > \alpha_{2})) = S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) + S(\text{\emph{reg}}(\alpha_{2})).
+    S(\text{\emph{reg}}(\phi_{1} > \phi_{2})) = S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).
     \]
 %\end{adjustwidth}
-\textbf{If} $\alpha$ \textbf{is} ``$\alpha_{1} = \alpha_{2}$'' \textbf{:}
+\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} = \phi_{2}$'' \textbf{:}
 %\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we first rewrite $\alpha_{1} = \alpha_{2}$ to the equivalent formula:
+    For this case in our \emph{reg} function, we first rewrite $\phi_{1} = \phi_{2}$ to the equivalent formula:
     \[ 
     \textit{equiv\_formula} = 
-    \text{``((''} + \alpha_{1} + \text{``} \& \text{''} + \alpha_{2} + \text{``)}
+    \text{``((''} + \phi_{1} + \text{``} \& \text{''} + \phi_{2} + \text{``)}
     \lor 
-    \text{(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1}) + \text{``} \& \text{''} +  \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2}) + \text{``))''}.
+    \text{(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1}) + \text{``} \& \text{''} +  \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{2}) + \text{``))''}.
     \]
@@
     \[ 
-    S(\text{\emph{reg}}(\alpha_{1} = \alpha_{2})) =
-    S(\text{\emph{reg}}(\alpha_{1})) \cdot S(\text{\emph{reg}}(\alpha_{2})) \; + \;  
-    S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{1})) \cdot S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{2})).
+    S(\text{\emph{reg}}(\phi_{1} = \phi_{2})) =
+    S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})) \; + \;  
+    S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1})) \cdot S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{2})).
     \]
 %\end{adjustwidth}
-\textbf{If} $\alpha$ \textbf{is} ``$\lor$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
+\textbf{If} $\phi$ \textbf{is} ``$\lor$ [ $\phi_{1}$, .., $\phi_{k}$]'' \textbf{:} 
 %\begin{adjustwidth}{10mm}{3em}
-For this case in our \emph{reg} function, we first rewrite $\lor [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \lor \alpha_{2}) \lor ... \alpha_{k})\text{''}.
+For this case in our \emph{reg} function, we first rewrite $\lor [\phi_{1}, .., \phi_{k}]$ to the equivalent formula:
+    \[ 
+    \textit{equiv\_formula} = \text{``}( ... (\phi_{1} \lor \phi_{2}) \lor ... \phi_{k})\text{''}.
     \]
@@
     \[
-    S(\text{\emph{reg}}(\lor [\alpha_{1}, .., \alpha_{k}])) = 
-    \sum_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
+    S(\text{\emph{reg}}(\lor [\phi_{1}, .., \phi_{k}])) = 
+    \sum_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i})).
     \]
 %\end{adjustwidth}
-\textbf{If} $\alpha$ \textbf{is} ``$\&$ [ $\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:} 
+\textbf{If} $\phi$ \textbf{is} ``$\&$ [ $\phi_{1}$, .., $\phi_{k}$]'' \textbf{:} 
 %\begin{adjustwidth}{10mm}{3em}
-For this case in our \emph{reg} function, we first rewrite $\& [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} \& \alpha_{2}) \& ... \alpha_{k})\text{''}.
+For this case in our \emph{reg} function, we first rewrite $\& [\phi_{1}, .., \phi_{k}]$ to the equivalent formula:
+    \[ 
+    \textit{equiv\_formula} = \text{``}( ... (\phi_{1} \& \phi_{2}) \& ... \phi_{k})\text{''}.
     \]
@@
     \[
-    S(\text{\emph{reg}}(\& [\alpha_{1}, .., \alpha_{k}])) = 
-    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i})).
+    S(\text{\emph{reg}}(\& [\phi_{1}, .., \phi_{k}])) = 
+    \prod_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i})).
     \]
 %\end{adjustwidth}
-\textbf{If} $\alpha$ \textbf{is} ``$=$ [$\alpha_{1}$, .., $\alpha_{k}$]'' \textbf{:}
+\textbf{If} $\phi$ \textbf{is} ``$=$ [$\phi_{1}$, .., $\phi_{k}$]'' \textbf{:}
 %\begin{adjustwidth}{10mm}{3em}
-For this case in our \emph{reg} function, we first rewrite $= [\alpha_{1}, .., \alpha_{k}]$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``}( ... (\alpha_{1} = \alpha_{2}) = ... \alpha_{k})\text{''}.
+For this case in our \emph{reg} function, we first rewrite $= [\phi_{1}, .., \phi_{k}]$ to the equivalent formula:
+    \[ 
+    \textit{equiv\_formula} = \text{``}( ... (\phi_{1} = \phi_{2}) = ... \phi_{k})\text{''}.
     \]
@@
     \[
-    S(\text{\emph{reg}}(= [\alpha_{1}, .., \alpha_{k}])) = 
-    \prod_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i}))
-    + \prod_{i=1}^{k} S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \alpha_{i}))).
+    S(\text{\emph{reg}}(= [\phi_{1}, .., \phi_{k}])) = 
+    \prod_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i}))
+    + \prod_{i=1}^{k} S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{i}))).
     \]
 %\end{adjustwidth}
- \textbf{If} $\alpha \text{ is } ``\mathcal{G}_{[a,b]} \alpha_{1}$"\textbf{:}
+ \textbf{If} $\phi \text{ is } ``\mathcal{G}_{[a,b]} \phi_{1}$"\textbf{:}
 % \begin{adjustwidth}{10mm}{3em}
- Recall that $\text{\emph{reg}}(\mathcal{G}_{[a,b]} \alpha) = \bigwedge_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\alpha) (,S^n)^{b-i}$.\\
- As shown in the \textit{Assoc\_Prop\_Conn} case, if $\alpha$ is ``$\&[\alpha_1, ... ,\alpha_k$]", then \\
- $\text{S(\emph{reg}}(\& [\alpha_{1}, .., \alpha_{k}])) = 
-    \prod_{i=1}^{k} \text{S(\emph{reg}}(\alpha_{i}))$. We have that:
- \begin{align*}
-     \text{S(\emph{reg}}(\alpha)) &= \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\alpha_{1}))\\
-     &< \Bigl([(n+1)b+1] \cdot \text{S(\emph{reg}}(\alpha_1))\Bigl)^\delta \\
-     &= \mathcal{C}_{G} \cdot \text{S(\emph{reg}}(\alpha_1)^\delta 
+ Recall that $\text{\emph{reg}}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi) (,S^n)^{b-i}$.\\
+ As shown in the \textit{Assoc\_Prop\_Conn} case, if $\phi$ is ``$\&[\phi_1, ... ,\phi_k$]", then \\
+ $\text{S(\emph{reg}}(\& [\phi_{1}, .., \phi_{k}])) = 
+    \prod_{i=1}^{k} \text{S(\emph{reg}}(\phi_{i}))$. We have that:
+ \begin{align*}
+     \text{S(\emph{reg}}(\phi)) &= \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1}))\\
+     &< \Bigl([(n+1)b+1] \cdot \text{S(\emph{reg}}(\phi_1))\Bigl)^\delta \\
+     &= \mathcal{C}_{G} \cdot \text{S(\emph{reg}}(\phi_1)^\delta 
  \end{align*}
@@
 % \end{adjustwidth}
- \textbf{If} $\alpha \text{ is } ``\mathcal{F}_{[a,b]} \alpha_{1}$"\textbf{:}
+ \textbf{If} $\phi \text{ is } ``\mathcal{F}_{[a,b]} \phi_{1}$"\textbf{:}
 % \begin{adjustwidth}{10mm}{3em}
- Recall that $\text{\emph{reg}}(\mathcal{F}_{[a,b]} \alpha) = \bigvee_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\alpha)(,S^n)^{b-i}$. \\
- As shown in the \textit{Assoc\_Prop\_Conn} case, if $\alpha$ is ``$\lor[\alpha_1, ... ,\alpha_k$]", then \\
- $S(\text{\emph{reg}}(\lor [\alpha_{1}, .., \alpha_{k}])) = 
-    \sum_{i=1}^{k} S(\text{\emph{reg}}(\alpha_{i}))$. Thus with similar calculation to $\mathcal{G}$,
- \begin{align*}
-     \text{S(\emph{reg}}(\alpha)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\alpha_{1})) \\
-     &< \delta\Bigl(((n+1)b+1) \cdot \text{S(\emph{reg}}(\alpha_1))\Bigl) \\
-     &= \mathcal{C}_{F} \cdot \text{S(\emph{reg}}(\alpha_1)
+ Recall that $\text{\emph{reg}}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi)(,S^n)^{b-i}$. \\
+ As shown in the \textit{Assoc\_Prop\_Conn} case, if $\phi$ is ``$\lor[\phi_1, ... ,\phi_k$]", then \\
+ $S(\text{\emph{reg}}(\lor [\phi_{1}, .., \phi_{k}])) = 
+    \sum_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i}))$. Thus with similar calculation to $\mathcal{G}$,
+ \begin{align*}
+     \text{S(\emph{reg}}(\phi)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) \\
+     &< \delta\Bigl(((n+1)b+1) \cdot \text{S(\emph{reg}}(\phi_1))\Bigl) \\
+     &= \mathcal{C}_{F} \cdot \text{S(\emph{reg}}(\phi_1)
  \end{align*}
@@
 
- \textbf{If $\alpha$ = $``\alpha_1 \mathcal{U}_{[a, b]} \alpha_2"$:}
+ \textbf{If $\phi$ = $``\phi_1 \mathcal{U}_{[a, b]} \phi_2"$:}
 % \begin{adjustwidth}{10mm}{3em}
     By our previous definitions, 
-    $\text{\emph{reg}}(\alpha_1 \ \mathcal{U}_{[a,b]} \alpha_2) =  \bigvee_{i=a}^{b} \text{\emph{reg}}\left(\mathcal{G}_{[a,i-1]}\alpha_1 \land \mathcal{G}_{[i, i]} \alpha_2\right)$. \\
-    We can bound $S(\text{\emph{reg}}(\mathcal{G}_{[i, i]} \alpha_2))$ by $(n+1) \cdot i \cdot S(\text{\emph{reg}}(\alpha_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
+    $\text{\emph{reg}}(\phi_1 \ \mathcal{U}_{[a,b]} \phi_2) =  \bigvee_{i=a}^{b} \text{\emph{reg}}\left(\mathcal{G}_{[a,i-1]}\phi_1 \land \mathcal{G}_{[i, i]} \phi_2\right)$. \\
+    We can bound $S(\text{\emph{reg}}(\mathcal{G}_{[i, i]} \phi_2))$ by $(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
     Thus using our previous results for the $\mathcal{G}$, $\&$ and $\lor$ operators, we have that:
     \begin{align*}
-        S(\text{\emph{reg}}(\alpha)) &= 
-        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\text{\emph{reg}}(\alpha_1))]^\delta 
-        [(n+1) \cdot i \cdot S(\text{\emph{reg}}(\alpha_2))] \\
-        &< \delta [((n+1)(b-1) + 1) \cdot S(\text{\emph{reg}}(\alpha_1))]^\delta 
-        [(n+1) \cdot b \cdot S(\text{\emph{reg}}(\alpha_2))] \\
-        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\text{\emph{reg}}(\alpha_1))^\delta \cdot S(\text{\emph{reg}}(\alpha_2)) \\
-        &= \mathcal{C}_U \cdot S(\text{\emph{reg}}(\alpha_1))^\delta \cdot S(\text{\emph{reg}}(\alpha_2))
+        S(\text{\emph{reg}}(\phi)) &= 
+        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
+        [(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))] \\
+        &< \delta [((n+1)(b-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
+        [(n+1) \cdot b \cdot S(\text{\emph{reg}}(\phi_2))] \\
+        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2)) \\
+        &= \mathcal{C}_U \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))
     \end{align*}
@@
 
-  \textbf{If $\alpha$ = $``\alpha_1 \mathcal{R}_{[a, b]} \alpha_2"$:}
+  \textbf{If $\phi$ = $``\phi_1 \mathcal{R}_{[a, b]} \phi_2"$:}
 %  \begin{adjustwidth}{10mm}{3em}
-        By our previous definitions, $\text{\emph{reg}}(\alpha_1 \mathcal{R}_{[a,b]} \alpha_2) =  \text{\emph{reg}}\left(\mathcal{G}_{[a,b]}\alpha_2\right) \lor \bigvee_{i=a}^{b-1} \text{\emph{reg}}\left(\mathcal{G}_{[a,i]}\alpha_2 \land \mathcal{G}_{[i, i]} \alpha_1\right)$.
+        By our previous definitions, $\text{\emph{reg}}(\phi_1 \mathcal{R}_{[a,b]} \phi_2) =  \text{\emph{reg}}\left(\mathcal{G}_{[a,b]}\phi_2\right) \lor \bigvee_{i=a}^{b-1} \text{\emph{reg}}\left(\mathcal{G}_{[a,i]}\phi_2 \land \mathcal{G}_{[i, i]} \phi_1\right)$.
 Thus, a similar argument to the $\mathcal{U}$ case gives us that:
         \begin{align*}
-            S(\text{\emph{reg}}(\alpha)) &< 
-            \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
-            \delta + \sum_{i = a}^{b-1} [\mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
-            \delta \cdot (n+1)\cdot i \cdot S(\text{\emph{reg}}(\alpha_2))] \\
-            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
-            \delta + \delta[\mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
-            \delta \cdot (n+1)(b-1) \cdot S(\text{\emph{reg}}(\alpha_2))] \\
-            &= \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
-            \delta [1 + \delta(n+1)(b-1)S(\text{\emph{reg}}(\alpha_2))] \\
-            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\alpha_1))^
-            \delta (\delta(n+1)d \cdot S(\text{\emph{reg}}(\alpha_2))) \\
-            &= \mathcal{C}_R \cdot S(\text{\emph{reg}}(\alpha_1))^\delta \cdot S(\text{\emph{reg}}(\alpha_2))
+            S(\text{\emph{reg}}(\phi)) &< 
+            \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
+            \delta + \sum_{i = a}^{b-1} [\mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
+            \delta \cdot (n+1)\cdot i \cdot S(\text{\emph{reg}}(\phi_2))] \\
+            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
+            \delta + \delta[\mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
+            \delta \cdot (n+1)(b-1) \cdot S(\text{\emph{reg}}(\phi_2))] \\
+            &= \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
+            \delta [1 + \delta(n+1)(b-1)S(\text{\emph{reg}}(\phi_2))] \\
+            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
+            \delta (\delta(n+1)d \cdot S(\text{\emph{reg}}(\phi_2))) \\
+            &= \mathcal{C}_R \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))
         \end{align*}
@@
 \begin{theorem}[\emph{Space Complexity}]
-Given a well formed MLTL formula $\alpha$, $\text{\emph{reg}}(\alpha)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\alpha$.
+Given a well formed MLTL formula $\phi$, $\text{\emph{reg}}(\phi)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
 \end{theorem}
@@
 However if the nesting is only from one side, such as formulas similar to $(((p_0 \mathcal{U} p_1) \mathcal{U} p_2) \mathcal{U} p_3)$, then the maximum depth of recursion is $O(\ell)$.
-Thus we'll focus on the formula $$\alpha = (((p_0 \mathcal{U}_{[a_1, b_1]} p_1) \mathcal{U}_{[a_2, b_2]} p_2) \mathcal{U}_{[a_3, b_3]}...
+Thus we'll focus on the formula $$\phi = (((p_0 \mathcal{U}_{[a_1, b_1]} p_1) \mathcal{U}_{[a_2, b_2]} p_2) \mathcal{U}_{[a_3, b_3]}...
 \mathcal{U}_{[a_{\ell - 1}, b_{\ell - 1}]} p_{\ell - 1}) \mathcal{U}_{[a_\ell, b_\ell]} p_\ell$$ where there are $\ell$ logical connectives $\mathcal{U}$ and $n = \ell + 1$ propositional variables.
 
-    We'll derive the complexity of $S(\text{\emph{reg}}(\alpha))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\text{\emph{reg}}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\text{\emph{reg}}(p_{k+1}))$.
+    We'll derive the complexity of $S(\text{\emph{reg}}(\phi))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\text{\emph{reg}}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\text{\emph{reg}}(p_{k+1}))$.
 The recurrence relation captures an extra nesting of the $\mathcal{U}$ operator, based on the complexity of $\mathcal{U}$ defined above.
@@
 
-    \noindent Thus we have that $S(\text{\emph{reg}}(\alpha)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
+    \noindent Thus we have that $S(\text{\emph{reg}}(\phi)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
 
@@
 For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
-In particular, the time complexities of $\alpha = p_k, \scriptstyle{\sim}\textstyle p_k, T, !$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{C}_U$ match their respective space complexities.
+In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, T, !$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{C}_U$ match their respective space complexities.
 Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.
@@
 Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$.
-$\gamma$ must be of the form $\mathcal{G}_{[a,b]}\alpha$, $\mathcal{F}_{[a,b]}\alpha$, $\alpha \mathcal{U}_{[a,b]} \beta$, or $\alpha \mathcal{R}_{[a,b]} \beta$, such that $\alpha$ and $\beta$ are of depth at most $d$, and $a$, $b$ are positive integers.
+$\gamma$ must be of the form $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are positive integers.
 The proof for all four cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.
-We give the explicit proof for the case $\gamma = \alpha \mathcal{U}_{[a,b]} \beta$ as an example.
-In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_alpha} = \textit{reg}(\alpha)$ and $\textit{reg\_beta} = \textit{reg}(\beta)$, which, by the induction hypothesis, are correctly and recursively computed.
+We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
+In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_alpha} = \textit{reg}(\phi)$ and $\textit{reg\_beta} = \textit{reg}(\psi)$, which, by the induction hypothesis, are correctly and recursively computed.
 The regular expression for the Until operator may be rewritten as follows: 
 \begin{align*}
-   \text{reg}(\alpha \ \mathcal{U}_{[a,b]} \beta) &=  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
-   &= \text{reg}\left(\mathcal{G}_{[a,a-1]}\alpha \land \mathcal{G}_{[a, a]} \beta\right) \lor \bigvee_{i=a+1}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right) \\
-   &= \text{reg}\left(\mathcal{G}_{[a, a]} \beta \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\alpha \land \mathcal{G}_{[i+1, i+1]} \beta\right)
+   \text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) &=  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
+   &= \text{reg}\left(\mathcal{G}_{[a,a-1]}\phi \land \mathcal{G}_{[a, a]} \psi\right) \lor \bigvee_{i=a+1}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
+   &= \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)
 \end{align*}
 The last line follows from the semantics of the Global operator, which defines out of bound time step behavior to be vacuously true.
-In the pseudocode for $reg\_U$ (\ref{regU}), the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_beta}, and is the regular expression for $\mathcal{G}_[a, a] \beta$.
+In the pseudocode for $reg\_U$ (\ref{regU}), the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_beta}, and is the regular expression for $\mathcal{G}_[a, a] \psi$.
 Next, the Or block from $i = a + 1$ to $b - 1$ is iteratively computed using \textit{set\_intersect} for the inner expression, and added to \textit{comp} with the \textit{join} function, which are both proven correct above.
@@
 \subsubsection{Verifying against Naive Brute Force}
- A relatively straight forward approach to generating the set of all satisfying computations of a MLTL formula $\alpha$ over $n$ variables, such that $m = \text{cplen}(\alpha)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
-The main work is done by an interpreter function that takes arguments of computation $\pi$ and MLTL formula $\alpha$ and determines if $\pi \vDash \alpha$ purely based on semantics that define MLTL.
+ A relatively straight forward approach to generating the set of all satisfying computations of a MLTL formula $\phi$ over $n$ variables, such that $m = \text{cplen}(\phi)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
+The main work is done by an interpreter function that takes arguments of computation $\pi$ and MLTL formula $\phi$ and determines if $\pi \vDash \phi$ purely based on semantics that define MLTL.
 Every first-order quantifier is easily translated to loops, and checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
-The full implementation details can be found on the \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{GitHub} repository. 
+The full implementation details can be found on the %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} %KYR: blind review
+{GitHub} repository. 
 As expected for a brute force implementation, extensive run time poses a major limitation; the previously mentioned infeasibility of not abstracting away subroutines and running test suites for deeper depths is primarily caused by this stage of verification.
@@
 The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safe critical systems, and the WEST program can aide in the debugging of such specifications.
-The WEST program accomplishes this: given MLTL formula $\alpha$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
+The WEST program accomplishes this: given MLTL formula $\phi$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
 The tool itself has demonstratively reasonable run time. 
@@
  The definition of Release is equivalent to the dual of Until: 
- $\alpha \mathcal{R} \beta \equiv \neg (\neg \alpha \mathcal{U} \neg \beta)$. That is to say,
-$\alpha \mathcal{R}_{[a,b]} \beta$ if and only if $|\pi| \le a \text{ or } \forall s \in [a,b] ,(\pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] , \pi_t \vDash \alpha)$.
+ $\phi \mathcal{R} \psi \equiv \neg (\neg \phi \mathcal{U} \neg \psi)$. That is to say,
+$\phi \mathcal{R}_{[a,b]} \psi$ if and only if $|\pi| \le a \text{ or } \forall s \in [a,b] ,(\pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] , \pi_t \vDash \phi)$.
  \end{lemma}
@@
 ($\Rightarrow$):\\
-\indent Suppose $\pi \vDash \alpha \mathcal{R}_{[a,b]} \beta$, so:
-\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \pi_k \vDash \beta \text{)} \]
+\indent Suppose $\pi \vDash \phi \mathcal{R}_{[a,b]} \psi$, so:
+\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \psi \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \pi_k \vDash \psi \text{)} \]
 We proceed by cases to show that:
 \[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)} \tag{A1}
+|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)} \tag{A1}
 \]
 \indent Case 0: If $|\pi| \leq a$, then we are immediately done.
-\indent Case 1: Suppose $\forall i \in [a,b] \text{, } \pi_i \vDash \beta$.\\
-\indent Through re-labeling, we have $\forall s \in [a,b] \text{, } \pi_s \vDash \beta$. Then we clearly have:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)} \tag{A1}
-\]
-\indent Case 2: Suppose $\exists i \in [a,b] \text{, } \pi_i \cancel{\vDash} \beta$.\\
+\indent Case 1: Suppose $\forall i \in [a,b] \text{, } \pi_i \vDash \psi$.\\
+\indent Through re-labeling, we have $\forall s \in [a,b] \text{, } \pi_s \vDash \psi$. Then we clearly have:
+\[
+|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)} \tag{A1}
+\]
+\indent Case 2: Suppose $\exists i \in [a,b] \text{, } \pi_i \cancel{\vDash} \psi$.\\
 \indent \indent Then we must have that:
-\[ \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{1} \]
-\indent \indent We want to show that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)}$.\\
+\[ \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{1} \]
+\indent \indent We want to show that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)}$.\\
 \\
 \indent \indent Suppose by contradiction that: 
-\[ \exists s \in [a,b] \text{, (} \forall t \in [a, s-1] \text{, } \pi_t \cancel{\vDash} \alpha \text{)} \tag{2} \]
+\[ \exists s \in [a,b] \text{, (} \forall t \in [a, s-1] \text{, } \pi_t \cancel{\vDash} \phi \text{)} \tag{2} \]
 \indent \indent Since $s \in [a,b] \text{ and }  t \in [a, s-1]$, we have that $t \in [a,b-1]$.\\
-\indent \indent Since $j \in [a,b-1]$ (from Line 1), we have that $\pi_j \cancel{\vDash} \alpha$ from Line 2.\\
-\indent \indent However from Line 1 we have that $\pi_j \vDash \alpha$ and have thus derived a contradiction.\\
-\indent \indent Thus, we now have that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)}$.\\ \indent \indent From this, we clearly have that:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{)} \tag{A1}
+\indent \indent Since $j \in [a,b-1]$ (from Line 1), we have that $\pi_j \cancel{\vDash} \phi$ from Line 2.\\
+\indent \indent However from Line 1 we have that $\pi_j \vDash \phi$ and have thus derived a contradiction.\\
+\indent \indent Thus, we now have that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)}$.\\ \indent \indent From this, we clearly have that:
+\[
+|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)} \tag{A1}
 \]
@@
 \noindent ($\Leftarrow$):\\
-\indent Suppose that $\pi \vDash \neg (\neg \alpha \mathcal{U} \neg \beta)$:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \alpha \text{) \tag{1}}
+\indent Suppose that $\pi \vDash \neg (\neg \phi \mathcal{U} \neg \psi)$:
+\[
+|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{) \tag{1}}
 \]
 $ $ \newline
-\indent We want to show $\pi \vDash \alpha R_{[a,b]} \beta$, that is:
-\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{B1} \]
+\indent We want to show $\pi \vDash \phi R_{[a,b]} \psi$, that is:
+\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \psi \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{B1} \]
 \indent Case 0: If $|\pi| \leq a$, again we are immediately done. \\
-\indent Case 1: Suppose $\forall s \in [a,b] \text{, (} \pi_s \vDash \beta \text{)}$.\\ 
-\indent \indent Relabeling $s$ to $i$, we now have that $\forall i \in [a, b] \text{, (}\pi_s \vDash \beta \text{)}$, which implies line B1. \\
-\indent Case 2: Suppose $\exists s \in [a,b], \pi_s \cancel{\vDash} \beta$.\\
-\indent \indent By re-labeling $s$ to $i$, we have that $\exists i \in [a,b], \pi_i \cancel{\vDash} \beta$.\\
-\indent \indent Since $[a,b]$ is a finite-discrete interval, there must exist a first $i_1$ s.t. $\pi_{i_1} \cancel{\vDash} \beta$, that is:
-\[ 
-\exists i_1 \in [a,b]\text{, (}  \pi_{i_1} \cancel{\vDash} \beta  \text{ and }  \forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \beta \text{)}
+\indent Case 1: Suppose $\forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{)}$.\\ 
+\indent \indent Relabeling $s$ to $i$, we now have that $\forall i \in [a, b] \text{, (}\pi_s \vDash \psi \text{)}$, which implies line B1. \\
+\indent Case 2: Suppose $\exists s \in [a,b], \pi_s \cancel{\vDash} \psi$.\\
+\indent \indent By re-labeling $s$ to $i$, we have that $\exists i \in [a,b], \pi_i \cancel{\vDash} \psi$.\\
+\indent \indent Since $[a,b]$ is a finite-discrete interval, there must exist a first $i_1$ s.t. $\pi_{i_1} \cancel{\vDash} \psi$, that is:
+\[ 
+\exists i_1 \in [a,b]\text{, (}  \pi_{i_1} \cancel{\vDash} \psi  \text{ and }  \forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \psi \text{)}
 \tag{2}\]
-\indent \indent Since (line 2) $\exists i_1 \in [a,b], \pi_{i_1} \cancel{\vDash} \beta$, by Line 1 we have that: $\pi_{i_1} \vDash \beta \text{ or } \exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \alpha$.\\
+\indent \indent Since (line 2) $\exists i_1 \in [a,b], \pi_{i_1} \cancel{\vDash} \psi$, by Line 1 we have that: $\pi_{i_1} \vDash \psi \text{ or } \exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \phi$.\\
 \indent \indent Thus, we have that: 
 \[
-\exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \alpha \tag{3}
-\]
-\indent \indent Since  $[a, t] \subseteq [a, i_1 - 1]$ and $\forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \beta$, we have that:
-\[ 
-\forall k \in [a, t]\text{, } \pi_{k} \vDash \beta \tag{4}
+\exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \phi \tag{3}
+\]
+\indent \indent Since  $[a, t] \subseteq [a, i_1 - 1]$ and $\forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \psi$, we have that:
+\[ 
+\forall k \in [a, t]\text{, } \pi_{k} \vDash \psi \tag{4}
 \]
@@
 \[
-\exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{5}
+\exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{5}
 \]
@@
 \[ 
-|\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \beta \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \alpha \text{ and } \forall k \in [a, j] \ \pi_k \vDash \beta \text{)} \tag{B1}
+|\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \psi \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{B1}
 \]
@@
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula G[a:b]$\alpha$}
-Inputs: Vector of strings representing the regex for $\alpha$, interval bounds, number of propositional variables, simplify boolean\\
+\caption{Computes the regex for a MLTL formula G[a:b]$\phi$}
+Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
 Output: Vector of strings that represents the appropriate satisfying computations
@@
     \EndIf
-    \For{($1 \leq i \leq b-a$)} \Comment{computing $\bigwedge_{i=1}^{b-a} (S^n,)^i \text{reg}(\alpha)$}
+    \For{($1 \leq i \leq b-a$)} \Comment{computing $\bigwedge_{i=1}^{b-a} (S^n,)^i \text{reg}(\phi)$}
         \State temp\_alpha $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_alpha
@@
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula F[a:b]$\alpha$}
-Inputs: Vector of strings representing the regex for $\alpha$, interval bounds, number of propositional variables, simplify boolean\\
+\caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
+Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
 Output: Vector of strings that represents the appropriate satisfying computations 
@@
     \EndIf
-    \For{($1 \leq i \leq b-a$) } \Comment{computing $\bigvee_{i=1}^{b-a} (S^n,)^i \text{reg}(\alpha)$}
+    \For{($1 \leq i \leq b-a$) } \Comment{computing $\bigvee_{i=1}^{b-a} (S^n,)^i \text{reg}(\phi)$}
         \State temp\_alpha $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_alpha
@@
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\alpha$U[a:b]$\beta$} 
-Inputs: Vectors of strings representing the regexes for $\alpha$ and $\beta$, interval bounds, number of propositional variables, simplify boolean\\
+\caption{Computes the regex for a MLTL formula $\phi$U[a:b]$\psi$} 
+Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
 Output: Vector of strings that represents the appropriate satisfying computations 
@@
     \EndIf
-    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\alpha \land \mathcal{G}_{[i, i]} \beta\right)$, loop ends at $b-1$ because comp is initialized to $i=a$ case and loop is reindexed}}\\
+    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$, loop ends at $b-1$ because comp is initialized to $i=a$ case and loop is reindexed}}\\
         \State{\parbox[t]{.9\linewidth}{temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_alpha, $a$, $i$, $n$), reg\_G(reg\_beta, $i+1$, $i+1$, $n$), $n$, simp)}}
@@
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\alpha$R[a:b]$\beta$}
-Inputs: Vectors of strings representing the regexes for $\alpha$ and $\beta$, interval bounds, number of propositional variables, simplify boolean\\
+\caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
+Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
 Output: Vector of strings that represents the appropriate satisfying computations 
@@
     \State comp $\leftarrow$ reg\_G(reg\_beta, $a$, $b$, $n$, simp)
-    \Comment{\parbox[t]{.5\linewidth}{initializing vector of strings for output regex with regex for G[a:b]$\beta$}}
+    \Comment{\parbox[t]{.5\linewidth}{initializing vector of strings for output regex with regex for G[a:b]$\psi$}}
     \If{$a > b$}
@@
     \EndIf
-    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\text{reg}\left(\mathcal{G}_{[a,b]}\beta\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\beta \land \mathcal{G}_{[i, i]} \alpha\right)$, first run through loop includes $\text{reg}\left(\mathcal{G}_{[a,b]}\beta\right)$}}\\
+    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$, first run through loop includes $\text{reg}\left(\mathcal{G}_{[a,b]}\psi\right)$}}\\
         \State temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_beta, $a$, $i$, $n$), reg\_G(reg\_alpha, $i$, $i$, $n$), $n$, simp)
@@
         \State equiv\_formula $\leftarrow$ ``" 
-        \Comment For instance, $\&[\alpha_1, \alpha_2, \alpha_3]$ is rewritten to $((\alpha_1 \& \alpha_2) \& \alpha_3)$
+        \Comment For instance, $\&[\phi_1, \phi_2, \phi_3]$ is rewritten to $((\phi_1 \& \phi_2) \& \phi_3)$
         \For{(array entry alpha in nnf\_array)}
@@
         \Comment{\parbox[t]{.45\linewidth}{recursively generate all formulas of $1$ lower depth}}
-        \For{(string $\alpha \in V$)}
-            \State add ``G[a:b]" + $\alpha$ to template
-            \State add ``F[a:b]" + $\alpha$ to template
+        \For{(string $\phi \in V$)}
+            \State add ``G[a:b]" + $\phi$ to template
+            \State add ``F[a:b]" + $\phi$ to template
             \Comment Add unary temporal operators to template
-            \For{string $\beta \in V$}
-                \State add $\alpha$ + ``U[a:b]" + $\beta$ to template
-                \State add  $\alpha$ + ``R[a:b]" + $\beta$ to template
-                \State add $\alpha$ + ``$\lor$" + $\beta$ to template
-                \State add $\alpha$ + ``\&" + $\beta$ to template
+            \For{string $\psi \in V$}
+                \State add $\phi$ + ``U[a:b]" + $\psi$ to template
+                \State add  $\phi$ + ``R[a:b]" + $\psi$ to template
+                \State add $\phi$ + ``$\lor$" + $\psi$ to template
+                \State add $\phi$ + ``\&" + $\psi$ to template
                 \Comment add binary operators to template

### 2022-10-10 paper/Paper.tex
putting figures in section 5 side by side

--- 2022-10-10 paper/Paper.tex
@@
 \tikzset{>={Latex[width=2mm,length=2mm]}}
+\usepackage{caption}
 
@@
 Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.
-\subsubsection{Simulation 1}
-For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. Below are some examples of generated formulas:
-\begin{itemize}
-  \item $(p_4 \land p_0) \mathcal{U}_{[2,3]} (\neg p_1)$.
-  \item $(\mathcal{G}_{[3,5]} p_3) \mathcal{R}_{[7,8]} (p_3 \rightarrow p_0)$.
-  \item $\mathcal{F}_{[1,6]} (p_4 = p_3)$.
-\end{itemize}
-We obtain the following plots:
+
+\noindent\textbf{Simulation 1}
+For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. We obtain the following plots:
+% ZILI: Seems redundant since example formulas are listed below for the outliers
+% Some examples of generated formulas:
+% \begin{itemize}
+%   \item $(p_4 \land p_0) \mathcal{U}_{[2,3]} (\neg p_1)$.
+%   \item $(\mathcal{G}_{[3,5]} p_3) \mathcal{R}_{[7,8]} (p_3 \rightarrow p_0)$.
+%   \item $\mathcal{F}_{[1,6]} (p_4 = p_3)$.
+% \end{itemize}
+\begin{minipage}{0.5 \textwidth}
     \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{images/Sim1Length.png}
-    \caption{Input length in number of characters vs output length in number of characters for simulation 1.
+    \includegraphics[scale=0.39]{images/Sim1Length.png}
+    \captionof{figure}{Input length vs output length in number of characters}
+    \end{figure}
+    \newline
+\struct\end{minipage}%
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim1Time.png}
+    \captionof{figure}{Input length in number of characters vs run time in milliseconds.}
+    \end{figure}
+    \newline
+\struct\end{minipage}%
+\hfill\allowbreak%
+
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim1Length.png}
+%     \caption{Input length in number of characters vs output length in number of characters for simulation 1.
 Input length counts all characters, including parentheses, of the inputted formulas.
 Output length counts all the characters outputted, including commas.}
-\end{figure}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{images/Sim1Time.png}
-    \caption{Input length in number of characters vs run time in milliseconds for simulation 1. Input length counts all characters, including parentheses, of the inputted formulas.}
-\end{figure}
-\noindent The extreme outlier seen in the output length plot corresponds to the formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$.\\
-The three extreme outliers seen in the time plot correspond to the formulas 
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim1Time.png}
+%     \caption{Input length in number of characters vs run time in milliseconds for simulation 1. Input length counts all characters, including parentheses, of the inputted formulas.}
+% \end{figure}
+
+% \noindent The extreme outlier seen in the output length plot corresponds to the formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$.\\
+% The three extreme outliers seen in the time plot correspond to the following formulas:
+\noindent The formulas corresponding to the outliers are as follows:
+\vspace{-10mm}
 \begin{itemize}
-    \item $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ (same formula as the complexity outlier).
-    \item $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$.
-    \item $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$.
+    \item $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ (both graphs).
+    \item $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ (time).
+    \item $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ (time).
 \end{itemize}
-\subsubsection{Simulation 2}
+\noindent\textbf{Simulation 2}
 For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Below are some examples of generated formulas:

### 2022-10-10 paper/Paper.tex

--- 2022-10-10 paper/Paper.tex
@@
 \begin{itemize}
-    \item $R \land T = 11,1S | S1, S1$.
-    \item $R \lor T = S1,SS | 1S,1S | S1,S1 = S1,SS | 1S,1S$.
+    \item $R \land T = 11,1S \lor S1, S1$.
+    \item $R \lor T = S1,SS \lor 1S,1S \lor S1,S1 = S1,SS \lor 1S,1S$.
 \end{itemize}

### 2022-10-10 paper/Paper.tex
edits to sections 3.0, 3.1

--- 2022-10-10 paper/Paper.tex
@@
 \usepackage{amsmath} %hdots
+\usepackage{amssymb} %blacksquare
 \usepackage{mathabx} %vDash
@@
 \renewcommand\UrlFont{\color{blue}\rmfamily}
+
+%for qed:
+%% \makeatletter
+%% \newcommand{\pushright}[1]{\ifmeasuring@#1\else\omit\hfill$\displaystyle#1$\fi\ignorespaces}
+%% \newcommand{\pushleft}[1]{\ifmeasuring@#1\else\omit$\displaystyle#1$\hfill\fi\ignorespaces}
+%% \makeatother
+%% \makeatletter
+%% \newcommand{\specialcell}[1]{\ifmeasuring@#1\else\omit$\displaystyle#1$\ignorespaces\fi}
+%% \makeatother
 
@@
 {\bf Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
-The syntax of an MLTL formula over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
+The syntax of an MLTL formula $\phi$ over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
 \vspace{-0.1in}
-$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \phi \ | \ \phi \land \phi \ | \ \phi \lor \phi \ | \ \mathcal{F}_{[a,b]} \phi \ | \ \mathcal{G}_{[a,b]} \phi \ | \ \phi \mathcal{U}_{[a,b]} \phi \ | \ \phi \mathcal{R}_{[a,b]} \phi \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
+$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \psi \ | \ \psi_1 \land \psi_2 \ | \ \psi_1 \lor \psi_2 \ | \ \mathcal{F}_{[a,b]} \psi \ | \ \mathcal{G}_{[a,b]} \psi \ | \ \psi_1 \mathcal{U}_{[a,b]} \psi_2 \ | \ \psi_1 \mathcal{R}_{[a,b]} \psi_2 \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
 We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
@@
 \begin{itemize}
-  \item \emph{(Concatenation)} Denoted $RT$, describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
- \item \emph{(Alternation)} Denoted $R \lor T$, describes the set union of the strings generated by $R$ and $T$.
+  \item \emph{(Concatenation)} $RT$ describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
+ \item \emph{(Alternation)} $R \lor T$ describes the set union of the strings generated by $R$ and $T$.
     \item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
@@
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
-Since $T$ is the longer regex by one time step, we concatenate $,S^2$ to the right of $R$.
+Since $T$ is the longer regex by one time step, we concatenate ``$,S^2$'' to the right of $R$.
 Thus $T =1S,1S | S1,S1$ and $R = S1,SS$.
@@
  %These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\phi)$, which is defined recursively below:
-We define computation length $\text{cplen}(\phi)$ of an MLTL formula recursively:\\
+We define computation length $\text{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
           %\begin{align}
@@
 Intuitively, $\text{cplen}(\phi)$ is the minimum computation length required to ensure that none of the intervals in $\phi$ are out of bounds.
-Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature.
-In \cite{KZJZR20}, $$\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi), \text{cplen}(\psi))$$
-
-whereas our minimum computation length for Until and Release is 
-$$\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\mathbf{\text{cplen}(\phi)-1}, \text{cplen}(\psi)).$$
-We provide the proof for the minimum computation length of Until and Release below.
-\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]
+Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature. In \cite{KZJZR20},\\
+%\vspace{-0.1in}
+\indent $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi), \text{cplen}(\psi))$ \\ 
+%\vspace{-0.1in}
+\noindent whereas Theorem \ref{thm1} proves our minimum computation length for Until and Release, \\
+%\vspace{-0.1in}
+\indent $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\mathbf{\text{cplen}(\phi)-1}, \text{cplen}(\psi)).$
+%We provide the proof for the minimum computation length of Until and Release below.
+\vspace{-0.1in}
+\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]\label{thm1}
     Let $0 \leq a\leq b \in \mathbb{N}$ and let $\phi, \psi$ be well-formed MLTL formulas in NNF.
@@
 \end{theorem}
-
+\vspace{-0.2in}
 \begin{proof}
@@
  \end{align*}
+ \vspace{-0.1in}
  Now recall that $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$.
-Thus
+Thus%
+\vspace{-0.1in}
  \begin{align*}
@@
  \end{align*}
- This completes the proof.
+% This completes the proof.
  \end{proof}
-
+ \vspace{-0.25in} \hfill $\blacksquare$\\
  \noindent Intuitively, this optimization of the minimum computation length of Until and Release makes sense:

### 2022-10-10 paper/Paper.tex
removed some useless lines for displaying graphs side by side
finished section 3

@@
 We extend the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of an MLTL formula.
-\begin{definition}[\emph{Temporal Regular Expression}]
+\begin{definition}[\emph{Temporal Regular Expression}] \label{TRE} 
 Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$.
@@
 
-     \vspace{-0.1in}
-     \subsection{Minimum Computation Length}
-          \vspace{-0.1in}
+%     \vspace{-0.1in}
+%     \subsection{Minimum Computation Length}
+%          \vspace{-0.1in}
  %These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\phi)$, which is defined recursively below:
-We define computation length $\text{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
+\begin{definition}[\emph{Computation Length}]
+We define the computation length $\text{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
           %\begin{align}
@@
 %\end{align}
-
+\end{definition}
+\vspace{-0.1in}
 Intuitively, $\text{cplen}(\phi)$ is the minimum computation length required to ensure that none of the intervals in $\phi$ are out of bounds.
@@
  \vspace{-0.25in} \hfill $\blacksquare$\\
- \noindent Intuitively, this optimization of the minimum computation length of Until and Release makes sense:
+ \noindent Intuitively, we can reduce the minimum computation length of Until/Release because:
  \begin{itemize}
@@
 
-\subsection{Soundness and Completeness}
- We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
-
- \begin{theorem}[\emph{Soundness and Completeness}]
+% \vspace{-0.1in}
+% \subsection{Soundness and Completeness}
+%  \vspace{-0.1in}
+ We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$).
+That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
+The proof of Theorem \ref{SoundComplete} appears in Appendix \ref{Appendix-SoundComplete}.
+
+ \begin{theorem}[\emph{Soundness and Completeness}] \label{SoundComplete}
  For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
  \end{theorem}
- \begin{proof}
- We proceed by induction on the length of the formula.\\
-
- \noindent \textbf{Base Cases.}\\
- \noindent\textbf{reg($\top$)}\\
- Any computation $\pi$ satisfies $\top$, and $\mathscr{L}(\text{reg}(\top))$ is the set of all computations of one time step.
+
+%KYR: this totally goes here in the journal version but in an appendix/on a website for the conference version
+%%  \begin{proof}
+%%  We proceed by induction on the length of the formula.\\
+
+%%  \noindent \textbf{Base Cases.}\\
+%%  \noindent\textbf{reg($\top$)}\\
+%%  Any computation $\pi$ satisfies $\top$, and $\mathscr{L}(\text{reg}(\top))$ is the set of all computations of one time step.
 Padding conventions extends this to the set of all computations of any positive number of time steps, so we are done.\\
 
- \noindent\textbf{reg($\bot$)}\\
- There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\
-
- \noindent\textbf{reg($p_k$)}\\
- For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
- $$S^{k} 1 S^{n-k-1}$$
- which is precisely reg($p_k$).\\
-
- \noindent\textbf{reg($\neg p_k$)}\\
- If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
- $$S^{k} 0 S^{n-k-1}$$
- which is precisely reg($\neg p_k$).\\
-
- \noindent\textbf{Inductive Step.}\\
- Suppose the theorem holds for MLTL formulas $\varphi$ and $\psi$.
+%%  \noindent\textbf{reg($\bot$)}\\
+%%  There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\
+
+%%  \noindent\textbf{reg($p_k$)}\\
+%%  For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
+%%  $$S^{k} 1 S^{n-k-1}$$
+%%  which is precisely reg($p_k$).\\
+
+%%  \noindent\textbf{reg($\neg p_k$)}\\
+%%  If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
+%%  $$S^{k} 0 S^{n-k-1}$$
+%%  which is precisely reg($\neg p_k$).\\
+
+%%  \noindent\textbf{Inductive Step.}\\
+%%  Suppose the theorem holds for MLTL formulas $\varphi$ and $\psi$.
 We now show that it holds for $\varphi \land \psi$, $\varphi \lor \psi$, $\mathcal{F}_{[a,b]} \varphi$, $\mathcal{G}_{[a,b]} \varphi$, $\varphi \ \mathcal{U}_{[a,b]} \psi$, and $\varphi \mathcal{R}_{[a,b]} \psi$.\\
 
- \noindent \textbf{reg($\varphi \land \psi$)}\\
- We know that $\pi \vDash \varphi \land \psi \text{ iff } \pi \vDash \varphi \text{ and } \pi \vDash \psi$.\\
- By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
- \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
- $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$
-
- \noindent \textbf{reg($\varphi \lor \psi$)}\\
- We know that $\pi \vDash \varphi \lor \psi \text{ iff } \pi \vDash \varphi \text{ or } \pi \vDash \psi$.\\
- By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
- \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
- $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$
-
- \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
- We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
- If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
+%%  \noindent \textbf{reg($\varphi \land \psi$)}\\
+%%  We know that $\pi \vDash \varphi \land \psi \text{ iff } \pi \vDash \varphi \text{ and } \pi \vDash \psi$.\\
+%%  By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
+%%  \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
+%%  $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$
+
+%%  \noindent \textbf{reg($\varphi \lor \psi$)}\\
+%%  We know that $\pi \vDash \varphi \lor \psi \text{ iff } \pi \vDash \varphi \text{ or } \pi \vDash \psi$.\\
+%%  By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
+%%  \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
+%%  $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$
+
+%%  \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
+%%  We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
+%%  If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
 Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
- By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
- $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
-
- \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
- We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
- Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
- By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
- $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
-
- \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
-  We have that 
-  $$\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } (\pi_i \vDash \psi \text{ and } \forall a \leq j < i, \pi_j \vDash \varphi).$$
-  As argued in the Finally case, the length condition is satisfied.\\
-  By the inductive hypothesis, $\pi_i \vDash \psi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\psi))$, or equivalently, \\
-  $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[i,i]} \psi))$. Also, $\pi_j \vDash \varphi$ if and only if $\pi_j \in \mathscr{L}(\text{reg}(\varphi))$.\\
-  By the argument used in the Global case, we see that $\forall a \leq j < i, \ \pi_j \vDash \varphi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a, i-1]} \varphi))$.\\
-  Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently,
-  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
-
-  \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
-  We have that
-  \begin{align*}
-    &\pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or } \\ 
-    &\exists j\in[a,b] \text{ such that }
-    (\pi_j \vDash \varphi \text{ and } \forall a\leq k \leq j, \pi_k \vDash \psi).
-  \end{align*}
-  As argued in the Global case, the first option for satisfying the formula never occurs.\\
-  By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case.
+%%  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
+%%  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
+
+%%  \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
+%%  We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
+%%  Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
+%%  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
+%%  $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
+
+%%  \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
+%%   We have that 
+%%   $$\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } (\pi_i \vDash \psi \text{ and } \forall a \leq j < i, \pi_j \vDash \varphi).$$
+%%   As argued in the Finally case, the length condition is satisfied.\\
+%%   By the inductive hypothesis, $\pi_i \vDash \psi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\psi))$, or equivalently, \\
+%%   $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[i,i]} \psi))$. Also, $\pi_j \vDash \varphi$ if and only if $\pi_j \in \mathscr{L}(\text{reg}(\varphi))$.\\
+%%   By the argument used in the Global case, we see that $\forall a \leq j < i, \ \pi_j \vDash \varphi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a, i-1]} \varphi))$.\\
+%%   Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently,
+%%   $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
+
+%%   \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
+%%   We have that
+%%   \begin{align*}
+%%     &\pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or } \\ 
+%%     &\exists j\in[a,b] \text{ such that }
+%%     (\pi_j \vDash \varphi \text{ and } \forall a\leq k \leq j, \pi_k \vDash \psi).
+%%   \end{align*}
+%%   As argued in the Global case, the first option for satisfying the formula never occurs.\\
+%%   By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case.
 the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)$.
@@
 
-  \begin{align*}
-    \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right) \\
-    &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)\\
-    &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
-  \end{align*}
-
- \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
- \end{proof}
- \newpage
-\subsection{Nested Until and Release Rewriting Theorem}
- We prove the following theorem using the regular expressions above.
-As detailed in section \ref{complex}, nested binary temporal operators create the worst case time and space complexity for the WEST program.
-Although the WEST program does not implement this theorem, we would expect an implementation of this theorem to improve runtime.
-On its own, this theorem can be used to simplify MLTL formulas, making them easier to interpret.
-
-\begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}]  Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas.
+%%   \begin{align*}
+%%     \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right) \\
+%%     &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)\\
+%%     &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
+%%   \end{align*}
+
+%%  \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
+%%  \end{proof}
+% \newpage
+%\vspace{-0,1in}
+%\subsection{Nested Until and Release Rewriting Theorem}
+%\vspace{-0,1in}
+ We prove the correctness of our formula rewriting algorithm using our regular expressions from Definition \ref{TRE}.
+As detailed in Section \ref{complex}, nested binary temporal operators create the worst-case time and space complexity for the WEST program.
+Although the WEST program does not implement this theorem by default, we would expect selected applications of rewriting to improve runtime.
+We use this theorem to simplify MLTL formulas, making them easier to interpret.
+Theorem \ref{NestedUR}'s proof appears in Appendix \ref{Appendix-NestedUR}.
+
+ \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}] \label{NestedUR}
+   Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas.
 Let $\mathcal{B} = \mathcal{R} \text{ or } \mathcal{U}$.
@@
 \end{theorem}
-\begin{proof}
-
-\textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\
-
-\noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
+%The proof of Theorem \ref{NestedUR} appears in Appendix \ref{Appendix-NestedUR}.
+
+%KYR: this totally goes here in the journal version but in an appendix/on a website for the conference version
+
+%% \begin{proof}
+
+%% \textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\
+
+%% \noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
 Then, $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
 
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right).
-\end{align*}
-$\mathcal{G}_{[i, i]}$ distributes over $\land$ and $\lor$, so
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right) \\
-&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
-\mathcal{G}_{[j, j]}\psi \right) \right) \right).
-\end{align*}
-Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right) \right) \right) \\
-&= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right).
-\end{align*}
-Since $\mathcal{G}_{[t_1,t_2-1]}\phi \land \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1,t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right)\\
-&= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right).
-\end{align*}
-Finally, let $k = i + j$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\psi  \right) \\
-&= \text{reg}\left(\phi \ \mathcal{U}_{[a,b+c]} \psi\right).
-\end{align*}
-This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
-
-\noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
-We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,  \\
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \text{reg}\left(\neg\left(\neg\phi \ \mathcal{U}_{[a,b]}\neg\psi\right)\right) \\
-&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\phi \land \mathcal{G}_{[i, i]}\neg\psi\right)\right).
-\end{align*}
-Global is the dual of Finally, so
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\phi \land \neg\mathcal{F}_{[i, i]}\psi\right)\right)\\
-&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\right)\\
-&= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right).
-\end{align*}
-This completes the rewriting of the regex for Release.
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
+%% &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right).
+%% \end{align*}
+%% $\mathcal{G}_{[i, i]}$ distributes over $\land$ and $\lor$, so
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right) \\
+%% &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
+%% \mathcal{G}_{[j, j]}\psi \right) \right) \right).
+%% \end{align*}
+%% Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \phi$, we have
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right) \right) \right) \\
+%% &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right).
+%% \end{align*}
+%% Since $\mathcal{G}_{[t_1,t_2-1]}\phi \land \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1,t_3]} \phi$, we have
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right)\\
+%% &= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right).
+%% \end{align*}
+%% Finally, let $k = i + j$. Thus
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\psi  \right) \\
+%% &= \text{reg}\left(\phi \ \mathcal{U}_{[a,b+c]} \psi\right).
+%% \end{align*}
+%% This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
+
+%% \noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
+%% We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,  \\
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \text{reg}\left(\neg\left(\neg\phi \ \mathcal{U}_{[a,b]}\neg\psi\right)\right) \\
+%% &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\phi \land \mathcal{G}_{[i, i]}\neg\psi\right)\right).
+%% \end{align*}
+%% Global is the dual of Finally, so
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\phi \land \neg\mathcal{F}_{[i, i]}\psi\right)\right)\\
+%% &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\right)\\
+%% &= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\\
+%% &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right).
+%% \end{align*}
+%% This completes the rewriting of the regex for Release.
 Now let $\gamma = \phi \ \mathcal{R}_{[0,c]} \psi$.
 Then $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) = \phi \ \mathcal{R}_{[a,b]}\gamma$ and
-$\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi \lor \mathcal{F}_{[j, j]}\psi\right)$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right).
-\end{align*}
-$\mathcal{F}_{[i, i]} \equiv \mathcal{G}_{[i, i]}$, so this operation distributes over $\land$ and $\lor$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right) \\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\psi \right) \right) \right).
-\end{align*}
-Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right) \right) \right) \\
-&= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right).
-\end{align*}
-Since $\mathcal{F}_{[t_1,t_2-1]} \phi \land \mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1, t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right) \\
-&= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right).
-\end{align*}
-Let $k = i + j$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\psi  \right) \\
-&= \text{reg}\left(\phi \ \mathcal{R}_{[a,b+c]} \psi\right).
-\end{align*}
-Thus  $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) \equiv \phi \ \mathcal{R}_{[a,b+c]} \psi$, so $\phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
+%% $\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi \lor \mathcal{F}_{[j, j]}\psi\right)$. Thus
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
+%% &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right).
+%% \end{align*}
+%% $\mathcal{F}_{[i, i]} \equiv \mathcal{G}_{[i, i]}$, so this operation distributes over $\land$ and $\lor$. Thus
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right) \\
+%% &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\psi \right) \right) \right).
+%% \end{align*}
+%% Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \phi$, we have
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right) \right) \right) \\
+%% &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right).
+%% \end{align*}
+%% Since $\mathcal{F}_{[t_1,t_2-1]} \phi \land \mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1, t_3]} \phi$, we have
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right) \\
+%% &= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right).
+%% \end{align*}
+%% Let $k = i + j$. Thus
+%% \begin{align*}
+%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\psi  \right) \\
+%% &= \text{reg}\left(\phi \ \mathcal{R}_{[a,b+c]} \psi\right).
+%% \end{align*}
+%% Thus  $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) \equiv \phi \ \mathcal{R}_{[a,b+c]} \psi$, so $\phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
 This completes the proof.
-\end{proof}
+%% \end{proof}
 
@@
 % \end{itemize}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim1Length.png}
-    \captionof{figure}{Input length vs output length in number of characters}
-    \end{figure}
-    \newline
-\struct\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim1Time.png}
-    \captionof{figure}{Input length in number of characters vs run time in milliseconds.}
-    \end{figure}
-    \newline
-\struct\end{minipage}%
-\hfill\allowbreak%
+%% \begin{minipage}{0.5 \textwidth}
+%%     \begin{figure}[H]
+%%     \centering
+%%     \includegraphics[scale=0.39]{images/Sim1Length.png}
+%%     \captionof{figure}{Input length vs output length in number of characters}
+%%     \end{figure}
+%%     \newline
+%% \struct\end{minipage}%
+%% \begin{minipage}{0.5 \textwidth}
+%%     \begin{figure}[H]
+%%     \centering
+%%     \includegraphics[scale=0.39]{images/Sim1Time.png}
+%%     \captionof{figure}{Input length in number of characters vs run time in milliseconds.}
+%%     \end{figure}
+%%     \newline
+%% \struct\end{minipage}%
+%% \hfill\allowbreak%
 
@@
 \renewcommand{\thesection}{\Roman{section}}
-Content in the appendix will appear online, on the paper's website, but appears here for now due to blind review.
+Content in the appendices will appear online, on the paper's website, but appears here for now due to blind review.
+
+ \subsection{Soundness and Completeness} \label{Appendix-SoundComplete}
+%  \vspace{-0.1in}
+ We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
+
+ %KYR: TODO: label this theorem 2!!!!!!!!!!!!!!!!!!!!!!
+ \begin{theorem}[\emph{Soundness and Completeness}]
+ For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
+ \end{theorem}
+ \begin{proof}
+ We proceed by induction on the length of the formula.\\
+
+ \noindent \textbf{Base Cases.}\\
+ \noindent\textbf{reg($\top$)}\\
+ Any computation $\pi$ satisfies $\top$, and $\mathscr{L}(\text{reg}(\top))$ is the set of all computations of one time step.
+Padding conventions extends this to the set of all computations of any positive number of time steps, so we are done.\\
+
+ \noindent\textbf{reg($\bot$)}\\
+ There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\
+
+ \noindent\textbf{reg($p_k$)}\\
+ For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
+ $$S^{k} 1 S^{n-k-1}$$
+ which is precisely reg($p_k$).\\
+
+ \noindent\textbf{reg($\neg p_k$)}\\
+ If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
+ $$S^{k} 0 S^{n-k-1}$$
+ which is precisely reg($\neg p_k$).\\
+
+ \noindent\textbf{Inductive Step.}\\
+ Suppose the theorem holds for MLTL formulas $\varphi$ and $\psi$.
+We now show that it holds for $\varphi \land \psi$, $\varphi \lor \psi$, $\mathcal{F}_{[a,b]} \varphi$, $\mathcal{G}_{[a,b]} \varphi$, $\varphi \ \mathcal{U}_{[a,b]} \psi$, and $\varphi \mathcal{R}_{[a,b]} \psi$.\\
+
+ \noindent \textbf{reg($\varphi \land \psi$)}\\
+ We know that $\pi \vDash \varphi \land \psi \text{ iff } \pi \vDash \varphi \text{ and } \pi \vDash \psi$.\\
+ By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
+ \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
+ $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$
+
+ \noindent \textbf{reg($\varphi \lor \psi$)}\\
+ We know that $\pi \vDash \varphi \lor \psi \text{ iff } \pi \vDash \varphi \text{ or } \pi \vDash \psi$.\\
+ By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
+ \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
+ $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$
+
+ \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
+ We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
+ If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
+Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
+ By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
+ $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
+
+ \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
+ We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
+ Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
+ By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
+ $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
+
+ \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
+  We have that 
+  $$\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } (\pi_i \vDash \psi \text{ and } \forall a \leq j < i, \pi_j \vDash \varphi).$$
+  As argued in the Finally case, the length condition is satisfied.\\
+  By the inductive hypothesis, $\pi_i \vDash \psi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\psi))$, or equivalently, \\
+  $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[i,i]} \psi))$. Also, $\pi_j \vDash \varphi$ if and only if $\pi_j \in \mathscr{L}(\text{reg}(\varphi))$.\\
+  By the argument used in the Global case, we see that $\forall a \leq j < i, \ \pi_j \vDash \varphi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a, i-1]} \varphi))$.\\
+  Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently,
+  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
+
+  \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
+  We have that
+  \begin{align*}
+    &\pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or } \\ 
+    &\exists j\in[a,b] \text{ such that }
+    (\pi_j \vDash \varphi \text{ and } \forall a\leq k \leq j, \pi_k \vDash \psi).
+  \end{align*}
+  As argued in the Global case, the first option for satisfying the formula never occurs.\\
+  By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case.
+the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)$.
+Hence
+
+  \begin{align*}
+    \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right) \\
+    &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)\\
+    &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
+  \end{align*}
+
+ \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
+ \end{proof}
+% \newpage
+
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Nested Until and Release Rewriting Theorem} \label{Appendix-NestedUR}
+
+ \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}] \label{NestedUR}
+   Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas.
+Let $\mathcal{B} = \mathcal{R} \text{ or } \mathcal{U}$.
+Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \phi,   \psi$ \text{be well-formed MLTL formulas in NNF.
+Then,} $ \phi \ \mathcal{B}_{[a,b+c]} \psi = \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
+That is, $ \phi \ \mathcal{U}_{[a,b+c]} \psi \equiv \phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi)$ and $ \phi \ \mathcal{R}_{[a,b+c]} \psi \equiv \phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi)$.
+\end{theorem}
+The proof of Theorem \ref{NestedUR} appears below.
+
+%KYR: this totally goes here in the journal version but in an appendix/on a website for the conference version
+
+\begin{proof}
+
+\textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\
+
+\noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
+Then, $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
+
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
+&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right).
+\end{align*}
+$\mathcal{G}_{[i, i]}$ distributes over $\land$ and $\lor$, so
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right) \\
+&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
+\mathcal{G}_{[j, j]}\psi \right) \right) \right).
+\end{align*}
+Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right) \right) \right) \\
+&= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right).
+\end{align*}
+Since $\mathcal{G}_{[t_1,t_2-1]}\phi \land \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1,t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right)\\
+&= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right).
+\end{align*}
+Finally, let $k = i + j$. Thus
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\psi  \right) \\
+&= \text{reg}\left(\phi \ \mathcal{U}_{[a,b+c]} \psi\right).
+\end{align*}
+This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
+
+\noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
+We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,  \\
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \text{reg}\left(\neg\left(\neg\phi \ \mathcal{U}_{[a,b]}\neg\psi\right)\right) \\
+&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\phi \land \mathcal{G}_{[i, i]}\neg\psi\right)\right).
+\end{align*}
+Global is the dual of Finally, so
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\phi \land \neg\mathcal{F}_{[i, i]}\psi\right)\right)\\
+&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\right)\\
+&= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\\
+&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right).
+\end{align*}
+This completes the rewriting of the regex for Release.
+Now let $\gamma = \phi \ \mathcal{R}_{[0,c]} \psi$.
+Then $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) = \phi \ \mathcal{R}_{[a,b]}\gamma$ and
+$\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi \lor \mathcal{F}_{[j, j]}\psi\right)$. Thus
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
+&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right).
+\end{align*}
+$\mathcal{F}_{[i, i]} \equiv \mathcal{G}_{[i, i]}$, so this operation distributes over $\land$ and $\lor$. Thus
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right) \\
+&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\psi \right) \right) \right).
+\end{align*}
+Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right) \right) \right) \\
+&= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right).
+\end{align*}
+Since $\mathcal{F}_{[t_1,t_2-1]} \phi \land \mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1, t_3]} \phi$, we have
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right) \\
+&= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right).
+\end{align*}
+Let $k = i + j$. Thus
+\begin{align*}
+\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\psi  \right) \\
+&= \text{reg}\left(\phi \ \mathcal{R}_{[a,b+c]} \psi\right).
+\end{align*}
+Thus  $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) \equiv \phi \ \mathcal{R}_{[a,b+c]} \psi$, so $\phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
+This completes the proof.
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2022-10-11 paper/Paper.tex
All figures in section 5 have been formatted side by side

--- 2022-10-10 paper/Paper.tex
@@
 Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.
-
+\\
+\\
 \noindent\textbf{Simulation 1}
@@
     \includegraphics[scale=0.39]{images/Sim1Length.png}
-    \captionof{figure}{Input length vs output length in number of characters}
+    \captionof{figure}{Input length vs output length.}
     \end{figure}
-    \newline
-\struct\end{minipage}%
+\end{minipage}%
 \begin{minipage}{0.5 \textwidth}
@@
     \includegraphics[scale=0.39]{images/Sim1Time.png}
-    \captionof{figure}{Input length in number of characters vs run time in milliseconds.}
+    \captionof{figure}{Input length vs run time.}
     \end{figure}
-    \newline
-\struct\end{minipage}%
-\hfill\allowbreak%
-
+\end{minipage}%
+
+% ZILI: I've reduced the length of the caption discription, otherwise the two captions display extremely close side by side
 % \begin{figure}[H]
@@
 
+\vspace{2mm}
+\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both figures, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for figure 2.
+
+% ZILI: Chose not to use itemize due to formatting difficulties with vertical spacing.
 % \noindent The extreme outlier seen in the output length plot corresponds to the formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$.\\
 % The three extreme outliers seen in the time plot correspond to the following formulas:
-\noindent The formulas corresponding to the outliers are as follows:
-\vspace{-10mm}
-\begin{itemize}
-    \item $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ (both graphs).
-    \item $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ (time).
-    \item $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ (time).
-\end{itemize}
+% \begin{itemize}
+%     \item $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ (both graphs).
+%     \item $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ (time).
+%     \item $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ (time).
+% \end{itemize}
+
+\vspace{\baselineskip}
 \noindent\textbf{Simulation 2}
-For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Below are some examples of generated formulas:
-\begin{itemize}
-    \item $\mathcal{F}_{[10,17]} p_4$.
-    \item $\neg p_6$.
-    \item $p_6 \mathcal{U}_{[6,14]} p_8$.
-\end{itemize}
-We obtain the following plots:
+For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Here are some examples of generated formulas:
+$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain the following plots:
+
+% ZILI: removed itemize due to vertical spacing issues.
+% \begin{itemize}
+%     \item $\mathcal{F}_{[10,17]} p_4$.
+%     \item $\neg p_6$.
+%     \item $p_6 \mathcal{U}_{[6,14]} p_8$.
+% \end{itemize}
+
+\vspace{-4mm}
+\begin{minipage}{0.5 \textwidth}
     \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{images/Sim2Length.png}
-    \caption{Input length in number of characters vs output length in number of characters for simulation 2.
+    \includegraphics[scale=0.39]{images/Sim2Length.png}
+    \captionof{figure}{Input length vs output length}
+    \end{figure}
+\end{minipage}%
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim2Time.png}
+    \captionof{figure}{Input length vs run time.}
+    \end{figure}
+\end{minipage}%
+% ZILI: Old graph formatting and captions
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim2Length.png}
+%     \caption{Input length in number of characters vs output length in number of characters for simulation 2.
 Input length counts all characters, including parentheses, of the inputted formulas.
 Output length counts all the characters outputted, including commas.}
-\end{figure}
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim2Time.png}
+%     \caption{Input length in number of characters vs run time in milliseconds for simulation 2. Input length counts all characters, including parentheses, of the inputted formulas.}
+% \end{figure}
+
+\subsubsection{Simulation 3}
+For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. 
+% Below are some examples of generated formulas:
+% \begin{itemize}
+%     \item $(p_5 \land p_0) = (p_8 \mathcal{U}_{[3,6]} p_8)$.
+%     \item $(\mathcal{G}_{[6,7]} p_4) \land (\mathcal{F}_{[5,7]} p_1)$.
+%     \item $\neg (p_0 \mathcal{U}_{[2,5]} p_7)$.
+% \end{itemize}
+We obtain the following plots:
+
+\begin{minipage}{0.5 \textwidth}
     \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{images/Sim2Time.png}
-    \caption{Input length in number of characters vs run time in milliseconds for simulation 2. Input length counts all characters, including parentheses, of the inputted formulas.}
+    \includegraphics[scale=0.39]{images/Sim3Length.png}
+    \captionof{figure}{Input length vs output length}
     \end{figure}
-\subsubsection{Simulation 3}
-For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. Below are some examples of generated formulas:
-\begin{itemize}
-    \item $(p_5 \land p_0) = (p_8 \mathcal{U}_{[3,6]} p_8)$.
-    \item $(\mathcal{G}_{[6,7]} p_4) \land (\mathcal{F}_{[5,7]} p_1)$.
-    \item $\neg (p_0 \mathcal{U}_{[2,5]} p_7)$.
-\end{itemize}
-We obtain the following plots:
+\end{minipage}%
+\begin{minipage}{0.5 \textwidth}
     \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{images/Sim3Length.png}
-    \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
+    \includegraphics[scale=0.39]{images/Sim3Time.png}
+    \captionof{figure}{Input length vs run time.}
     \end{figure}
+\end{minipage}%
+% ZILI: Old graph formatting and captions
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim3Length.png}
+%     \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim3Time.png}
+%     \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
+% \end{figure}
+\vspace{\baselineskip}
+The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both figures, and figure 5 had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
+% The three outliers in the output length plot are the formulas 
+% \begin{itemize}
+%     \item $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$.
+%     \item $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$.
+%     \item $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
+% \end{itemize}
+% The former two are also the time complexity outliers.
+\\
+\\
+\noindent\textbf{Simulation 4}
+For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. Some examples of generated formulas are: 
+$\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
+% \begin{itemize}
+%     \item $\neg p_1$.
+%     \item $p_1 \mathcal{R}_{[6,7]} p_3$.
+%     \item $\mathcal{F}_{[5,5]} p_3$.
+% \end{itemize}
+We obtain the following plots:
+
+\begin{minipage}{0.5 \textwidth}
     \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{images/Sim3Time.png}
-    \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
+    \includegraphics[scale=0.39]{images/Sim4Length.png}
+    \captionof{figure}{Input length vs output length}
     \end{figure}
-The three outliers in the output length plot are the formulas 
-\begin{itemize}
-    \item $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$.
-    \item $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$.
-    \item $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
-\end{itemize}
-The former two are also the time complexity outliers.
-\subsubsection{Simulation 4}
-For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. Below are some examples of generated formulas:
-\begin{itemize}
-    \item $\neg p_1$.
-    \item $p_1 \mathcal{R}_{[6,7]} p_3$.
-    \item $\mathcal{F}_{[5,5]} p_3$.
-\end{itemize}
-We obtain the following plots:
+\end{minipage}%
+\begin{minipage}{0.5 \textwidth}
     \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.75]{images/Sim4Length.png}
-    \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
+    \includegraphics[scale=0.39]{images/Sim4Time.png}
+    \captionof{figure}{Input length vs run time.}
     \end{figure}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.75]{images/Sim4Time.png}
-    \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
-\end{figure}
+\end{minipage}%
+
+% ZILI: Old figures
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim4Length.png}
+%     \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
+% \end{figure}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.75]{images/Sim4Time.png}
+%     \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
+% \end{figure}
+\vspace{\baselineskip}
 \noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively sparse.

### 2022-10-11 paper/Paper.tex

--- 2022-10-10 paper/Paper.tex
@@
 % \end{itemize}
-%% \begin{minipage}{0.5 \textwidth}
-%%     \begin{figure}[H]
-%%     \centering
-%%     \includegraphics[scale=0.39]{images/Sim1Length.png}
-%%     \captionof{figure}{Input length vs output length in number of characters}
-%%     \end{figure}
-%%     \newline
-%% \struct\end{minipage}%
-%% \begin{minipage}{0.5 \textwidth}
-%%     \begin{figure}[H]
-%%     \centering
-%%     \includegraphics[scale=0.39]{images/Sim1Time.png}
-%%     \captionof{figure}{Input length in number of characters vs run time in milliseconds.}
-%%     \end{figure}
-%%     \newline
-%% \struct\end{minipage}%
-%% \hfill\allowbreak%
-
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim1Length.png}
+    \captionof{figure}{Input length vs output length.}
+    \end{figure}
+\end{minipage}%
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim1Time.png}
+    \captionof{figure}{Input length vs run time.}
+    \end{figure}
+\end{minipage}%
+
+% ZILI: I've reduced the length of the caption discription, otherwise the two captions display extremely close side by side
 % \begin{figure}[H]

### 2022-10-11 paper/Paper.tex
updates through section 4

@@
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \vspace{-0.1in}
  \section{WEST Code Specifications} \label{specs}
+  \vspace{-0.1in}
 The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
-{Github} repository.
+{GitHub} repository.
 The MLTL syntax for our program is given as the context free grammar below.
@@
 \begin{align*}
-    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `>' ,}\\
+    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `\mbox{$>$}' ,}\\
     &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
@@
 For two propositional variables, the associative equivalence operator functions identically to the binary propositional connective equivalence operator.
-For formulas with 3 or more propositional variables, however , the associative equivalence operator does not mean that each propositional variable in the list is equivalent.
+For formulas with 3 or more propositional variables, however, the associative equivalence operator does not mean that each propositional variable in the list is equivalent.
 Instead, it means that the equivalence of the first two propositional variables in the list is equivalent to the next propositional variable in the list, and the truth value for this expression is equivalent to the next propositional variable, and so on.
-For example, =[p1,p2,p3] is equivalent to (p1=p2)=p3 rather than p1=p2=p3.
+For example, $=[p1,p2,p3]$ is equivalent to $(p1=p2)=p3$ rather than $p1=p2=p3$.
 \end{remark}
@@
 In Appendix \ref{pseudocode appendix}, we provide the full pseudocode of the WEST program.
-Below we summarize only the important points to provide analysis of time and space complexity in the next section.
+We summarize the important points to provide analysis of time and space complexity.
 The regular expression $R = \{R_1 | R_2 | ...
@@
 
-If the user would like to see the satisfying computations for all the subformulas in their original formula, \textit{reg} contains a boolean to enable this functionality.
+If the user would like to see the satisfying computations for all the subformulas in their original formula, \textit{reg} contains a Boolean to enable this functionality.
 

### 2022-10-11 paper/Paper.tex
added image files and modified figure 9

@@
     \centering
-    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, star/.style={circle, draw=red!60, fill=red!5, very thick, minimum size=1mm}]
+    \begin{tikzpicture}[ node/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=10mm},
+    bignode/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=12mm},
+    star/.style={circle, draw=red!60, fill=red!5, thick, minimum size=1mm} ]
 
     %Nodes
-    \node[bignode](reg){\textbf{Reg}};
-    \node[node](prop_var)[left=2 cm of reg]{Prop\_Var};
-    \node[node](prop_cons)[below=of prop_var]{Prop\_Cons};
-    \node[star](unary_star)[below=2 cm of reg]{};
-    \node[node](reg_f)[below=of unary_star]{Reg\_F};
-    \node[node](reg_g)[left= of reg_f]{Reg\_G};
-    \node[star](temp_binary_star1)[right=2 cm of unary_star]{};
-    \node[star](temp_binary_star2)[below= of temp_binary_star1]{};
-    \node[node](reg_u)[below=of temp_binary_star2]{Reg\_U};
-    \node[node](reg_r)[right=of reg_u]{Reg\_R};
+    \node[bignode] (reg) {\textbf{Reg}};
     \node[star](prop_binary_star1)[right= of reg]{};
@@
     \node[node](join)[right=of prop_binary_star2]{Join};
-    \node[node](set_intersect)[below=of join]{Set\_Intersect};
+    \node[node](set_intersect)[below=0.5 cm of join]{Set\_Intersect};
+    \node[node] (prop_var) [left=of reg] {Prop\_Var};
+    \node[node] (prop_cons) [below=0.5 cm of prop_var] {Prop\_Cons};
+    \node[star](unary_star)[below=0.9 cm of reg]{};
+    \node[node](reg_f)[below=0.7 cm of unary_star]{Reg\_F};
+    \node[node](reg_g)[left= of reg_f]{Reg\_G};
+    \node[star](temp_binary_star1)[below=0.5 cm of prop_binary_star1]{};
+    \node[star](temp_binary_star2)[below=0.5 cm of temp_binary_star1]{};
+    \node[node](reg_u)[below=0.7 cm of temp_binary_star2]{Reg\_U};
+    \node[node](reg_r)[right=of reg_u]{Reg\_R};
 
     %Lines
-    \draw[->] (reg.west) -- (prop_var.east);
-    \draw[->] (reg.south) -- (prop_cons.north);
-    \draw[->] (reg.south) -- (unary_star.north);
+    \draw[->] (reg.west) -- (prop_var);
+    \draw[->] (reg.south) -- (prop_cons);
+    \draw[->] (reg.south) -- (unary_star);
     \draw[->] (unary_star.south) -- (reg_f.north);
-    \draw[->] (unary_star.south) -- (reg_g.north);
-    \draw[->] (reg.south) -- (temp_binary_star1.north);
+    \draw[->] (unary_star.south) -- (reg_g);
+    \draw[->] (reg.south) -- (temp_binary_star1);
     \draw[->] (reg.east) -- (prop_binary_star1.west);
     \draw[->] (temp_binary_star1.south) -- (temp_binary_star2.north);
-    \draw[->] (temp_binary_star2.south) -- (reg_r.north);
+    \draw[->] (temp_binary_star2.south) -- (reg_r);
     \draw[->] (temp_binary_star2.south) -- (reg_u.north);
@@
     \draw[->] (prop_binary_star2.east) -- (join.west);
-    \draw[->] (prop_binary_star2.south) -- (set_intersect.north);
+    \draw[->] (prop_binary_star2.south) -- (set_intersect);
     \end{tikzpicture}

### 2022-10-11 paper/Paper.tex
squished example of regex simp theorem
initial draft of WEST algorithm in section 4

@@
 \usepackage{caption}
-
+\usepackage{mwe}
 %% \hypersetup{
@@
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{WEST Algorithm and Analysis} \label{WESTalg}
+We now present the  full WEST algorithm, which takes MLTL formula $\phi$ (in NNF) and number of propositional variables $n$, and recursively computes all satisfying temporal regular expressions to $\phi$.
+We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$.
+
+    \begin{algorithm}[H]
+    \caption{WEST Algorithm}
+\begin{algorithmic}[1]
+    \Procedure{reg}{string $\phi$, int $n$}
+        \If{$\alpha$ is $\top$ or $\bot$}
+            \State return reg\_prop\_const($\alpha$, n)
+        \EndIf
+
+        \If{$\alpha$ is $p_k$ or $\neg p_k$}
+            \State return reg\_prop\_var($\alpha$, n)
+        \EndIf
+
+        \If{$\alpha  = \alpha_1 \land \alpha_2$}
+            \State return set\_intersect(reg($\alpha_1$), reg($\alpha_2$), n)
+        \EndIf
+
+        \If{$\alpha  = \alpha_1 \lor \alpha_2$}
+            \State return join(reg($\alpha_1$), reg($\alpha_2$), n)
+        \EndIf
+
+        \If{$\alpha = \mathcal{F}_{[a, b]}\alpha_1$}
+            \State return reg\_F(reg($\alpha_1$), a, b, n)
+        \EndIf
+
+        \If{$\alpha = \mathcal{G}_{[a, b]}\alpha_1$}
+            \State return reg\_G(reg($\alpha_1$), a, b, n)
+        \EndIf
+
+        \If{$\alpha = \alpha_1 \mathcal{U}_{[a, b]} \alpha_2$}
+            \State return reg\_U(reg($\alpha_1$), reg($alpha_2$), a, b, n)
+        \EndIf
+
+        \If{$\alpha = \alpha_1 \mathcal{R}_{[a, b]} \alpha_2$}
+            \State return reg\_R(reg($\alpha_1$), reg($\alpha_2$), a, b, n)
+        \EndIf
+    \EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
  \vspace{-0.1in}
@@
 If each column has one `$1$', one `$0$', and $n-1$ `$S$'s, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.
+\footnote{See Appendix \ref{simp appendix} for the proof of the theorem.}
 \end{theorem}
+\begin{figure}[h!]
+\begin{minipage}{.50\textwidth}
     \noindent \textbf{Example:}
     \vspace{-0.05\textwidth}
-\begin{center}
-\[
-    \begin{pmatrix} \label{example1}
+    \begin{equation*}
+        \begin{pmatrix} \label{example1_regex_simp_thm}
         1 & S & S & S\\
@@
         \end{pmatrix} = SSSS.
-\]
-\end{center}
-\noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\
+    \end{equation*}
+    % \noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\
+    \end{minipage}
+    \begin{minipage}{.50\textwidth}
     Note that the theorem is a sufficient but not necessary condition for simplification to the arbitrary computation.
 One such example is the regular expression $101|S1S|1S0|0SS$, which fails the hypothesis of the  simplification theorem but is still equivalent to $SSS$.
+    \end{minipage}
+\end{figure}
+
 \subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
@@
 Our program outputs the following union of regular expressions to represent this formula:
-\begin{center}
-    $
+% \begin{wrapfigure}{l}{0.5\textwidth} \vspace{-\baselineskip}
+\[
     \begin{pmatrix}
@@
     \end{pmatrix}.
-$
-\end{center}
+\]
+% \end{wrapfigure}
 Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation.

### 2022-10-12 paper/Paper.tex
Added WEST algorithm to section4, rewrote/removed parts of theoretical complexity, more efficient formatting in section7, lots of touchingup of appendix format - Chiara, Laura, Zili

--- 2022-10-11 paper/Paper.tex
@@
 %% A \emph{regular expression} is a string that describes the form of a language. 
-%% Let $\Sigma$ denote a finite alphabet. The empty set $\emptyset$, the empty string $\epsilon = ``"$, and any character in $\Sigma$ are constants defined to be a regular expression. 
+%% Let $\Sigma$ denote a finite phibet. The empty set $\emptyset$, the empty string $\epsilon = ``"$, and any character in $\Sigma$ are constants defined to be a regular expression. 
 %% Beyond that, we define regular expressions recursively. 
@@
 %% \begin{example}
-%% Let `$a$', `$b$', and `$c$' denote characters in a finite alphabet.
+%% Let `$a$', `$b$', and `$c$' denote characters in a finite phibet.
 %% \begin{itemize}
@@
      \item Likewise, in the case for $\phi \mathcal{R}_{[a,b]} \psi$, if $\psi$ is true from the first to the last time-step, the truth value of $\phi$ at the final time-step doesn't matter - the computation satisfies $\phi \mathcal{R}_{[a,b]} \psi$ regardless of whether $\phi$ is true or false.
- \end{itemize}
-
-% \vspace{-0.1in}
-% \subsection{Soundness and Completeness}
-%  \vspace{-0.1in}
+ \end{itemize} % \vspace{-0.1in} % \subsection{Soundness and Completeness} %  \vspace{-0.1in}
  We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$).
 That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
-The proof of Theorem \ref{SoundComplete} appears in Appendix \ref{Appendix-SoundComplete}.
+% The proof of Theorem \ref{SoundComplete} appears in Appendix \ref{Appendix-SoundComplete}.
 
@@
 We use this theorem to simplify MLTL formulas, making them easier to interpret.
-Theorem \ref{NestedUR}'s proof appears in Appendix \ref{Appendix-NestedUR}.
+% Theorem \ref{NestedUR}'s proof appears in Appendix \ref{Appendix-NestedUR}.
 
@@
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- \vspace{-0.1in}
- \section{WEST Code Specifications} \label{specs}
-  \vspace{-0.1in}
-The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
-{GitHub} repository.
-The MLTL syntax for our program is given as the context free grammar below.
-In the alphabet, $T$ and $!$ refer to the propositional constants `true' and `false', respectively.
-$\&$, $v$, $=$, $>$ refer to propositional logic operators `and', `or, `equivalent', and `implies', respectively.
-Note that the last comma listed is not a typo and indeed part of the alphabet.
-\\
-\textbf{Alphabet}: 
-\begin{align*}
-    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `\mbox{$>$}' ,}\\
-    &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
-\end{align*}
-
-\begin{align*}
-    \text{Digit} &\to 0 \,|\, 1 \,|\,2 \,|\,3 \,|\,4 \,|\,5 \,|\,6 \,|\,7 \,|\, 8 \,|\, 9 \\
-    \text{Num} &\to \text{Digit} \; \text{Num} \,|\, \text{Digit} \\
-    \text{Interval} &\to [ \; \text{Num} \; : \; \text{Num} \; ] \\
-    \text{Prop\_cons} &\to \text{T} \;|\; ! \\
-    \text{Prop\_var} &\to \text{p} \; \text{Num} \\
-    \text{Unary\_Prop\_conn} &\to \hspace{1mm}\scriptstyle{\sim} \\
-    \text{Binary\_Prop\_conn} &\to \text{v} \;|\; \& \;|\; = \;|\; > \\
-    \text{Assoc\_Prop\_conn} &\to \text{v} \;|\; \& \;|\; = \\
-    \text{Array\_entry} &\to \text{Wff} \; , \; \text{Array\_entry} \;|\; \text{Wff} \\
-    \text{Unary\_Temp\_conn} &\to \text{F} \;|\; \text{G} \\
-    \text{Binary\_Temp\_conn} &\to \text{U} \;|\; \text{R} \\
-    \text{Wff} &\to \text{Prop\_cons} \;|\; \text{Prop\_var} \\
-               &\hspace{5mm} \;|\; \text{Unary\_Prop\_conn} \;\; \text{Wff} \\
-               &\hspace{5mm} \;|\; \text{Wff} \;\; \text{Binary\_Prop\_conn} \;\; \text{Wff}\\
-               &\hspace{5mm} \;|\; ( \; \text{Assoc\_Prop\_conn} \; [ \; \text{Array\_entry} \; ] \; ) \\
-               &\hspace{5mm} \;|\; \text{Unary\_Temp\_conn} \;\; \text{Interval} \;\; \text{Wff} \\
-               &\hspace{5mm} \;|\; ( \; \text{Wff} \;\; \text{Binar\_Temp\_conn} \;\; \text{Interval} \;\; \text{Wff} \; )
-\end{align*}
-
-In the grammar, associative propositional connectives (\textit{Assoc\_Prop\_conn}) are included for the ease of the user.
-Given well-formed formulas $\phi_1, \phi_2, \phi_3$, the following formula in prefix notation $(\lor[\phi_1, \phi_2, \phi_3])$ is parsed into $((\phi_1 \lor \phi_2) \lor \phi_3)$, which is in turn equivalent to $(\phi_1 \lor \phi_2 \lor \phi_3)$.
-\\
-\begin{remark}
-For two propositional variables, the associative equivalence operator functions identically to the binary propositional connective equivalence operator.
-For formulas with 3 or more propositional variables, however, the associative equivalence operator does not mean that each propositional variable in the list is equivalent.
-Instead, it means that the equivalence of the first two propositional variables in the list is equivalent to the next propositional variable in the list, and the truth value for this expression is equivalent to the next propositional variable, and so on.
-For example, $=[p1,p2,p3]$ is equivalent to $(p1=p2)=p3$ rather than $p1=p2=p3$.
-\end{remark}
-
-In Appendix \ref{pseudocode appendix}, we provide the full pseudocode of the WEST program.
-We summarize the important points to provide analysis of time and space complexity.
-The regular expression $R = \{R_1 | R_2 | ...
-| R_k\}$, where for all $1 \leq i \leq k$, $R_i \in \{$`0', `1', `S', `,'$\}^*$, is represented as a vector $R = {R_1, R_2, ..., R_k}$.
-
-In order to compute MLTL operations, we define functions for handling union and intersection of such vectors. 
-The \textit{join} function performs simple concatenation of two vectors, while the \textit{set\_intersect} function calculates pairwise intersection of strings from two vectors.
-The intersection of two strings is performed by \textit{bit\_wise\_and}, which computes intersection character by character.
-For example, \textit{bit\_wise\_and}$(1s, 0s)$ is the empty string while \textit{bit\_wise\_and}$(s11, 0s1) = 011$.
-
-The main focus is on the recursive function \textit{reg}, which is based on the structure of the grammar.
-It computes the propositional logic operators $>$ and  $=$ through formula rewriting in terms of And and Or.
-The four temporal operators in the grammar are computed according to the definitions of their regexes (See section \ref{regex}).
-
-If the user would like to see the satisfying computations for all the subformulas in their original formula, \textit{reg} contains a Boolean to enable this functionality.
-
-It is often the case that a vector of regular expression strings contains many redundancies, and can be simplified to a smaller vector of regular expressions that improves space complexity and drastically enhances user readability.
-As such, the \textit{simplify} function performs this by iterating through pairs of strings from the vector to search for valid simplifications. 
-If a pair of strings$(w, v)$ can be written in the form $w = w_1 c_w w_2$ and $v = v_1 c_v v_2$ such that $w_1 = v_1$ and $w_2 = v_2$, then they are combined into one string $w_1 (c_w | c_v) w_2$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Complexity} \label{complex}
-
-\subsection{Theoretical Complexity}
- In order to reason about the complexity of our algorithms, we make a few reasonable assumptions about our inputs.
-Suppose that the lower and upper intervals of temporal operators are bounded by some constant $d \in \mathbb{N}$, and that the difference between any bound is less than some constant $\delta \in \mathbb{N}$.
-We provide a summary of the complexity of each of the helper functions described for \textit{reg}. 
-For any function $f(\phi)$ taking a string argument $\phi$, we use $|\phi|$ to denote the number of characters in $\phi$ and $S(f(\phi))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
-
-\textbf{If $\phi$ is a propositional constant or variable:}
-%\begin{adjustwidth}{10mm}{3em}
-    It's easy to see that $S(\text{\emph{reg}}(!)) = 0$ since only the empty vector is returned. \\
-    By definition $\text{\emph{reg}}(T) = S^n$, so we have that $S(\text{\emph{reg}}(T)) = O(n)$.
-Similar to $\phi = T$, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)$ both return strings of the same length and thus we also have $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\scriptstyle{\sim} \textstyle p_k)) = S(\text{\emph{reg}}(T)) = n$.\\
-%\end{adjustwidth}
-
-\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} \lor \phi_{2}$'' \textbf{:}
-%\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we return $\textit{join}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}))$ \\
-    Thus, our space complexity is:
-    \[
-    S(\text{\emph{reg}}(\phi_{1} \lor \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).
-    \]
-%\end{adjustwidth}
-
-\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} \; \& \; \phi_{2}$'' \textbf{:}
-%\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we return $ \textit{set\_intersect}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}), n)$ \\
-    In the worst case, \textit{set\_intersect}($A$, $B$, $n$) will return a vector of size $S(A) \cdot S(B)$.\\
-    Thus, our space complexity is:
-    \[ 
-    S(\text{\emph{reg}}(\phi_{1} \; \& \; \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})).
-    \]
-%\end{adjustwidth}
-
-\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} >  \phi_{2}$'' \textbf{:}
-%\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we first rewrite $\phi_{1} > \phi_{2}$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1}) + \text{``} \lor \text{''} + \phi_{2} + \text{``)''}.
-    \]
-    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
-    So for space complexity, we have:
-    \[ 
-    S(\text{\emph{reg}}(\phi_{1} > \phi_{2})) = S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).
-    \]
-%\end{adjustwidth}
-\textbf{If} $\phi$ \textbf{is} ``$\phi_{1} = \phi_{2}$'' \textbf{:}
-%\begin{adjustwidth}{10mm}{3em}
-    For this case in our \emph{reg} function, we first rewrite $\phi_{1} = \phi_{2}$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = 
-    \text{``((''} + \phi_{1} + \text{``} \& \text{''} + \phi_{2} + \text{``)}
-    \lor 
-    \text{(''} + \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1}) + \text{``} \& \text{''} +  \textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{2}) + \text{``))''}.
-    \]
-    Then we return $\text{\emph{reg}}(\textit{equiv\_formula})$.
-    So for space complexity, we have:
-    \[ 
-    S(\text{\emph{reg}}(\phi_{1} = \phi_{2})) =
-    S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})) \; + \;  
-    S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{1})) \cdot S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{2})).
-    \]
-%\end{adjustwidth}
-\textbf{If} $\phi$ \textbf{is} ``$\lor$ [ $\phi_{1}$, .., $\phi_{k}$]'' \textbf{:} 
-%\begin{adjustwidth}{10mm}{3em}
-For this case in our \emph{reg} function, we first rewrite $\lor [\phi_{1}, .., \phi_{k}]$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``}( ... (\phi_{1} \lor \phi_{2}) \lor ... \phi_{k})\text{''}.
-    \]
-Using the space complexity of $\lor$, we have that:
-    \[
-    S(\text{\emph{reg}}(\lor [\phi_{1}, .., \phi_{k}])) = 
-    \sum_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i})).
-    \]
-%\end{adjustwidth}
-\textbf{If} $\phi$ \textbf{is} ``$\&$ [ $\phi_{1}$, .., $\phi_{k}$]'' \textbf{:} 
-%\begin{adjustwidth}{10mm}{3em}
-For this case in our \emph{reg} function, we first rewrite $\& [\phi_{1}, .., \phi_{k}]$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``}( ... (\phi_{1} \& \phi_{2}) \& ... \phi_{k})\text{''}.
-    \]
-Using the space complexity of $\&$, we have that:
-    \[
-    S(\text{\emph{reg}}(\& [\phi_{1}, .., \phi_{k}])) = 
-    \prod_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i})).
-    \]
-%\end{adjustwidth}
-\textbf{If} $\phi$ \textbf{is} ``$=$ [$\phi_{1}$, .., $\phi_{k}$]'' \textbf{:}
-%\begin{adjustwidth}{10mm}{3em}
-For this case in our \emph{reg} function, we first rewrite $= [\phi_{1}, .., \phi_{k}]$ to the equivalent formula:
-    \[ 
-    \textit{equiv\_formula} = \text{``}( ... (\phi_{1} = \phi_{2}) = ... \phi_{k})\text{''}.
-    \]
-Based on the space complexities of $\&$ and $\lor$, this gives:
-    \[
-    S(\text{\emph{reg}}(= [\phi_{1}, .., \phi_{k}])) = 
-    \prod_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i}))
-    + \prod_{i=1}^{k} S(\text{\emph{reg}}(\textit{wff\_to\_nnf}(\scriptstyle{\sim}\textstyle \phi_{i}))).
-    \]
-%\end{adjustwidth}
- \textbf{If} $\phi \text{ is } ``\mathcal{G}_{[a,b]} \phi_{1}$"\textbf{:}
-% \begin{adjustwidth}{10mm}{3em}
- Recall that $\text{\emph{reg}}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi) (,S^n)^{b-i}$.\\
- As shown in the \textit{Assoc\_Prop\_Conn} case, if $\phi$ is ``$\&[\phi_1, ... ,\phi_k$]", then \\
- $\text{S(\emph{reg}}(\& [\phi_{1}, .., \phi_{k}])) = 
-    \prod_{i=1}^{k} \text{S(\emph{reg}}(\phi_{i}))$. We have that:
- \begin{align*}
-     \text{S(\emph{reg}}(\phi)) &= \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1}))\\
-     &< \Bigl([(n+1)b+1] \cdot \text{S(\emph{reg}}(\phi_1))\Bigl)^\delta \\
-     &= \mathcal{C}_{G} \cdot \text{S(\emph{reg}}(\phi_1)^\delta 
- \end{align*}
- where $\mathcal{C}_{G} = [(n+1)b+1]^{\delta}$.
- In the calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a vector of only length 1 strings. \\
-% \end{adjustwidth}
- \textbf{If} $\phi \text{ is } ``\mathcal{F}_{[a,b]} \phi_{1}$"\textbf{:}
-% \begin{adjustwidth}{10mm}{3em}
- Recall that $\text{\emph{reg}}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi)(,S^n)^{b-i}$. \\
- As shown in the \textit{Assoc\_Prop\_Conn} case, if $\phi$ is ``$\lor[\phi_1, ... ,\phi_k$]", then \\
- $S(\text{\emph{reg}}(\lor [\phi_{1}, .., \phi_{k}])) = 
-    \sum_{i=1}^{k} S(\text{\emph{reg}}(\phi_{i}))$. Thus with similar calculation to $\mathcal{G}$,
- \begin{align*}
-     \text{S(\emph{reg}}(\phi)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) \\
-     &< \delta\Bigl(((n+1)b+1) \cdot \text{S(\emph{reg}}(\phi_1))\Bigl) \\
-     &= \mathcal{C}_{F} \cdot \text{S(\emph{reg}}(\phi_1)
- \end{align*}
- where $\mathcal{C}_{F} = \delta[(n+1)b+1]$.
-% \end{adjustwidth}
-
- \textbf{If $\phi$ = $``\phi_1 \mathcal{U}_{[a, b]} \phi_2"$:}
-% \begin{adjustwidth}{10mm}{3em}
-    By our previous definitions, 
-    $\text{\emph{reg}}(\phi_1 \ \mathcal{U}_{[a,b]} \phi_2) =  \bigvee_{i=a}^{b} \text{\emph{reg}}\left(\mathcal{G}_{[a,i-1]}\phi_1 \land \mathcal{G}_{[i, i]} \phi_2\right)$. \\
-    We can bound $S(\text{\emph{reg}}(\mathcal{G}_{[i, i]} \phi_2))$ by $(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
-    Thus using our previous results for the $\mathcal{G}$, $\&$ and $\lor$ operators, we have that:
-    \begin{align*}
-        S(\text{\emph{reg}}(\phi)) &= 
-        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
-        [(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))] \\
-        &< \delta [((n+1)(b-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
-        [(n+1) \cdot b \cdot S(\text{\emph{reg}}(\phi_2))] \\
-        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2)) \\
-        &= \mathcal{C}_U \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))
-    \end{align*}
-    where $\mathcal{C}_U = \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d$.
-%  \end{adjustwidth}
-
-  \textbf{If $\phi$ = $``\phi_1 \mathcal{R}_{[a, b]} \phi_2"$:}
-%  \begin{adjustwidth}{10mm}{3em}
-        By our previous definitions, $\text{\emph{reg}}(\phi_1 \mathcal{R}_{[a,b]} \phi_2) =  \text{\emph{reg}}\left(\mathcal{G}_{[a,b]}\phi_2\right) \lor \bigvee_{i=a}^{b-1} \text{\emph{reg}}\left(\mathcal{G}_{[a,i]}\phi_2 \land \mathcal{G}_{[i, i]} \phi_1\right)$.
-Thus, a similar argument to the $\mathcal{U}$ case gives us that:
-        \begin{align*}
-            S(\text{\emph{reg}}(\phi)) &< 
-            \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
-            \delta + \sum_{i = a}^{b-1} [\mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
-            \delta \cdot (n+1)\cdot i \cdot S(\text{\emph{reg}}(\phi_2))] \\
-            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
-            \delta + \delta[\mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
-            \delta \cdot (n+1)(b-1) \cdot S(\text{\emph{reg}}(\phi_2))] \\
-            &= \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
-            \delta [1 + \delta(n+1)(b-1)S(\text{\emph{reg}}(\phi_2))] \\
-            &< \mathcal{C}_G \cdot S(\text{\emph{reg}}(\phi_1))^
-            \delta (\delta(n+1)d \cdot S(\text{\emph{reg}}(\phi_2))) \\
-            &= \mathcal{C}_R \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))
-        \end{align*}
-        where $\mathcal{C}_R = \mathcal{C}_G \cdot \delta (n+1)d$. \\
-%  \end{adjustwidth}
-\begin{theorem}[\emph{Space Complexity}]
-Given a well formed MLTL formula $\phi$, $\text{\emph{reg}}(\phi)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
-\end{theorem}
-\begin{proof}
-    To analyze worst-case complexity, it's clear from the analysis above that $\mathcal{U}$ and $\mathcal{R}$ give the largest complexity.
-From the constants in their respective bounds, we can show that $\mathcal{C}_U = ((n+1)d - n)^\delta \cdot \mathcal{C}_R > \mathcal{C}_R$, and so we'll analyze only repeated nesting of the operator $\mathcal{U}$.
-
-    However, notice that the structure of the parse tree is important.
-For example, formulas similar to $(a \mathcal{U} b) \mathcal{U} (c \mathcal{U} d)$ generate a balanced binary parse tree where the maximum depth of recursion is $O(\log \ell)$.
-However if the nesting is only from one side, such as formulas similar to $(((p_0 \mathcal{U} p_1) \mathcal{U} p_2) \mathcal{U} p_3)$, then the maximum depth of recursion is $O(\ell)$.
-Thus we'll focus on the formula $$\phi = (((p_0 \mathcal{U}_{[a_1, b_1]} p_1) \mathcal{U}_{[a_2, b_2]} p_2) \mathcal{U}_{[a_3, b_3]}...
-\mathcal{U}_{[a_{\ell - 1}, b_{\ell - 1}]} p_{\ell - 1}) \mathcal{U}_{[a_\ell, b_\ell]} p_\ell$$ where there are $\ell$ logical connectives $\mathcal{U}$ and $n = \ell + 1$ propositional variables.
-
-    We'll derive the complexity of $S(\text{\emph{reg}}(\phi))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\text{\emph{reg}}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\text{\emph{reg}}(p_{k+1}))$.
-The recurrence relation captures an extra nesting of the $\mathcal{U}$ operator, based on the complexity of $\mathcal{U}$ defined above.
-We calculate $S(p_m) = n = \ell + 1$ for all $m$ such that $0 \leq m \leq \ell$, thus $s_1 = \mathcal{C}_U(\ell + 1)^{\delta + 1}$ and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot (\ell + 1)$.
-
-    The explicit formula is given by $s_k = \mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}$.
-It's easy to check that the base case $k = 1$ holds, and we prove the claim by induction:
-    \begin{align*}
-        S_{k + 1} &= \mathcal{C}_U (\mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}) ^ \delta \cdot (\ell + 1) \\
-        &= \mathcal{C}_U^{1 + \sum_{i = 0}^{k - 1} \delta^{i + 1}} \cdot (\ell + 1)^{1 + \sum_{i = 0}^{k} \delta^{i + 1}} \\
-        &= \mathcal{C}_U^{\sum_{i = 0}^k \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k+1} \delta^i}.
-    \end{align*}
-
-    \noindent Thus we have that $S(\text{\emph{reg}}(\phi)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
-
- \end{proof}
-For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
-In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, T, !$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{C}_U$ match their respective space complexities.
-Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.
-One feature within our implementation of \textit{reg} is to apply the \textit{simplify} function to all intermediary vector calculations in order to decrease the output size.
-In the worst case if no simplification occurs, space complexity remains unchanged, but time complexity of \textit{simplify} is cubic in input size.
-In practice however, both time and space complexities are much more optimistic than worst-case estimates.
-
-\subsection{Experimental Benchmarking}
- Along with theoretical space and time complexity, we provide some experimental benchmarking of these complexities using randomly generated MLTL formulas.
-This was done on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
-For each simulation, we generated 1000 MLTL formulas using the parameters DELTA, INTERVAL\_MAX, number of propositional variables, and number of iterations.
-DELTA is the maximum length we allow for any interval.
-INTERVAL\_MAX is the largest allowed upper bound for any interval.
-Number of iterations refers to the level of nesting in the generated formulas.
-For example, $\mathcal{G}_{[0,2]}p_0$ is a formula generated with one iteration, while $\mathcal{G}_{[0,2]}(p_0 \land p_1)$ is a formula generated with two iterations.
-We measure the number of characters in the output and the amount of time in milliseconds taken to run the program.
-Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.
-\\
-\\
-\noindent\textbf{Simulation 1}
-For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. We obtain the following plots:
-% ZILI: Seems redundant since example formulas are listed below for the outliers
-% Some examples of generated formulas:
-% \begin{itemize}
-%   \item $(p_4 \land p_0) \mathcal{U}_{[2,3]} (\neg p_1)$.
-%   \item $(\mathcal{G}_{[3,5]} p_3) \mathcal{R}_{[7,8]} (p_3 \rightarrow p_0)$.
-%   \item $\mathcal{F}_{[1,6]} (p_4 = p_3)$.
-% \end{itemize}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim1Length.png}
-    \captionof{figure}{Input length vs output length.}
-    \end{figure}
-\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim1Time.png}
-    \captionof{figure}{Input length vs run time.}
-    \end{figure}
-\end{minipage}%
-
-% ZILI: I've reduced the length of the caption discription, otherwise the two captions display extremely close side by side
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim1Length.png}
-%     \caption{Input length in number of characters vs output length in number of characters for simulation 1.
-Input length counts all characters, including parentheses, of the inputted formulas.
-Output length counts all the characters outputted, including commas.}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim1Time.png}
-%     \caption{Input length in number of characters vs run time in milliseconds for simulation 1. Input length counts all characters, including parentheses, of the inputted formulas.}
-% \end{figure}
-
-\vspace{2mm}
-\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both figures, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for figure 2.
-
-% ZILI: Chose not to use itemize due to formatting difficulties with vertical spacing.
-% \noindent The extreme outlier seen in the output length plot corresponds to the formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$.\\
-% The three extreme outliers seen in the time plot correspond to the following formulas:
-% \begin{itemize}
-%     \item $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ (both graphs).
-%     \item $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ (time).
-%     \item $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ (time).
-% \end{itemize}
-
-\vspace{\baselineskip}
-\noindent\textbf{Simulation 2}
-For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Here are some examples of generated formulas:
-$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain the following plots:
-
-% ZILI: removed itemize due to vertical spacing issues.
-% \begin{itemize}
-%     \item $\mathcal{F}_{[10,17]} p_4$.
-%     \item $\neg p_6$.
-%     \item $p_6 \mathcal{U}_{[6,14]} p_8$.
-% \end{itemize}
-
-\vspace{-4mm}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim2Length.png}
-    \captionof{figure}{Input length vs output length}
-    \end{figure}
-\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim2Time.png}
-    \captionof{figure}{Input length vs run time.}
-    \end{figure}
-\end{minipage}%
-% ZILI: Old graph formatting and captions
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim2Length.png}
-%     \caption{Input length in number of characters vs output length in number of characters for simulation 2.
-Input length counts all characters, including parentheses, of the inputted formulas.
-Output length counts all the characters outputted, including commas.}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim2Time.png}
-%     \caption{Input length in number of characters vs run time in milliseconds for simulation 2. Input length counts all characters, including parentheses, of the inputted formulas.}
-% \end{figure}
-
-\subsubsection{Simulation 3}
-For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. 
-% Below are some examples of generated formulas:
-% \begin{itemize}
-%     \item $(p_5 \land p_0) = (p_8 \mathcal{U}_{[3,6]} p_8)$.
-%     \item $(\mathcal{G}_{[6,7]} p_4) \land (\mathcal{F}_{[5,7]} p_1)$.
-%     \item $\neg (p_0 \mathcal{U}_{[2,5]} p_7)$.
-% \end{itemize}
-We obtain the following plots:
-
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim3Length.png}
-    \captionof{figure}{Input length vs output length}
-    \end{figure}
-\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim3Time.png}
-    \captionof{figure}{Input length vs run time.}
-    \end{figure}
-\end{minipage}%
-% ZILI: Old graph formatting and captions
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim3Length.png}
-%     \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim3Time.png}
-%     \caption{Input length in number of characters vs run time in milliseconds for simulation 3. Input length counts all characters, including parentheses, of the inputted formulas.}
-% \end{figure}
-\vspace{\baselineskip}
-The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both figures, and figure 5 had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
-% The three outliers in the output length plot are the formulas 
-% \begin{itemize}
-%     \item $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$.
-%     \item $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$.
-%     \item $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
-% \end{itemize}
-% The former two are also the time complexity outliers.
-\\
-\\
-\noindent\textbf{Simulation 4}
-For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. Some examples of generated formulas are: 
-$\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
-% \begin{itemize}
-%     \item $\neg p_1$.
-%     \item $p_1 \mathcal{R}_{[6,7]} p_3$.
-%     \item $\mathcal{F}_{[5,5]} p_3$.
-% \end{itemize}
-We obtain the following plots:
-
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim4Length.png}
-    \captionof{figure}{Input length vs output length}
-    \end{figure}
-\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.39]{images/Sim4Time.png}
-    \captionof{figure}{Input length vs run time.}
-    \end{figure}
-\end{minipage}%
-
-% ZILI: Old figures
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim4Length.png}
-%     \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
-% \end{figure}
-% \begin{figure}[H]
-%     \centering
-%     \includegraphics[scale=0.75]{images/Sim4Time.png}
-%     \caption{Input length in number of characters vs run time in milliseconds for simulation 4. Input length counts all characters, including parentheses, of the inputted formulas.}
-% \end{figure}
-\vspace{\baselineskip}
-\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively sparse.
-We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators.
-As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in practical applications.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Verification of Correctness} \label{test}
- The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program). 
-On one hand, correctness of an algorithm is assured by mathematical analysis of the algorithm on all possible inputs and showing that it behaves as desired. 
-However, assuring correctness of the program is a difficult task.
-One naive approach is to test every possible input up to a certain size, and verify the output or behavior of the program.
-This often times involves a test suite that is too large to be computationally feasible, and the test suite may be overtly redundant. 
-For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program for any reasonable party.
-We approach this problem more intelligently.
-In the following sections, we prove the correctness of our algorithm and also test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm.
-A control path can be thought of as a sequence of lines of code that are executed in one calculation of an input formula.
-Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST program.
+
+\section{WEST Algorithm and Analysis} \label{WESTalg}
+We now present the  full WEST algorithm, which takes MLTL formula $\phi$ (in NNF) and number of propositional variables $n$, and recursively computes all satisfying temporal regular expressions to $\phi$.
+We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
+Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{F}$. 
+Note how the algorithm parallels the regular expression defined for $\mathcal{F}$, and the algorithms for the other three temporal operators follow an identical structure.
+
+One major detail that drastically improves running time is applying a simplifying function to the output of set intersection. 
+This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
+Although set intersection does blow up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
+We simplify alternation by using the fact that for regular expressions $w_1$ and $w_2$, $w_1 1 w_2 \lor w_1 0 w_2 = w_1 s w_2$, and check for the reduction between at every index between every pair of strings in a given vector.
+
+% \begin{algorithm}[H]
+% \caption{WEST Algorithm}
+% \begin{algorithmic}[1]
+%     \Procedure{reg}{string $\phi$, int $n$}
+%         \If{$\phi$ is $\top$ or $\bot$} return reg\_prop\_const($\phi$, n)
+%         \EndIf
+
+%         \If{$\phi$ is $p_k$ or $\neg p_k$} return reg\_prop\_var($\phi$, n)
+%         \EndIf
+
+%         \If{$\phi  = \phi_1 \land \phi_2$} return set\_intersect(reg($\phi_1$), reg($\phi_2$), n)
+%         \EndIf
+
+%         \If{$\phi  = \phi_1 \lor \phi_2$} return join(reg($\phi_1$), reg($\phi_2$), n)
+%         \EndIf
+
+%         \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$} return reg\_F(reg($\phi_1$), a, b, n)
+%         \EndIf
+
+%         \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$} return reg\_G(reg($\phi_1$), a, b, n)
+%         \EndIf
+
+%         \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$} return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
+%         \EndIf
+
+%         \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$} return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
+%         \EndIf
+%     \EndProcedure
+% \end{algorithmic}
+% \end{algorithm}
+
+% ZILI: Presenting algorithm vertically instead
+\hspace{-5mm}
+\begin{minipage}{0.52\textwidth}
+\begin{algorithm}[H]
+\caption{WEST Algorithm}
+\begin{algorithmic}[1]
+    \Procedure{reg}{string $\phi$, int $n$}
+        \If{$\phi$ is $\top$ or $\bot$}
+            \State return reg\_prop\_const($\phi$, n)
+        \EndIf
+
+        \If{$\phi$ is $p_k$ or $\neg p_k$}
+            \State return reg\_prop\_var($\phi$, n)
+        \EndIf
+
+        \If{$\phi  = \phi_1 \land \phi_2$}
+            \State \parbox[t]{.82\linewidth}{return set\_intersect(reg($\phi_1$), reg($\phi_2$), \hspace*{5mm}n)}
+        \EndIf
+
+        \If{$\phi  = \phi_1 \lor \phi_2$}
+            \State return join(reg($\phi_1$), reg($\phi_2$), n)
+        \EndIf
+
+        \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$}
+            \State return reg\_F(reg($\phi_1$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$}
+            \State return reg\_G(reg($\phi_1$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$}
+            \State return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
+            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
+        \EndIf
+    \EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+\hfill
+\begin{minipage}{0.48\textwidth}
+\begin{algorithm}[H]
+\caption{Takes set intersection of the languages of two regexes}
+%Input: Vectors of strings that represent regexes, simplify boolean\\
+%Output: Vector of strings that represents set intersection of the languages of the inputted regexes
+\begin{algorithmic}
+\Procedure{set\_intersect}{vector $R$, vector $T$, bool simp}
+    \State Pad($R$, $T$), return $\leftarrow \{\}$
+    \For{$(r, t) \in R\times T$}
+            \State add bit\_wise\_and($r, t$) to ret 
+    \EndFor
+    \State return simplify(ret)
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\begin{algorithm}[H]
+\caption{Computes the regex for a MLTL formula $\phi$U[a:b]$\psi$} 
+%Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
+%Output: Vector of strings that represents the appropriate satisfying computations 
+\begin{algorithmic}
+\Procedure{reg\_U}{vector reg\_phi, vector reg\_psi int $a$, int $b$, int $n$, bool simp} 
+    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ reg\_psi
+    \If{$a > b$} return $\{\}$
+    \EndIf
+    \For{($a \leq i \leq b-1$) }
+        \State temp\_G1 $\leftarrow$ reg\_G(reg\_phi, $a$, $i$, $n$)
+        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(reg\_psi, $i+1$, \hspace*{5mm}$i+1$, $n$)}
+        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, $n$, simp)}
+        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp, \hspace*{5mm}simp)}
+    \EndFor
+    \State return comp
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+
 \subsection{Theoretical Correctness of the WEST Algorithm}
@@
 The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
-\textit{Join} takes as input two vectors of computation strings $R$ and $T$, and simply returns a vector containing all strings in $R$ and $T$, which is equivalent to $R \cup T$. 
+\textit{Join} takes as input two vectors of computation strings $R$ and $B$, and simply returns a vector containing all strings in $R$ and $B$, which is equivalent to $R \cup B$. 
 \textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ...
@@
 We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
-In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_alpha} = \textit{reg}(\phi)$ and $\textit{reg\_beta} = \textit{reg}(\psi)$, which, by the induction hypothesis, are correctly and recursively computed.
-The regular expression for the Until operator may be rewritten as follows: 
-\begin{align*}
-   \text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) &=  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
-   &= \text{reg}\left(\mathcal{G}_{[a,a-1]}\phi \land \mathcal{G}_{[a, a]} \psi\right) \lor \bigvee_{i=a+1}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
-   &= \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)
-\end{align*}
-The last line follows from the semantics of the Global operator, which defines out of bound time step behavior to be vacuously true.
-In the pseudocode for $reg\_U$ (\ref{regU}), the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_beta}, and is the regular expression for $\mathcal{G}_[a, a] \psi$.
+In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_phi} = \textit{reg}(\phi)$ and $\textit{reg\_psi} = \textit{reg}(\psi)$, which, by the induction hypothesis, are correctly and recursively computed.
+The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$.
+In the pseudocode for $reg\_U$, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_psi}, and is the regular expression for $\mathcal{G}_[a, a] \psi$.
 Next, the Or block from $i = a + 1$ to $b - 1$ is iteratively computed using \textit{set\_intersect} for the inner expression, and added to \textit{comp} with the \textit{join} function, which are both proven correct above.
@@
 Continue in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.
-\subsection{Correctness of WEST}
+
+\subsection{Theoretical Complexity}
+\begin{flushleft}
+In order to reason about the complexity of our algorithms, we make a few reasonable assumptions about our inputs.
+Suppose that the lower and upper intervals of temporal operators are bounded by some constant $d \in \mathbb{N}$, and that the difference between any bound is less than some constant $\delta \in \mathbb{N}$.
+We provide a summary of the complexity of each of the helper functions that contribute to the worst case behavior of final output.\\
+For any function $f(\phi)$ taking a string argument $\phi$, we use $|\phi|$ to denote the number of characters in $\phi$ and $S(f(\phi))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
+\hspace{3mm} If $\phi$ is a propositional constant or variable, it's easy to see that $S(\text{\emph{reg}}(\bot)) = 0$ since only the empty vector is returned.
+By definition $\text{\emph{reg}}(\top) = S^n$, so we have that $S(\text{\emph{reg}}(\top)) = O(n)$.
+Similarly, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\neg p_k)$ both return strings of the same length and thus $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\neg p_k)) = S(\text{\emph{reg}}(\top)) = n$.\\
+\hspace{3mm} If $\phi$ is ``$\phi_{1} \lor \phi_{2}$'' we return $\textit{join}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}))$, which simply concatenates the contents of the two vectors. 
+Thus $S(\text{\emph{reg}}(\phi_{1} \lor \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).$\\
+\hspace{3mm} If $\phi$ is ``$\phi_{1} \land \phi_{2}$''
+$ \textit{set\_intersect}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}), n)$ returns a vector of size $S(A) \cdot S(B)$ in the worst case when no simplification can be made. 
+Thus, our space complexity is $S(\text{\emph{reg}}(\phi_{1} \land \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})).$\\
+\hspace{3mm} For the next cases, we use these two bounds and define the constants $\mathcal{C}_G$ and $\mathcal{C}_F$:
+{\centering $\prod_{i = a}^b (n+1)i &= (n+1)^{b-a} \cdot \frac{b!}{(a-1)!} \leq (n+1)^\delta b!
+\leq (n+1)^\delta d!
+= \mathcal{C}_G$ \\ $\sum_{i = a}^b (n+1)i &\leq (n+1)b\delta \leq (n+1)d\delta  = \mathcal{C}_F$\par}\\
+\hspace{3mm} If $\phi \text{ is } ``\mathcal{G}_{[a,b]} \phi_{1}$":
+recall that $\text{\emph{reg}}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi) (,S^n)^{b-i}$.
+From the analysis of \textit{set\_intersect}, worst case space complexity is multiplicative.
+Thus\\ $\text{S(\emph{reg}}(\phi)) = \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_G \text{S(\emph{reg}}(\phi_1))$.
+In this calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a vector of only length 1 strings. \\
+\hspace{3mm} If $\phi \text{ is } ``\mathcal{F}_{[a,b]} \phi_{1}$":
+Recall that $\text{\emph{reg}}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi)(,S^n)^{b-i}$. \\
+From the analysis of \textit{join}, worst case space complexity is additive and thus 
+$\text{S(\emph{reg}}(\phi)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_{F} \text{S(\emph{reg}}(\phi_1)$.\\
+\hspace{3mm}If $\phi$ = $``\phi_1 \mathcal{U}_{[a, b]} \phi_2"$: Recall that 
+    $\text{\emph{reg}}(\phi_1 \ \mathcal{U}_{[a,b]} \phi_2) =  \bigvee_{i=a}^{b} \text{\emph{reg}}\left(\mathcal{G}_{[a,i-1]}\phi_1 \land \mathcal{G}_{[i, i]} \phi_2\right)$.
+    We can bound $S(\text{\emph{reg}}(\mathcal{G}_{[i, i]} \phi_2))$ by $(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
+    Thus using our previous results for the $\mathcal{G}$, $\land$ and $\lor$ operators, we have that:
+    \vspace{-.4cm}
+    \begin{align*}
+        S(\text{\emph{reg}}(\phi)) &= 
+        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
+        [(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))] \\
+        &< \delta [((n+1)(b-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
+        [(n+1) \cdot b \cdot S(\text{\emph{reg}}(\phi_2))] \\
+        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2)) \\
+        &= \mathcal{C}_U \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))
+    \end{align*}
+    where $\mathcal{C}_U = \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d$.\\
+\hspace{3mm} If $\phi$ = $``\phi_1 \mathcal{R}_{[a, b]} \phi_2"$:
+    $\text{\emph{reg}}(\phi_1 \mathcal{R}_{[a,b]} \phi_2) =  \text{\emph{reg}}\left(\mathcal{G}_{[a,b]}\phi_2\right) \lor \bigvee_{i=a}^{b-1} \text{\emph{reg}}\left(\mathcal{G}_{[a,i]}\phi_2 \land \mathcal{G}_{[i, i]} \phi_1\right)$.
+Thus, a similar argument to the $\mathcal{U}$ case shows
+    $S(\text{\emph{reg}}(\phi)) < \mathcal{C}_R \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))$, \\
+    where $\mathcal{C}_R = \mathcal{C}_G \cdot \delta (n+1)d$.
+\end{flushleft}
+\begin{theorem}[\emph{Space Complexity}]
+Given a well formed MLTL formula $\phi$, $\text{\emph{reg}}(\phi)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
+\end{theorem}
+\begin{proof}
+    To analyze worst-case complexity, it's clear from the analysis above that $\mathcal{U}$ and $\mathcal{R}$ give the largest complexity.
+From the constants in their respective bounds, we can show that $\mathcal{C}_U = ((n+1)d - n)^\delta \cdot \mathcal{C}_R > \mathcal{C}_R$, and so we'll analyze only repeated nesting of the operator $\mathcal{U}$.\\
+    However, notice that the structure of the parse tree is important.
+For example, formulas similar to $(a \mathcal{U} b) \mathcal{U} (c \mathcal{U} d)$ generate a balanced binary parse tree where the maximum depth of recursion is $O(\log \ell)$.
+However if the nesting is only from one side, such as formulas similar to $(((p_0 \mathcal{U} p_1) \mathcal{U} p_2) \mathcal{U} p_3)$, then the maximum depth of recursion is $O(\ell)$.
+Thus we'll focus on the formula $$\phi = (((p_0 \mathcal{U}_{[a_1, b_1]} p_1) \mathcal{U}_{[a_2, b_2]} p_2) \mathcal{U}_{[a_3, b_3]}...
+\mathcal{U}_{[a_{\ell - 1}, b_{\ell - 1}]} p_{\ell - 1}) \mathcal{U}_{[a_\ell, b_\ell]} p_\ell$$ where there are $\ell$ logical connectives $\mathcal{U}$ and $n = \ell + 1$ propositional variables.\\
+    We'll derive the complexity of $S(\text{\emph{reg}}(\phi))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\text{\emph{reg}}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\text{\emph{reg}}(p_{k+1}))$.
+The recurrence relation captures an extra nesting of the $\mathcal{U}$ operator, based on the complexity of $\mathcal{U}$ defined above.
+We calculate $S(p_m) = n = \ell + 1$ for all $m$ such that $0 \leq m \leq \ell$, thus $s_1 = \mathcal{C}_U(\ell + 1)^{\delta + 1}$ and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot (\ell + 1)$.
+\\
+    The explicit formula is given by $s_k = \mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}$.
+It's easy to check that the base case $k = 1$ holds, and we prove the claim by induction:
+    \vspace{-0.2cm}
+    \begin{align*}
+        S_{k + 1} &= \mathcal{C}_U (\mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}) ^ \delta \cdot (\ell + 1) \\
+        &= \mathcal{C}_U^{1 + \sum_{i = 0}^{k - 1} \delta^{i + 1}} \cdot (\ell + 1)^{1 + \sum_{i = 0}^{k} \delta^{i + 1}} \\
+        &= \mathcal{C}_U^{\sum_{i = 0}^k \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k+1} \delta^i}.
+    \end{align*}
+    Thus we have that $S(\text{\emph{reg}}(\phi)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
+ \end{proof}
+For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
+In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, \top, \bot$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{U}$ match their respective space complexities.
+Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.
+If in the worst case no simplification occurs in any call of \textit{set\_intersect}, space complexity remains unchanged, but simplifying a vector of regular expressions is cubic in input size.
+In practice however, both time and space complexities are much more optimistic than worst-case estimates.
+
+\subsection{Experimental Benchmarking}
+ Along with theoretical space and time complexity, we provide some experimental benchmarking of these complexities using randomly generated MLTL formulas.
+This was done on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
+For each simulation, we generated 1000 MLTL formulas using the parameters DELTA, INTERVAL\_MAX, number of propositional variables, and number of iterations.
+DELTA is the maximum length we allow for any interval.
+INTERVAL\_MAX is the largest allowed upper bound for any interval.
+Number of iterations refers to the level of nesting in the generated formulas.
+For example, $\mathcal{G}_{[0,2]}p_0$ is a formula generated with one iteration, while $\mathcal{G}_{[0,2]}(p_0 \land p_1)$ is a formula generated with two iterations.
+We measure the number of characters in the output and the amount of time in milliseconds taken to run the program.
+Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.\\
+\noindent\textbf{Simulation 1}
+For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. We obtain the following plots:\\
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim1Length.png}
+    \captionof{figure}{Input length vs output length.\vspace{3mm}}
+    \end{figure}
+\end{minipage}
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim1Time.png}
+    \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \end{figure}
+\end{minipage}\\
+\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both figures, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for figure 2.\\
+\noindent\textbf{Simulation 2}
+For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Here are some examples of generated formulas:
+$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain the following plots:\\
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim2Length.png}
+    \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \end{figure}
+\end{minipage}
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim2Time.png}
+    \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \end{figure}
+\end{minipage}\\
+\noindent\textbf{Simulation 3}
+For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. We obtain the following plots:\\
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim3Length.png}
+    \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \end{figure}
+\end{minipage}
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim3Time.png}
+    \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \end{figure}
+\end{minipage}\\
+The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both figures, and figure 5 had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
+\\
+\noindent\textbf{Simulation 4}
+For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX.
+Some examples of generated formulas are: $\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
+We obtain the following plots:\\
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim4Length.png}
+    \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \end{figure}
+\end{minipage}%
+\begin{minipage}{0.5 \textwidth}
+    \begin{figure}[H]
+    \centering
+    \includegraphics[scale=0.39]{images/Sim4Time.png}
+    \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \end{figure}
+\end{minipage}
+\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively sparse.
+We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators.
+As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in practical applications.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Correctness of WEST} \label{test}
+ The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program). 
+On one hand, correctness of an algorithm is assured by mathematical analysis of the algorithm on all possible inputs and showing that it behaves as desired. 
+However, assuring correctness of the program is a difficult task.
+One naive approach is to test every possible input up to a certain size, and verify the output or behavior of the program.
+This often times involves a test suite that is too large to be computationally feasible, and the test suite may be overtly redundant. 
+For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program for any reasonable party.
+We approach this problem more intelligently.
+In the following section, we test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm.
+A control path can be thought of as a sequence of lines of code that are executed in one calculation of an input formula.
+Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST program.
+
+\subsection{Intelligent Fuzzing}
 Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; fuzz testing (also know as fuzzing) is a form of negative testing.
@@
  We choose to represent the states space of algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
-The core of the WEST program is executed in the recursive routine, \textit{reg}, which calls the $8$ different subroutines discussed earlier, as shown in the graph below: 
-\begin{figure}[H]
+The core of the WEST program is executed in the recursive routine, \textit{reg}, which calls the $8$ different subroutines discussed earlier, as shown in \ref{fig:abstracted graph}.
+\begin{figure}[t]
     \centering
@@
 
-    \caption{Abstracted graph of the \textit{reg} main routine (refer to Appendix \ref{graphs appendix} for expanded graph and graphs of helper functions).
-Red nodes signal recursive calls to \textit{reg} on sub formulas of the input formula.}
+    \caption{Abstracted graph of the \textit{reg} main routine. Red nodes signal recursive calls to \textit{reg} on sub formulas of the input formula.}
     \label{fig:abstracted graph}
@@
 Without this abstraction, attempting to explore all execution paths in this finer graph is infeasible due to the explosion in the number of paths \cite{Pham_2016}, some of which are provably impossible to construct a test input to explore.
-Additionally, the astute reader may observe that analysis of the $>$, $=$, and \textit{assoc\_prop\_conn} operators are not included in the state diagram. 
-These cases are handled in the algorithm through only formula rewriting to the core operators.
-This is done through simple string manipulation, which is relatively simple to guarantee and test correctness of through unit testing.
 \subsubsection{Creating the Test Suite}
@@
 For $d = 0$, only the paths leading to \textit{prop\_var} and \textit{prop\_cons} can be explored, so $\phi(0) = 2$.
-For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \textit{reg\_G} and \textit{reg\_F} is counted in the linear term, and paths \textit{reg\_U}, \textit{reg\_R}, \textit{set\_intersect}, and \textit{join} is counted by the quadratic term.
+For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \textit{reg\_G} and \textit{reg\_F} is counted in the linear term, and paths to \textit{reg\_U}, \textit{reg\_R}, \textit{set\_intersect}, and \textit{join} is counted by the quadratic term.
 This gives $\phi(1) = 20$, $\phi(2) = 1640$, and $\phi(3) = 10761680$. 
@@
 Then for any $d \geq 1$, the test suite is constructed by iterating through all formulas in the depth $d-1$ test suite for \textit{reg\_G} and \textit{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths.
-To ensure wider coverage, each of the propositional variables or their negation and propositional constants are randomly generated (full pseudocode description in Appendix \ref{pseudocode appendix}).
+To ensure wider coverage, each of the propositional variables or their negation and propositional constants are randomly generated.
 \subsubsection{Verifying against Naive Brute Force}
@@
 Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of `$S$'s when a formula holds true for every computation.
-We first define some vocabulary.
-\begin{definition}[\emph{Arbitrary Computation}]
-We say a regular expression composed entirely of `$S$'s and commas is an \emph{arbitrary computation}. For the purposes of the following theorem, we remove all commas from computations.
-\end{definition}
-\begin{definition}[\emph{Fixed Truth Value}]
+We first define some vocabulary.\\
+ We say a regular expression composed entirely of `$S$'s and commas is an \emph{arbitrary computation}.
+For the purposes of the following theorem, we remove all commas from computations.
 We say `0' or a `1' in a regular expression is a \emph{fixed truth value}.
-\end{definition}
-\begin{definition}[\emph{Matrix}]
 We overload the definition of a matrix and say that a \emph{matrix} is a representation of a union of regular expressions, where each row is a regular expression.
 This aids significantly in the description and proof of the theorem; note, however, that matrix algebra does not apply in this definition.
-\end{definition}
 \begin{theorem}[\emph{Regular Expression Simplification Theorem}] \label{simp}
@@
 \end{theorem}
-\noindent \textbf{Example:}
-\vspace{-0.05\textwidth}
-\begin{center}
-\[
-    \begin{pmatrix} \label{example1}
-    1 & S & S & S\\
-    S & 1 & S & S\\
-    S & S & 1 & S\\
-    S & S & S & 1\\
-    0 & 0 & 0 & 0
-    \end{pmatrix} = SSSS.
-\]
-\end{center}
-\noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\
-Note that the theorem is a sufficient but not necessary condition for simplification to the arbitrary computation.
+Note that this theorem gives us a sufficient but not a necessary condition for simplification to the arbitrary computation.
 One such example is the regular expression $101|S1S|1S0|0SS$, which fails the hypothesis of the  simplification theorem but is still equivalent to $SSS$.
 \subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
+\begin{figure}[H]
+\begin{minipage}{.62\textwidth}
 \begin{example} \label{example1}
 Consider the MLTL formula:
-$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$
+$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$.
+The WEST program outputs a union of regular expressions represented by the matrix in \eqref{matrix_ex3}.
+Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation.
+However, we foresee some challenges to the implementation of this algorithm.
 \end{example}
-Our program outputs the following union of regular expressions to represent this formula:
-\begin{center}
-    $
+\end{minipage}
+\begin{minipage}{.38\textwidth}
+%     \noindent \textbf{Example:}
+    % \vspace{-0.05\textwidth}
+\begin{equation} \label{matrix_ex3}
     \begin{pmatrix}
@@
     0 & 0 & 0 & 0
-    \end{pmatrix}.
-$
-\end{center}
-Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation.
-However, we foresee some challenges to the implementation of this algorithm.
+    \end{pmatrix}
+\end{equation}
+\end{minipage}
+\end{figure}
+
 First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
@@
 For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
-Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end. Consider the following MLTL formula:
+Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end. 
+\begin{figure}[h!]
+\begin{minipage}{.62\textwidth}
 \begin{example} \label{example2}
-$T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$
+Consider the following MLTL formula: $T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$.
+The WEST program generates a union of regular expressions corresponding to the matrix shown in \eqref{matrix_ex4}.
+It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
 \end{example}
-\noindent The WEST program generates the following union of regular expressions:
-\begin{center}
-$
+\end{minipage}
+\begin{minipage}{.38\textwidth}
+\begin{equation} \label{matrix_ex4}
     \begin{pmatrix}
-    S & S & 1 & S\\
-    S & S & S & 1\\
+      S & S & 1 & S \\
+      S & S & S & 1 \\
       S & S & 0 & 0
-    \end{pmatrix}.
-$
-\end{center}
-It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
+    \end{pmatrix}
+\end{equation}
+\end{minipage}
+\end{figure}
+
 Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
 Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up" by common substrings.
-Consider the following modification to the matrix generated by example \ref{example1}:
+Consider the following modification to the matrix generated by example \ref{example1}:\\
+\begin{minipage}{.5\textwidth}
+The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively.
+In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
+Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.
+\end{minipage}
+\begin{minipage}{.5\textwidth}
 \begin{center}
@@
   0 & \mathbf{0} & \mathbf{0} & 1 & S & 0 & \mathbf{0} & \mathbf{0} & 1\\
-    \end{pmatrix} \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
+    \end{pmatrix} 
+    \vspace{2mm}
+    \\\equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
 $
 \end{center}
-The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively.
-In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
-Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.
+\end{minipage}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
- \subsection{Soundness and Completeness} \label{Appendix-SoundComplete}
+ \section{Soundness and Completeness} \label{Appendix-SoundComplete}
 %  \vspace{-0.1in}
@@
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Nested Until and Release Rewriting Theorem} \label{Appendix-NestedUR}
+\section{Nested Until and Release Rewriting Theorem} \label{Appendix-NestedUR}
 
@@
 To compute the satisfying computations of an MLTL formula, many of the functions in the WEST program require the regular expressions of the satisfying computations of the subformulas as inputs.
-We denote these regexes by $R$ and $B$, where $R = R_1 | R_2 | ...
-| R_k$ is represented as a vector of strings $R = {R_1, R_2, ..., R_k}$, and $B = B_1 | B_2 | ...
-| B_\ell$ is represented as a vector of strings $B = {B_1, B_2, ..., B_\ell}$.
+We denote these regexes by $R$ and $T$, where $R = R_1 | R_2 | ...
+| R_k$ is represented as a vector of strings $R = {R_1, R_2, ..., R_k}$, and $T = T_1 | T_2 | ...
+| T_\ell$ is represented as a vector of strings $T = {T_1, T_2, ..., T_\ell}$.
 Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.
@@
 \caption{Pad a vector to elements of all equal length}
-Input: Vector of strings that represents a regex, number of propositional variables \\
-Output: Vector of strings padded to equal length
+%Input: Vector of strings that represents a regex, number of propositional variables \\
+%Output: Vector of strings padded to equal length
 \begin{algorithmic}
 \Procedure{Pad}{vector $R$, int $n$} 
-    \State max\_Length $\leftarrow$ $max_{\{r \in R\}}$($r$.length()) \Comment{determines length to pad all strings to}
+    \State max\_Length $\leftarrow$ $\max_{\{r \in R\}}$($r$.length())
     \For{($r \in R$)}
         \State diff $\leftarrow$ (max\_length$- r$.length()) / $(n+1)$ 
-        \Comment{determines how many $S^n$s to append}
         \State  $r \leftarrow r + (,S^n)^{\text{diff}}$
@@
 \caption{Computes regex for propositional constant}
-Input: String that is either ``T" or ``!", number of propositional variables\\
-Output: Vector of strings that represents the appropriate satisfying computations
+%Input: String that is either ``T" or ``!", number of propositional variables\\
+%Output: Vector of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
 \Procedure{reg\_prop\_cons}{string nnf, int $n$}
-    \If {(nnf $=$ ``T" and $n \neq 0$)}
-        \State return $\{S^n\}$ \Comment{regex of satisfying computations for ``T"}
-    \Else 
-        \State return $\{\}$ \Comment{regex of satisfying computations for ``!"}
+    \If {(nnf $=$ ``T" and $n \neq 0$)} return $\{S^n\}$
+    \Else \hspace{1mm} return $\{\}$ 
     \EndIf
@@
 \caption{Output the vector of computation satisfying a propositional variable.}
-Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
-Output: Vector of strings that represents the appropriate satisfying computations
+%Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
+%Output: Vector of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
 \Procedure{reg\_prop\_var}{string nnf, int $n$}
-    \If {(nnf $=$ ``p$k$", where $k$ is a nonnegative integer)}
-        \State return $\{S^k1S^{n-k-1}\}$ \Comment{regex of satisfying computations for ``p$k$"}
-    \EndIf 
-    \If {(nnf $=$ ``$\scriptstyle{\sim}$p$k$", where $k$ is a nonnegative integer)}
-        \State return $\{S^k0S^{n-k-1}\}$ \Comment{regex of satisfying computations for ``$\scriptstyle{\sim}$p$k$"}
+    \If {(nnf $=$ ``p$k$", where $k$ is a nonnegative integer)} return $\{S^k1S^{n-k-1}\}$
+    \EndIf 
+    \If {(nnf $=$ ``$\scriptstyle{\sim}$p$k$", where $k$ is a nonnegative integer)} return $\{S^k0S^{n-k-1}\}$
     \EndIf
@@
 \caption{Combines two strings that differ only by one character into one}
-Input: Two strings that represent regexes\\
-Output: Single string that represents computations represented by both input strings or FAIL
+%Input: Two strings that represent regexes\\
+%Output: Single string that represents computations represented by both input strings or FAIL
 \begin{algorithmic}
-\Procedure{simplify\_string}{string $r$, string $b$}   
-    \If{($r$.length() $\neq$ $b$.length())}
-        \State exit \Comment{cannot compare strings if they differ in length}
+\Procedure{simplify\_string}{string $r$, string $t$}   
+    \If{($r$.length() $\neq$ $t$.length())} exit
         \EndIf
     \For{($0 \leq i < r$.length())}
-        \State pre\_r $\leftarrow r[0, i-1]$ \Comment{stores string $r$ up to comparison character}
-        \State char\_r $\leftarrow r[i]$ \Comment{stores character to compare in $r$}
-        \State post\_r $\leftarrow r[i+1, r\text{.length()}-1]$ \Comment{stores remaining part of string $r$}
-        \\
-        \State pre\_b $\leftarrow b[0, i-1]$ \Comment{stores string $b$ up to comparison character}
-        \State char\_b $\leftarrow b[i]$ \Comment{stores character to compare in $b$}
-        \State post\_b $\leftarrow b[i+1, b\text{.length()}-1]$ \Comment{stores remaining part of string $b$}
-        \\
-        \If{(pre\_r $=$ pre\_b and post\_r $=$ post\_b)} \Comment{\parbox[t]{.4\linewidth}{checks that strings $r$ and $b$ match for all but one character}}
-            \If{(char\_r $\neq$ char\_b)}
-                \State return pre\_r +``$S$" + post\_r \Comment{\parbox[t]{.5\linewidth}{if the comparison characters differ, replace character with $``S"$}}
+        \State pre\_r $\leftarrow r[0, i-1]$ 
+        \State char\_r $\leftarrow r[i]$ 
+        \State post\_r $\leftarrow r[i+1, r\text{.length()}-1]$ 
+        \State pre\_t $\leftarrow t[0, i-1]$ 
+        \State char\_t $\leftarrow t[i]$ 
+        \State post\_t $\leftarrow t[i+1, t\text{.length()}-1]$
+        \If{(pre\_r $=$ pre\_t and post\_r $=$ post\_t)}
+            \If{(char\_r $\neq$ char\_t)}
+                \State return pre\_r +``$S$" + post\_r 
             \Else
-                \State return $r$ \Comment{if the comparison character match, strings are identical}
+                \State return $r$
             \EndIf
@@
     \State return FAIL 
-    \Comment{Indicates strings differed by more than one character}
 \EndProcedure
@@
 \caption{Simplifies a vector of strings using simplify\_string}
-Input: Vector of strings representing a regex\\
-Output: Vector of strings representing a regex simplified using simplify\_string
+%Input: Vector of strings representing a regex\\
+%Output: Vector of strings representing a regex simplified using simplify\_string
 \begin{algorithmic}
 \Procedure{simplify}{vector $R$}    
-    \State Pad all strings in $R$ to the same length \Comment{ensures all inputs to simplify\_string are valid}
-    \If{($R$.length() $\leq 1$)}
-        \State return $R$ \Comment{insufficient strings in $R$ to use simplify\_string}
-        \EndIf
-
+    \State Pad all strings in $R$ to the same length
+    \If{($R$.length() $\leq 1$)} return $R$
+        \EndIf
     \State $i = R\text{.length} - 1$
@@
         \While{($j \geq 0$)}
-            \State simplified = simplify\_string($R[i]$, $R[j]$) \Comment{\parbox[t]{.4\linewidth}{for each combination of strings in $R$, apply simplify\_string}}
+            \State simplified = simplify\_string($R[i]$, $R[j]$) 
             \If{(simplified $\neq$ FAIL)}
-                \State replace string at index $j$ with simplified \Comment{updating $R[j]$ to be combined string}
-                \State remove string at index $i$ from $R$ \Comment{remove $R[i]$, as it's redundant}
+                \State replace string at index $j$ with simplified
+                \State remove string at index $i$ from $R$
                 \State $i = R\text{.length()} - 1$
@@
                 \EndIf
-
             \State -{}-$j$
             \EndWhile
-
         \State -{}-$i$
@@
 \caption{Takes the intersection of two computations}
-Input: Two strings representing regexes\\
-Output: Bitwise AND of the inputted strings
+%Input: Two strings representing regexes\\
+%Output: Bitwise AND of the inputted strings
 \begin{algorithmic}
-\Procedure{bit\_wise\_and}{string $r$, string $b$}
-    \State ret $\leftarrow$ ``" \Comment{initializing string to store bitwise AND}
+\Procedure{bit\_wise\_and}{string $r$, string $t$}
+    \State ret $\leftarrow$ ``" 
     \For {(i $\in [0, \ r\text{.length()}]$)}
-        \If{($r[i] \land$ $b[i] = ``"$)}
-        \State return ``" \Comment{if bitwise AND is ever empty, entire string intersection is empty}
-        \Else 
-        \State ret $\leftarrow$ ret $+$ $r[i] \land b[i]$ \Comment{for each character, store bitwise AND}
+        \If{($r[i] \land$ $t[i] = ``"$)} return ``"
+        \Else \hspace{1mm} ret $\leftarrow$ ret $+$ $r[i] \land t[i]$
         \EndIf
@@
 \end{algorithm}
+
 \begin{algorithm}[H]
-\caption{Takes set intersection of the languages of two regexes}
-Input: Vectors of strings that represent regexes, simplify boolean\\
-Output: Vector of strings that represents set intersection of the languages of the inputted regexes
+\caption{Takes union of two regexes (combines two vectors into one)}
+%Input: Vectors of strings that represent regexes, simplify boolean\\
+%Output: Vector of strings that represents union of inputted regexes
 \begin{algorithmic}
-\Procedure{set\_intersect}{vector $R$, vector $B$, bool simp}
-    \State Pad $R$ and $B$ to the same length
-    \State ret $\leftarrow \{\}$ \Comment{initializing a vector of strings to store set intersection}
-    \For{($r \in R$)}
-        \For{($b \in B$)} \Comment{take bitwise AND of every combination of strings from $R$ and $B$}
-            \State add bit\_wise\_and($r, b$) to ret 
-            \Comment{store results in ret}
+\Procedure{join}{vector $R$, vector $T$, bool simp}
+    \State ret $\leftarrow \{\}$
+    \For{($r \in R$)} add $r$ to ret
     \EndFor
+    \For{($t \in T$)} add $t$ to ret
     \EndFor
-    \If{(simp is true)}
-    \State return simplify(ret) \Comment{if user requests simplified output, run ret through simplify}
-    \Else
-    \State return ret
+    \If{(simp is true)} return simplify(ret)
+    \Else \hspace{1mm}return ret
     \EndIf
@@
 \begin{algorithm}[H]
-\caption{Takes union of two regexes (combines two vectors into one)}
-Input: Vectors of strings that represent regexes, simplify boolean\\
-Output: Vector of strings that represents union of inputted regexes
+\caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
+% Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
+% Output: Vector of strings that represents the appropriate satisfying computations 
 \begin{algorithmic}
-\Procedure{join}{vector $R$, vector $B$, bool simp}
-    \State ret $\leftarrow \{\}$ \Comment{initializing a vector of strings to store union}
-    \For{($r \in R$)}
-        \State add $r$ to ret \Comment{add all vectors in $R$ to ret}
+\Procedure{reg\_F}{vector reg\_phi, int $a$, int $b$, int $n$, bool simp} 
+    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
+    \State comp $\leftarrow$ reg\_phi
+    \If{$a > b$} return $\{\}$
+    \EndIf
+    \For{($1 \leq i \leq b-a$) }
+        \State temp\_phi $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_phi
+        \State comp $\leftarrow$ join(comp, temp\_phi, simp)
     \EndFor
-    \For{($b \in B$)}
-        \State add $b$ to ret \Comment{add all vectors in $B$ to ret}
-    \EndFor
-    \If{(simp is true)}
-    \State return simplify(ret) \Comment{if user requests simplified output, run ret through simplify}
-    \Else
-    \State return ret
-    \EndIf
+    \State return pre + comp
 \EndProcedure
@@
 \caption{Computes the regex for a MLTL formula G[a:b]$\phi$}
-Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: Vector of strings that represents the appropriate satisfying computations
+%Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
+%Output: Vector of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
-\Procedure{reg\_G}{vector reg\_alpha, int $a$, int $b$, int $n$, bool simp} 
-    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$ \Comment{before the start of the interval, computation is arbitrary}
-    \State comp $\leftarrow$ reg\_alpha \Comment{\parbox[t]{.7\linewidth}{initializing vector of strings for outputted regex with subformula regex}}
-    \If{$a > b$} \Comment{empty interval, Global is trivially true}
-        \State return $\{S^n\}$
-    \EndIf
-    \For{($1 \leq i \leq b-a$)} \Comment{computing $\bigwedge_{i=1}^{b-a} (S^n,)^i \text{reg}(\phi)$}
-        \State temp\_alpha $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_alpha
-        \State comp $\leftarrow$ set\_intersect(comp, temp\_alpha, simp)
+\Procedure{reg\_G}{vector reg\_phi, int $a$, int $b$, int $n$, bool simp} 
+    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
+    \State comp $\leftarrow$ reg\_phi 
+    \If{$a > b$} return $\{S^n\}$
+    \EndIf
+    \For{($1 \leq i \leq b-a$)}
+        \State temp\_phi $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_phi
+        \State comp $\leftarrow$ set\_intersect(comp, temp\_phi, simp)
     \EndFor
-    \State return pre + comp \Comment{\parbox[t]{.6\linewidth}{prepending string pre to every string in comp; result is regex for Global defined in section \ref{regex}}}
+    \State return pre + comp
 \EndProcedure
@@
 \end{algorithm}
-
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
-Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: Vector of strings that represents the appropriate satisfying computations 
+\caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
+%Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
+%Output: Vector of strings that represents the appropriate satisfying computations 
 \begin{algorithmic}
-\Procedure{reg\_F}{vector reg\_alpha, int $a$, int $b$, int $n$, bool simp} 
-    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$ \Comment{before the start of the interval, computation is arbitrary}
-    \State comp $\leftarrow$ reg\_alpha \Comment{\parbox[t]{.7\linewidth}{initializing vector of strings for outputted regex with subformula regex}}
-    \If{$a > b$} \Comment{empty interval, Finally is trivially false}
-        \State return $\{\}$
-    \EndIf
-    \For{($1 \leq i \leq b-a$) } \Comment{computing $\bigvee_{i=1}^{b-a} (S^n,)^i \text{reg}(\phi)$}
-        \State temp\_alpha $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_alpha
-        \State comp $\leftarrow$ join(comp, temp\_alpha, simp)
-    \EndFor
-    \State return pre + comp \Comment{\parbox[t]{.6\linewidth}{prepending string pre to every string in comp; result is regex for Finally defined in section \ref{regex}}}
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\label{regU}
-\begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\phi$U[a:b]$\psi$} 
-Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: Vector of strings that represents the appropriate satisfying computations 
-\begin{algorithmic}
-\Procedure{reg\_U}{vector reg\_alpha, vector reg\_beta int $a$, int $b$, int $n$, bool simp} 
-    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ reg\_beta \Comment{\parbox[t]{.55\linewidth}{initializing vector of strings for outputted regex with regex for beta, prepended with $`S'$s up to start of interval}}
-    \If{$a > b$}
-        \State return $\{\}$ \Comment{empty interval, Until is trivially false}
-    \EndIf
-    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$, loop ends at $b-1$ because comp is initialized to $i=a$ case and loop is reindexed}}\\
-        \State{\parbox[t]{.9\linewidth}{temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_alpha, $a$, $i$, $n$), reg\_G(reg\_beta, $i+1$, $i+1$, $n$), $n$, simp)}}
+\Procedure{reg\_R}{vector reg\_phi, vector reg\_psi, int $a$, int $b$, int $n$, bool simp} 
+    \State comp $\leftarrow$ reg\_G(reg\_psi, $a$, $b$, $n$, simp)
+    \If{$a > b$} return $\{S^n\}$
+    \EndIf
+    \For{($a \leq i \leq b-1$) }
+        \State temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_psi, $a$, $i$, $n$), reg\_G(reg\_phi, $i$, $i$, $n$), $n$, simp)
         \State comp $\leftarrow$ join(comp, temp\_comp, simp)
     \EndFor
-
     \State return comp
@@
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
-Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: Vector of strings that represents the appropriate satisfying computations 
-\begin{algorithmic}
-\Procedure{reg\_R}{vector reg\_alpha, vector reg\_beta int $a$, int $b$, int $n$, bool simp} 
-    \State comp $\leftarrow$ reg\_G(reg\_beta, $a$, $b$, $n$, simp)
-    \Comment{\parbox[t]{.5\linewidth}{initializing vector of strings for output regex with regex for G[a:b]$\psi$}}
-    \If{$a > b$}
-        \State return $\{S^n\}$
-        \Comment empty interval, Release is trivially true
-    \EndIf
-    \For{($a \leq i \leq b-1$) } \Comment{\parbox[t]{.65\linewidth}{computing $\text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$, first run through loop includes $\text{reg}\left(\mathcal{G}_{[a,b]}\psi\right)$}}\\
-        \State temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_beta, $a$, $i$, $n$), reg\_G(reg\_alpha, $i$, $i$, $n$), $n$, simp)
-        \State comp $\leftarrow$ join(comp, temp\_comp, simp)
-    \EndFor
-
-    \State return comp
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Computes the regex for an MLTL formula in NNF}
-Inputs: MLTL formula in negation normal form, number of propositional variables, boolean sub for storing subformula computations in global variable FORMULAS, simplify boolean\\
-Output: Vector of strings that represents the appropriate satisfying computations
-\begin{algorithmic}
-\Procedure{reg}{string nnf, int $n$, bool sub, bool simp} 
-    \If{(nnf is a prop. var. or $\scriptstyle{\sim}$prop. var)}
-        \If{(sub)}
-            \State Run reg on formula and store formula with its regular expression
-        \EndIf
-        \State return reg\_prop\_var(nnf, $n$)
-        \Comment call helper function for propositional variable
-    \EndIf\\
-    \If{(nnf is $T$ or $!$)}
-        \If{(sub)}
-            \State Run reg on formula and store formula with its regular expression
-        \EndIf
-        \State return reg\_prop\_cons(nnf, $n$)
-        \Comment call helper function for propositional constant
-    \EndIf
-    \\
-    \If{(nnf is of the form unary\_temp\_conn interval alpha)}
-        \State unary\_temp\_conn $\leftarrow$ unary\_temp\_conn in nnf
-        \Comment parse formula to find unary operator
-        \State $a$ $\leftarrow$ start of interval
-        \State $b$ $\leftarrow$ end of interval
-        \State reg\_alpha $\leftarrow$ reg(alpha, $n$, sub, simp)
-        \Comment recursive call to reg on subformula\\
-        \If{(unary\_temp\_conn $=$ `F')}
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return reg\_F(reg\_alpha, $a$, $b$, $n$, simp)
-            \Comment Call helper function for Finally operator
-        \EndIf\\
-        \If{(unary\_temp\_conn $=$ `G')}
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return reg\_G(reg\_alpha, $a$, $b$, $n$, simp)
-            \Comment Call helper function for Global operator
-        \EndIf
-    \EndIf
-    \\
-    \If{(nnf is of the form ``(Assoc\_prop\_conn[nnf\_array])")}
-    \Comment{Rewrite nnf in non-array form}
-        \State assoc\_prop\_conn $\leftarrow$ assoc\_prop\_conn in nnf
-        \State equiv\_formula $\leftarrow$ ``" 
-        \Comment For instance, $\&[\phi_1, \phi_2, \phi_3]$ is rewritten to $((\phi_1 \& \phi_2) \& \phi_3)$
-        \For{(array entry alpha in nnf\_array)}
-            \If{(alpha is first entry)}
-                \State equiv\_formula $\leftarrow$ alpha
-                \Comment First entry doesn't need parentheses
-            \Else
-                \State equiv\_formula $=$ ``(" + equiv\_formula + assoc\_prop\_conn + alpha + ``)"
-            \EndIf
-        \EndFor
-        \If{(sub)}
-            \State Run reg on formula and store formula with its regular expression
-        \EndIf
-        \State return reg(equiv\_formula, $n$, sub, simp)
-        \Comment recursively call reg on the rewritten formula
-    \EndIf
-    \algstore{myalg}
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\begin{algorithmic}
-\algrestore{myalg}
-    \If{(nnf is of the form alpha binary\_prop\_conn beta)}
-        \State binary\_prop\_conn $\leftarrow$ binary\_prop\_conn in nnf
-        \Comment parse formula to find binary operator
-        \State reg\_alpha $\leftarrow$ reg(alpha, $n$, sub, simp)
-        \Comment recursive call to reg on subformula
-        \State reg\_beta $\leftarrow$ reg(beta, $n$, sub, simp)
-        \Comment recursive call to reg on subformula\\
-        \If{(binary\_prop\_conn $=$ ``\&")}
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return set\_intersect(reg\_alpha, reg\_beta, $n$, simp)
-            \Comment Call helper function for \& operator
-        \EndIf\\
-        \If{(binary\_prop\_conn $=$ ``$\lor$")}
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return join(reg\_alpha, reg\_beta, $n$, simp)
-            \Comment Call helper function for $\lor$ operator
-        \EndIf\\
-        \If{(binary\_prop\_conn $=$ ``=")}
-            \Comment{Rewrite in terms of OR, AND, and NOT}
-            \State equiv\_formula $=$ ``((" + alpha + ``\&" + beta + ``)$\lor$(" + wff\_to\_nnf($\scriptstyle{\sim}$alpha) + 
-            \State ``\&" + wff\_to\_nnf($\scriptstyle{\sim}$beta) + ``))"
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return reg(equiv\_formula, $n$, sub, simp)
-            \Comment recursive call to reg on rewritten formula
-        \EndIf\\
-        \If{(binary\_prop\_conn $=$ ``\textgreater")}
-            \Comment{Rewrite in terms of OR, AND, and NOT}
-            \State equiv\_formula $=$ ``(" + wff\_to\_nnf($\scriptstyle{\sim}$alpha) + "$\lor$" + beta + ``)"
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return reg(equiv\_formula, $n$, sub, simp)
-            \Comment recursive call to reg on rewritten formula
-        \EndIf
-    \EndIf\\
-   \If{(nnf is of the form alpha binary\_temp\_conn interval beta)}
-        \State binary\_temp\_conn $\leftarrow$ binary\_temp\_conn in nnf
-        \Comment parse for binary operator
-        \State $a$ $\leftarrow$ start of interval
-        \State $b$ $\leftarrow$ end of interval
-        \State reg\_alpha $\leftarrow$ reg(alpha, $n$, sub, simp)
-        \Comment recursive call to reg on subformula
-        \State reg\_beta $\leftarrow$ reg(beta, $n$, sub, simp)
-        \Comment recursive call to reg on subformula
-        \\
-        \If{(binary\_temp\_conn $=$ `U')}
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return reg\_U(reg\_alpha, reg\_beta, $a$, $b$, $n$, simp)
-            \Comment Call helper function for Until\\
-        \ElsIf{(binary\_temp\_conn $=$ `R')}
-            \If{(sub)}
-                \State Run reg on formula and store formula with its regular expression
-            \EndIf
-            \State return reg\_R(reg\_alpha, reg\_beta, $a$, $b$, $n$, simp)
-            \Comment Call helper function for Release
-        \EndIf
-    \EndIf\\
-    \State Throw exception \Comment{\parbox[t]{.7\linewidth}{If none of the previous statements held, there's an error with the formula nnf}}
-    \State return \{\}
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
     \caption{Generates test suite template without propositional constants, propositional variables, or negations of propositional variables filled in}
-    Inputs: Depth of desired test suite template to generate, interval bounds\\
-    Output: Vector of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
+    %Inputs: Depth of desired test suite template to generate, interval bounds\\
+    %Output: Vector of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
     \begin{algorithmic}
         \Procedure{generate\_test\_template}{int depth, int $a$, int $b$}
-        \If{(depth = 0)}
-            \State return $\{p, q\}$
-            \Comment{\parbox[t]{.54\linewidth}{$p$ represents a propositional variable or its negation, $q$ represents a propositional constant}}
-        \EndIf
-
+        \If{(depth = 0)} return $\{p, q\}$
+        \EndIf
         \State template $\leftarrow \{\}$
-        \Comment initialize variable to store final template
         \State $V \leftarrow$ generate\_test\_template(depth$- 1$, $a$, $b$)
-        \Comment{\parbox[t]{.45\linewidth}{recursively generate all formulas of $1$ lower depth}}
         \For{(string $\phi \in V$)}
@@
             \State add ``F[a:b]" + $\phi$ to template
-            \Comment Add unary temporal operators to template
             \For{string $\psi \in V$}
@@
                 \State add $\phi$ + ``\&" + $\psi$ to template
-                \Comment add binary operators to template
             \EndFor
@@
     \caption{Generates a complete test suite of MLTL formulas in negation normal form up to a certain depth}
-    Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
-    Output: Vector of MLTL formulas
+    %Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
+    %Output: Vector of MLTL formulas
     \begin{algorithmic}
@@
                 \If{ch $ = p$}
-                \Comment{\parbox[t]{.52\linewidth}{replace $a$ with a random propositional variable or the negation of a random propositional variable}}
                     \State $k \leftarrow \text{rand()} \% n$ 
-                    \Comment assign $k$ as a random int between $0$ and $n - 1$
-                    \If{rand() $\% 2 = 0$}
-                    \Comment imitate randomness of a coin toss
-                        \State replace ch with p$k$
-                    \Else 
-                        \State replace ch with $\scriptstyle{\sim}$p$k$
+                    \If{rand() $\% 2 = 0$} replace ch with p$k$
+                    \Else \hspace{1mm}replace ch with $\scriptstyle{\sim}$p$k$
                     \EndIf
                 \ElsIf{ch $= q$}
-                \Comment Replace $q$ with a random propositional constant
-                    \If{rand() $\% 2 = 0$}
-                        \State replace ch with T
-                    \Else 
-                        \State replace ch with $!$
+                    \If{rand() $\% 2 = 0$} replace ch with T
+                    \Else \hspace{1mm}replace ch with $!$
                     \EndIf
@@
 \end{algorithm}
-\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{State Diagram Graphs} \label{graphs appendix}
-Below we provide the graphs of state diagrams of the critical functions examined in our intelligent fuzzing.
-In general, nodes in the graph represent portions of the code without control flow statements.
-As a result, a single node can represent large chunks of code.
+\vspace{-1.5cm}
+Below we provide the state diagram graphs of the functions examined in our intelligent fuzzing.
+Nodes in the graph represent portions of the code without control flow statements, so a single node can represent large chunks of code.
 Directed edges represent branching of control flow, such as IF statements and loops.
 Each graph directly corresponds with the pseudocode of their corresponding function, with nodes and edges being labeled accordingly.
-Note that these graphs, the option to run the \textit{simplify} function has been omitted for clarity.
-For the graph of the \textit{reg} function, the option to store subformulas has been omitted as well.\\
+Note that the option to run \textit{simplify} has been omitted for clarity.\\
+
+\begin{minipage}{0.4\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{7cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     \node[emptynode](empty_vector)[rotate=-70, left=1cm of body]{R $=\{\}$};
-    \node[emptynode](for_loop)[right=.75cm of body]{for r in R};
+    \node[emptynode](for_loop)[right=1.1cm of body]{for r in R};
     \node[node](return)[below=of body]{return R};
@@
     \end{tikzpicture}
-
+    }
     \caption{Pad Function}
@@
 \end{figure}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{8.5cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){strings r, b};
+    \node[emptynode](inputs){strings r, t};
     \node[node](initialize)[below=of inputs]{Initialize string Ret};
@@
     \node[emptynode](placeholder)[below=0.05cm of loop_entry]{};
-    \node[emptynode](emptytext)[rotate=35, left=.75cm of placeholder]{\small{r$[i] \land$ b$[i] = ``"$}};
+    \node[emptynode](emptytext)[rotate=35, left=.75cm of placeholder]{\small{r$[i] \land$ t$[i] = ``"$}};
     \node[emptynode](placeholder2)[below=0.05cm of placeholder]{};
@@
     \end{tikzpicture}
+    }
     \caption{Bitwise\_And Function}
@@
 \end{figure}
+\end{minipage}
+
+\begin{minipage}{0.5\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{8cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){vectors R, B};
+    \node[emptynode](inputs){vectors R, T};
     \node[node](initialize)[below=of inputs]{Initialize vector Ret};
     \node[node](add_r)[below=of initialize]{Add r to Ret};
-    \node[node](add_t)[below=of add_r]{Add b to Ret};
+    \node[node](add_t)[below=of add_r]{Add t to Ret};
     \node[node](return)[below=of add_t]{return Ret};
-    \node[emptynode](rtext)[right=of add_r]{for string r$\in$R};
-    \node[emptynode](ttext)[left=of add_t]{for string b$\in$B};
+    \node[emptynode](rtext)[right=1.2cm of add_r]{for string r$\in$R};
+    \node[emptynode](ttext)[left=1.2cm of add_t]{for string t$\in$T};
 
@@
     \end{tikzpicture}
+    }
     \caption{Join Function}
@@
 \end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}{0.5\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{8cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){vectors R,B};
-    \node[node](initialize)[below=of inputs]{Pad R and B, Initialize vector Ret=\{\}};
+    \node[emptynode](inputs){vectors R,T};
+    \node[node](initialize)[below=of inputs]{Pad R and T, Initialize vector Ret=\{\}};
     \node[node](outer_loop)[below=of initialize]{Outer Loop Entry};
@@
     \node[node](return)[below=of outer_exit]{return Ret};
-    \node[emptynode](inner_text)[right=1.25cm of inner_loop]{for b$\in$B};
+    \node[emptynode](inner_text)[right=1.25cm of inner_loop]{for t$\in$T};
     \node[emptynode](outer_text)[left=2.25 cm of inner_loop]{for r$\in$R};
@@
     \end{tikzpicture}
+    }
     \caption{Set\_Intersect Function}
@@
 \end{figure}
-\newpage
+\end{minipage}
+
+\begin{minipage}{0.4\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){vector reg\_alpha, integers a, b, n};
+    \node[emptynode](inputs){vector reg\_phi, integers a, b, n};
     \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
@@
     \node[node](return)[below=of loop]{return pre + Comp};
-    \node[emptynode](loop_text)[right= of loop]{for $i \in [1, \text{b}-\text{a}]$};
+    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [1, \text{b}-\text{a}]$};
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
@@
     \end{tikzpicture}
-
+    }
     \caption{Reg\_F Function}
@@
 \end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     \end{tikzpicture}
-
+    }
     \caption{Reg\_G Function}
@@
 \end{figure}
+\end{minipage}
+\vfill
+\begin{minipage}{0.4\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){vector reg\_alpha, reg\_beta and integers a, b, n};
+    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
     \node[node](initialize)[below=of inputs]{Initialize vector Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};
-    \node[node](empty)[left=of loop]{return \{$S^n$\}};
+    \node[node](empty)[left=of loop]{return \{\}};
     \node[node](return)[below=of loop]{return Comp};
-    \node[emptynode](loop_text)[right= of loop]{for $i \in [\text{a}, \text{b}-1]$};
+    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
@@
     \end{tikzpicture}
-
-    \caption{Reg\_R Function}
-    \label{fig:reg_r graph}
+    }
+    \caption{Reg\_U Function}
+    \label{fig:reg_u graph}
 \end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}{0.4\textwidth}
 \begin{figure}[H]
     \centering
+    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){vector reg\_alpha, reg\_beta and integers a, b, n};
+    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
     \node[node](initialize)[below=of inputs]{Initialize vector Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};
-    \node[node](empty)[left=of loop]{return \{\}};
+    \node[node](empty)[left=of loop]{return \{$S^n$\}};
     \node[node](return)[below=of loop]{return Comp};
-    \node[emptynode](loop_text)[right= of loop]{for $i \in [\text{a}, \text{b}-1]$};
+    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
@@
     \end{tikzpicture}
-
-    \caption{Reg\_U Function}
-    \label{fig:reg_u graph}
+    }
+    \caption{Reg\_R Function}
+    \label{fig:reg_r graph}
 \end{figure}
+\end{minipage}
+
 \begin{landscape}
+
 \begin{figure}[htbp]
     \centering
+    \resizebox{20cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, text width=3cm,text centered, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none,text width=3cm,text centered, very thick, minimum size=1mm}, rednode/.style={rounded rectangle, draw=red!60, fill=red!5, text width=3cm,text centered, very thick, minimum size=15mm}]
@@
 
-    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, alpha and call reg(alpha, n)};
-    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F(alpha)};
-    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G(alpha)};
-
-    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, alpha, beta};
-    \node[rednode](prop_alpha)[below=of parse_binary_prop]{reg\_alpha $\leftarrow$ reg(alpha,n)};
-    \node[rednode](prop_beta)[below=of prop_alpha]{reg\_beta $\leftarrow$ reg(beta,n)};
-    \node[rednode](equals)[left=0.5cm of prop_beta]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};
-    \node[node](set_intersect)[below=of prop_beta]{return set\_intersect};
+    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, phi and call reg(phi, n)};
+    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F(phi)};
+    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G(phi)};
+
+    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, phi, psi};
+    \node[rednode](prop_phi)[below=of parse_binary_prop]{reg\_phi $\leftarrow$ reg(phi,n)};
+    \node[rednode](prop_psi)[below=of prop_phi]{reg\_psi $\leftarrow$ reg(psi,n)};
+    \node[rednode](equals)[left=0.5cm of prop_psi]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};
+    \node[node](set_intersect)[below=of prop_psi]{return set\_intersect};
     \node[node](join)[left=of set_intersect]{return join};
@@
 
-    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, alpha, beta};
-    \node[rednode](temp_alpha)[below=of parse_binary_temp]{reg\_alpha $\leftarrow$ reg(alpha,n)};
-    \node[rednode](temp_beta)[below=of temp_alpha]{reg\_beta $\leftarrow$ reg(beta,n)};
-    \node[node](until)[below=of temp_beta]{return reg\_U};
+    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, phi, psi};
+    \node[rednode](temp_phi)[below=of parse_binary_temp]{reg\_phi $\leftarrow$ reg(phi,n)};
+    \node[rednode](temp_psi)[below=of temp_phi]{reg\_psi $\leftarrow$ reg(psi,n)};
+    \node[node](until)[below=of temp_psi]{return reg\_U};
     \node[node](release)[right=of until]{return reg\_R};
@@
 
-    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] alpha}};
+    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] phi}};
     \node[emptynode](reg_g_text)[above=0.2cm of reg_g]{X is G};
@@
 
-    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is alpha X[a,b] beta}};
+    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is phi X[a,b] psi}$$~$$};
     \node[emptynode](release_text)[above=0.2cm of release]{X is R};
@@
     \node[emptynode](assoc_text)[rotate=45, above=1.1cm of binary_temp_text]{\footnotesize{nnf is X[nnf\_array]}};
-    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for alpha in nnf\_array};
-
-    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is alpha X beta};
+    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for phi in nnf\_array};
+
+    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is phi X psi};
     \node[emptynode](join_text)[above=0.2cm of join]{X is v};
     \node[emptynode](intersect_text)[right=1.75cm of join_text]{X is \&};
-    \node[emptynode](implies_text)[right=-0.25cm of prop_beta]{X is $>$};
+    \node[emptynode](implies_text)[right=-0.25cm of prop_psi]{X is $>$};
     \node[emptynode](equals_text)[right=-1.2cm of reg_f_text]{X is =};
@@
     \draw[->] (start.south) -- (parse_binary_prop.north);
-    \draw[->] (parse_binary_prop.south) -- (prop_alpha.north);
-    \draw[->] (prop_alpha.south) -- (prop_beta.north);
-    \draw[->] (prop_beta.south) -- (set_intersect.north);
-    \draw[->] (prop_beta.south) -- (join.north);
+    \draw[->] (parse_binary_prop.south) -- (prop_phi.north);
+    \draw[->] (prop_phi.south) -- (prop_psi.north);
+    \draw[->] (prop_psi.south) -- (set_intersect.north);
+    \draw[->] (prop_psi.south) -- (join.north);
     \draw[->] (parse_binary_prop.east) .. controls +(down:2cm) .. (implies.north);
@@
     \draw[->] (start.east) -- (parse_binary_temp.west);
-    \draw[->] (parse_binary_temp.south) -- (temp_alpha.north);
-    \draw[->] (temp_alpha.south) -- (temp_beta.north);
-    \draw[->] (temp_beta.south) -- (until.north);
-    \draw[->] (temp_beta.south) -- (release.north);
+    \draw[->] (parse_binary_temp.south) -- (temp_phi.north);
+    \draw[->] (temp_phi.south) -- (temp_psi.north);
+    \draw[->] (temp_psi.south) -- (until.north);
+    \draw[->] (temp_psi.south) -- (release.north);
     \draw[->] (start.east) -- (parse_assoc.west);
@@
     \end{tikzpicture}
+    }
+    $$~$$
     \caption{Control Flow of Reg. Red nodes indicate a recursive call to Reg.}

### 2022-10-12 paper/Paper.tex
small changes
fixed proof of correctness of WEST, added input / output to the 3 algorithms

@@
 \section{WEST Algorithm and Analysis} \label{WESTalg}
-We now present the  full WEST algorithm, which takes MLTL formula $\phi$ (in NNF) and number of propositional variables $n$, and recursively computes all satisfying temporal regular expressions to $\phi$.
+We now present the  full WEST algorithm, which recursively computes all satisfying temporal regular expressions to a given MLTL formula (in NNF). 
 We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
@@
 This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
-Although set intersection does blow up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
-We simplify alternation by using the fact that for regular expressions $w_1$ and $w_2$, $w_1 1 w_2 \lor w_1 0 w_2 = w_1 s w_2$, and check for the reduction between at every index between every pair of strings in a given vector.
+Although repeated set intersection blows up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
+We simplify alternation by using the fact that for regular expressions $w_1$ and $w_2$, $\mathscr{L}(w_1 1 w_2 \lor w_1 0 w_2) = \mathscr{L}(w_1 s w_2)$, and check if the reduction applies at every index between every pair of strings in a given vector.
 
@@
 \begin{algorithm}[H]
-\caption{WEST Algorithm}
+\caption{WEST Algorithm \\
+Inputs: $\phi$ - MLTL formula in NNF \\
+$\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
+$n$ - number of propositional variables \\
+Output: Vector of REGEX satsfying $\phi$}
 \begin{algorithmic}[1]
@@
 \end{algorithm}
+\vspace{5.9mm}
 \end{minipage}
@@
 \begin{algorithm}[H]
-\caption{Takes set intersection of the languages of two regexes}
-%Input: Vectors of strings that represent regexes, simplify boolean\\
-%Output: Vector of strings that represents set intersection of the languages of the inputted regexes
-\begin{algorithmic}
-\Procedure{set\_intersect}{vector $R$, vector $T$, bool simp}
-    \State Pad($R$, $T$), return $\leftarrow \{\}$
+\caption{set\_intersect}
+Inputs: $R, T$ - Two Vectors of REGEX\\
+$n$ - number of propositional variables\\
+Output: Vector equal to $R \land T$
+\begin{algorithmic}[1]
+\Procedure{set\_intersect}{$R$, $T$, n}
+    \State Pad($R$, $T$, n), return $\leftarrow \{\}$
     \For{$(r, t) \in R\times T$}
@@
 \end{algorithm}
+\vspace{-6.5mm}
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\phi$U[a:b]$\psi$} 
-%Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
-%Output: Vector of strings that represents the appropriate satisfying computations 
-\begin{algorithmic}
-\Procedure{reg\_U}{vector reg\_phi, vector reg\_psi int $a$, int $b$, int $n$, bool simp} 
-    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ reg\_psi
+\caption{reg\_U} 
+Inputs: r\_phi, r\_psi - vectors of REGEX for MLTL formulas $\phi$ and $\psi$ \\
+$a, b$ - integers representing interval bound \\
+$n$ - number of propositional variables\\
+Output: Vector of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
+\begin{algorithmic}[1]
+\Procedure{reg\_U}{r\_phi, r\_psi, $a$, $b$, $n$} 
+    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_psi
     \If{$a > b$} return $\{\}$
@@
     \For{($a \leq i \leq b-1$) }
-        \State temp\_G1 $\leftarrow$ reg\_G(reg\_phi, $a$, $i$, $n$)
-        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(reg\_psi, $i+1$, \hspace*{5mm}$i+1$, $n$)}
-        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, $n$, simp)}
-        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp, \hspace*{5mm}simp)}
+        \State temp\_G1 $\leftarrow$ reg\_G(r\_phi, $a$, $i$, $n$)
+        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(r\_psi, $i+1$, \hspace*{5mm}$i+1$, $n$)}
+        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, n)}
+        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
+        % , \hspace*{5mm}simp)}
     \EndFor
@@
 The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
-\textit{Join} takes as input two vectors of computation strings $R$ and $B$, and simply returns a vector containing all strings in $R$ and $B$, which is equivalent to $R \cup B$. 
+\textit{Join} concatenates two input vectors of computation strings $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
 \textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ...
@@
 Assume that all strings of regular expressions are right padded to equal length. 
-We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$.
-Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that
+We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that 
 \begin{align*}
@@
 \end{align*}
-\textit{Set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
+The for loop in line 3 of \textit{set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
 Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. 
 $\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$.
-Note that this operation is commutative.
-This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$.
+Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. 
 Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.
+
 The correctness for \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, \textit{reg\_R}, and \textit{reg} will be proven by induction on depth of recursion to \textit{reg}. 
@@
 Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$.
-$\gamma$ must be of the form $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are positive integers.
-The proof for all four cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.
+$\gamma$ must be of the form $\phi \lor \psi$, $\phi \land \psi$, $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are positive integers.
+Correctness of the first two cases have been proven. 
+The proof for the four temporal cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.
+
 We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
-In this case, \textit{reg} will call the helper function \textit{reg\_U} and pass in the parameters $\textit{reg\_phi} = \textit{reg}(\phi)$ and $\textit{reg\_psi} = \textit{reg}(\psi)$, which, by the induction hypothesis, are correctly and recursively computed.
+\textit{reg\_U} takes as input \textit{r\_phi} $=$ reg($\phi$) and \textit{r\_psi} $ = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
 The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$.
-In the pseudocode for $reg\_U$, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{reg\_psi}, and is the regular expression for $\mathcal{G}_[a, a] \psi$.
-Next, the Or block from $i = a + 1$ to $b - 1$ is iteratively computed using \textit{set\_intersect} for the inner expression, and added to \textit{comp} with the \textit{join} function, which are both proven correct above.
-This shows correctness of \textit{reg\_U}.
-Continue in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.
+In line $2$ of \textit{reg\_U}, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{r\_psi}, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
+Next, the $\lor$ from $i = a + 1$ to $b - 1$ is computed by the for loop in line 4; lines 5 through 7 computes $\text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. 
+This shows correctness of \textit{reg\_U} (note that in a complete proof, correctness of \textit{reg\_G} needs to be shown first since lines 5 and 6 calls \textit{reg\_G}).
+Continuing in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.
 
@@
 \hspace{3mm} For the next cases, we use these two bounds and define the constants $\mathcal{C}_G$ and $\mathcal{C}_F$:
-{\centering $\prod_{i = a}^b (n+1)i &= (n+1)^{b-a} \cdot \frac{b!}{(a-1)!} \leq (n+1)^\delta b!
+{\centering $\prod_{i = a}^b (n+1)i = (n+1)^{b-a} \cdot \frac{b!}{(a-1)!} \leq (n+1)^\delta b!
 \leq (n+1)^\delta d!
-= \mathcal{C}_G$ \\ $\sum_{i = a}^b (n+1)i &\leq (n+1)b\delta \leq (n+1)d\delta  = \mathcal{C}_F$\par}\\
+= \mathcal{C}_G$ \\ $\sum_{i = a}^b (n+1)i \leq (n+1)b\delta \leq (n+1)d\delta  = \mathcal{C}_F$\par}
 \hspace{3mm} If $\phi \text{ is } ``\mathcal{G}_{[a,b]} \phi_{1}$":
@@
 From the analysis of \textit{join}, worst case space complexity is additive and thus 
-$\text{S(\emph{reg}}(\phi)) &= \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_{F} \text{S(\emph{reg}}(\phi_1)$.\\
+$\text{S(\emph{reg}}(\phi)) = \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_{F} \text{S(\emph{reg}}(\phi_1)$.\\
 \hspace{3mm}If $\phi$ = $``\phi_1 \mathcal{U}_{[a, b]} \phi_2"$: Recall that 
@@
 \subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
-\begin{figure}[H]
+First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
+A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof.
+
+\begin{figure}[h!]
 \begin{minipage}{.62\textwidth}
@@
 
-First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
-A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof.
 For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
 Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end.
+
 \begin{figure}[h!]
@@
     \vspace{2mm}
-    \\\equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
+    \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
 $

### 2022-10-13 paper/Paper.tex
increased figure title and axis font sizes

@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim1Length.png}
+    \includegraphics[scale=0.38]{images/Sim1Length_large.png}
     \captionof{figure}{Input length vs output length.\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim1Time.png}
+    \includegraphics[scale=0.38]{images/Sim1Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim2Length.png}
+    \includegraphics[scale=0.38]{images/Sim2Length_large.png}
     \captionof{figure}{Input length vs output length\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim2Time.png}
+    \includegraphics[scale=0.38]{images/Sim2Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim3Length.png}
+    \includegraphics[scale=0.38]{images/Sim3Length_large.png}
     \captionof{figure}{Input length vs output length\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim3Time.png}
+    \includegraphics[scale=0.38]{images/Sim3Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim4Length.png}
+    \includegraphics[scale=0.38]{images/Sim4Length_large.png}
     \captionof{figure}{Input length vs output length\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.39]{images/Sim4Time.png}
+    \includegraphics[scale=0.38]{images/Sim4Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
-    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};
+    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};
 

### 2022-10-13 MLTL_reg/MLTL/complexity_graph/complexity_graph.py
now takes command prompt arguments to generate plots more conveniently

@@ -1,11 +1,39 @@
 import pandas as pd
 import matplotlib.pyplot as plt
+import sys
 
-data = pd.read_csv("/Users/ctrave/Downloads/Research/ISU REU 2022/complexities4.txt", sep=" ", header=None, names=["Input Length", "Time(ms)", "Output Length"])
-print(data)
+# Run python3 ./complexity_graph.py {experiment number} {plot_length}
+# Set plot_length = 1 to plot length vs length
+# Set plot_length = 0 to plot length vs time
+
+experiment = int(sys.argv[1])
+plot_length = int(sys.argv[2])
+x_font = 16
+y_font = 16
+title_font = 16
+
+data = pd.read_csv("./complexities"+str(experiment)+".txt", sep=" ", header=None, names=["Input Length", "Time(ms)", "Output Length"])
+# print(data)
 #print(data.nlargest(2, "Time(ms)"))
 #print(data.nlargest(3, "Output Length"))
-#data.plot.scatter(x="Input Length", y="Output Length", color="Blue", marker="x")
-data.plot.scatter(x="Input Length", y="Time(ms)", color="Red", marker="x")
-plt.title("1 Iteration, 5 Propositional Variables, Delta = 10, Interval Max = 10", y=1.05)
+
+if plot_length:
+    data.plot.scatter(x="Input Length", y="Output Length", color="Blue", marker="x")
+    plt.ylabel("Output Length", fontsize = y_font)
+else: # plot time
+    data.plot.scatter(x="Input Length", y="Time(ms)", color="Red", marker="x")
+    plt.ylabel("Time(ms)", fontsize=y_font)
+
+plt.xlabel('Input Length', fontsize=x_font)
+
+if experiment == 1:
+    title = "iter=2, prop vars=5, delta=10, interval max=10"
+elif experiment == 2:
+    title = "iter=1, prop vars=10, delta=20, interval max=20"
+elif experiment == 3:
+    title = "iter=2, prop vars=10, delta=5, interval max=10"
+elif experiment == 4:
+    title = "iter=1, prop vars=5, delta=10, interval max=10"
+
+plt.title(title, y=1.05, fontsize=title_font)
 plt.show()

### 2022-10-13 paper/Paper.tex
small fixes

@@
 \begin{proof}
-The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Global, And, and Or.\\
+The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for \texttt{Until} and \texttt{Release} and the minimum computation lengths for \texttt{Future}, \texttt{Globally}, \texttt{AND}, and \texttt{OR}.\\
  Recall that $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$. Thus
@@
 Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}.
-The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} takes as input a MLTL formula of the appropriate form, and returns the regular expression as previously defined in section \ref{regex}.
+The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} take as input a MLTL formula of the appropriate form, and return the regular expression as %previously
+defined in section \ref{regex}.
 \textit{Join} concatenates two input vectors of computation strings $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
@@
 Assume that all strings of regular expressions are right padded to equal length. 
-We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$. Since a vector of regular expressions is synonymous to the collective Or of each of them, we have that 
+We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$.
+Since a vector of regular expressions is synonymous to the collective \texttt{OR} of each of them, we have that
 \begin{align*}

### 2022-10-13 paper/Paper.tex
small fixes

@@
 Finally, we generate a test suite using control flow diagrams to robustly test the code.
+
+        %We demonstrate that formula validation examples generated via regular expressions encapsulating the sets of all satisfying/unsatisfying assingments is tractable, both theoreteically and experimentally.
+We present an efficient algorithm for automatic characterization of an MLTL formula by its satisfying assingments, proove the theoretical correctness, time complexisty, and space complexity of hte algorithm.
+Then we provide a robust implementattion of the algorithm, demonstrate expreimentally its performance and correctness, and utilize intelligent fuzzing to increaes confidence int eh resulting open-source tool, which we release for public use.
+The result of our contributions are improvements to existing algorithms for MLTL analsysis applicable to many other tools and a new tool called WEST for provably correct, atomated, efficient MLTL formula validation.%
+%        Our work connects existing tools to enable improvmeents in satisfiabiity tools and automated synthesis of verified code from MLTL behavior descriptions.
+
         \vspace{-0.1in}
@@
 \subsection{Experimental Benchmarking}
- Along with theoretical space and time complexity, we provide some experimental benchmarking of these complexities using randomly generated MLTL formulas.
-This was done on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
+We accompany theoretical space and time complexity with experimental evaluation of these complexities using randomly-generated MLTL formulas.
+We ran these experiments on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
 For each simulation, we generated 1000 MLTL formulas using the parameters DELTA, INTERVAL\_MAX, number of propositional variables, and number of iterations.
@@
     \captionof{figure}{Input length vs output length.\vspace{3mm}}
+    \label{InputLengthVsOutputLength}
     \end{figure}
@@
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \label{InputLengthVsRuntime}
     \end{figure}
 \end{minipage}\\
-\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both figures, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for figure 2.\\
+\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both figures, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InputLengthVsRuntime}.
+\\
 \noindent\textbf{Simulation 2}
@@
 \end{minipage}\\
-The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both figures, and figure 5 had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
+The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both figures, and Figure 5 had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
 \\

### 2022-10-13 paper/Paper.tex
edits to experiments/citations

@@
     \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \label{fig:InVsOutLen}
     \end{figure}
@@
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \label{fig:InLenVsRunTime}
     \end{figure}
@@
     \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \label{fig:InLenVsOutLen3}
     \end{figure}
@@
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \label{fig:InLenVsRunTime3}
     \end{figure}
@@
     \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \label{InLenVsOutLen4}
     \end{figure}
@@
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
+    \label{InLenVsRunTime4}
     \end{figure}
 \end{minipage}
-\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively sparse.
+\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively rare.
 We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Correctness of WEST} \label{test}
- The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program). 
-On one hand, correctness of an algorithm is assured by mathematical analysis of the algorithm on all possible inputs and showing that it behaves as desired. 
-However, assuring correctness of the program is a difficult task.
-One naive approach is to test every possible input up to a certain size, and verify the output or behavior of the program.
-This often times involves a test suite that is too large to be computationally feasible, and the test suite may be overtly redundant. 
-For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program for any reasonable party.
-We approach this problem more intelligently.
-In the following section, we test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm.
-A control path can be thought of as a sequence of lines of code that are executed in one calculation of an input formula.
-Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST program.
+\section{Correctness of WEST Tool Implementation} \label{test}
+We accompany our proof of algorithmic correctness with a rigourous evaluation of implementation correctness: that our WEST tool correctly implements our WEST algorithm.
+% The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program).
+%On one hand, correctness of an algorithm is assured by mathematical analysis of the algorithm on all possible inputs and showing that it behaves as desired. 
+%However, assuring correctness of the program is a difficult task.
+Since our proof of algorithmic correctness is manual and our focus is on usability for validation by humans, we utilize more traditional techniques for robust software engineering with testing-based evaluation.
+An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
+Since the primary purpose of the WEST tool is valiation of formulas for humans, we focused on writing a tool with an intutiive human-facing interface then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.
+
+One naive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
+For WEST, this strategy would generate a very large test suite with signficant redundancy. 
+For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program.
+We approach this problem more intelligently: we test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm.
+A control path is a sequence of lines of code that are executed in one calculation of an input formula.
+Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST tool.
 
 \subsection{Intelligent Fuzzing}
-Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; fuzz testing (also know as fuzzing) is a form of negative testing.
-The earliest use of fuzzing by Miller \cite{Miller} was to discover bugs in Unix utilities by randomly generating command line inputs, and monitoring for unexpected crashes or security.
+Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; we employ fuzz testing (also know as fuzzing), a form of negative testing.
+%The earliest use of fuzzing by Miller \cite{Miller} was to discover bugs in Unix utilities by randomly generating command line inputs, and monitoring for unexpected crashes or security.
 This style of black box testing assumes no prior knowledge of the target program, and is centered on generating a large quantity of inputs.
 Miller describes his approach in \cite{Miller} as follows: \\
+We deviate from traditional black-box fuzzing defined by \cite{Miller} as follows: \\
 \textit{``If we consider a program to
 be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''} \\
-Intelligent fuzzing (sometimes referred to as whitebox fuzzing) is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
+Instead we utilize intelligent fuzzing (sometimes referred to as whitebox fuzzing), which is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
 Borrowing the words of Miller, our approach to testing the WEST program can be thought of as walking all possible paths up to a certain depth of the state space of our algorithm. 
@@
  We choose to represent the states space of algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
-The core of the WEST program is executed in the recursive routine, \textit{reg}, which calls the $8$ different subroutines discussed earlier, as shown in \ref{fig:abstracted graph}.
+ The core of the WEST program lies in the recursive routine, \textit{reg}, which calls the $8$ different subroutines %discussed earlier,
+ as shown in \ref{fig:abstracted graph}.
 \begin{figure}[t]

### 2022-10-13 paper/Paper.tex
edits to section 5 and unification of " marks

@@
 Intelligent fuzzing techniques contribute to test suite construction from a state diagram representing the control flow of the algorithm.
-We also verify the correctness of outputs of the WEST program against a naive brute force implementation.
+We also verify the correctness of outputs of the WEST program against a na\"ive brute force implementation.
 %
@@
 
-One naive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
+One na\"ive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
 For WEST, this strategy would generate a very large test suite with signficant redundancy. 
@@
     \item Construct a test suite that explores all possible paths in the digraph up to a certain depth. Run the WEST program on the test suite to produce a set of output files.
-    \item Run a naive brute force generator of satisfying computations on the test suite and verify that both outputs match for all test cases.
+    \item Run a na\"ive brute force generator of satisfying computations on the test suite and verify that both outputs match for all test cases.
 \end{enumerate}
 \subsubsection{State Diagram Construction}
- We choose to represent the states space of algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
+ We can represent the state space of the WEST algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
  The core of the WEST program lies in the recursive routine, \textit{reg}, which calls the $8$ different subroutines %discussed earlier,
@@
 Without this abstraction, attempting to explore all execution paths in this finer graph is infeasible due to the explosion in the number of paths \cite{Pham_2016}, some of which are provably impossible to construct a test input to explore.
-\subsubsection{Creating the Test Suite}
- We now give the procedure of how the intelligent fuzzing test suite is generated. 
-Firstly, we count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
+\subsubsection{Creating the Test Suite} %KYR: edited to remove excessive passive voice (active voice is best for research papers!)
+To generate our ntelligent fuzzing test suite, 
+first, we count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
 For $d = 0$, only the paths leading to \textit{prop\_var} and \textit{prop\_cons} can be explored, so $\phi(0) = 2$.
@@
 This gives $\phi(1) = 20$, $\phi(2) = 1640$, and $\phi(3) = 10761680$. 
-$d = 3$ is computationally infeasible, and $d = 1$ doesn't give us assurance about operators interacting with each other through nesting. Thus $d = 2$ is a happy medium. 
-The full test suite is generated in a similar recursive manner. 
-Firstly, the $d = 0$ test suite comprises of two formulas: a propositional variable or its negation, and a propositional constant. 
-Then for any $d \geq 1$, the test suite is constructed by iterating through all formulas in the depth $d-1$ test suite for \textit{reg\_G} and \textit{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths.
-To ensure wider coverage, each of the propositional variables or their negation and propositional constants are randomly generated.
-\subsubsection{Verifying against Naive Brute Force}
- A relatively straight forward approach to generating the set of all satisfying computations of a MLTL formula $\phi$ over $n$ variables, such that $m = \text{cplen}(\phi)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
-The main work is done by an interpreter function that takes arguments of computation $\pi$ and MLTL formula $\phi$ and determines if $\pi \vDash \phi$ purely based on semantics that define MLTL.
-Every first-order quantifier is easily translated to loops, and checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
-The full implementation details can be found on the %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} %KYR: blind review
-{GitHub} repository. 
-As expected for a brute force implementation, extensive run time poses a major limitation; the previously mentioned infeasibility of not abstracting away subroutines and running test suites for deeper depths is primarily caused by this stage of verification.
+$d = 3$ is computationally infeasible, and $d = 1$ doesn't give us assurance about operators interacting with each other through nesting. Thus we select $d = 2$ as a happy medium. 
+We generate the full test suite in a similar recursive manner. 
+Firstly, the $d = 0$ test suite consists of two formulas: a propositional variable or its negation, and a propositional constant. 
+Then for any $d \geq 1$, we iterate through all formulas in the depth $d-1$ test suite for \textit{reg\_G} and \textit{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths.
+To ensure wider coverage, we randomly generate each of the propositional variables or their negation and propositional constants.
+\subsubsection{Verifying against Na\"ive Brute Force}
+ A relatively straightforward approach to generating the set of all satisfying computations of an MLTL formula $\phi$ over $n$ variables, such that $m = \text{cplen}(\phi)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
+An interpreter function takes two arguments of computation $\pi$ and MLTL formula $\phi$ and determines if $\pi \vDash \phi$ purely based on the semantics that define MLTL.
+Our test program translates every first-order quantifier into a loop; then checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
+The full implementation details are available in the WEST %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} %KYR: blind review
+{GitHub} repository.\footnote{Links have been redacted for blind review.} 
+%As expected for a brute force implementation, extensive run time poses a major limitation; the previously mentioned infeasibility of not abstracting away subroutines and running test suites for deeper depths is primarily caused by this stage of verification.
 On an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM, the brute force program took nearly nine hours to execute the depth two test suite of $1640$ formulas. 
-For this test suite, the number of propositional variables was fixed at $n = 4$ and the largest computation length was $m = 5$, from formulas with doubly-nested temporal operators. 
+For this test suite, we fixed the number of propositional variables at $n = 4$ and the largest computation length was $m = 5$, from formulas with doubly-nested temporal operators. 
 In comparison, the WEST program executed the same test suite in under thirty minutes on the same machine.
-One thing to note is that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the `$S$' characters in the regular expressions.
-For instance, the regular expression ``$1SS0SS1$" yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
+One thing to note is that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the ``$S$'' characters in the regular expressions.
+For instance, the regular expression ``$1SS0SS1$'' yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
 It's important to state that although the full test suite matches between both implementations, absolute correctness on all inputs is not guaranteed for either program.
@@
 \section{Regular Expression Simplification Theorem} \label{simpsection}
- As a final result of our paper, we provide a regular expression simplification theorem.
-This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all `$S$'s.
-Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of `$S$'s when a formula holds true for every computation.
+ As a final result, we provide a regular expression simplification theorem.
+This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all ``$S$'' characters.
+Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of ``$S$'' characters when a formula holds true for every computation.
 We first define some vocabulary.\\
- We say a regular expression composed entirely of `$S$'s and commas is an \emph{arbitrary computation}.
+ We say a regular expression composed entirely of ``$S$'' characters and commas is an \emph{arbitrary computation}.
 For the purposes of the following theorem, we remove all commas from computations.
-We say `0' or a `1' in a regular expression is a \emph{fixed truth value}.
+We say ``0'' or a ``1'' in a regular expression is a \emph{fixed truth value}.
 We overload the definition of a matrix and say that a \emph{matrix} is a representation of a union of regular expressions, where each row is a regular expression.
@@
 \begin{theorem}[\emph{Regular Expression Simplification Theorem}] \label{simp}
-Let M be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length n with commas stripped.
-If each column has one `$1$', one `$0$', and $n-1$ `$S$'s, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.
+Let $M$ be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length $n$ with commas stripped.
+If each column has one ``$1$,'' one ``$0$,'' and $n-1$ ``$S$'' characters, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.
 \end{theorem}
@@
 For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
-Next, it is possible that a regular expression could be appended with a substring of `$S$'s at the beginning or end.
+Next, it is possible that a regular expression could be appended with a substring of ``$S$'' characters at the beginning or end.
 
@@
 The WEST program generates a union of regular expressions corresponding to the matrix shown in \eqref{matrix_ex4}.
-It can clearly be seen that this is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
+This is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
 \end{example}
@@
 Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
-Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up" by common substrings.
+Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up'' by common substrings.
 Consider the following modification to the matrix generated by example \ref{example1}:\\
 \begin{minipage}{.5\textwidth}
-The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively.
+The substrings ``$0$,'' ``$1S0$,'' and ``$1$'' are inserted at the beginning, middle, and end, respectively.
 In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.

### 2022-10-13 paper/Paper.tex
vector->set + other wording changes

--- 2022-10-13 paper/Paper.tex
@@
 \begin{definition}[\emph{Temporal Regular Expression}] \label{TRE} 
-Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$.
+Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$.\\
 Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula.
@@
 \begin{example} %KYR: NICE example!
-Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.\\
+Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
@@
 We now present the  full WEST algorithm, which recursively computes all satisfying temporal regular expressions to a given MLTL formula (in NNF). 
-We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
+For convenience, we use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
 Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{F}$. 
-Note how the algorithm parallels the regular expression defined for $\mathcal{F}$, and the algorithms for the other three temporal operators follow an identical structure.
+Note how reg\_U parallels the regular expression defined for $\mathcal{F}$, and the algorithms for the other three temporal operators follow an identical structure.
 
@@
 Although repeated set intersection blows up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
-We simplify alternation by using the fact that for regular expressions $w_1$ and $w_2$, $\mathscr{L}(w_1 1 w_2 \lor w_1 0 w_2) = \mathscr{L}(w_1 s w_2)$, and check if the reduction applies at every index between every pair of strings in a given vector.
+We simplify alternation by using the fact that for regular expressions $w_0$ and $w_1$, $\mathscr{L}(w_0 1 w_1 \lor w_0 0 w_1) = \mathscr{L}(w_0 s w_1)$, and check if the reduction applies at every index between every pair of strings in a given set.
 
@@
 $n$ - number of propositional variables \\
-Output: Vector of REGEX satsfying $\phi$}
+Output: set of REGEX satisfying $\phi$}
 \begin{algorithmic}[1]
@@
 \caption{set\_intersect}
-Inputs: $R, T$ - Two Vectors of REGEX\\
+Inputs: $R, T$ - two sets of REGEX\\
 $n$ - number of propositional variables\\
-Output: Vector equal to $R \land T$
+Output: set of REGEX equal to $R \land T$
 \begin{algorithmic}[1]
@@
 \caption{reg\_U} 
-Inputs: r\_phi, r\_psi - vectors of REGEX for MLTL formulas $\phi$ and $\psi$ \\
+Inputs: r\_$\phi$, r\_$\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
 $a, b$ - integers representing interval bound \\
 $n$ - number of propositional variables\\
-Output: Vector of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
+Output: set of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
 \begin{algorithmic}[1]
-\Procedure{reg\_U}{r\_phi, r\_psi, $a$, $b$, $n$} 
-    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_psi
+\Procedure{reg\_U}{r\_$\phi$, r\_$\psi$, $a$, $b$, $n$} 
+    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
     \If{$a > b$} return $\{\}$
@@
     \For{($a \leq i \leq b-1$) }
-        \State temp\_G1 $\leftarrow$ reg\_G(r\_phi, $a$, $i$, $n$)
-        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(r\_psi, $i+1$, \hspace*{5mm}$i+1$, $n$)}
+        \State temp\_G1 $\leftarrow$ reg\_G(r\_$\phi$, $a$, $i$, $n$)
+        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(r\_$\psi$, $i+1$, \hspace*{5mm}$i+1$, $n$)}
         \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, n)}
@@
 defined in section \ref{regex}.
-\textit{Join} concatenates two input vectors of computation strings $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
-\textit{Set\_intersect} takes as input two vectors of computation strings $R$ and $T$, where $R$ represents $r_1 | ...
+\textit{Join} concatenates two sets of regular expressions $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$. 
+\textit{Set\_intersect} takes as input two sets of regular expressions $R$ and $T$, where $R$ represents $r_1 | ...
 | r_a$ and $T$ represents $t_1 | ...
@@
 Assume that all strings of regular expressions are right padded to equal length. 
-We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$.
-Since a vector of regular expressions is synonymous to the collective \texttt{OR} of each of them, we have that
+We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$:
 \begin{align*}
@@
 For any function $f(\phi)$ taking a string argument $\phi$, we use $|\phi|$ to denote the number of characters in $\phi$ and $S(f(\phi))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
-\hspace{3mm} If $\phi$ is a propositional constant or variable, it's easy to see that $S(\text{\emph{reg}}(\bot)) = 0$ since only the empty vector is returned.
+\hspace{3mm} If $\phi$ is a propositional constant or variable, it's easy to see that $S(\text{\emph{reg}}(\bot)) = 0$ since only the empty set is returned.
 By definition $\text{\emph{reg}}(\top) = S^n$, so we have that $S(\text{\emph{reg}}(\top)) = O(n)$.
 Similarly, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\neg p_k)$ both return strings of the same length and thus $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\neg p_k)) = S(\text{\emph{reg}}(\top)) = n$.\\
-\hspace{3mm} If $\phi$ is ``$\phi_{1} \lor \phi_{2}$'' we return $\textit{join}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}))$, which simply concatenates the contents of the two vectors. 
+\hspace{3mm} If $\phi$ is ``$\phi_{1} \lor \phi_{2}$'' we return $\textit{join}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}))$, which simply concatenates the contents of the two sets. 
 Thus $S(\text{\emph{reg}}(\phi_{1} \lor \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).$\\
 \hspace{3mm} If $\phi$ is ``$\phi_{1} \land \phi_{2}$''
-$ \textit{set\_intersect}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}), n)$ returns a vector of size $S(A) \cdot S(B)$ in the worst case when no simplification can be made. 
+$ \textit{set\_intersect}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}), n)$ returns a set of size $S(A) \cdot S(B)$ in the worst case when no simplification can be made. 
 Thus, our space complexity is $S(\text{\emph{reg}}(\phi_{1} \land \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})).$\\
@@
 Thus\\ $\text{S(\emph{reg}}(\phi)) = \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_G \text{S(\emph{reg}}(\phi_1))$.
-In this calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a vector of only length 1 strings. \\
+In this calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a set of only length 1 strings. \\
 \hspace{3mm} If $\phi \text{ is } ``\mathcal{F}_{[a,b]} \phi_{1}$":
@@
 Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.
-If in the worst case no simplification occurs in any call of \textit{set\_intersect}, space complexity remains unchanged, but simplifying a vector of regular expressions is cubic in input size.
+If in the worst case no simplification occurs in any call of \textit{set\_intersect}, space complexity remains unchanged, but simplifying a set of regular expressions is cubic in input size.
 In practice however, both time and space complexities are much more optimistic than worst-case estimates.
@@
 \section{Correctness of WEST Tool Implementation} \label{test}
-We accompany our proof of algorithmic correctness with a rigourous evaluation of implementation correctness: that our WEST tool correctly implements our WEST algorithm.
+We accompany our proof of algorithmic correctness with a rigorous evaluation of implementation correctness: that our WEST tool correctly implements our WEST algorithm.
 % The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program).
@@
 An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
-Since the primary purpose of the WEST tool is valiation of formulas for humans, we focused on writing a tool with an intutiive human-facing interface then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.
+Since the primary purpose of the WEST tool is validation of formulas for humans, we focused on writing a tool with an intuitive human-facing interface then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.
 
 One naive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
-For WEST, this strategy would generate a very large test suite with signficant redundancy. 
+For WEST, this strategy would generate a very large test suite with significant redundancy. 
 For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program.
@@
 The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively.
-In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
+In general, a set of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
 Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.
@@
 \noindent \textbf{Simplifying unions of regular expressions to a minimal representation.}
-Theorem \ref{simp} addresses a non-trivial situation in which a vector of regular expressions may be simplified.
+Theorem \ref{simp} addresses a non-trivial situation in which a set of regular expressions may be simplified.
 A natural question to ask is what is the minimum number of strings of regular expressions needed to represent a language of computations.
@@
 We denote these regexes by $R$ and $T$, where $R = R_1 | R_2 | ...
-| R_k$ is represented as a vector of strings $R = {R_1, R_2, ..., R_k}$, and $T = T_1 | T_2 | ...
-| T_\ell$ is represented as a vector of strings $T = {T_1, T_2, ..., T_\ell}$.
+| R_k$ is represented as a set of strings $R = {R_1, R_2, ..., R_k}$, and $T = T_1 | T_2 | ...
+| T_\ell$ is represented as a set of strings $T = {T_1, T_2, ..., T_\ell}$.
 Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.
 \begin{algorithm}[H]
-\caption{Pad a vector to elements of all equal length}
-%Input: Vector of strings that represents a regex, number of propositional variables \\
-%Output: Vector of strings padded to equal length
+\caption{Pad a set to elements of all equal length}
+%Input: set of strings that represents a regex, number of propositional variables \\
+%Output: set of strings padded to equal length
 \begin{algorithmic}
-\Procedure{Pad}{vector $R$, int $n$} 
+\Procedure{Pad}{set $R$, int $n$} 
     \State max\_Length $\leftarrow$ $\max_{\{r \in R\}}$($r$.length())
@@
 %Input: String that is either ``T" or ``!", number of propositional variables\\
-%Output: Vector of strings that represents the appropriate satisfying computations
+%Output: set of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
@@
 \begin{algorithm}[H]
-\caption{Output the vector of computation satisfying a propositional variable.}
+\caption{Output the set of computation satisfying a propositional variable.}
 %Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
-%Output: Vector of strings that represents the appropriate satisfying computations
+%Output: set of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
@@
 \begin{algorithm}[H]
-\caption{Simplifies a vector of strings using simplify\_string}
-%Input: Vector of strings representing a regex\\
-%Output: Vector of strings representing a regex simplified using simplify\_string
+\caption{Simplifies a set of strings using simplify\_string}
+%Input: set of strings representing a regex\\
+%Output: set of strings representing a regex simplified using simplify\_string
 \begin{algorithmic}
-\Procedure{simplify}{vector $R$}    
+\Procedure{simplify}{set $R$}    
     \State Pad all strings in $R$ to the same length
@@
 \begin{algorithm}[H]
-\caption{Takes union of two regexes (combines two vectors into one)}
-%Input: Vectors of strings that represent regexes, simplify boolean\\
-%Output: Vector of strings that represents union of inputted regexes
+\caption{Takes union of two regexes (combines two sets into one)}
+%Input: sets of strings that represent regexes, simplify boolean\\
+%Output: set of strings that represents union of inputted regexes
 \begin{algorithmic}
-\Procedure{join}{vector $R$, vector $T$, bool simp}
+\Procedure{join}{set $R$, set $T$, bool simp}
     \State ret $\leftarrow \{\}$
@@
 \caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
-% Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-% Output: Vector of strings that represents the appropriate satisfying computations 
+% Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
+% Output: set of strings that represents the appropriate satisfying computations 
 \begin{algorithmic}
-\Procedure{reg\_F}{vector reg\_phi, int $a$, int $b$, int $n$, bool simp} 
+\Procedure{reg\_F}{set reg\_phi, int $a$, int $b$, int $n$, bool simp} 
     \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
@@
 \caption{Computes the regex for a MLTL formula G[a:b]$\phi$}
-%Inputs: Vector of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-%Output: Vector of strings that represents the appropriate satisfying computations
+%Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
+%Output: set of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
-\Procedure{reg\_G}{vector reg\_phi, int $a$, int $b$, int $n$, bool simp} 
+\Procedure{reg\_G}{set reg\_phi, int $a$, int $b$, int $n$, bool simp} 
     \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
@@
 \caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
-%Inputs: Vectors of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
-%Output: Vector of strings that represents the appropriate satisfying computations 
+%Inputs: sets of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
+%Output: set of strings that represents the appropriate satisfying computations 
 \begin{algorithmic}
-\Procedure{reg\_R}{vector reg\_phi, vector reg\_psi, int $a$, int $b$, int $n$, bool simp} 
+\Procedure{reg\_R}{set reg\_phi, set reg\_psi, int $a$, int $b$, int $n$, bool simp} 
     \State comp $\leftarrow$ reg\_G(reg\_psi, $a$, $b$, $n$, simp)
@@
     %Inputs: Depth of desired test suite template to generate, interval bounds\\
-    %Output: Vector of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
+    %Output: set of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
     \begin{algorithmic}
@@
     %Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
-    %Output: Vector of MLTL formulas
+    %Output: set of MLTL formulas
     \begin{algorithmic}
@@
     %Nodes
-    \node[emptynode](inputs){vector R, \# of propositional variables n};
+    \node[emptynode](inputs){set R, \# of propositional variables n};
     \node[node](length)[below=of inputs]{Run max\_length on R};
     \node[node](body)[below=of length]{pad r, update R};
-    \node[emptynode](empty_vector)[rotate=-70, left=1cm of body]{R $=\{\}$};
+    \node[emptynode](empty_set)[rotate=-70, left=1cm of body]{R $=\{\}$};
     \node[emptynode](for_loop)[right=1.1cm of body]{for r in R};
@@
     %Nodes
-    \node[emptynode](inputs){vectors R, T};
-    \node[node](initialize)[below=of inputs]{Initialize vector Ret};
+    \node[emptynode](inputs){sets R, T};
+    \node[node](initialize)[below=of inputs]{Initialize set Ret};
     \node[node](add_r)[below=of initialize]{Add r to Ret};
@@
     %Nodes
-    \node[emptynode](inputs){vectors R,T};
-    \node[node](initialize)[below=of inputs]{Pad R and T, Initialize vector Ret=\{\}};
+    \node[emptynode](inputs){sets R,T};
+    \node[node](initialize)[below=of inputs]{Pad R and T, Initialize set Ret=\{\}};
     \node[node](outer_loop)[below=of initialize]{Outer Loop Entry};
@@
     %Nodes
-    \node[emptynode](inputs){vector reg\_phi, integers a, b, n};
-    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
+    \node[emptynode](inputs){set reg\_phi, integers a, b, n};
+    \node[node](initialize)[below=of inputs]{Initialize string pre, set Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};
@@
     %Nodes
-    \node[emptynode](inputs){vector reg\_phi, reg\_psi and integers a, b, n};
-    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
+    \node[emptynode](inputs){set reg\_phi, reg\_psi and integers a, b, n};
+    \node[node](initialize)[below=of inputs]{Initialize set Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};

### 2022-10-13 paper/Paper.tex
resolved merging, now reference labeled figures

@@
 \end{minipage}\\
-\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both figures, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InputLengthVsRuntime}.
+\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both Figures \ref{InputLengthVsOutputLength} and \ref{InputLengthVsRuntime}, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InputLengthVsRuntime}.
 \\
@@
 \end{minipage}\\
-The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both figures, and Figure 5 had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
+The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both Figures \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}, and Figure \ref{fig:InLenVsOutLen3} had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
 \\
@@
 
-One naive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
+One na\"ive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
 For WEST, this strategy would generate a very large test suite with significant redundancy. 
@@
 Without this abstraction, attempting to explore all execution paths in this finer graph is infeasible due to the explosion in the number of paths \cite{Pham_2016}, some of which are provably impossible to construct a test input to explore.
-\subsubsection{Creating the Test Suite}
- We now give the procedure of how the intelligent fuzzing test suite is generated. 
-Firstly, we count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
+\subsubsection{Creating the Test Suite} %KYR: edited to remove excessive passive voice (active voice is best for research papers!)
+To generate our intelligent fuzzing test suite, 
+first, we count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
 For $d = 0$, only the paths leading to \textit{prop\_var} and \textit{prop\_cons} can be explored, so $\phi(0) = 2$.
@@
 \section{Regular Expression Simplification Theorem} \label{simpsection}
- As a final result of our paper, we provide a regular expression simplification theorem.
-This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all `$S$'s.
-Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of `$S$'s when a formula holds true for every computation.
+As a final result, we provide a regular expression simplification theorem.
+This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all ``$S$'' characters.
+Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of ``$S$'' characters when a formula holds true for every computation.
 We first define some vocabulary.\\
- We say a regular expression composed entirely of `$S$'s and commas is an \emph{arbitrary computation}.
+ We say a regular expression composed entirely of ``$S$'' characters and commas is an \emph{arbitrary computation}.
 For the purposes of the following theorem, we remove all commas from computations.
-We say `0' or a `1' in a regular expression is a \emph{fixed truth value}.
+We say ``0'' or a ``1'' in a regular expression is a \emph{fixed truth value}.
 We overload the definition of a matrix and say that a \emph{matrix} is a representation of a union of regular expressions, where each row is a regular expression.
@@
 Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
-Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up" by common substrings.
+Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up'' by common substrings.
 Consider the following modification to the matrix generated by example \ref{example1}:\\
 \begin{minipage}{.5\textwidth}
-The substrings ``$0$", ``$1S0$", and ``$1$" are inserted at the beginning, middle, and end, respectively.
-In general, a set of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
+The substrings ``$0$,'' ``$1S0$,'' and ``$1$'' are inserted at the beginning, middle, and end, respectively.
+In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
 Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.

### 2022-10-14 paper/Paper.tex
many format edits,turned correctness proof and time complexity into theorems, more edits to correctness proof, etc - Chiara, Jeremy, Laura, Zili

@@
 %
-We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in section \ref{specs} %, we give the WEST code specifications.
+We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in section \ref{WESTalg} %, we give the WEST code specifications.
 In particular, we describe the grammar that the program follows and give an overview of the important functions in the program.
 %
-and calculate its space and time complexity, both theoretically and experimentally, in section \ref{complex}.
+and calculate its space and time complexity, both theoretically and experimentally.
 We show that the theoretical worst-case complexity for both space and time is doubly exponential, but that the average case fares far better.
@@
 \vspace{-0.1in}
-$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \psi \ | \ \psi_1 \land \psi_2 \ | \ \psi_1 \lor \psi_2 \ | \ \mathcal{F}_{[a,b]} \psi \ | \ \mathcal{G}_{[a,b]} \psi \ | \ \psi_1 \mathcal{U}_{[a,b]} \psi_2 \ | \ \psi_1 \mathcal{R}_{[a,b]} \psi_2 \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{specs}).
+$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \psi \ | \ \psi_1 \land \psi_2 \ | \ \psi_1 \lor \psi_2 \ | \ \mathcal{F}_{[a,b]} \psi \ | \ \mathcal{G}_{[a,b]} \psi \ | \ \psi_1 \mathcal{U}_{[a,b]} \psi_2 \ | \ \psi_1 \mathcal{R}_{[a,b]} \psi_2 \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{WESTalg}).
 We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
@@
 
-To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{`$0$' , `$1$', `$,$'\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
-Let $p_0, p_2, ..., p_{n-1}$ be propositional variables, $\phi, \psi$ well-formed MLTL formulas in negation normal form.
+To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{``$0$'' , ``$1$'', ``$,$''\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
+Let $p_0, p_1, ..., p_{n-1}$ be propositional variables, $\phi, \psi$ well-formed MLTL formulas in negation normal form.
 We define the regular expression of satisfying computations for an MLTL formula as follows:\\
-%
-%
-% ZILI: Failed attempt to get formulas side by side
-% \begin{minipage}{0.45 \textwidth}
-%     \begin{align}
-%     &\text{reg}(\top) = S^n\\
-%     &\text{reg}(\bot) = \emptyset \\
-%     &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
-%     &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-%     &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
-%     &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi)
-%     \end{align}
-% \end{minipage}
-% \begin{minipage}{0.55 \textwidth}
-%     \begin{align}
-%     &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi) \\
-%     &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)\\
-%     &\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
-%     &\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
-%     \end{align}
-% \end{minipage}
-%
-%ORIGINAL:
-%% \begin{align}
-%%      &\text{reg}(\top) = S^n\\
-%%      &\text{reg}(\bot) = \emptyset \\
-%%      &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
-%%      &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-%%      &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
-%%      &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi) \\
-%%      &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi) \\
-%%      &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)\\
-%%      &\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right) \\
-%%      &\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
-%% \end{align}
-%%
-     $\text{reg}(\top) = S^n$ \hfill 
-     $\text{reg}(\bot) = \emptyset$ \\
-     $\text{reg}(p_k) = S^{k}1S^{n-k-1}$ \hfill
-     $\text{reg}(\neg p_k) = S^{k}0S^{n-k-1}$ \\
-     $\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)$\hfill
-     $\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi)$ \\
-     $\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)$ \hfill
-     $\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)$\\
-     $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$ \\
-     $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$ %\label{release} %KYR: I notice this label was not used...
-
-%     \vspace{-0.1in}
-%     \subsection{Minimum Computation Length}
-%          \vspace{-0.1in}
- %These regular expressions describe all the satisfying computations of an MLTL formula of computation length $\text{cplen}(\phi)$, which is defined recursively below:
+
+% ZILI: Left Aligned Version
+\vspace{-7mm}
+\hspace{-8.5mm}
+\begin{minipage}{0.45 \textwidth}
+    \begin{align}
+    &\text{reg}(\top) = S^n\\
+    &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
+    &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
+    &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)
+    \end{align}
+\end{minipage}
+\begin{minipage}{0.55\textwidth}
+    \begin{align}
+    &\text{reg}(\bot) = \emptyset \\
+    &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
+    &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi) \\
+    &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)
+    \end{align}
+\end{minipage}
+\vspace{-5mm}\\
+\begin{minipage}{0.99\textwidth}
+\begin{align}
+&\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\\
+\vspace*{-10mm}&\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
+\end{align}
+\end{minipage}
 \begin{definition}[\emph{Computation Length}]
-We define the computation length $\text{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
+We define the computation length $\emph{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
           %\begin{align}
-\indent \qquad   $\text{cplen}(p_k) = \text{cplen}(\neg p_k) = 1$\\
-\indent \qquad   $\text{cplen}(\phi \land \psi) = \text{cplen}(\phi \lor \psi) = \max(\text{cplen}(\phi), \text{cplen}(\psi))$\\
-\indent \qquad   $\text{cplen}(\mathcal{G}_{[a,b]} \phi) = \text{cplen}(\mathcal{F}_{[a,b]} \phi) = b + \text{cplen}(\phi)$\\
-\indent \qquad   $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi))$
+\indent \qquad   $\emph{cplen}(p_k) = \emph{cplen}(\neg p_k) = 1$\\
+\indent \qquad   $\emph{cplen}(\phi \land \psi) = \emph{cplen}(\phi \lor \psi) = \max(\emph{cplen}(\phi), \emph{cplen}(\psi))$\\
+\indent \qquad   $\emph{cplen}(\mathcal{G}_{[a,b]} \phi) = \emph{cplen}(\mathcal{F}_{[a,b]} \phi) = b + \emph{cplen}(\phi)$\\
+\indent \qquad   $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$
 %\end{align}
@@
     Let $0 \leq a\leq b \in \mathbb{N}$ and let $\phi, \psi$ be well-formed MLTL formulas in NNF.
-The minimum computation length of Until and Release is given by $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi))$.
+The minimum computation length of Until and Release is given by $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$.
 \end{theorem}
@@
  \end{itemize} % \vspace{-0.1in} % \subsection{Soundness and Completeness} %  \vspace{-0.1in}
- We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$).
-That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
-% The proof of Theorem \ref{SoundComplete} appears in Appendix \ref{Appendix-SoundComplete}.
-
+ We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
  \begin{theorem}[\emph{Soundness and Completeness}] \label{SoundComplete}
- For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
+ For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \emph{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
  \end{theorem}
-
-%KYR: this totally goes here in the journal version but in an appendix/on a website for the conference version
-%%  \begin{proof}
-%%  We proceed by induction on the length of the formula.\\
-
-%%  \noindent \textbf{Base Cases.}\\
-%%  \noindent\textbf{reg($\top$)}\\
-%%  Any computation $\pi$ satisfies $\top$, and $\mathscr{L}(\text{reg}(\top))$ is the set of all computations of one time step.
-Padding conventions extends this to the set of all computations of any positive number of time steps, so we are done.\\
-
-%%  \noindent\textbf{reg($\bot$)}\\
-%%  There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\
-
-%%  \noindent\textbf{reg($p_k$)}\\
-%%  For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
-%%  $$S^{k} 1 S^{n-k-1}$$
-%%  which is precisely reg($p_k$).\\
-
-%%  \noindent\textbf{reg($\neg p_k$)}\\
-%%  If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
-%%  $$S^{k} 0 S^{n-k-1}$$
-%%  which is precisely reg($\neg p_k$).\\
-
-%%  \noindent\textbf{Inductive Step.}\\
-%%  Suppose the theorem holds for MLTL formulas $\varphi$ and $\psi$.
-We now show that it holds for $\varphi \land \psi$, $\varphi \lor \psi$, $\mathcal{F}_{[a,b]} \varphi$, $\mathcal{G}_{[a,b]} \varphi$, $\varphi \ \mathcal{U}_{[a,b]} \psi$, and $\varphi \mathcal{R}_{[a,b]} \psi$.\\
-
-%%  \noindent \textbf{reg($\varphi \land \psi$)}\\
-%%  We know that $\pi \vDash \varphi \land \psi \text{ iff } \pi \vDash \varphi \text{ and } \pi \vDash \psi$.\\
-%%  By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
-%%  \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
-%%  $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$
-
-%%  \noindent \textbf{reg($\varphi \lor \psi$)}\\
-%%  We know that $\pi \vDash \varphi \lor \psi \text{ iff } \pi \vDash \varphi \text{ or } \pi \vDash \psi$.\\
-%%  By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
-%%  \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
-%%  $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$
-
-%%  \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
-%%  We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
-%%  If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
-Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
-%%  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
-%%  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
-
-%%  \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
-%%  We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
-%%  Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
-%%  By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
-%%  $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
-
-%%  \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
-%%   We have that 
-%%   $$\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } (\pi_i \vDash \psi \text{ and } \forall a \leq j < i, \pi_j \vDash \varphi).$$
-%%   As argued in the Finally case, the length condition is satisfied.\\
-%%   By the inductive hypothesis, $\pi_i \vDash \psi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\psi))$, or equivalently, \\
-%%   $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[i,i]} \psi))$. Also, $\pi_j \vDash \varphi$ if and only if $\pi_j \in \mathscr{L}(\text{reg}(\varphi))$.\\
-%%   By the argument used in the Global case, we see that $\forall a \leq j < i, \ \pi_j \vDash \varphi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a, i-1]} \varphi))$.\\
-%%   Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently,
-%%   $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
-
-%%   \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
-%%   We have that
-%%   \begin{align*}
-%%     &\pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or } \\ 
-%%     &\exists j\in[a,b] \text{ such that }
-%%     (\pi_j \vDash \varphi \text{ and } \forall a\leq k \leq j, \pi_k \vDash \psi).
-%%   \end{align*}
-%%   As argued in the Global case, the first option for satisfying the formula never occurs.\\
-%%   By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case.
-the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)$.
-Hence
-
-%%   \begin{align*}
-%%     \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right) \\
-%%     &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)\\
-%%     &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
-%%   \end{align*}
-
-%%  \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
-%%  \end{proof}
-% \newpage
-%\vspace{-0,1in}
-%\subsection{Nested Until and Release Rewriting Theorem}
-%\vspace{-0,1in}
  We prove the correctness of our formula rewriting algorithm using our regular expressions from Definition \ref{TRE}.
-As detailed in Section \ref{complex}, nested binary temporal operators create the worst-case time and space complexity for the WEST program.
+As detailed in Section \ref{WESTalg}, nested binary temporal operators create the worst-case time and space complexity for the WEST program.
 Although the WEST program does not implement this theorem by default, we would expect selected applications of rewriting to improve runtime.
@@
 We now present the  full WEST algorithm, which recursively computes all satisfying temporal regular expressions to a given MLTL formula (in NNF). 
-For convenience, we use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$. 
+For convenience, we use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_0, ..., t_{n-1}\} = \bigcup_{i=0}^{n-1} t_i$. 
 Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{F}$. 
@@
 \begin{algorithm}[H] 
-\caption{WEST Algorithm \\
+\caption{WEST Algorithm}
 Inputs: $\phi$ - MLTL formula in NNF \\
@@
 $n$ - number of propositional variables \\
-Output: set of REGEX satisfying $\phi$}
+Output: set of REGEX satisfying $\phi$
 \begin{algorithmic}[1]
@@
 \caption{reg\_U} 
-Inputs: r\_$\phi$, r\_$\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
+Inputs: $r_\phi$, $r_\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
 $a, b$ - integers representing interval bound \\
@@
 \begin{algorithmic}[1]
-\Procedure{reg\_U}{r\_$\phi$, r\_$\psi$, $a$, $b$, $n$} 
+\Procedure{reg\_U}{$r_\phi$, $r_\psi$, $a$, $b$, $n$} 
     \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
@@
     \For{($a \leq i \leq b-1$) }
-        \State temp\_G1 $\leftarrow$ reg\_G(r\_$\phi$, $a$, $i$, $n$)
-        \State \parbox[t]{.8\linewidth}{temp\_G2 $\leftarrow$ reg\_G(r\_$\psi$, $i+1$, \hspace*{5mm}$i+1$, $n$)}
-        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect( \hspace*{5mm}temp\_G1, temp\_G2, n)}
+        \State G1 $\leftarrow$ reg\_G($r_\phi$, $a$, $i$, $n$)
+        \State \parbox[t]{.8\linewidth}{G2 $\leftarrow$ reg\_G($r_\psi$, $i+1$, $i+1$, $n$)}
+        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect(G1,  \hspace*{5mm}G2, n)}
         \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
@@
 
-\subsection{Theoretical Correctness of the WEST Algorithm}
+\subsection{Proof of Correctness of WEST}
+\begin{theorem}[\emph{Theoretical Correctness of WEST}] \label{theocorrect}
+  Given a well-formed MLTL formula, The WEST Algorithm outputs the regular expressions of the satisfying computations as described in section \ref{regex}.
+\end{theorem}
+
 Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}.
@@
 defined in section \ref{regex}.
+
 \textit{Join} concatenates two sets of regular expressions $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$.
-\textit{Set\_intersect} takes as input two sets of regular expressions $R$ and $T$, where $R$ represents $r_1 | ...
-| r_a$ and $T$ represents $t_1 | ...
-| t_b$ such that each $r_i$ and $t_j$ are regular expressions over $\Sigma = \{`0', `1', `S', `,'\}$.
+\textit{Set\_intersect} takes as input two sets of regular expressions $R = \{r_0, ..., r_{a-1}\}$ and $T = \{t_0, ..., t_{b-1}\}$, such that each $r_i$
+and $t_j$ are regular expressions over $\Sigma =$ \{``$0$'' , ``$1$'', ``$S$'', ``$,$''\}.
 Assume that all strings of regular expressions are right padded to equal length. 
@@
 \begin{align*}
-    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^a \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^b \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^a \bigcup_{j = 0}^b \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
+    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^{a-1} \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^{b-1} \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^{a-1} \bigcup_{j = 0}^{b-1} \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
 \end{align*}
@@
 We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
-\textit{reg\_U} takes as input \textit{r\_phi} $=$ reg($\phi$) and \textit{r\_psi} $ = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
+\textit{reg\_U} takes as input $r_\phi =$ reg($\phi$) and $r_\psi = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
 The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$.
-In line $2$ of \textit{reg\_U}, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to \textit{r\_psi}, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
+In line $2$ of \textit{reg\_U}, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to $r_\psi$, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
 Next, the $\lor$ from $i = a + 1$ to $b - 1$ is computed by the for loop in line 4; lines 5 through 7 computes $\text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. 
@@
  \end{proof}
+
 For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
 In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, \top, \bot$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{U}$ match their respective space complexities.
-Thus the worst case time complexity is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$ as well.
-If in the worst case no simplification occurs in any call of \textit{set\_intersect}, space complexity remains unchanged, but simplifying a set of regular expressions is cubic in input size.
+\begin{theorem}[\emph{Time Complexity}]
+Given a well formed MLTL formula $\phi$, $\text{\emph{reg}}(\phi)$ has worst-case time complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
+\end{theorem}
+If in the worst case no simplification occurs in any call of \textit{set\_intersect}, space complexity remains unchanged, but simplifying a vector of regular expressions is cubic in input size.
 In practice however, both time and space complexities are much more optimistic than worst-case estimates.
@@
 \noindent\textbf{Simulation 1}
-For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. We obtain the following plots:\\
+For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. We obtain plots \ref{InVsOutputLen} and \ref{InLenVsRunTime}:\\
 \begin{minipage}{0.5 \textwidth}
@@
     \captionof{figure}{Input length vs output length.\vspace{3mm}}
-    \label{InputLengthVsOutputLength}
+    \label{InVsOutputLen}
     \end{figure}
@@
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{InputLengthVsRuntime}
+    \label{InLenVsRunTime}
     \end{figure}
 \end{minipage}\\
-\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both Figures \ref{InputLengthVsOutputLength} and \ref{InputLengthVsRuntime}, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InputLengthVsRuntime}.
+\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both Figures \ref{InVsOutputLen} and \ref{InLenVsRunTime}, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InLenVsRunTime}.
 \\
@@
 For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Here are some examples of generated formulas:
-$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain the following plots:\\
+$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain plots \ref{fig:InVsOutLen2} and \ref{fig:InLenVsRunTime2}:\\
 \begin{minipage}{0.5 \textwidth}
@@
     \captionof{figure}{Input length vs output length\vspace{3mm}}
-    \label{fig:InVsOutLen}
+    \label{fig:InVsOutLen2}
     \end{figure}
@@
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{fig:InLenVsRunTime}
+    \label{fig:InLenVsRunTime2}
     \end{figure}
@@
 \noindent\textbf{Simulation 3}
-For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. We obtain the following plots:\\
+For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. We obtain plots \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}:\\
 \begin{minipage}{0.5 \textwidth}
@@
 Some examples of generated formulas are: $\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
-We obtain the following plots:\\
+We obtain plots \ref{InLenVsOutLen4} and \ref{InLenVsRunTime4}:\\
 \begin{minipage}{0.5 \textwidth}
@@
     \centering
-    \begin{tikzpicture}[ node/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=10mm},
-    bignode/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=12mm},
+    \begin{tikzpicture}[ node/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=8mm},
+    bignode/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=10mm},
     star/.style={circle, draw=red!60, fill=red!5, thick, minimum size=1mm} ]
@@
 %
+\newpage
 \bibliographystyle{splncs04}
@@
 \begin{algorithmic}
-\Procedure{reg\_F}{set reg\_phi, int $a$, int $b$, int $n$, bool simp} 
+\Procedure{reg\_F}{set $r_\phi$, int $a$, int $b$, int $n$, bool simp} 
     \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
-    \State comp $\leftarrow$ reg\_phi
+    \State comp $\leftarrow$ $r_\phi$
     \If{$a > b$} return $\{\}$
@@
     \For{($1 \leq i \leq b-a$) }
-        \State temp\_phi $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_phi
-        \State comp $\leftarrow$ join(comp, temp\_phi, simp)
+        \State temp$_\phi$ $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + $r_\phi$
+        \State comp $\leftarrow$ join(comp, temp$_\phi$, simp)
     \EndFor
@@
 \begin{algorithmic}
-\Procedure{reg\_G}{set reg\_phi, int $a$, int $b$, int $n$, bool simp} 
+\Procedure{reg\_G}{set $r_\phi$, int $a$, int $b$, int $n$, bool simp} 
     \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
-    \State comp $\leftarrow$ reg\_phi 
+    \State comp $\leftarrow$ $r_\phi$ 
     \If{$a > b$} return $\{S^n\}$
@@
     \For{($1 \leq i \leq b-a$)}
-        \State temp\_phi $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + reg\_phi
-        \State comp $\leftarrow$ set\_intersect(comp, temp\_phi, simp)
+        \State temp$_\phi$ $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + $r_\phi$
+        \State comp $\leftarrow$ set\_intersect(comp, temp$_\phi$, simp)
     \EndFor
@@
 \begin{algorithmic}
-\Procedure{reg\_R}{set reg\_phi, set reg\_psi, int $a$, int $b$, int $n$, bool simp} 
-    \State comp $\leftarrow$ reg\_G(reg\_psi, $a$, $b$, $n$, simp)
+\Procedure{reg\_R}{set $r_\phi$, set $r_\psi$, int $a$, int $b$, int $n$, bool simp} 
+    \State comp $\leftarrow$ reg\_G($r_\psi$, $a$, $b$, $n$, simp)
     \If{$a > b$} return $\{S^n\}$
@@
     \For{($a \leq i \leq b-1$) }
-        \State temp\_comp $\leftarrow$ set\_intersect(reg\_G(reg\_psi, $a$, $i$, $n$), reg\_G(reg\_phi, $i$, $i$, $n$), $n$, simp)
+        \State temp\_comp $\leftarrow$ set\_intersect(reg\_G($r_\psi$, $a$, $i$, $n$), reg\_G($r_\phi$, $i$, $i$, $n$), $n$, simp)
         \State comp $\leftarrow$ join(comp, temp\_comp, simp)
@@
     %Nodes
-    \node[emptynode](inputs){set reg\_phi, integers a, b, n};
+    \node[emptynode](inputs){set $r_\phi$, integers a, b, n};
     \node[node](initialize)[below=of inputs]{Initialize string pre, set Comp};
@@
     %Nodes
-    \node[emptynode](inputs){set reg\_phi, reg\_psi and integers a, b, n};
+    \node[emptynode](inputs){set $r_\phi$, $r_\psi$ and integers a, b, n};
     \node[node](initialize)[below=of inputs]{Initialize set Comp};
@@
 
-    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, phi and call reg(phi, n)};
-    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F(phi)};
-    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G(phi)};
-
-    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, phi, psi};
-    \node[rednode](prop_phi)[below=of parse_binary_prop]{reg\_phi $\leftarrow$ reg(phi,n)};
-    \node[rednode](prop_psi)[below=of prop_phi]{reg\_psi $\leftarrow$ reg(psi,n)};
+    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, $\phi$ and call reg($\phi$, n)};
+    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F($\phi$)};
+    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G($\phi$)};
+
+    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, $\phi$, $\psi$};
+    \node[rednode](prop_phi)[below=of parse_binary_prop]{$r_\phi$ $\leftarrow$ reg($\phi$,n)};
+    \node[rednode](prop_psi)[below=of prop_phi]{$r_\psi$ $\leftarrow$ reg($\psi$,n)};
     \node[rednode](equals)[left=0.5cm of prop_psi]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};
@@
 
-    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, phi, psi};
-    \node[rednode](temp_phi)[below=of parse_binary_temp]{reg\_phi $\leftarrow$ reg(phi,n)};
-    \node[rednode](temp_psi)[below=of temp_phi]{reg\_psi $\leftarrow$ reg(psi,n)};
+    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, $\phi$, $\psi$};
+    \node[rednode](temp_phi)[below=of parse_binary_temp]{$r_\phi$ $\leftarrow$ reg($\phi$,n)};
+    \node[rednode](temp_psi)[below=of temp_phi]{$r_\psi$ $\leftarrow$ reg($\psi$,n)};
     \node[node](until)[below=of temp_psi]{return reg\_U};
@@
 
-    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] phi}};
+    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] $\phi$}};
     \node[emptynode](reg_g_text)[above=0.2cm of reg_g]{X is G};
@@
 
-    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is phi X[a,b] psi}$$~$$};
+    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is $\phi$ X[a,b] $\psi$}$$~$$};
     \node[emptynode](release_text)[above=0.2cm of release]{X is R};
@@
     \node[emptynode](assoc_text)[rotate=45, above=1.1cm of binary_temp_text]{\footnotesize{nnf is X[nnf\_array]}};
-    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for phi in nnf\_array};
-
-    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is phi X psi};
+    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for $\phi$ in nnf\_array};
+
+    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is $\phi$ X $\psi$};
     \node[emptynode](join_text)[above=0.2cm of join]{X is v};

### 2022-10-14 paper/Paper.tex
changes to title
last fixes to paper for submission

@@
 %
-\titlerunning{Abbreviated paper title}
+\titlerunning{MLTL Formula Validation Via Regular Expressions}
 % If the paper title is too long for the running head, you can set
@@
 %
+\vspace{-0.1in}
 %\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
@@
 
-\vspace{-0.1in}
+\vspace{-0.3in}
 \begin{abstract}
-        \noindent Mission-time Linear Temporal Logic (MLTL) is an extension of propositional logic that allows temporal quantifiers over finite discrete intervals.
-A computation is a finite sequence of truth assignments.
+  \noindent Mission-time Linear Temporal Logic (MLTL) represents the most practical fragment of Metric Temporal Logic; MLTL resembles the popular logic LTL with finite closed-interval integer bounds on the temporal operators.
+Increasingly many tools reason over MLTL specifications yet these tools are only useful when system designers can validate the input specifications.
+We design an automated characterization of the structure of the computations that satisfy a given MLTL formula using regular expressions.
+We prove soundness and completeness of our structure.
+We also give an algorithm for automated MLTL formula validation and analyze its complexity both theoretically and experimentally.
+Additionally, we generate a test suite using control flow diagrams to robustly test our implementation and release an open-source tool.
+The result of our contributions are improvements to existing algorithms for MLTL analysis applicable to many other tools and the WEST tool for automated, efficient MLTL formula validation.
+  %
+%        Our work connects existing tools to enable improvmeents in satisfiabiity tools and automated synthesis of verified code from MLTL behavior descriptions.
+% 
+  %
+%  A computation is a finite sequence of truth assignments.
 In this paper, we use regular expressions to describe the structure of the computations that satisfy a given MLTL formula.
@@
 %        Our work connects existing tools to enable improvmeents in satisfiabiity tools and automated synthesis of verified code from MLTL behavior descriptions.
+%
+% Contributions:
+%
 
         \vspace{-0.1in}
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Mission-time Linear Temporal Logic (MLTL)  \and MLTL Satisfiability \and Temporal Logic Validation.}
 \end{abstract}
 
-\vspace{-0.1in}
+\vspace{-0.4in}
 \section{Introduction}
@@
 We structure the paper around our contributions as follows.
-In section \ref{prereq}, we build on the semantics of MLTL to define a computation, and its bit string representation.
+In Section \ref{prereq}, we build on the semantics of MLTL to define a computation, and its bit string representation.
 % of a computation that is used throughout the paper and the WEST program.
@@
 %
-In section \ref{regex}, we recursively define regular expressions encapsulating the satisfying computations of MLTL formulas and prove that our new translation algorithm is both sound and complete.
+In Section \ref{regex}, we recursively define regular expressions encapsulating the satisfying computations of MLTL formulas and prove that our new translation algorithm is both sound and complete.
 In addition, we provide a calculation for the minimum computation length required to describe all the satisfying computations of a MLTL formula that slightly improves upon existing calculations in the literature.
@@
 %
-We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in section \ref{WESTalg} %, we give the WEST code specifications.
+We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in Section \ref{WESTalg} %, we give the WEST code specifications.
 In particular, we describe the grammar that the program follows and give an overview of the important functions in the program.
@@
 %We provide the proof for the minimum computation length of Until and Release below.
-\vspace{-0.1in}
+%\vspace{-0.1in}
 \begin{theorem}[\emph{Minimum Computation Length of Until and Release}]\label{thm1}
@@
 \begin{theorem}[\emph{Theoretical Correctness of WEST}] \label{theocorrect}
-  Given a well-formed MLTL formula, The WEST Algorithm outputs the regular expressions of the satisfying computations as described in section \ref{regex}.
+  Given a well-formed MLTL formula, The WEST Algorithm outputs the regular expressions of the satisfying computations as described in Section \ref{regex}.
 \end{theorem}
@@
 The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} take as input a MLTL formula of the appropriate form, and return the regular expression as %previously
-defined in section \ref{regex}.
+defined in Section \ref{regex}.
 
@@
 \textit{``If we consider a program to
-be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''} \\
+be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''} 
 Instead we utilize intelligent fuzzing (sometimes referred to as whitebox fuzzing), which is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
@@
 In comparison, the WEST program executed the same test suite in under thirty minutes on the same machine.
-One thing to note is that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the ``$S$'' characters in the regular expressions.
+Note that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the ``$S$'' characters in the regular expressions.
 For instance, the regular expression ``$1SS0SS1$'' yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
@@
 Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of ``$S$'' characters when a formula holds true for every computation.
-We first define some vocabulary.\\
+We first define some vocabulary.
  We say a regular expression composed entirely of ``$S$'' characters and commas is an \emph{arbitrary computation}.
@@
  One goal of this research project is to visually represent MLTL formulas as truth tables, similar to classical truth tables in propositional logic. 
-The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safe critical systems, and the WEST program can aide in the debugging of such specifications.
+The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safety-critical systems, and the WEST program can aid in the debugging of such specifications.
 The WEST program accomplishes this: given MLTL formula $\phi$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
 The tool itself has demonstratively reasonable run time. 
-Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very sparse in practice. 
+Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very rare in practice. 
 We have also applied techniques in intelligent fuzzing to explore the state space of the algorithm in a structured way. 
@@
 Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used in algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
-\subsection{Additional Research Directions}
+\subsection{Additional Research Directions} The resease of the WEST algorithm and open-source tool open many promising avenues for future research, including the following.\\
 \textbf{Describe all satisfying computations to LTL formulas using $\omega$-regular expressions.}
-$\omega$-regular expression are defined to match only infinite words, and can be used to describe satisfying computations to LTL formulas (which has infinite time steps). 
-Our original efforts were spent reasoning about the general LTL case before restricting to MLTL.
-Particular difficulties revolves around the need for the Kleene star operation, which leads to messy arithmetic of infinite unions and intersections of regular expressions.
+By definition, $\omega$-regular expressions match only infinite words, and can be used to describe satisfying computations to LTL formulas (which have infinite time steps). 
+Our work on validation for MLTL formulas lays the groundwork for future work on validation of the finite-trace logic LTLf \cite{GV13} as well as LTL formulas.
+For the infinite-trace semantics of LTL, the particular difficulties revolve around the need for the Kleene star operation, which may lead to blow-up due to arithmetic of infinite unions and intersections of regular expressions.
 \\
@@
 Additional care should be put into allowing for varying levels of abstractions of execution due to concerns of the path explosion problem.
+We note that such avenues for code-level verification will still be necessary even upon the completion of potential future work avenues like synthesizing the core implemention of the WEST algorithm from an interactive theorem prover.
+This is because the goal of explainability to humans will require at least some manual code authorship for the forseeable future.
+\\
+\noindent \textbf{Synthesizing verified code from MLTL behavior descriptions.} The truth tables generated by the WEST tool can now serve as input to a recently-published toolchain \cite{dasc-2022}.
+This newly-enabled workflow would produce encodings of the represented MLTL behavior for the interactive theorem prover ACL2, including automatically generating related properties of general interest such as unambiguousness \cite{DBLP:journals/corr/abs-2205-11707,ACL2-Site,ACL2-Doc}.
+Next, a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL.
+By providing a new front-end for this toolchain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system.
+Considering the rising popularity of MLTL for describing such behaviors, we expect this to be a rewarding avenue for future exploration.
+
 % FUTURE WORK:

### 2022-10-15 paper/Paper.tex
fixed typos and inconsistent formatting

@@
   \noindent Mission-time Linear Temporal Logic (MLTL) represents the most practical fragment of Metric Temporal Logic; MLTL resembles the popular logic LTL with finite closed-interval integer bounds on the temporal operators.
-Increasingly many tools reason over MLTL specifications yet these tools are only useful when system designers can validate the input specifications.
+Increasingly, many tools reason over MLTL specifications, yet these tools are only useful when system designers can validate the input specifications.
 We design an automated characterization of the structure of the computations that satisfy a given MLTL formula using regular expressions.
@@
 We can cite examples of this from NASA's Automated Airspace Concept \cite{EH10}, the U.~S.~Navy's Aircraft Carrier Deck Scheduler \cite{RCRBS11}, the JAXA-NASA Global Precipitation Measurement (GPM) Observatory \cite{GPM}, and many others.
-Formal methods provide continuously-advancing tools and techniques to rigorously analyze timelines expressed in the form of temporal logic requirements, from early design-time model checking and theorem proving to on-board runtime verification.
+Formal methods provide continuously advancing tools and techniques to rigorously analyze timelines expressed in the form of temporal logic requirements, from early design-time model checking and theorem proving to on-board runtime verification.
 The U.~S.~Federal Aviation Administration (FAA) even advocates the use of formal methods for flight certification of these critical systems \cite{DO-178C,DO-254,DO-333}.
@@
 
-Many specifications from case studies, in logics such as MTL \cite{AH90} and STL \cite{MN04} fall within the MLTL fragments of these logics. 
-Variations on Metric Temporal Logic (MTL) such as MLTL grow increasingly popular, in part due to their comparatively tractable complexity-to-expressibility trade-offs \cite{OW08}.
+Many specifications from case studies, in logics such as MTL \cite{AH90} and STL \cite{MN04}, fall within the MLTL fragments of these logics. 
+Variations on Metric Temporal Logic (MTL) such as MLTL have grown increasingly popular, in part due to their comparatively tractable complexity-to-expressibility trade-offs \cite{OW08}.
 The model checker {\sf nuXmv} encodes a popular subset of MLTL for use in symbolic model checking \cite{nuXmv-v1.1.0}.%, where the $\Box$ and $\Diamond$ operators of an \texttt{LTLSPEC} can have integer bounds \cite{nuXmv-v1.1.0}, though bounds cannot be placed on the $\U$ or $\V$ (the Release operator of \nuxmv) operators.
@@
 We structure the paper around our contributions as follows.
-In Section \ref{prereq}, we build on the semantics of MLTL to define a computation, and its bit string representation.
+In Section \ref{prereq}, we build on the semantics of MLTL to define a computation and its bit string representation.
 % of a computation that is used throughout the paper and the WEST program.
@@
 %
-We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in Section \ref{WESTalg} %, we give the WEST code specifications.
-In particular, we describe the grammar that the program follows and give an overview of the important functions in the program.
-%
+We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in Section \ref{WESTalg}
 and calculate its space and time complexity, both theoretically and experimentally.
@@
 {\bf Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
-The syntax of an MLTL formula $\phi$ over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
+The syntax of a MLTL formula $\phi$ over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
 \vspace{-0.1in}
@@
 \vspace{-0.1in}
-We extend the standard definition of Regular Expressions (regex) \cite{sipser} to introduce notation that describes the satisfying computations of an MLTL formula.
+We extend the standard definition of Regular Expressions (Regex) \cite{sipser} to introduce notation that describes the satisfying computations of an MLTL formula.
 \begin{definition}[\emph{Temporal Regular Expression}] \label{TRE} 
@@
  \item \emph{(Alternation)} $R \lor T$ describes the set union of the strings generated by $R$ and $T$.
-\item Pad($R$, $T$) determines which regular expression is longer and concatenate $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
-Note that in the bit string representation, $(,S^n)$, denotes a time step in which the truth value of all $n$ propositional variables does not matter.
+\item Pad($R$, $T$) determines which regular expression is longer and concatenates $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
+Note that in the bit string representation, $(,S^n)$ denotes a time step in which the truth value of all $n$ propositional variables does not matter.
 \item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
@@
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
-Since $T$ is the longer regex by one time step, we concatenate ``$,S^2$'' to the right of $R$.
+Since $T$ is the longer regex by one time step, we concatenate $(,S^2)$ to the right of $R$.
 Thus $T =1S,1S | S1,S1$ and $R = S1,SS$.
@@
 To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{``$0$'' , ``$1$'', ``$,$''\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
-Let $p_0, p_1, ..., p_{n-1}$ be propositional variables, $\phi, \psi$ well-formed MLTL formulas in negation normal form.
-We define the regular expression of satisfying computations for an MLTL formula as follows:\\
+Let $p_0, p_1, ..., p_{n-1}$ be propositional variables and $\phi, \psi$ well-formed MLTL formulas in negation normal form.
+We define the regular expression of satisfying computations for a MLTL formula as follows:\\
 
@@
     Let $0 \leq a\leq b \in \mathbb{N}$ and let $\phi, \psi$ be well-formed MLTL formulas in NNF.
-The minimum computation length of Until and Release is given by $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$.
+The minimum computation length of \emph{Until} and \emph{Release} is given by $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$.
 \end{theorem}
@@
 \begin{proof}
-The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for \texttt{Until} and \texttt{Release} and the minimum computation lengths for \texttt{Future}, \texttt{Globally}, \texttt{AND}, and \texttt{OR}.\\
+The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Globally, AND, and OR.\\
  Recall that $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$. Thus
@@
 For convenience, we use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_0, ..., t_{n-1}\} = \bigcup_{i=0}^{n-1} t_i$. 
-Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{F}$. 
-Note how reg\_U parallels the regular expression defined for $\mathcal{F}$, and the algorithms for the other three temporal operators follow an identical structure.
+Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{U}$. 
+Note how \texttt{reg\_U} parallels the regular expression defined for $\mathcal{U}$, and the algorithms for the other three temporal operators follow an identical structure.
 
@@
 \end{theorem}
-
-Correctness of the WEST algorithm is dependent on the correctness of subroutines \textit{reg\_prop\_cons}, \textit{reg\_prop\_var}, \textit{join}, \textit{set\_intersect}, \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, and \textit{reg\_R}.
-The routines \textit{reg\_prop\_cons} and \textit{reg\_prop\_var} take as input a MLTL formula of the appropriate form, and return the regular expression as %previously
-defined in Section \ref{regex}.
-
-\textit{Join} concatenates two sets of regular expressions $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$.
-\textit{Set\_intersect} takes as input two sets of regular expressions $R = \{r_0, ..., r_{a-1}\}$ and $T = \{t_0, ..., t_{b-1}\}$, such that each $r_i$
+Correctness of the WEST algorithm is dependent on the correctness of subroutines \texttt{reg\_prop\_cons}, \texttt{reg\_prop\_var}, \texttt{join}, \texttt{set\_intersect}, \texttt{reg\_F}, \texttt{reg\_G}, \texttt{reg\_U}, and \texttt{reg\_R}.
+The routines \texttt{reg\_prop\_cons} and \texttt{reg\_prop\_var} take as input a MLTL formula of the appropriate form and return the regular expression defined in Section \ref{regex}.\\
+\texttt{Join} concatenates two sets of regular expressions $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$.
+\texttt{set\_intersect} takes as input two sets of regular expressions $R = \{r_0, ..., r_{a-1}\}$ and $T = \{t_0, ..., t_{b-1}\}$, such that each $r_i$
 and $t_j$ are regular expressions over $\Sigma =$ \{``$0$'' , ``$1$'', ``$S$'', ``$,$''\}.
 Assume that all strings of regular expressions are right padded to equal length. 
-We show that $\mathscr{L}(\textit{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$:
-\begin{align*}
-    \mathscr{L}(R) \cap \mathscr{L}(T) &= \left(\bigcup_{i = 0}^{a-1} \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^{b-1} \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^{a-1} \bigcup_{j = 0}^{b-1} \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).
-\end{align*}
-The for loop in line 3 of \textit{set\_intersect} computes the union of \textit{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
+We show that $\mathscr{L}(\texttt{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$:
+\vspace{-3mm}$$\mathscr{L}(R) \cap \mathscr{L}(T) = \left(\bigcup_{i = 0}^{a-1} \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^{b-1} \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^{a-1} \bigcup_{j = 0}^{b-1} \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).$$
+The loop in line 3 of \texttt{set\_intersect} computes the union of \texttt{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\texttt{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
 Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. 
-$\textit{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$.
+$\texttt{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$.
 Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. 
-Thus $\mathscr{L}(\textit{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.
-
-The correctness for \textit{reg\_F}, \textit{reg\_G}, \textit{reg\_U}, \textit{reg\_R}, and \textit{reg} will be proven by induction on depth of recursion to \textit{reg}. 
+Thus $\mathscr{L}(\texttt{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.\\
+The correctness for \texttt{reg\_F}, \texttt{reg\_G}, \texttt{reg\_U}, \texttt{reg\_R}, and \texttt{reg} will be proven by induction on depth of recursion to \texttt{reg}. 
 The depth of recursion is exactly the depth of the parse tree of the input formula.
-For the base case (depth $0$), \textit{reg\_prop\_var} and \textit{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.
-Then assume \textit{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$. 
+For the base case (depth $0$), \texttt{reg\_prop\_var} and \texttt{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.
+Then assume \texttt{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$. 
 Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$.
-$\gamma$ must be of the form $\phi \lor \psi$, $\phi \land \psi$, $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are positive integers.
+$\gamma$ must be of the form $\phi \lor \psi$, $\phi \land \psi$, $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are nonnegative integers.
 Correctness of the first two cases have been proven. 
-The proof for the four temporal cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \textit{join} and \textit{set\_intersect}.
-
+The proof for the four temporal cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \texttt{join} and \texttt{set\_intersect}.\\
 We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
-\textit{reg\_U} takes as input $r_\phi =$ reg($\phi$) and $r_\psi = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
+\texttt{reg\_U} takes as input $r_\phi =$ reg($\phi$) and $r_\psi = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
 The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$.
-In line $2$ of \textit{reg\_U}, the variable \textit{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to $r_\psi$, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
+In line $2$ of \texttt{reg\_U}, the variable \texttt{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to $r_\psi$, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
 Next, the $\lor$ from $i = a + 1$ to $b - 1$ is computed by the for loop in line 4; lines 5 through 7 computes $\text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. 
-This shows correctness of \textit{reg\_U} (note that in a complete proof, correctness of \textit{reg\_G} needs to be shown first since lines 5 and 6 calls \textit{reg\_G}).
-Continuing in the same fashion to prove the other three cases, \textit{reg} is correct on all depth $d+1$ inputs, and thus \textit{reg} is correct on all inputs by induction.
+This shows correctness of \texttt{reg\_U} (note that in a complete proof, correctness of \texttt{reg\_G} needs to be shown first since lines 5 and 6 calls \texttt{reg\_G}).
+Continuing in the same fashion to prove the other three cases, \texttt{reg} is correct on all depth $d+1$ inputs, and thus \texttt{reg} is correct on all inputs by induction.
 
@@
 For any function $f(\phi)$ taking a string argument $\phi$, we use $|\phi|$ to denote the number of characters in $\phi$ and $S(f(\phi))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
-\hspace{3mm} If $\phi$ is a propositional constant or variable, it's easy to see that $S(\text{\emph{reg}}(\bot)) = 0$ since only the empty set is returned.
-By definition $\text{\emph{reg}}(\top) = S^n$, so we have that $S(\text{\emph{reg}}(\top)) = O(n)$.
-Similarly, $\text{\emph{reg}}(p_k)$ and $\text{\emph{reg}}(\neg p_k)$ both return strings of the same length and thus $S(\text{\emph{reg}}(p_k)) = S(\text{\emph{reg}}(\neg p_k)) = S(\text{\emph{reg}}(\top)) = n$.\\
-\hspace{3mm} If $\phi$ is ``$\phi_{1} \lor \phi_{2}$'' we return $\textit{join}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}))$, which simply concatenates the contents of the two sets. 
-Thus $S(\text{\emph{reg}}(\phi_{1} \lor \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) + S(\text{\emph{reg}}(\phi_{2})).$\\
+\hspace{3mm} If $\phi$ is a propositional constant or variable, it's easy to see that $S(\texttt{reg}(\bot)) = 0$ since only the empty set is returned.
+By definition $\texttt{reg}(\top) = S^n$, so we have that $S(\texttt{reg}(\top)) = O(n)$.
+Similarly, $\texttt{reg}(p_k)$ and $\texttt{reg}(\neg p_k)$ both return strings of the same length and thus $S(\texttt{reg}(p_k)) = S(\texttt{reg}(\neg p_k)) = S(\texttt{reg}(\top)) = n$.\\
+\hspace{3mm} If $\phi$ is ``$\phi_{1} \lor \phi_{2}$'' we return $\texttt{join}(\texttt{reg}(\phi_{1}), \texttt{reg}(\phi_{2}))$, which simply concatenates the contents of the two sets. 
+Thus $S(\texttt{reg}(\phi_{1} \lor \phi_{2})) = S(\texttt{reg}(\phi_{1})) + S(\texttt{reg}(\phi_{2})).$\\
 \hspace{3mm} If $\phi$ is ``$\phi_{1} \land \phi_{2}$''
-$ \textit{set\_intersect}(\text{\emph{reg}}(\phi_{1}), \text{\emph{reg}}(\phi_{2}), n)$ returns a set of size $S(A) \cdot S(B)$ in the worst case when no simplification can be made. 
-Thus, our space complexity is $S(\text{\emph{reg}}(\phi_{1} \land \phi_{2})) = S(\text{\emph{reg}}(\phi_{1})) \cdot S(\text{\emph{reg}}(\phi_{2})).$\\
+$ \texttt{set\_intersect}(\texttt{reg}(\phi_{1}), \texttt{reg}(\phi_{2}), n)$ returns a set of size $S(A) \cdot S(B)$ in the worst case when no simplification can be made. 
+Thus, our space complexity is $S(\texttt{reg}(\phi_{1} \land \phi_{2})) = S(\texttt{reg}(\phi_{1})) \cdot S(\texttt{reg}(\phi_{2})).$\\
 \hspace{3mm} For the next cases, we use these two bounds and define the constants $\mathcal{C}_G$ and $\mathcal{C}_F$:
@@
 \hspace{3mm} If $\phi \text{ is } ``\mathcal{G}_{[a,b]} \phi_{1}$":
-recall that $\text{\emph{reg}}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi) (,S^n)^{b-i}$.
-From the analysis of \textit{set\_intersect}, worst case space complexity is multiplicative.
-Thus\\ $\text{S(\emph{reg}}(\phi)) = \prod_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_G \text{S(\emph{reg}}(\phi_1))$.
+recall that $\texttt{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \texttt{reg}(\phi) (,S^n)^{b-i}$.
+From the analysis of \texttt{set\_intersect}, worst case space complexity is multiplicative.
+Thus\\ $S(\texttt{reg}(\phi)) = \prod_{i=a}^{b} (n+1)i \cdot S(\texttt{reg}(\phi_{1})) < \mathcal{C}_G S(\texttt{reg}(\phi_1))$.
 In this calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a set of only length 1 strings. \\
 \hspace{3mm} If $\phi \text{ is } ``\mathcal{F}_{[a,b]} \phi_{1}$":
-Recall that $\text{\emph{reg}}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{\emph{reg}}(\phi)(,S^n)^{b-i}$. \\
-From the analysis of \textit{join}, worst case space complexity is additive and thus 
-$\text{S(\emph{reg}}(\phi)) = \sum_{i=a}^{b} (n+1)i \cdot \text{S(\emph{reg}}(\phi_{1})) < \mathcal{C}_{F} \text{S(\emph{reg}}(\phi_1)$.\\
+Recall that $\texttt{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \texttt{reg}(\phi)(,S^n)^{b-i}$. \\
+From the analysis of \texttt{join}, worst case space complexity is additive and thus 
+$S(\texttt{reg}(\phi)) = \sum_{i=a}^{b} (n+1)i \cdot S(\texttt{reg}(\phi_{1})) < \mathcal{C}_{F} S(\texttt{reg}(\phi_1))$.\\
 \hspace{3mm}If $\phi$ = $``\phi_1 \mathcal{U}_{[a, b]} \phi_2"$: Recall that
-    $\text{\emph{reg}}(\phi_1 \ \mathcal{U}_{[a,b]} \phi_2) =  \bigvee_{i=a}^{b} \text{\emph{reg}}\left(\mathcal{G}_{[a,i-1]}\phi_1 \land \mathcal{G}_{[i, i]} \phi_2\right)$.
-    We can bound $S(\text{\emph{reg}}(\mathcal{G}_{[i, i]} \phi_2))$ by $(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
+    $\texttt{reg}(\phi_1 \ \mathcal{U}_{[a,b]} \phi_2) =  \bigvee_{i=a}^{b} \texttt{reg}\left(\mathcal{G}_{[a,i-1]}\phi_1 \land \mathcal{G}_{[i, i]} \phi_2\right)$.
+    We can bound $S(\texttt{reg}(\mathcal{G}_{[i, i]} \phi_2))$ by $(n+1) \cdot i \cdot S(\texttt{reg}(\phi_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
     Thus using our previous results for the $\mathcal{G}$, $\land$ and $\lor$ operators, we have that:
@@
     \begin{align*}
-        S(\text{\emph{reg}}(\phi)) &= 
-        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
-        [(n+1) \cdot i \cdot S(\text{\emph{reg}}(\phi_2))] \\
-        &< \delta [((n+1)(b-1) + 1) \cdot S(\text{\emph{reg}}(\phi_1))]^\delta 
-        [(n+1) \cdot b \cdot S(\text{\emph{reg}}(\phi_2))] \\
-        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2)) \\
-        &= \mathcal{C}_U \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))
+        S(\texttt{reg}(\phi)) &= 
+        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\texttt{reg}(\phi_1))]^\delta 
+        [(n+1) \cdot i \cdot S(\texttt{reg}(\phi_2))] \\
+        &< \delta [((n+1)(b-1) + 1) \cdot S(\texttt{reg}(\phi_1))]^\delta 
+        [(n+1) \cdot b \cdot S(\texttt{reg}(\phi_2))] \\
+        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2)) \\
+        &= \mathcal{C}_U \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2))
     \end{align*}
@@
 \hspace{3mm} If $\phi$ = $``\phi_1 \mathcal{R}_{[a, b]} \phi_2"$:
-    $\text{\emph{reg}}(\phi_1 \mathcal{R}_{[a,b]} \phi_2) =  \text{\emph{reg}}\left(\mathcal{G}_{[a,b]}\phi_2\right) \lor \bigvee_{i=a}^{b-1} \text{\emph{reg}}\left(\mathcal{G}_{[a,i]}\phi_2 \land \mathcal{G}_{[i, i]} \phi_1\right)$.
+    $\texttt{reg}(\phi_1 \mathcal{R}_{[a,b]} \phi_2) =  \texttt{reg}\left(\mathcal{G}_{[a,b]}\phi_2\right) \lor \bigvee_{i=a}^{b-1} \texttt{reg}\left(\mathcal{G}_{[a,i]}\phi_2 \land \mathcal{G}_{[i, i]} \phi_1\right)$.
 Thus, a similar argument to the $\mathcal{U}$ case shows
-    $S(\text{\emph{reg}}(\phi)) < \mathcal{C}_R \cdot S(\text{\emph{reg}}(\phi_1))^\delta \cdot S(\text{\emph{reg}}(\phi_2))$, \\
+    $S(\texttt{reg}(\phi)) < \mathcal{C}_R \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2))$, \\
     where $\mathcal{C}_R = \mathcal{C}_G \cdot \delta (n+1)d$.
@@
 \begin{theorem}[\emph{Space Complexity}]
-Given a well formed MLTL formula $\phi$, $\text{\emph{reg}}(\phi)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
+Given a well formed MLTL formula $\phi$, $\emph{\texttt{reg}}(\phi)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
 \end{theorem}
@@
 \mathcal{U}_{[a_{\ell - 1}, b_{\ell - 1}]} p_{\ell - 1}) \mathcal{U}_{[a_\ell, b_\ell]} p_\ell$$ where there are $\ell$ logical connectives $\mathcal{U}$ and $n = \ell + 1$ propositional variables.\\
-    We'll derive the complexity of $S(\text{\emph{reg}}(\phi))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\text{\emph{reg}}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\text{\emph{reg}}(p_{k+1}))$.
+    We'll derive the complexity of $S(\texttt{reg}(\phi))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\texttt{reg}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\texttt{reg}(p_{k+1}))$.
 The recurrence relation captures an extra nesting of the $\mathcal{U}$ operator, based on the complexity of $\mathcal{U}$ defined above.
@@
     \end{align*}
-    Thus we have that $S(\text{\emph{reg}}(\phi)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
+    Thus we have that $S(\texttt{reg}(\phi)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
  \end{proof}
@@
 For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
-In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, \top, \bot$, as well as that of set intersection, \textit{join}, and the operator $\mathcal{U}$ match their respective space complexities.
+In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, \top, \bot$, as well as that of \texttt{set\_intersect}, \texttt{join}, and the operator $\mathcal{U}$ match their respective space complexities.
 \begin{theorem}[\emph{Time Complexity}]
-Given a well formed MLTL formula $\phi$, $\text{\emph{reg}}(\phi)$ has worst-case time complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
+Given a well formed MLTL formula $\phi$, $\emph{\texttt{reg}}(\phi)$ has worst-case time complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
 \end{theorem}
-If in the worst case no simplification occurs in any call of \textit{set\_intersect}, space complexity remains unchanged, but simplifying a vector of regular expressions is cubic in input size.
+If in the worst case no simplification occurs in any call of \texttt{set\_intersect}, space complexity remains unchanged, but simplifying a set of regular expressions is cubic in input size.
 In practice however, both time and space complexities are much more optimistic than worst-case estimates.
@@
 We ran these experiments on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
-For each simulation, we generated 1000 MLTL formulas using the parameters DELTA, INTERVAL\_MAX, number of propositional variables, and number of iterations.
-DELTA is the maximum length we allow for any interval.
-INTERVAL\_MAX is the largest allowed upper bound for any interval.
+For each simulation, we generated 1000 MLTL formulas using the parameters \texttt{delta}, \texttt{interval\_max}, number of propositional variables, and number of iterations.
+\texttt{delta} is the maximum length we allow for any interval.
+\texttt{interval\_max} is the largest allowed upper bound for any interval.
 Number of iterations refers to the level of nesting in the generated formulas.
@@
 We measure the number of characters in the output and the amount of time in milliseconds taken to run the program.
-Note that these simulations run the \textit{reg} function with the subformula boolean set to false and the simplify boolean set to true.\\
+Note that these simulations run the \texttt{reg} function with the subformula boolean set to false and the simplify boolean set to true.\\
 \noindent\textbf{Simulation 1}
-For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX. We obtain plots \ref{InVsOutputLen} and \ref{InLenVsRunTime}:\\
+For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}. We obtain plots \ref{InVsOutputLen} and \ref{InLenVsRunTime}:\\
 \begin{minipage}{0.5 \textwidth}
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim1Length_large.png}
+    \includegraphics[scale=0.35]{images/Sim1Length_large.png}
     \captionof{figure}{Input length vs output length.\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim1Time_large.png}
+    \includegraphics[scale=0.35]{images/Sim1Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
 \noindent\textbf{Simulation 2}
-For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for DELTA, and 20 for INTERVAL\_MAX. Here are some examples of generated formulas:
+For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for \texttt{delta}, and 20 for \texttt{interval\_max}. Here are some examples of generated formulas:
 $\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain plots \ref{fig:InVsOutLen2} and \ref{fig:InLenVsRunTime2}:\\
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim2Length_large.png}
+    \includegraphics[scale=0.35]{images/Sim2Length_large.png}
     \captionof{figure}{Input length vs output length\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim2Time_large.png}
+    \includegraphics[scale=0.35]{images/Sim2Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
 \noindent\textbf{Simulation 3}
-For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for DELTA, and 10 for INTERVAL\_MAX. We obtain plots \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}:\\
+For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for \texttt{delta}, and 10 for \texttt{interval\_max}.
+We obtain plots \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}:\\
 \begin{minipage}{0.5 \textwidth}
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim3Length_large.png}
+    \includegraphics[scale=0.35]{images/Sim3Length_large.png}
     \captionof{figure}{Input length vs output length\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim3Time_large.png}
+    \includegraphics[scale=0.35]{images/Sim3Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
 \noindent\textbf{Simulation 4}
-For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for DELTA, and 10 for INTERVAL\_MAX.
+For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}.
 Some examples of generated formulas are: $\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim4Length_large.png}
+    \includegraphics[scale=0.35]{images/Sim4Length_large.png}
     \captionof{figure}{Input length vs output length\vspace{3mm}}
@@
     \centering
-    \includegraphics[scale=0.38]{images/Sim4Time_large.png}
+    \includegraphics[scale=0.35]{images/Sim4Time_large.png}
     \captionof{figure}{Input length vs run time.\vspace{3mm}}
@@
 \section{Correctness of WEST Tool Implementation} \label{test}
-We accompany our proof of algorithmic correctness with a rigorous evaluation of implementation correctness: that our WEST tool correctly implements our WEST algorithm.
-% The correctness of an abstract algorithm one can describe on pencil and paper differs from the correctness of an actual implementation of the algorithm (the program).
-%On one hand, correctness of an algorithm is assured by mathematical analysis of the algorithm on all possible inputs and showing that it behaves as desired. 
-%However, assuring correctness of the program is a difficult task.
+We accompany our proof of algorithmic correctness with a rigorous evaluation of implementation correctness, showing that our WEST tool correctly implements our WEST algorithm.
 Since our proof of algorithmic correctness is manual and our focus is on usability for validation by humans, we utilize more traditional techniques for robust software engineering with testing-based evaluation.
 An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
-Since the primary purpose of the WEST tool is validation of formulas for humans, we focused on writing a tool with an intuitive human-facing interface then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.
-
+Since the primary purpose of the WEST tool is validation of formulas for humans, we focused on writing a tool with an intuitive human-facing interface and then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.\\
 One na\"ive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
@@
 Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; we employ fuzz testing (also know as fuzzing), a form of negative testing.
-%The earliest use of fuzzing by Miller \cite{Miller} was to discover bugs in Unix utilities by randomly generating command line inputs, and monitoring for unexpected crashes or security.
-This style of black box testing assumes no prior knowledge of the target program, and is centered on generating a large quantity of inputs.
-Miller describes his approach in \cite{Miller} as follows: \\
-We deviate from traditional black-box fuzzing defined by \cite{Miller} as follows: \\
+We deviate from traditional black-box fuzzing defined by \cite{Miller}:
 \textit{``If we consider a program to
-be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''} 
+be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''}\\
 Instead we utilize intelligent fuzzing (sometimes referred to as whitebox fuzzing), which is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
@@
  We can represent the state space of the WEST algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
- The core of the WEST program lies in the recursive routine, \textit{reg}, which calls the $8$ different subroutines %discussed earlier,
- as shown in \ref{fig:abstracted graph}.
+ The core of the WEST program lies in the recursive routine, \texttt{reg}, which calls the $8$ different subroutines as shown in \ref{fig:abstracted graph}.
 \begin{figure}[t]
@@
 
-    \caption{Abstracted graph of the \textit{reg} main routine. Red nodes signal recursive calls to \textit{reg} on sub formulas of the input formula.}
+    \caption{Abstracted graph of the \texttt{reg} main routine. Red nodes signal recursive calls to \texttt{reg} on sub formulas of the input formula.}
     \label{fig:abstracted graph}
@@
 \subsubsection{Creating the Test Suite} %KYR: edited to remove excessive passive voice (active voice is best for research papers!)
-To generate our intelligent fuzzing test suite, 
-first, we count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
-For $d = 0$, only the paths leading to \textit{prop\_var} and \textit{prop\_cons} can be explored, so $\phi(0) = 2$.
-For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \textit{reg\_G} and \textit{reg\_F} is counted in the linear term, and paths to \textit{reg\_U}, \textit{reg\_R}, \textit{set\_intersect}, and \textit{join} is counted by the quadratic term.
+To generate our intelligent fuzzing test suite, we first count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
+For $d = 0$, only the paths leading to \texttt{prop\_var} and \texttt{prop\_cons} can be explored, so $\phi(0) = 2$.
+For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \texttt{reg\_G} and \texttt{reg\_F} is counted in the linear term, and paths to \texttt{reg\_U}, \texttt{reg\_R}, \texttt{set\_intersect}, and \texttt{join} is counted by the quadratic term.
 This gives $\phi(1) = 20$, $\phi(2) = 1640$, and $\phi(3) = 10761680$. 
@@
 Firstly, the $d = 0$ test suite consists of two formulas: a propositional variable or its negation, and a propositional constant. 
-Then for any $d \geq 1$, we iterate through all formulas in the depth $d-1$ test suite for \textit{reg\_G} and \textit{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths.
+Then for any $d \geq 1$, we iterate through all formulas in the depth $d-1$ test suite for \texttt{reg\_G} and \texttt{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths.
 To ensure wider coverage, we randomly generate each of the propositional variables or their negation and propositional constants.
 \subsubsection{Verifying against Na\"ive Brute Force}
- A relatively straightforward approach to generating the set of all satisfying computations of an MLTL formula $\phi$ over $n$ variables, such that $m = \text{cplen}(\phi)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
-An interpreter function takes two arguments of computation $\pi$ and MLTL formula $\phi$ and determines if $\pi \vDash \phi$ purely based on the semantics that define MLTL.
+A relatively straightforward approach to generating the set of all satisfying computations of a MLTL formula $\phi$ over $n$ variables, such that $m = \text{cplen}(\phi)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
+An interpreter function takes computation $\pi$ and MLTL formula $\phi$ and determines if $\pi \vDash \phi$ purely based on the semantics that define MLTL.
 Our test program translates every first-order quantifier into a loop; then checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
-The full implementation details are available in the WEST %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} %KYR: blind review
-{GitHub} repository.\footnote{Links have been redacted for blind review.} 
-%As expected for a brute force implementation, extensive run time poses a major limitation; the previously mentioned infeasibility of not abstracting away subroutines and running test suites for deeper depths is primarily caused by this stage of verification.
+The full implementation details are available in the WEST GitHub repository.\footnote{Links have been redacted for blind review.} 
 On an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM, the brute force program took nearly nine hours to execute the depth two test suite of $1640$ formulas. 
@@
 For the purposes of the following theorem, we remove all commas from computations.
-We say ``0'' or a ``1'' in a regular expression is a \emph{fixed truth value}.
+We say a ``0'' or a ``1'' in a regular expression is a \emph{fixed truth value}.
 We overload the definition of a matrix and say that a \emph{matrix} is a representation of a union of regular expressions, where each row is a regular expression.
@@
 \end{figure}
-
 For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
 Next, it is possible that a regular expression could be appended with a substring of ``$S$'' characters at the beginning or end.
-
 \begin{figure}[h!]
@@
 The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safety-critical systems, and the WEST program can aid in the debugging of such specifications.
-The WEST program accomplishes this: given MLTL formula $\phi$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
+The WEST program accomplishes this: given a MLTL formula $\phi$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
 The tool itself has demonstratively reasonable run time. 
@@
 However, basing testing on a (manually constructed) graph of the algorithm provides a middle ground where some level of coverage is guaranteed. 
-Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used in algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
-\subsection{Additional Research Directions} The resease of the WEST algorithm and open-source tool open many promising avenues for future research, including the following.\\
+Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used for algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
+\subsection{Additional Research Directions} The release of the WEST algorithm and open-source tool open many promising avenues for future research, including the following.\\
 \textbf{Describe all satisfying computations to LTL formulas using $\omega$-regular expressions.}
@@
 A tool to systematically convert a recursive algorithm (perhaps written in some strictly defined pseudocode syntax) into a directed graph representation of the state space would be a helpful aid for generating test suites.
-Significant efforts were made to construct the graph of the WEST algorithm by hand, and an automated process would invaluable. 
+Significant efforts were made to construct the graph of the WEST algorithm by hand, and an automated process would be invaluable. 
 Additional care should be put into allowing for varying levels of abstractions of execution due to concerns of the path explosion problem.
@@
  We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
-
- %KYR: TODO: label this theorem 2!!!!!!!!!!!!!!!!!!!!!!
+\begingroup
+\renewcommand\thetheorem{2}
  \begin{theorem}[\emph{Soundness and Completeness}]
@@
 \end{theorem}
+\endgroup
  \begin{proof}
  We proceed by induction on the length of the formula.\\
-
  \noindent \textbf{Base Cases.}\\
@@
 Padding conventions extends this to the set of all computations of any positive number of time steps, so we are done.\\
-
  \noindent\textbf{reg($\bot$)}\\
  There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\
-
  \noindent\textbf{reg($p_k$)}\\
@@
  which is precisely reg($p_k$).\\
-
  \noindent\textbf{reg($\neg p_k$)}\\
@@
  which is precisely reg($\neg p_k$).\\
-
  \noindent\textbf{Inductive Step.}\\
@@
 We now show that it holds for $\varphi \land \psi$, $\varphi \lor \psi$, $\mathcal{F}_{[a,b]} \varphi$, $\mathcal{G}_{[a,b]} \varphi$, $\varphi \ \mathcal{U}_{[a,b]} \psi$, and $\varphi \mathcal{R}_{[a,b]} \psi$.\\
-
  \noindent \textbf{reg($\varphi \land \psi$)}\\
@@
  $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$
-
  \noindent \textbf{reg($\varphi \lor \psi$)}\\
@@
  $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$
-
  \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
@@
  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
-
  \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
@@
  $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
-
  \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
@@
   $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
-
   \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
@@
 Hence
-
   \begin{align*}
@@
   \end{align*}
-
  \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
@@
 \section{Nested Until and Release Rewriting Theorem} \label{Appendix-NestedUR}
-
+\begingroup
+\renewcommand\thetheorem{3}
  \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}] \label{NestedUR}
@@
 \end{theorem}
+\endgroup
 The proof of Theorem \ref{NestedUR} appears below.
-
-%KYR: this totally goes here in the journal version but in an appendix/on a website for the conference version
-
 \begin{proof}
-
 \textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\
-
 \noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
-Then, $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
-
+Then,  $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and\\ $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
 \begin{align*}
@@
 This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
-
 \noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
-We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,  \\
+We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,
 \begin{align*}
@@
  \end{lemma}
-
 \begin{proof} $ $\newline
@@
 \indent Again the 3 cases are exhaustive of all cases in the assumption, this we have the ($\Leftarrow$) direction.\\
-\\
 This finishes the proof.
@@
 \section{Regular Expression Simplification Theorem} \label{simp appendix}
-\begin{proof}[Proof of \ref{simp}]
+\begin{proof}[Theorem \ref{simp}]
 Assume no row is the arbitrary computation, because then the union of the set of regular expressions would trivially simplify to the arbitrary computation.\\
@@
 \section{Pseudocode for the WEST Algorithm Functions} \label{pseudocode appendix}
-
 To compute the satisfying computations of an MLTL formula, many of the functions in the WEST program require the regular expressions of the satisfying computations of the subformulas as inputs.
-We denote these regexes by $R$ and $T$, where $R = R_1 | R_2 | ...
-| R_k$ is represented as a set of strings $R = {R_1, R_2, ..., R_k}$, and $T = T_1 | T_2 | ...
-| T_\ell$ is represented as a set of strings $T = {T_1, T_2, ..., T_\ell}$.
+We denote these regexes by $R$ and $T$.
 Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.
@@
 \caption{Pad a set to elements of all equal length}
-%Input: set of strings that represents a regex, number of propositional variables \\
-%Output: set of strings padded to equal length
+Input: set of strings that represents a regex, number of propositional variables \\
+Output: set of strings padded to equal length
 \begin{algorithmic}
@@
 \caption{Computes regex for propositional constant}
-%Input: String that is either ``T" or ``!", number of propositional variables\\
-%Output: set of strings that represents the appropriate satisfying computations
+Input: String that is either ``T" or ``!", number of propositional variables\\
+Output: set of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
@@
 \caption{Output the set of computation satisfying a propositional variable.}
-%Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
-%Output: set of strings that represents the appropriate satisfying computations
+Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
+Output: set of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
@@
 \caption{Combines two strings that differ only by one character into one}
-%Input: Two strings that represent regexes\\
-%Output: Single string that represents computations represented by both input strings or FAIL
+Input: Two strings that represent regexes\\
+Output: Single string that represents computations represented by both input strings or FAIL
 \begin{algorithmic}
@@
 \caption{Simplifies a set of strings using simplify\_string}
-%Input: set of strings representing a regex\\
-%Output: set of strings representing a regex simplified using simplify\_string
+Input: set of strings representing a regex\\
+Output: set of strings representing a regex simplified using simplify\_string
 \begin{algorithmic}
@@
 \caption{Takes the intersection of two computations}
-%Input: Two strings representing regexes\\
-%Output: Bitwise AND of the inputted strings
+Input: Two strings representing regexes\\
+Output: Bitwise AND of the inputted strings
 \begin{algorithmic}
@@
 \caption{Takes union of two regexes (combines two sets into one)}
-%Input: sets of strings that represent regexes, simplify boolean\\
-%Output: set of strings that represents union of inputted regexes
+Input: sets of strings that represent regexes, simplify boolean\\
+Output: set of strings that represents union of inputted regexes
 \begin{algorithmic}
@@
 \caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
-% Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-% Output: set of strings that represents the appropriate satisfying computations 
+Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
+Output: set of strings that represents the appropriate satisfying computations 
 \begin{algorithmic}
@@
 \caption{Computes the regex for a MLTL formula G[a:b]$\phi$}
-%Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-%Output: set of strings that represents the appropriate satisfying computations
+Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
+Output: set of strings that represents the appropriate satisfying computations
 \begin{algorithmic}
@@
 \caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
-%Inputs: sets of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
-%Output: set of strings that represents the appropriate satisfying computations 
+Inputs: sets of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
+Output: set of strings that represents the appropriate satisfying computations 
 \begin{algorithmic}
@@
     \caption{Generates test suite template without propositional constants, propositional variables, or negations of propositional variables filled in}
-    %Inputs: Depth of desired test suite template to generate, interval bounds\\
-    %Output: set of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
+    Inputs: Depth of desired test suite template to generate, interval bounds\\
+    Output: set of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
     \begin{algorithmic}
@@
     \caption{Generates a complete test suite of MLTL formulas in negation normal form up to a certain depth}
-    %Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
-    %Output: set of MLTL formulas
+    Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
+    Output: set of MLTL formulas
     \begin{algorithmic}
@@
 \section{State Diagram Graphs} \label{graphs appendix}
-\vspace{-1.5cm}
 Below we provide the state diagram graphs of the functions examined in our intelligent fuzzing.
@@
 Each graph directly corresponds with the pseudocode of their corresponding function, with nodes and edges being labeled accordingly.
-Note that the option to run \textit{simplify} has been omitted for clarity.\\
+Note that the option to run \texttt{simplify} has been omitted for clarity.\\
 

### 2022-10-15 paper/Paper.tex
fixed formula overlay
fixed small typo in the intro

@@
 Finally, we show an application of the regular expressions of the satisfying computations by using them to prove an MLTL theorem.
-In particular, we show that $\phi\mathcal{U}_{[a,b]}(\phi\mathcal{U}_{[0,c]}\psi) = \phi\mathcal{U}_{[a,b+c]}\psi$ and $\phi\mathcal{R}_{[a,b]}(\phi\mathcal{R}_{[0,c]}\psi) = \phi\mathcal{R}_{[a,b+c]}\psi$.
+In particular, we show that $\phi\mathcal{U}_{[a,b]}(\phi\mathcal{U}_{[0,c]}\psi) \equiv \phi\mathcal{U}_{[a,b+c]}\psi$ and $\phi\mathcal{R}_{[a,b]}(\phi\mathcal{R}_{[0,c]}\psi) \equiv \phi\mathcal{R}_{[a,b+c]}\psi$.
 %
@@
 Thus%
-\vspace{-0.1in}
+% \vspace{-0.1in}
  \begin{align*}

### 2022-10-20 paper/Paper.tex
Minor fix to Theorem 3
fixed spaces in labels

@@
 Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \phi,   \psi$ \text{be well-formed MLTL formulas in NNF.
-Then,} $ \phi \ \mathcal{B}_{[a,b+c]} \psi = \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
+Then,} $ \phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
 That is, $ \phi \ \mathcal{U}_{[a,b+c]} \psi \equiv \phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi)$ and $ \phi \ \mathcal{R}_{[a,b+c]} \psi \equiv \phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi)$.
@@
  We can represent the state space of the WEST algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
- The core of the WEST program lies in the recursive routine, \texttt{reg}, which calls the $8$ different subroutines as shown in \ref{fig:abstracted graph}.
+ The core of the WEST program lies in the recursive routine, \texttt{reg}, which calls the $8$ different subroutines as shown in \ref{fig:abstracted_graph}.
 \begin{figure}[t]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Regular Expression Simplification Theorem} \label{simp appendix}
+\section{Regular Expression Simplification Theorem} \label{simp_appendix}
 \begin{proof}[Theorem \ref{simp}]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pseudocode for the WEST Algorithm Functions} \label{pseudocode appendix}
+\section{Pseudocode for the WEST Algorithm Functions} \label{pseudocode_appendix}
 To compute the satisfying computations of an MLTL formula, many of the functions in the WEST program require the regular expressions of the satisfying computations of the subformulas as inputs.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{State Diagram Graphs} \label{graphs appendix}
+\section{State Diagram Graphs} \label{graphs_appendix}
 Below we provide the state diagram graphs of the functions examined in our intelligent fuzzing.
@@
     \caption{Pad Function}
-    \label{fig:pad graph}
+    \label{fig:pad_graph}
 \end{figure}
@@
     \caption{Bitwise\_And Function}
-    \label{fig:bitwise_and graph}
+    \label{fig:bitwise_and_graph}
 \end{figure}
@@
     \caption{Join Function}
-    \label{fig:join graph}
+    \label{fig:join_graph}
 \end{figure}
@@
     \caption{Set\_Intersect Function}
-    \label{fig:set_intersect graph}
+    \label{fig:set_intersect_graph}
 \end{figure}
@@
     \caption{Reg\_F Function}
-    \label{fig:reg_f graph}
+    \label{fig:reg_f_graph}
 \end{figure}
@@
     \caption{Reg\_G Function}
-    \label{fig:reg_g graph}
+    \label{fig:reg_g_graph}
 \end{figure}
@@
     \caption{Reg\_U Function}
-    \label{fig:reg_u graph}
+    \label{fig:reg_u_graph}
 \end{figure}
@@
     \caption{Reg\_R Function}
-    \label{fig:reg_r graph}
+    \label{fig:reg_r_graph}
 \end{figure}
@@
     \caption{Control Flow of Reg. Red nodes indicate a recursive call to Reg.}
-    \label{fig:big boy}
+    \label{fig:big_boy}
 \end{figure}

### 2022-10-21 paper/Paper.tex
last fixes

@@
     \caption{Abstracted graph of the \texttt{reg} main routine. Red nodes signal recursive calls to \texttt{reg} on sub formulas of the input formula.}
-    \label{fig:abstracted graph}
+    \label{fig:abstracted_graph}
 \end{figure}
@@
 This newly-enabled workflow would produce encodings of the represented MLTL behavior for the interactive theorem prover ACL2, including automatically generating related properties of general interest such as unambiguousness \cite{DBLP:journals/corr/abs-2205-11707,ACL2-Site,ACL2-Doc}.
-Next, a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL.
+Next, a synthesis pipeline consisting of a verified program transformation suite \cite{Kestrel-APT} along with a proof-generating C code generator \cite{DBLP:journals/corr/abs-2205-11708} (both built on ACL2) generates verified software implementing the behaviors originally described in MLTL.
+%a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL.
 By providing a new front-end for this toolchain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system.

### 2022-11-06 MLTL_reg/MLTL/simulation_main.cpp
editing simulation_main and README

@@ -11,21 +11,14 @@
 #include <fstream>
 #include <vector>
 #include <chrono>
-#define MAX_ITER 3
-// Maximum distance of any interval
-// in MLTL formula
-#define DELTA 5
-// Maximum upperbound of any interval
-// in MLTL formula
-#define INTERVAL_MAX 10
-// Number of random MLTL formulas
-// to be generated
 #define FUNC_NUM 1000
 #define NUM_PROP_VAR 5
+int MAX_ITER;
+int DELTA;
+int INTERVAL_MAX;
 
 using namespace std;
 using namespace std::chrono;
-
 
 /*
 * Generate a random MLTL formula with a iteration depth
@@ -147,7 +140,7 @@ void simulate(string formulas, string out) {
         outfile << line.size();
         outfile << " ";
         auto start = high_resolution_clock::now();
-        output = reg(Wff_to_Nnf(line), NUM_PROP_VAR);
+        output = reg(Wff_to_Nnf(line), NUM_PROP_VAR, false, true);
         output = simplify(output, NUM_PROP_VAR);
         auto stop = high_resolution_clock::now();
         auto duration = duration_cast<microseconds>(stop - start);
@@ -159,7 +152,7 @@ void simulate(string formulas, string out) {
         // into 'out' file
         outfile << sum_of_characters(output);
         outfile << "\n";
-        cout << formula_num << " Wrote a line to complexities.txt\n";
+        cout << formula_num << " Wrote a line to output file\n";
         ++formula_num;
     }
     infile.close();
@@ -171,15 +164,38 @@ void simulate(string formulas, string out) {
 * Driver function for simulation_main.cpp file
 */
 int main() {
-    string formulas = "random_mltl.txt";
-    string out = "complexities.txt";
-    srand(time(NULL));
-    // Write FUNC_NUM number of random MLTL formulas
-    // to "random_mltl.txt"
-    run_rand_function(formulas);
-    cout << "Wrote to random_mltl.txt\n";
-    // Write simulation results to "complexities.txt"
+    cout << "Generate formulas? (y/n) \n";
+    char gen;
+    cin >> gen;
+    string formulas;
+
+    if (gen == 'y') {
+        cout << "MAX_ITER: ";
+        cin >> MAX_ITER;
+
+        // Maximum distance of any interval
+        cout << "DELTA: ";
+        cin >> DELTA;
+
+        // Maximum upperbound of any interval
+        cout << "INTERVAL_MAX: ";
+        cin >> INTERVAL_MAX;
+
[…]

### 2022-11-06 MLTL_reg/MLTL/verify_main.cpp
edited verify_main and brute force

@@ -116,84 +116,85 @@ vector<string> generate_test(int depth, int n, int a = 0, int b = 2, bool large 
 
 
 int main() {
-	//string f1 = "C:/Users/Jonathanandzili/summer_2022_REU/2022-Iowa-State-REU-Temporal-Logic-/MLTL_brute_forcer/Python/0.txt";
-	//string f2 = "./test.txt";
-	//string wff = "(G[0:2]~p2U[0:2]G[0:2]p2)";
-	//int n = 3;
-	//vector<string> reg_wff = reg(wff, n);
-	//// Pad output to comp length
-	//int cp = Comp_len(wff);
-	//reg_wff = pad(reg_wff, n, cp * (n + 1) - 1);
-	//reg_wff = expand(reg_wff);
-	//write_to_file(reg_wff, f2);
-	//compare_files(f1, f2);
+	string formulas_file; 
 
+	int n;
+	//cout << "Enter number of propositional variables" << endl;
+	//cin >> n;
 
-	string formulas_file = "./verify/formulas_d1.txt";
-	string verify_reg = "./verify/reg_outputs_d1/";
-	string verify_brute_force = "./verify/brute_force_outputs_d1/";
+	char gen_formulas;
+	cout << "Generate new formulas? (y/n)" << endl; 
+	cin >> gen_formulas;
+	if (gen_formulas == 'y') {
+		int a = 0;
+		int b = 2;
+		int depth;
+		bool large = false;
 
+		cout << "Enter depth of formula to be generated" << endl; 
+		cin >> depth;
+		n = pow(2, depth);
 
-	int n = 4;
-	/*int depth = 2;
-	int a = 0; 
-	int b = 2;
-	bool large = false;
+		cout << "Enter name of file to write formulas to" << endl; 
+		cin >> formulas_file;
 
-	srand(time(NULL));
-	vector<string> test = generate_test(depth, n, a, b, large);
-	for (string wff : test) {
-		if (!Wff_check(wff)) {
-			cout << wff << " failed wff check" << endl; 
+		srand(time(NULL));
+		vector<string> test = generate_test(depth, n, a, b, large);
+		for (string wff : test) {
+			if (!Wff_check(wff)) {
+				cout << wff << " failed wff check" << endl;
+			}
+		}
+		write_to_file(test, formulas_file, false);
+		cout << "Formulas written to " + formulas_file << endl;
+	}
+	else {
+		cout << "Enter number of propositional variables" << endl;
[…]

### 2022-11-06 MLTL_brute_forcer/Python/MLTL_truth_table.py
edited verify_main and brute force

@@ -1,5 +1,6 @@
 from MLTL_semantics import *
 import pathlib
+import sys
 
 '''
 Given input: wff, num_states, current_state, end_state
@@ -171,15 +172,18 @@ if __name__ == "__main__":
     # for line in comparison_output(wff, output_file, n):
     #     print(line)
 
+    formulas_file = sys.argv[1] #"formulas_d{depth}.txt"
+    output_folder = sys.argv[2] #"/brute_force_outputs_d{depth}"
+    n = int(sys.argv[3])
+
     path = str(pathlib.Path(__file__).parent.resolve())
     verify_path = path[:-25] + "/MLTL_reg/MLTL/verify/"
-    n = 1
     i = 0
     start = 0
-    with open(verify_path + "formulas_d0.txt") as f:
+    with open(verify_path + formulas_file) as f:
         for wff in f:
             if i >= start:
-                output_file = verify_path + "/brute_force_outputs_d0" + "/" + str(i) + ".txt"
+                output_file = verify_path + output_folder + "/" + str(i) + ".txt"
                 comparison_output(wff, output_file, n)
                 print("Wrote to", output_file, "for", wff)
                 i += 1

### 2022-11-06 MLTL_reg/MLTL/complexity_graph/complexity_graph.py
updated graph units from ms to us, changes to abstract.txt

@@ -12,17 +12,17 @@ x_font = 16
 y_font = 16
 title_font = 16
 
-data = pd.read_csv("./complexities"+str(experiment)+".txt", sep=" ", header=None, names=["Input Length", "Time(ms)", "Output Length"])
+data = pd.read_csv("./complexities"+str(experiment)+".txt", sep=" ", header=None, names=["Input Length", "Time(us)", "Output Length"])
 # print(data)
-#print(data.nlargest(2, "Time(ms)"))
+#print(data.nlargest(2, "Time(us)"))
 #print(data.nlargest(3, "Output Length"))
 
 if plot_length:
     data.plot.scatter(x="Input Length", y="Output Length", color="Blue", marker="x")
     plt.ylabel("Output Length", fontsize = y_font)
 else: # plot time
-    data.plot.scatter(x="Input Length", y="Time(ms)", color="Red", marker="x")
-    plt.ylabel("Time(ms)", fontsize=y_font)
+    data.plot.scatter(x="Input Length", y="Time(us)", color="Red", marker="x")
+    plt.ylabel("Time(us)", fontsize=y_font)
 
 plt.xlabel('Input Length', fontsize=x_font)
 

### 2023-01-19 paper/Paper.tex
updated graph units from ms to us, changes to abstract.txt
some updates

@@
 
+There are a number of SAT solvers for MLTL \textcolor{red}{CITE SAT SOLVERS IDK THEM}, but there are currently no tools to check for MLTL formula validation, i.e.
+there are no tools available that allow people to \emph{validate} that a proposed MLTL formula is indeed capturing a specification for a system they want to verify.
+%It is necessary to perform validation before even being able to utilize SAT solvers in any meaningful way.
+This is precisely the role of the WEST tool, which is introduced in this paper.
+In this paper we introduce the WEST tool, which takes an MLTL formula and produces a description of the set of all finite time lines (of a fixed length) that satisfy the given formula, similar to filling out a truth table for propositional formulas and looking at the rows on which the formula holds.
+As a consequence, MLTL validation can be done by verifying that the output of the WEST program on a given input indeed matches the behaviour of the specification in question.
+
 We show that our contributions not only fill a critical gap in temporal logic validation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C code from temporal logic behavior descriptions.
@@
 %\subsection{Mission-time Linear Temporal Logic}
-{\bf Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
-The syntax of a MLTL formula $\phi$ over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
+\emph{Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
+The syntax of MLTL formulas, $\phi$ and $\psi$, over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
 \vspace{-0.1in}
-$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \psi \ | \ \psi_1 \land \psi_2 \ | \ \psi_1 \lor \psi_2 \ | \ \mathcal{F}_{[a,b]} \psi \ | \ \mathcal{G}_{[a,b]} \psi \ | \ \psi_1 \mathcal{U}_{[a,b]} \psi_2 \ | \ \psi_1 \mathcal{R}_{[a,b]} \psi_2 \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{WESTalg}).
+$$\phi, \psi := \top \ | \ \bot \ | \ p \ | \ \neg \phi \ | \ \phi \land \psi \ | \ \phi \lor \psi \ | \ \mathcal{F}_{[a,b]} \phi \ | \ \mathcal{G}_{[a,b]} \phi \ | \ \phi \mathcal{U}_{[a,b]} \psi \ | \ \phi \mathcal{R}_{[a,b]} \psi \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{WESTalg}).
 We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
-\vspace{-0.1in}
-%
-\begin{definition}[\emph{Computation}]
-A computation $\pi$ of length $m$ is a sequence $\{\pi[i]\}_{i = 0}^{m-1}$ of sets of propositional variables, $\pi[i] \subseteq \mathcal{AP}$, where the $i^{th}$ set holds the propositional variables that are satisfied at the $i^{th}$ time step.
+MLTL formulas can be interpreted using both finite and infinite ``time lines'' that are called \emph{computations}, which represent a discrete sequence of time instances and the truth values for the propositional variables on each one of these.
+For the purpose of this paper, we are only going to deal with \emph{finite} computations, that is, computations that represent only finitely many time steps.
+% \vspace{-0.1in}
+%
+\begin{definition}[\emph{Finite computations}]
+A \emph{computation} $\pi$ of length $m$ is a sequence $\{\pi[i]\}_{i = 0}^{m-1}$ of sets of propositional variables, $\pi[i] \subseteq \mathcal{AP}$, where the $i^{th}$ set holds the propositional variables that are satisfied at the $i^{th}$ time step.
 That is, a propositional variable $p$ is true at time step $i$ if and only if $p \in \pi[i]$.
-We denote the suffix of $\pi$ starting at $i$ (including $i$) by $\pi_i$.
+{\color{blue} What is the semantics for the other logical and temporal operators?
+Where can we find a formal definition for this?
+This is never explicitly said before \texttt{reg} is introduced and it can lead to misinterpretations from the reviewers.} We denote the suffix of $\pi$ starting at $i$ (including $i$) by $\pi_i$.
 Note that $\pi_0 = \pi$.
@@
 \vspace{-0.1in}
-We extend the standard definition of Regular Expressions (Regex) \cite{sipser} to introduce notation that describes the satisfying computations of an MLTL formula.
+We modify the standard definition of Regular Expressions (Regex) to introduce notation that describes the satisfying computations of an MLTL formula.
+We begin by quoting the parts of the standard definition of a regex from \cite{sipser} that we use to describe our computations:
+
+\begin{definition}[\emph{Regular Expression}] \label{sipser regex} 
+    Let $\Sigma$ denote an alphabet, and let $a\in \Sigma$. We say that $R$ is a \emph{regular expression} if one of the following holds:
+    \begin{itemize}
+        \item $R = a$
+        \item $R = \epsilon$, where $\epsilon$ is the language containing the empty string
+        \item $R = \emptyset$
+        \item $R = (R_1 \lor R_2)$, where $R_1, R_2$ are regexes and $\lor$ denotes \emph{alternation}; the set union of all the strings described by $R_1$ and $R_2$
+        \item $R = R_1R_2$, which denotes \emph{concatenation}, i.e., the set of strings obtained by concatenating any string generated by $R_1$ with any string generated by $R_2$, in that order
+    \end{itemize}
+\end{definition}
+Now we introduce the additions to the definition of a regex that we utilize to describe the computations.
+These additions allow us to write regexes of a known, finite, fixed length, which is required when describing the computations in MLTL.
+
 \begin{definition}[\emph{Temporal Regular Expression}] \label{TRE} 
-Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$.\\
+Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ \lor \ 1)$.\\
 Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula.
@@
 \begin{itemize}
-  \item \emph{(Concatenation)} $RT$ describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
- \item \emph{(Alternation)} $R \lor T$ describes the set union of the strings generated by $R$ and $T$.
 \item Pad($R$, $T$) determines which regular expression is longer and concatenates $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
 Note that in the bit string representation, $(,S^n)$ denotes a time step in which the truth value of all $n$ propositional variables does not matter.
-\item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
+\item $R \land T$ is the intersection of the sets of strings described by $R$ and $T$.
+To perform this operation, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
 \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$. %KYR: is this one relevant or should we take it out?
-\item We do not use the Kleene star since our computations are a fixed finite length.
 \end{itemize}
 \end{definition}
+Note that our regular expressions do not use the Kleene star. This is because are computations are of a fixed, finite length.
 %An example of these operations follows.
 \begin{example} %KYR: NICE example!
-Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.
+Let $n = 2$, and let $R = S1$ and $T = 1S,1S \lor S1,S1$.
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
 Since $T$ is the longer regex by one time step, we concatenate $(,S^2)$ to the right of $R$.
-Thus $T =1S,1S | S1,S1$ and $R = S1,SS$.
+Thus $T =1S,1S \lor S1,S1$ and $R = S1,SS$.
 Now the regexes are the same length, so we can perform set intersection and alternation:
@@
 
-To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{``$0$'' , ``$1$'', ``$,$''\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
+To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{``$0$'' , ``$1$'', ``$,$''\} and define $S$ as an abbreviation for $(0 \ \lor \ 1)$.
 Let $p_0, p_1, ..., p_{n-1}$ be propositional variables and $\phi, \psi$ well-formed MLTL formulas in negation normal form.
@@
 We accompany theoretical space and time complexity with experimental evaluation of these complexities using randomly-generated MLTL formulas.
+What we observed from the simulations is that the worst case complexity, both for space and time, is relatively rare.
+We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators.
+As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in the literature and in practical applications.
+
 We ran these experiments on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
@@
 For example, $\mathcal{G}_{[0,2]}p_0$ is a formula generated with one iteration, while $\mathcal{G}_{[0,2]}(p_0 \land p_1)$ is a formula generated with two iterations.
-We measure the number of characters in the output and the amount of time in milliseconds taken to run the program.
+We measure the number of characters in the output and the amount of time in microseconds taken to run the program.
 Note that these simulations run the \texttt{reg} function with the subformula boolean set to false and the simplify boolean set to true.\\
@@
 \end{minipage}
-\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively rare.
-We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators.
-As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in practical applications.
+What we conclude from the simulations is that for most practical purposes, the WEST algorithm demonstrates good space and time complexity.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-01-19 extras/graphs.tex
formulas in the wild

--- 2022-10-20 paper/Paper.tex
@@
-\documentclass[runningheads]{llncs}
-
-%KYR: need to ensure included packages don't interfere with LNCS style
-%\usepackage[utf8]{inputenc}
-%\usepackage{amsthm, amsmath, amssymb}
-\usepackage{amsfonts} %mathbb
-\usepackage{amsmath} %hdots
-\usepackage{amssymb} %blacksquare
-\usepackage{mathabx} %vDash
-\usepackage{mathrsfs} %mathscr
-\usepackage{blkarray} %for blockarray
-%\usepackage{textcomp}
-%\usepackage{xcolor}
-%\usepackage{soul}
-%\usepackage{ dsfont }
+\documentclass{article}
+\usepackage[utf8]{inputenc}
+\usepackage{amsthm, amsmath, amssymb}
+\usepackage[letterpaper,width=150mm,top=20mm,bottom=25mm]{geometry}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\usepackage{soul}
+\usepackage{ dsfont }
+\usepackage{ mathrsfs }
 \usepackage{hyperref}
-\usepackage{cancel} %for \cancel
-\usepackage{algorithm} %for algorithm environment
+\usepackage{cancel}
+\usepackage{algorithm}
 \usepackage{algcompatible}
 \usepackage[noend]{algpseudocode}
-%\usepackage{changepage}%http://ctan.org/pkg/changepage
-\usepackage{graphicx} %for includegraphics
+\usepackage{changepage}%http://ctan.org/pkg/changepage
+\usepackage{lipsum}% http://ctan.org/pkg/lipsum
+\usepackage{graphicx}
 \usepackage{tikz}
-\usepackage{lscape} %for landscape orientation
-%\usepackage{float} %for figures
+\usepackage{lscape}
 \usetikzlibrary{shapes.misc, positioning}
@@
 \tikzset{>={Latex[width=2mm,length=2mm]}}
-\usepackage{caption}
-\usepackage{mwe}
-%% \hypersetup{
-%%     colorlinks=true,
-%%     linkcolor=blue,
-%%     filecolor=magenta,
-%%     urlcolor=red,
-%%     citecolor=teal
-%% }
 
-%LNCS:
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-\renewcommand\UrlFont{\color{blue}\rmfamily}
+\title{Control Flow Graphs so i don't mess up the big document}
+\begin{document}
+\maketitle
 
-%for qed:
-%% \makeatletter
-%% \newcommand{\pushright}[1]{\ifmeasuring@#1\else\omit\hfill$\displaystyle#1$\fi\ignorespaces}
-%% \newcommand{\pushleft}[1]{\ifmeasuring@#1\else\omit$\displaystyle#1$\hfill\fi\ignorespaces}
-%% \makeatother
-%% \makeatletter
-%% \newcommand{\specialcell}[1]{\ifmeasuring@#1\else\omit$\displaystyle#1$\ignorespaces\fi}
-%% \makeatother
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Spacing Magic
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage{pslatex} % DON'T REMOVE!  BUYS US HALF A PAGE OR MORE!!!!!
-%Use only in case of emergencies: \linespread{0.98} %KYR: make lines spaces .99 instead of 1 to save space
-\usepackage{times} %KYR: substitute for pslatex that does not mess up math :)
-%\usepackage{savetrees} %KYR: maybe also helps... if we can fix the text to enable this
-
-\usepackage{enumitem}
-\setlist[itemize]{noitemsep, nolistsep, topsep=0pt, partopsep={0pt}}
-
-%CAUTION: dirty trick; questionably allowed... use ONLY in case of emergencies!
-% \linespread{0.99}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Figure Magic
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\usepackage{epsfig}
-\usepackage{float} % put figure in minipage
-%\usepackage{framed}
-%\usepackage{subfigure}
-
-% diagonal line in the table
-%\usepackage{diagbox}
-
-\usepackage{enumitem}
-\newlist{Properties}{enumerate}{2}
-\setlist[Properties]{label=Property \arabic*.,itemindent=*}
-
-%\usepackage{tikz}
-%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
-%            \node[shape=circle,draw,inner sep=0.5pt] (char) {#1};}}
-%
-%\newcommand{\VarPhiSequence}{\ensuremath{\langle T_{\varphi} \rangle}\xspace}
-%\newcommand{\ExSeq}[1]{\ensuremath{\langle T_{#1} \rangle}\xspace}
-%\newcommand{\ExSeqElement}[2]{\ensuremath{\langle T^{#1}_{#2} \rangle}\xspace}
-%\newcommand{\IN}{\mathbb{N}}
-
-% draw box around text
-\usepackage{tcolorbox}
-
-\renewcommand{\topfraction}{.99} %figures can take up at most 99% of the page before being alone
-\renewcommand{\bottomfraction}{.99} %figures can take up at most 99% of the page before being alone
-\renewcommand{\textfraction}{.01} %at most this % of page will be text before making figure-only page
-\addtolength{\textfloatsep}{-5mm}
-\addtolength{\floatsep}{-5mm}
-\addtolength{\intextsep}{-5mm}
-\addtolength{\abovecaptionskip}{-3mm}
-\addtolength{\belowcaptionskip}{-2mm}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\renewcommand{\phi}{\varphi}
-
-%\theoremstyle{definition}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{remark}{Remark}
-%\newtheorem{example}{Example}
-%\newtheorem{definition}{Definition}
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-
-\newcommand{\R}{\mathbb{R}}
-\newcommand{\C}{\mathbb{C}}
-\newcommand{\Z}{\mathbb{Z}}
-
-\def\nuXmv{{\sf nuXmv}\xspace}
-
-\begin{document}
-%
-%\title{Contribution Title\thanks{Supported by organization x.}}
-\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}}
-%
-\titlerunning{MLTL Formula Validation Via Regular Expressions}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\vspace{-0.1in}
-%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
-%\author{Jenna Elwing\thanks{University of Michigan, Ann Arbor} \and Laura Gamboa Guzmán\thanks{Iowa State University} \and Jeremy Sorkin\thanks{The Ohio State University} \and Chiara Travesset\thanks{Purdue University} \and Zili Wang\thanks{University of California, Berkeley} \and Kristin Y.
-Rozier\footnotemark[2]}
-%
-%\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-%\institute{Princeton University, Princeton NJ 08544, USA \and
-%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-%\email{lncs@springer.com}\\
-%\url{http://www.springer.com/gp/computer-science/lncs} \and
-%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-%\email{\{abc,lncs\}@uni-heidelberg.de}}
-%
-\maketitle              % typeset the header of the contribution
-%
-
-\vspace{-0.3in}
-\begin{abstract}
-  \noindent Mission-time Linear Temporal Logic (MLTL) represents the most practical fragment of Metric Temporal Logic; MLTL resembles the popular logic LTL with finite closed-interval integer bounds on the temporal operators.
-Increasingly, many tools reason over MLTL specifications, yet these tools are only useful when system designers can validate the input specifications.
-We design an automated characterization of the structure of the computations that satisfy a given MLTL formula using regular expressions.
-We prove soundness and completeness of our structure.
-We also give an algorithm for automated MLTL formula validation and analyze its complexity both theoretically and experimentally.
-Additionally, we generate a test suite using control flow diagrams to robustly test our implementation and release an open-source tool.
-The result of our contributions are improvements to existing algorithms for MLTL analysis applicable to many other tools and the WEST tool for automated, efficient MLTL formula validation.
-  %
-%        Our work connects existing tools to enable improvmeents in satisfiabiity tools and automated synthesis of verified code from MLTL behavior descriptions.
-% 
-  %
-%  A computation is a finite sequence of truth assignments.
-In this paper, we use regular expressions to describe the structure of the computations that satisfy a given MLTL formula.
-We prove soundness and completeness of our structure.
-We also give an implemented algorithm (the WEST program) and analyze its complexity both theoretically and experimentally.
-Finally, we generate a test suite using control flow diagrams to robustly test the code.
-
-        %We demonstrate that formula validation examples generated via regular expressions encapsulating the sets of all satisfying/unsatisfying assingments is tractable, both theoreteically and experimentally.
-We present an efficient algorithm for automatic characterization of an MLTL formula by its satisfying assingments, proove the theoretical correctness, time complexisty, and space complexity of hte algorithm.
-Then we provide a robust implementattion of the algorithm, demonstrate expreimentally its performance and correctness, and utilize intelligent fuzzing to increaes confidence int eh resulting open-source tool, which we release for public use.
-The result of our contributions are improvements to existing algorithms for MLTL analsysis applicable to many other tools and a new tool called WEST for provably correct, atomated, efficient MLTL formula validation.%
-%        Our work connects existing tools to enable improvmeents in satisfiabiity tools and automated synthesis of verified code from MLTL behavior descriptions.
-%
-% Contributions:
-%
-
-        \vspace{-0.1in}
-\keywords{Mission-time Linear Temporal Logic (MLTL)  \and MLTL Satisfiability \and Temporal Logic Validation.}
-\end{abstract}
-
-\vspace{-0.4in}
-\section{Introduction}
-\vspace{-0.1in}
-System specifications, such as aerospace operational concepts, often utilize timelines to express critical requirements.
-We can cite examples of this from NASA's Automated Airspace Concept \cite{EH10}, the U.~S.~Navy's Aircraft Carrier Deck Scheduler \cite{RCRBS11}, the JAXA-NASA Global Precipitation Measurement (GPM) Observatory \cite{GPM}, and many others.
-Formal methods provide continuously advancing tools and techniques to rigorously analyze timelines expressed in the form of temporal logic requirements, from early design-time model checking and theorem proving to on-board runtime verification.
-The U.~S.~Federal Aviation Administration (FAA) even advocates the use of formal methods for flight certification of these critical systems \cite{DO-178C,DO-254,DO-333}.
-Yet, a significant hurdle to the use of formal methods remains: how to convincingly demonstrate to the humans in the loop, from system designers to certifiers, that the analyzed formulas truly represent the system requirements \cite{Roz16}.
-We creatively address this validation question using regular expressions and truth tables.
-
-NASA, for example, has developed several tools that operate over temporal logic requirements, such as FRET\cite{GMRPSS20}, R2U2\cite{RS17}, and a PVS library \cite{CTGPD22} for the logic MLTL (Mission-time Linear Temporal Logic) \cite{RRS14,LVR22}.
-MLTL was the logic used recently in NASA's Robonaut2 verification project \cite{KZJZR20} and is being used currently for both design-time and runtime verification of the NASA Lunar Gateway Vehicle System Manager \cite{DBR21}.
-Other recent verification %verification-for-certification
-efforts involving MLTL include a JAXA autonomous satellite \cite{JAXA}, a UAS Traffic Management (UTM) system involving Collins and Mosaic Aerospace \cite{HCHJR21}, a sounding rocket \cite{HLR21}, and multiple small satellites \cite{LLR21,LJBHCLR22,AJR22}.
-However, all of these successful verification efforts were carried out by groups specializing in formal methods research.
-To enable broader application of formal verification, and adoption across larger projects, we critically need better validation, e.g., so that analysis over MLTL-specified requirements can transparently contribute to flight certification.
-
-Many specifications from case studies, in logics such as MTL \cite{AH90} and STL \cite{MN04}, fall within the MLTL fragments of these logics. 
-Variations on Metric Temporal Logic (MTL) such as MLTL have grown increasingly popular, in part due to their comparatively tractable complexity-to-expressibility trade-offs \cite{OW08}.
-The model checker {\sf nuXmv} encodes a popular subset of MLTL for use in symbolic model checking \cite{nuXmv-v1.1.0}.%, where the $\Box$ and $\Diamond$ operators of an \texttt{LTLSPEC} can have integer bounds \cite{nuXmv-v1.1.0}, though bounds cannot be placed on the $\U$ or $\V$ (the Release operator of \nuxmv) operators.
-
-We show that our contributions not only fill a critical gap in temporal logic validation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C code from temporal logic behavior descriptions.
-
-%% Mission-time Linear Temporal Logic (MLTL) extends propositional logic by including temporal operators over finite discrete intervals.
-It is useful for writing specifications for spacecraft, rovers, aircraft, and other robotic missions \cite{LVR22}.
-In standard propositional logic, a convenient way to check that a formula captures a specification correctly is to write out its truth table and check that the formula behaves in the desired manner.
-The same strategy can be employed for MLTL, but the truth tables increase in size at a much faster rate, making them too large to be useful.
-For instance, an MLTL formula with just two propositional variables and 10 time steps would require $\left(2^{10}\right)^2 = 2^{20}$ rows.
-This is often called the ``State Explosion Problem" \cite{stateexp}.
-
-%% In this paper, we offer a remedy to the state explosion problem by using regular expressions to describe the set of all computations satisfying a MLTL formula, which significantly reduces the space needed to express the computations.
-We implement these regular expressions into the WEST program, which allows the user to input a MLTL formula and obtain the satisfying computations.
-The WEST program can be found on its \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git}{Github} repository.
-
-We structure the paper around our contributions as follows.
-In Section \ref{prereq}, we build on the semantics of MLTL to define a computation and its bit string representation.
-% of a computation that is used throughout the paper and the WEST program.
-Finally, we describe negation normal form (NNF), a standardized way to express MLTL formulas.
-By writing the MLTL formulas in NNF, the WEST program is able to run much more efficiently.
-%
-In Section \ref{regex}, we recursively define regular expressions encapsulating the satisfying computations of MLTL formulas and prove that our new translation algorithm is both sound and complete.
-In addition, we provide a calculation for the minimum computation length required to describe all the satisfying computations of a MLTL formula that slightly improves upon existing calculations in the literature.
-Finally, we show an application of the regular expressions of the satisfying computations by using them to prove an MLTL theorem.
-In particular, we show that $\phi\mathcal{U}_{[a,b]}(\phi\mathcal{U}_{[0,c]}\psi) \equiv \phi\mathcal{U}_{[a,b+c]}\psi$ and $\phi\mathcal{R}_{[a,b]}(\phi\mathcal{R}_{[0,c]}\psi) \equiv \phi\mathcal{R}_{[a,b+c]}\psi$.
-%
-We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in Section \ref{WESTalg}
-and calculate its space and time complexity, both theoretically and experimentally.
-We show that the theoretical worst-case complexity for both space and time is doubly exponential, but that the average case fares far better.
-%
-Section \ref{test} proves correctness of the algorithms and provides a test suite to show correctness of implementation with high confidence.
-Intelligent fuzzing techniques contribute to test suite construction from a state diagram representing the control flow of the algorithm.
-We also verify the correctness of outputs of the WEST program against a na\"ive brute force implementation.
-%
-Section \ref{simpsection}, provides a combinatorial theorem for simplifying certain outputs of the WEST program.
-Formulas of the form $\phi \equiv \psi$ to check for equivalence between two expressions can lead to outputs that are non-trivial to simplify.
-Section \ref{Conclusion} discusses impacts and future work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-0.1in}
-\section{Preliminaries: Mission-time LTL and Bit String Computations} \label{prereq}
-\vspace{-0.1in}
-%\subsection{Mission-time Linear Temporal Logic}
-{\bf Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
-The syntax of a MLTL formula $\phi$ over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
-\vspace{-0.1in}
-$$\phi := \top \ | \ \bot \ | \ p \ | \ \neg \psi \ | \ \psi_1 \land \psi_2 \ | \ \psi_1 \lor \psi_2 \ | \ \mathcal{F}_{[a,b]} \psi \ | \ \mathcal{G}_{[a,b]} \psi \ | \ \psi_1 \mathcal{U}_{[a,b]} \psi_2 \ | \ \psi_1 \mathcal{R}_{[a,b]} \psi_2 \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{WESTalg}).
-We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
-\vspace{-0.1in}
-%
-\begin{definition}[\emph{Computation}]
-A computation $\pi$ of length $m$ is a sequence $\{\pi[i]\}_{i = 0}^{m-1}$ of sets of propositional variables, $\pi[i] \subseteq \mathcal{AP}$, where the $i^{th}$ set holds the propositional variables that are satisfied at the $i^{th}$ time step.
-That is, a propositional variable $p$ is true at time step $i$ if and only if $p \in \pi[i]$.
-We denote the suffix of $\pi$ starting at $i$ (including $i$) by $\pi_i$.
-Note that $\pi_0 = \pi$.
-\end{definition}
-
-%We use a bit string representation for our computations. This representation is easy to describe using regular expressions and is convenient to code.
-
-\begin{definition}[\emph{Bit String Representation of a Computation}]
-Let $p_0, p_1, ..., p_{n-1}$ be propositional variables for a fixed $n \in \mathbb{N}$.
-We represent a (finite) computation $\pi$ of length $m \in \mathbb{N}$ using a bit string representation as follows:
-\begin{itemize}
-%KYR: redundant    \item We represent a true assignment to a propositional variable by $1$ and a false assignment by $0$.
-    \item For each time step $j \in [0,1,\hdots,m-1]$, we have a bit string of length $n$ where the $k^{th}$ bit represents the truth assignment of the proposition $p_{k-1}$.
-    \item We separate each time step by a comma and order the time steps chronologically.
-\end{itemize}
-\end{definition}
-
-%\noindent We write that a computation $\pi$ is equal to its bit string representation. An example is given below.
-
-\begin{example}
-Suppose $n=2$.
-The bit string representation $\pi = 10, 01$ means that $p_0$ is true in the first time step and false in the second one, and that $p_1$ is false in the first time step and true in the second one.
-\end{example}
-
-%KYR: the following is very useful for a tech report, but in a space-constrained conference paper, we refer the reader to LVR22 instead.
-(Maybe if there's a journal version we can include semantics again.)
-%
-%% \subsubsection{Semantics}
-%% We say a computation $\pi$ as satisfies a given MLTL formula $\phi$, written $\pi \vDash \phi$, when\footnote{In MLTL, we do not include the Next ($\chi$) operator since $\mathcal{G}_{[1,1]}$ is equivalent to it.}:
-%% \begin{align}
-%%     &\pi \vDash p \text{ iff } p \in \pi[0]\\
-%%     &\pi \vDash \neg \phi \text{ iff } \pi \nvDash \phi\\
-%%     &\pi \vDash \phi \land \psi \text{ iff } \pi \vDash \phi \text{ and } \pi \vDash \psi\\
-%%     &\pi \vDash \phi \lor \psi \text{ iff } \pi \vDash \phi \text{ or } \pi \vDash \psi\\
-%%     &\pi \vDash \mathcal{F}_{[a,b]}\phi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \phi\\
-%%     &\pi \vDash \mathcal{G}_{[a,b]}\phi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \phi\\
-%%     &\pi \vDash \phi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \psi \text{ and }\\
-%%     & \indent \forall j \in [a, i-1]\ \pi_j \vDash \phi \nonumber \\
-%%     &\pi \vDash \phi \ \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or }\\
-%%     & \indent \exists j \in [a,b-1] \text{ such that } \pi_j \vDash \phi \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \psi \nonumber
-%% \end{align}
-
-%KYR: moved up to earlier footnote
-%% The reader may observe that in this paper, we define Release independently from Until. 
-%% It is not uncommon for Release instead to be defined as the dual of Until \cite{bmc} \cite{LVR22}. 
-%% These two definitions are in fact equivalent, and the full proof is provided in Appendix \ref{duality appendix}.
-
-%\subsection{Negation Normal Form}
-
-%KYR: TODO: represent the following sentiment when introducing the translation instead:
-%All MLTL formulas can be written in negation normal form (NNF) \cite{bmc}.
-We require MLTL formulas to be written in NNF to generate the satisfying computations using regular expressions.
-Without this requirement, generating the satisfying computations requires taking complements of the languages described by regular expressions, which is a very expensive operation.
-
-%KYR: not necessary for TACAS; the audience already knows this
-%% \begin{definition}[\emph{Negation Normal Form \cite{nnf}}] 
-%% An MLTL formula $\phi$ is in \emph{negation normal form} if
-%% \begin{itemize}
-%%     \item Any negation symbols appear only in front of propositional variables.
-%%     \item We allow only the operations $\top$, $\bot$, $\land$, and $\lor$ from propositional logic.
-%%     \item We allow only the operations $\mathcal{U}$ and $\mathcal{R}$ from MLTL.
-%% \end{itemize}
-%% \end{definition}
-
-%% In the literature, NNF does not include the Finally and Global operators, as $\bot \mathcal{R}_{[a,b]} \phi = \mathcal{G}_{[a,b]} \phi$ and $\top \mathcal{U}_{[a,b]} \phi = \mathcal{F}_{[a,b]} \phi$.
-In this paper, we stray from the literature and include Finally and Global as part of NNF, as this is far more natural for writing our regular expressions that describe the satisfying computations of a MLTL formula.
-
-%\subsection{Regular Expressions}
-%  We use regular expressions (regex) to describe the form of the satisfying computations.
-
-%KYR: Take this out and replace it with a statement that we use the standard RE operators:...
-%% \begin{definition}[\emph{Regular Expression \cite{sipser}}]
-%% A \emph{regular expression} is a string that describes the form of a language. 
-%% Let $\Sigma$ denote a finite phibet. The empty set $\emptyset$, the empty string $\epsilon = ``"$, and any character in $\Sigma$ are constants defined to be a regular expression. 
-%% Beyond that, we define regular expressions recursively. 
-%% Suppose $R$ and $T$ are regular expressions. 
-%% Then the following operations generate regular expressions:
-%% \begin{itemize}
-%%     \item \emph{(Concatenation)} Denoted $RT$, this operation describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
-%%     \item \emph{(Alternation)} Denoted $R | T$, this operation describes the set union of the strings generated by $R$ and $T$.
-%%     \item \emph{(Kleene Star)} Denoted $R^*$, this operation describes the set of all strings made by concatenating any finite number (including zero) of strings described by $R$ together.
-%%     \item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$.
-%% \end{itemize}
-%% \end{definition}
-%
-%KYR: Examples are super nice, but if we have them we should have them after the MLTL regex example
-%\noindent We provide an example of each operation.
-%% \begin{example}
-%% Let $R$ describe \{`$a$', `$b$'\} and $T$ describe \{ `$c$', `$d$' \}.
-%% \begin{itemize}
-%%     \item $RT$ describes the set \{ `$ac$', `$ad$', `$bc$', `$bd$' \}.
-%%     \item $R | T$ describes the set \{`$a$', `$b$', `$c$', `$d$' \}.
-%%     \item $R^*$ describes the set \{ $\epsilon$, `$a$', `$b$', `$aa$', `$bb$', `$ab$', `$ba$', `$aaa$', `$aba$',... \}.
-%%     \item $R^2$ describes the set \{ `$aa$', `$bb$', `$ab$', `$ba$' \}.
-%% \end{itemize}
-%% \end{example}
-
-%% %\noindent We provide examples of different regex and possible combinations of the above operations.
-%% \begin{example}
-%% Let `$a$', `$b$', and `$c$' denote characters in a finite phibet.
-%% \begin{itemize}
-%%     \item $ab^*$ describes the set \{ `$a$', `$ab$', `$abb$', `$abbb$', ... \}.
-%%     \item $a^*|b$ describes the set \{ $\epsilon$, `$b$', `$a$', `$aa$', `$aaa$', ...\}.
-%%     \item $a(b^*)c$ describes the set \{ `$ac$', `$abc$', `$abbc$', `$abbbc$', ... \}.
-%%     \item $(a | b)^3$ describes the set \{ `$aaa$', `$aba$', `$aab$', `$abb$', `$bbb$', ... \}.
-%% \end{itemize}
-%% \end{example}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-0.1in}
-\section{MLTL Regular Expressions} \label{regex}
-\vspace{-0.1in}
-We extend the standard definition of Regular Expressions (Regex) \cite{sipser} to introduce notation that describes the satisfying computations of an MLTL formula.
-\begin{definition}[\emph{Temporal Regular Expression}] \label{TRE} 
-Let $R$ and $T$ denote regular expressions, and let $S$ be an abbreviation for $(0 \ | \ 1)$.\\
-Let fixed $n \in \mathbb{N}$ denote the number of propositional variables in a MLTL formula.
-We use the following operations to describe the form of satisfying computations of the formula in the bit string representation:
-\begin{itemize}
-  \item \emph{(Concatenation)} $RT$ describes the set of strings obtained by concatenating any string generated by $R$ and any string generated by $T$ in that order.
- \item \emph{(Alternation)} $R \lor T$ describes the set union of the strings generated by $R$ and $T$.
-\item Pad($R$, $T$) determines which regular expression is longer and concatenates $(,S^n)$ repeatedly to the end of the shorter regular expression until the two regular expressions are the same length.
-Note that in the bit string representation, $(,S^n)$ denotes a time step in which the truth value of all $n$ propositional variables does not matter.
-\item For $R \land T$, we first use Pad($R$, $T$), and then take the set intersection of the sets of strings described by the two regular expressions.
-\item $R^i$ denotes regular expression consisting of $R$ repeated $i$ times for $i \geq 0$. $R^0 = \epsilon$. %KYR: is this one relevant or should we take it out?
-\item We do not use the Kleene star since our computations are a fixed finite length.
-\end{itemize}
-\end{definition}
-%An example of these operations follows.
-\begin{example} %KYR: NICE example!
-Let $n = 2$, and let $R = S1$ and $T = 1S,1S | S1,S1$.
-To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
-Since $T$ is the longer regex by one time step, we concatenate $(,S^2)$ to the right of $R$.
-Thus $T =1S,1S | S1,S1$ and $R = S1,SS$.
-Now the regexes are the same length, so we can perform set intersection and alternation:
-\begin{itemize}
-    \item $R \land T = 11,1S \lor S1, S1$.
-    \item $R \lor T = S1,SS \lor 1S,1S \lor S1,S1 = S1,SS \lor 1S,1S$.
-\end{itemize}
-\end{example}
-
-To describe the bit string representations of the satisfying computations for a given MLTL formula, we use the alphabet $\Sigma =$ \{``$0$'' , ``$1$'', ``$,$''\} and define $S$ as an abbreviation for $(0 \ | \ 1)$.
-Let $p_0, p_1, ..., p_{n-1}$ be propositional variables and $\phi, \psi$ well-formed MLTL formulas in negation normal form.
-We define the regular expression of satisfying computations for a MLTL formula as follows:\\
-
-% ZILI: Left Aligned Version
-\vspace{-7mm}
-\hspace{-8.5mm}
-\begin{minipage}{0.45 \textwidth}
-    \begin{align}
-    &\text{reg}(\top) = S^n\\
-    &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
-    &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
-    &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)
-    \end{align}
-\end{minipage}
-\begin{minipage}{0.55\textwidth}
-    \begin{align}
-    &\text{reg}(\bot) = \emptyset \\
-    &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-    &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi) \\
-    &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)
-    \end{align}
-\end{minipage}
-\vspace{-5mm}\\
-\begin{minipage}{0.99\textwidth}
-\begin{align}
-&\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\\
-\vspace*{-10mm}&\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
-\end{align}
-\end{minipage}
-\begin{definition}[\emph{Computation Length}]
-We define the computation length $\emph{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
-          %\begin{align}
-\indent \qquad   $\emph{cplen}(p_k) = \emph{cplen}(\neg p_k) = 1$\\
-\indent \qquad   $\emph{cplen}(\phi \land \psi) = \emph{cplen}(\phi \lor \psi) = \max(\emph{cplen}(\phi), \emph{cplen}(\psi))$\\
-\indent \qquad   $\emph{cplen}(\mathcal{G}_{[a,b]} \phi) = \emph{cplen}(\mathcal{F}_{[a,b]} \phi) = b + \emph{cplen}(\phi)$\\
-\indent \qquad   $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$
-%\end{align}
-\end{definition}
-\vspace{-0.1in}
-Intuitively, $\text{cplen}(\phi)$ is the minimum computation length required to ensure that none of the intervals in $\phi$ are out of bounds.
-Our minimum computation length for Until and Release are slight optimizations of what was previously considered the minimum computation length in the literature. In \cite{KZJZR20},\\
-%\vspace{-0.1in}
-\indent $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\text{cplen}(\phi), \text{cplen}(\psi))$ \\ 
-%\vspace{-0.1in}
-\noindent whereas Theorem \ref{thm1} proves our minimum computation length for Until and Release, \\
-%\vspace{-0.1in}
-\indent $\text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\mathbf{\text{cplen}(\phi)-1}, \text{cplen}(\psi)).$
-%We provide the proof for the minimum computation length of Until and Release below.
-%\vspace{-0.1in}
-\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]\label{thm1}
-    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\phi, \psi$ be well-formed MLTL formulas in NNF.
-The minimum computation length of \emph{Until} and \emph{Release} is given by $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$.
-\end{theorem}
-\vspace{-0.2in}
-\begin{proof}
-The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Globally, AND, and OR.\\
- Recall that $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$. Thus
- \begin{align*}
-     \text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \phi \land \mathcal{G}_{[i,i]} \psi) \right)\\
-     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\phi), i + \text{cplen}(\psi))\right)\\
-     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi))\right)\\
-     &= b + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi)).
- \end{align*}
- \vspace{-0.1in}
- Now recall that $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$.
-Thus%
-% \vspace{-0.1in}
- \begin{align*}
-     \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \psi), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)  \right)\\
-     &= \max\left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)\\
-     &= \max \left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\psi), i + \text{cplen}(\phi))\right) \right)\\
-     &= \max \left( b + \text{cplen}(\psi), \max(b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\right)\\
-     &= \max(b + \text{cplen}(\psi), b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\\
-     &= b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi)). 
- \end{align*}
-% This completes the proof.
- \end{proof}
- \vspace{-0.25in} \hfill $\blacksquare$\\
- \noindent Intuitively, we can reduce the minimum computation length of Until/Release because:
- \begin{itemize}
-     \item At the final time-step for $\phi \mathcal{U}_{[a,b]} \psi$, if $\psi$ has not yet been assigned to be true in the computation, it will be assigned true because $\phi \mathcal{U}_{[a,b]} \psi$ is a strong operator.
-Semantically, the truth value of $\phi$ at this time interval doesn't matter; whether $\phi$ is true or false, the computation for $\phi \mathcal{U}_{[a,b]} \psi$ is satisfied.
-     \item Likewise, in the case for $\phi \mathcal{R}_{[a,b]} \psi$, if $\psi$ is true from the first to the last time-step, the truth value of $\phi$ at the final time-step doesn't matter - the computation satisfies $\phi \mathcal{R}_{[a,b]} \psi$ regardless of whether $\phi$ is true or false.
- \end{itemize} % \vspace{-0.1in} % \subsection{Soundness and Completeness} %  \vspace{-0.1in}
- We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
- \begin{theorem}[\emph{Soundness and Completeness}] \label{SoundComplete}
- For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \emph{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
- \end{theorem}
- We prove the correctness of our formula rewriting algorithm using our regular expressions from Definition \ref{TRE}.
-As detailed in Section \ref{WESTalg}, nested binary temporal operators create the worst-case time and space complexity for the WEST program.
-Although the WEST program does not implement this theorem by default, we would expect selected applications of rewriting to improve runtime.
-We use this theorem to simplify MLTL formulas, making them easier to interpret.
-% Theorem \ref{NestedUR}'s proof appears in Appendix \ref{Appendix-NestedUR}.
-
- \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}] \label{NestedUR}
-   Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas.
-Let $\mathcal{B} = \mathcal{R} \text{ or } \mathcal{U}$.
-Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \phi,   \psi$ \text{be well-formed MLTL formulas in NNF.
-Then,} $ \phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
-That is, $ \phi \ \mathcal{U}_{[a,b+c]} \psi \equiv \phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi)$ and $ \phi \ \mathcal{R}_{[a,b+c]} \psi \equiv \phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi)$.
-\end{theorem}
-%The proof of Theorem \ref{NestedUR} appears in Appendix \ref{Appendix-NestedUR}.
-
-%KYR: this totally goes here in the journal version but in an appendix/on a website for the conference version
-
-%% \begin{proof}
-
-%% \textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\
-
-%% \noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
-Then, $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
-
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-%% &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right).
-%% \end{align*}
-%% $\mathcal{G}_{[i, i]}$ distributes over $\land$ and $\lor$, so
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right) \\
-%% &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
-%% \mathcal{G}_{[j, j]}\psi \right) \right) \right).
-%% \end{align*}
-%% Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \phi$, we have
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right) \right) \right) \\
-%% &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right).
-%% \end{align*}
-%% Since $\mathcal{G}_{[t_1,t_2-1]}\phi \land \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1,t_3]} \phi$, we have
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right)\\
-%% &= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right).
-%% \end{align*}
-%% Finally, let $k = i + j$. Thus
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\psi  \right) \\
-%% &= \text{reg}\left(\phi \ \mathcal{U}_{[a,b+c]} \psi\right).
-%% \end{align*}
-%% This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
-
-%% \noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
-%% We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,  \\
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \text{reg}\left(\neg\left(\neg\phi \ \mathcal{U}_{[a,b]}\neg\psi\right)\right) \\
-%% &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\phi \land \mathcal{G}_{[i, i]}\neg\psi\right)\right).
-%% \end{align*}
-%% Global is the dual of Finally, so
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\phi \land \neg\mathcal{F}_{[i, i]}\psi\right)\right)\\
-%% &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\right)\\
-%% &= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\\
-%% &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right).
-%% \end{align*}
-%% This completes the rewriting of the regex for Release.
-Now let $\gamma = \phi \ \mathcal{R}_{[0,c]} \psi$.
-Then $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) = \phi \ \mathcal{R}_{[a,b]}\gamma$ and
-%% $\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi \lor \mathcal{F}_{[j, j]}\psi\right)$. Thus
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-%% &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right).
-%% \end{align*}
-%% $\mathcal{F}_{[i, i]} \equiv \mathcal{G}_{[i, i]}$, so this operation distributes over $\land$ and $\lor$. Thus
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right) \\
-%% &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\psi \right) \right) \right).
-%% \end{align*}
-%% Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \phi$, we have
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right) \right) \right) \\
-%% &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right).
-%% \end{align*}
-%% Since $\mathcal{F}_{[t_1,t_2-1]} \phi \land \mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1, t_3]} \phi$, we have
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right) \\
-%% &= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right).
-%% \end{align*}
-%% Let $k = i + j$. Thus
-%% \begin{align*}
-%% \text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\psi  \right) \\
-%% &= \text{reg}\left(\phi \ \mathcal{R}_{[a,b+c]} \psi\right).
-%% \end{align*}
-%% Thus  $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) \equiv \phi \ \mathcal{R}_{[a,b+c]} \psi$, so $\phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
-This completes the proof.
-%% \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{WEST Algorithm and Analysis} \label{WESTalg}
-We now present the  full WEST algorithm, which recursively computes all satisfying temporal regular expressions to a given MLTL formula (in NNF). 
-For convenience, we use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_0, ..., t_{n-1}\} = \bigcup_{i=0}^{n-1} t_i$. 
-Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{U}$. 
-Note how \texttt{reg\_U} parallels the regular expression defined for $\mathcal{U}$, and the algorithms for the other three temporal operators follow an identical structure.
-
-One major detail that drastically improves running time is applying a simplifying function to the output of set intersection. 
-This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
-Although repeated set intersection blows up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
-We simplify alternation by using the fact that for regular expressions $w_0$ and $w_1$, $\mathscr{L}(w_0 1 w_1 \lor w_0 0 w_1) = \mathscr{L}(w_0 s w_1)$, and check if the reduction applies at every index between every pair of strings in a given set.
-
-% \begin{algorithm}[H]
-% \caption{WEST Algorithm}
-% \begin{algorithmic}[1]
-%     \Procedure{reg}{string $\phi$, int $n$}
-%         \If{$\phi$ is $\top$ or $\bot$} return reg\_prop\_const($\phi$, n)
-%         \EndIf
-
-%         \If{$\phi$ is $p_k$ or $\neg p_k$} return reg\_prop\_var($\phi$, n)
-%         \EndIf
-
-%         \If{$\phi  = \phi_1 \land \phi_2$} return set\_intersect(reg($\phi_1$), reg($\phi_2$), n)
-%         \EndIf
-
-%         \If{$\phi  = \phi_1 \lor \phi_2$} return join(reg($\phi_1$), reg($\phi_2$), n)
-%         \EndIf
-
-%         \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$} return reg\_F(reg($\phi_1$), a, b, n)
-%         \EndIf
-
-%         \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$} return reg\_G(reg($\phi_1$), a, b, n)
-%         \EndIf
-
-%         \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$} return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
-%         \EndIf
-
-%         \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$} return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
-%         \EndIf
-%     \EndProcedure
-% \end{algorithmic}
-% \end{algorithm}
-
-% ZILI: Presenting algorithm vertically instead
-\hspace{-5mm}
-\begin{minipage}{0.52\textwidth} 
-\begin{algorithm}[H] 
-\caption{WEST Algorithm}
-Inputs: $\phi$ - MLTL formula in NNF \\
-$\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
-$n$ - number of propositional variables \\
-Output: set of REGEX satisfying $\phi$
-\begin{algorithmic}[1]
-    \Procedure{reg}{string $\phi$, int $n$}
-        \If{$\phi$ is $\top$ or $\bot$}
-            \State return reg\_prop\_const($\phi$, n)
-        \EndIf
-
-        \If{$\phi$ is $p_k$ or $\neg p_k$}
-            \State return reg\_prop\_var($\phi$, n)
-        \EndIf
-
-        \If{$\phi  = \phi_1 \land \phi_2$}
-            \State \parbox[t]{.82\linewidth}{return set\_intersect(reg($\phi_1$), reg($\phi_2$), \hspace*{5mm}n)}
-        \EndIf
-
-        \If{$\phi  = \phi_1 \lor \phi_2$}
-            \State return join(reg($\phi_1$), reg($\phi_2$), n)
-        \EndIf
-
-        \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$}
-            \State return reg\_F(reg($\phi_1$), a, b, n)
-        \EndIf
-
-        \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$}
-            \State return reg\_G(reg($\phi_1$), a, b, n)
-        \EndIf
-
-        \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$}
-            \State return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
-        \EndIf
-
-        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
-            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
-        \EndIf
-    \EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\vspace{5.9mm}
-\end{minipage}
-\hfill
-\begin{minipage}{0.48\textwidth}
-\begin{algorithm}[H]
-\caption{set\_intersect}
-Inputs: $R, T$ - two sets of REGEX\\
-$n$ - number of propositional variables\\
-Output: set of REGEX equal to $R \land T$
-\begin{algorithmic}[1]
-\Procedure{set\_intersect}{$R$, $T$, n}
-    \State Pad($R$, $T$, n), return $\leftarrow \{\}$
-    \For{$(r, t) \in R\times T$}
-            \State add bit\_wise\_and($r, t$) to ret 
-    \EndFor
-    \State return simplify(ret)
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\vspace{-6.5mm}
-\begin{algorithm}[H]
-\caption{reg\_U} 
-Inputs: $r_\phi$, $r_\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
-$a, b$ - integers representing interval bound \\
-$n$ - number of propositional variables\\
-Output: set of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
-\begin{algorithmic}[1]
-\Procedure{reg\_U}{$r_\phi$, $r_\psi$, $a$, $b$, $n$} 
-    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
-    \If{$a > b$} return $\{\}$
-    \EndIf
-    \For{($a \leq i \leq b-1$) }
-        \State G1 $\leftarrow$ reg\_G($r_\phi$, $a$, $i$, $n$)
-        \State \parbox[t]{.8\linewidth}{G2 $\leftarrow$ reg\_G($r_\psi$, $i+1$, $i+1$, $n$)}
-        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect(G1,  \hspace*{5mm}G2, n)}
-        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
-        % , \hspace*{5mm}simp)}
-    \EndFor
-    \State return comp
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\end{minipage}
-
-\subsection{Proof of Correctness of WEST}
-\begin{theorem}[\emph{Theoretical Correctness of WEST}] \label{theocorrect}
-  Given a well-formed MLTL formula, The WEST Algorithm outputs the regular expressions of the satisfying computations as described in Section \ref{regex}.
-\end{theorem}
-Correctness of the WEST algorithm is dependent on the correctness of subroutines \texttt{reg\_prop\_cons}, \texttt{reg\_prop\_var}, \texttt{join}, \texttt{set\_intersect}, \texttt{reg\_F}, \texttt{reg\_G}, \texttt{reg\_U}, and \texttt{reg\_R}.
-The routines \texttt{reg\_prop\_cons} and \texttt{reg\_prop\_var} take as input a MLTL formula of the appropriate form and return the regular expression defined in Section \ref{regex}.\\
-\texttt{Join} concatenates two sets of regular expressions $R$ and $T$, which is equivalent to $\mathscr{L}(R) \cup \mathscr{L}(T)$.
-\texttt{set\_intersect} takes as input two sets of regular expressions $R = \{r_0, ..., r_{a-1}\}$ and $T = \{t_0, ..., t_{b-1}\}$, such that each $r_i$
-and $t_j$ are regular expressions over $\Sigma =$ \{``$0$'' , ``$1$'', ``$S$'', ``$,$''\}.
-Assume that all strings of regular expressions are right padded to equal length. 
-We show that $\mathscr{L}(\texttt{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$:
-\vspace{-3mm}$$\mathscr{L}(R) \cap \mathscr{L}(T) = \left(\bigcup_{i = 0}^{a-1} \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^{b-1} \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^{a-1} \bigcup_{j = 0}^{b-1} \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).$$
-The loop in line 3 of \texttt{set\_intersect} computes the union of \texttt{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\texttt{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
-Given a computation $\pi$, $\pi \in \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ if and only if $\pi$ matches every character of both $r_i$ and $t_j$. 
-$\texttt{Bit\_wise\_and}(r_i, t_j)$ compares $r_i$ and $t_j$ character by character and computes their intersection, which is defined naturally: $0 \cap 1 = \emptyset,\ 0 \cap S = 0,\ 1 \cap S = 1, \ 0 \cap 0 = 0, \ 1 \cap 1= 1,\text{ and } S \cap S = S$.
-Note that this operation is commutative. This exhaustively captures all the cases for which $\pi$ must match corresponding characters from $r_i$ and $t_j$. 
-Thus $\mathscr{L}(\texttt{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$ and the claim holds.\\
-The correctness for \texttt{reg\_F}, \texttt{reg\_G}, \texttt{reg\_U}, \texttt{reg\_R}, and \texttt{reg} will be proven by induction on depth of recursion to \texttt{reg}. 
-The depth of recursion is exactly the depth of the parse tree of the input formula.
-For the base case (depth $0$), \texttt{reg\_prop\_var} and \texttt{reg\_prop\_cons} are called to handle input formulas that consist of a propositional variable, the negation of a propositional variable, or a propositional constant.
-Then assume \texttt{reg} is correct on all formulas of depth at most $d$, for some integer $d \geq 0$. 
-Let $\gamma$ be a MLTL formula in negation normal form of depth $d + 1$.
-$\gamma$ must be of the form $\phi \lor \psi$, $\phi \land \psi$, $\mathcal{G}_{[a,b]}\phi$, $\mathcal{F}_{[a,b]}\phi$, $\phi \mathcal{U}_{[a,b]} \psi$, or $\phi \mathcal{R}_{[a,b]} \psi$, such that $\phi$ and $\psi$ are of depth at most $d$, and $a$, $b$ are nonnegative integers.
-Correctness of the first two cases have been proven. 
-The proof for the four temporal cases are of similar structure, and it suffices to verify that the algorithms compute appropriate regular expressions correctly using \texttt{join} and \texttt{set\_intersect}.\\
-We give the explicit proof for the case $\gamma = \phi \mathcal{U}_{[a,b]} \psi$ as an example.
-\texttt{reg\_U} takes as input $r_\phi =$ reg($\phi$) and $r_\psi = $ reg($\psi$), which by the induction hypothesis are correctly and recursively computed. 
-The regular expression for the Until operator may be rewritten as $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) = \text{reg}\left(\mathcal{G}_{[a, a]} \psi \right)\lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$.
-In line $2$ of \texttt{reg\_U}, the variable \texttt{comp} is initialized to $(`1S"^n + ``,")^a$ pre-concatenated to $r_\psi$, and is the regular expression for $\mathcal{G}_[a, a] \psi$. 
-Next, the $\lor$ from $i = a + 1$ to $b - 1$ is computed by the for loop in line 4; lines 5 through 7 computes $\text{reg}\left(\mathcal{G}_{[a,i]}\phi \land \mathcal{G}_{[i+1, i+1]} \psi\right)$. 
-This shows correctness of \texttt{reg\_U} (note that in a complete proof, correctness of \texttt{reg\_G} needs to be shown first since lines 5 and 6 calls \texttt{reg\_G}).
-Continuing in the same fashion to prove the other three cases, \texttt{reg} is correct on all depth $d+1$ inputs, and thus \texttt{reg} is correct on all inputs by induction.
-
-\subsection{Theoretical Complexity}
-\begin{flushleft}
-In order to reason about the complexity of our algorithms, we make a few reasonable assumptions about our inputs.
-Suppose that the lower and upper intervals of temporal operators are bounded by some constant $d \in \mathbb{N}$, and that the difference between any bound is less than some constant $\delta \in \mathbb{N}$.
-We provide a summary of the complexity of each of the helper functions that contribute to the worst case behavior of final output.\\
-For any function $f(\phi)$ taking a string argument $\phi$, we use $|\phi|$ to denote the number of characters in $\phi$ and $S(f(\phi))$ to denote the space complexity of $f$ in terms of the number of characters in the output.\\
-\hspace{3mm} If $\phi$ is a propositional constant or variable, it's easy to see that $S(\texttt{reg}(\bot)) = 0$ since only the empty set is returned.
-By definition $\texttt{reg}(\top) = S^n$, so we have that $S(\texttt{reg}(\top)) = O(n)$.
-Similarly, $\texttt{reg}(p_k)$ and $\texttt{reg}(\neg p_k)$ both return strings of the same length and thus $S(\texttt{reg}(p_k)) = S(\texttt{reg}(\neg p_k)) = S(\texttt{reg}(\top)) = n$.\\
-\hspace{3mm} If $\phi$ is ``$\phi_{1} \lor \phi_{2}$'' we return $\texttt{join}(\texttt{reg}(\phi_{1}), \texttt{reg}(\phi_{2}))$, which simply concatenates the contents of the two sets. 
-Thus $S(\texttt{reg}(\phi_{1} \lor \phi_{2})) = S(\texttt{reg}(\phi_{1})) + S(\texttt{reg}(\phi_{2})).$\\
-\hspace{3mm} If $\phi$ is ``$\phi_{1} \land \phi_{2}$''
-$ \texttt{set\_intersect}(\texttt{reg}(\phi_{1}), \texttt{reg}(\phi_{2}), n)$ returns a set of size $S(A) \cdot S(B)$ in the worst case when no simplification can be made. 
-Thus, our space complexity is $S(\texttt{reg}(\phi_{1} \land \phi_{2})) = S(\texttt{reg}(\phi_{1})) \cdot S(\texttt{reg}(\phi_{2})).$\\
-\hspace{3mm} For the next cases, we use these two bounds and define the constants $\mathcal{C}_G$ and $\mathcal{C}_F$:
-{\centering $\prod_{i = a}^b (n+1)i = (n+1)^{b-a} \cdot \frac{b!}{(a-1)!} \leq (n+1)^\delta b!
-\leq (n+1)^\delta d!
-= \mathcal{C}_G$ \\ $\sum_{i = a}^b (n+1)i \leq (n+1)b\delta \leq (n+1)d\delta  = \mathcal{C}_F$\par}
-\hspace{3mm} If $\phi \text{ is } ``\mathcal{G}_{[a,b]} \phi_{1}$":
-recall that $\texttt{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \texttt{reg}(\phi) (,S^n)^{b-i}$.
-From the analysis of \texttt{set\_intersect}, worst case space complexity is multiplicative.
-Thus\\ $S(\texttt{reg}(\phi)) = \prod_{i=a}^{b} (n+1)i \cdot S(\texttt{reg}(\phi_{1})) < \mathcal{C}_G S(\texttt{reg}(\phi_1))$.
-In this calculation, $(n+1)i$ counts the concatenation of the padded component of the computation in the worse case when we have a set of only length 1 strings. \\
-\hspace{3mm} If $\phi \text{ is } ``\mathcal{F}_{[a,b]} \phi_{1}$":
-Recall that $\texttt{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \texttt{reg}(\phi)(,S^n)^{b-i}$. \\
-From the analysis of \texttt{join}, worst case space complexity is additive and thus 
-$S(\texttt{reg}(\phi)) = \sum_{i=a}^{b} (n+1)i \cdot S(\texttt{reg}(\phi_{1})) < \mathcal{C}_{F} S(\texttt{reg}(\phi_1))$.\\
-\hspace{3mm}If $\phi$ = $``\phi_1 \mathcal{U}_{[a, b]} \phi_2"$: Recall that
-    $\texttt{reg}(\phi_1 \ \mathcal{U}_{[a,b]} \phi_2) =  \bigvee_{i=a}^{b} \texttt{reg}\left(\mathcal{G}_{[a,i-1]}\phi_1 \land \mathcal{G}_{[i, i]} \phi_2\right)$.
-    We can bound $S(\texttt{reg}(\mathcal{G}_{[i, i]} \phi_2))$ by $(n+1) \cdot i \cdot S(\texttt{reg}(\phi_2))$ because the operation is equivalent to simply prepending $(S^n ,)^i$.
-    Thus using our previous results for the $\mathcal{G}$, $\land$ and $\lor$ operators, we have that:
-    \vspace{-.4cm}
-    \begin{align*}
-        S(\texttt{reg}(\phi)) &= 
-        \sum_{i = a}^b [((n+1)(i-1) + 1) \cdot S(\texttt{reg}(\phi_1))]^\delta 
-        [(n+1) \cdot i \cdot S(\texttt{reg}(\phi_2))] \\
-        &< \delta [((n+1)(b-1) + 1) \cdot S(\texttt{reg}(\phi_1))]^\delta 
-        [(n+1) \cdot b \cdot S(\texttt{reg}(\phi_2))] \\
-        &< \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2)) \\
-        &= \mathcal{C}_U \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2))
-    \end{align*}
-    where $\mathcal{C}_U = \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d$.\\
-\hspace{3mm} If $\phi$ = $``\phi_1 \mathcal{R}_{[a, b]} \phi_2"$:
-    $\texttt{reg}(\phi_1 \mathcal{R}_{[a,b]} \phi_2) =  \texttt{reg}\left(\mathcal{G}_{[a,b]}\phi_2\right) \lor \bigvee_{i=a}^{b-1} \texttt{reg}\left(\mathcal{G}_{[a,i]}\phi_2 \land \mathcal{G}_{[i, i]} \phi_1\right)$.
-Thus, a similar argument to the $\mathcal{U}$ case shows
-    $S(\texttt{reg}(\phi)) < \mathcal{C}_R \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2))$, \\
-    where $\mathcal{C}_R = \mathcal{C}_G \cdot \delta (n+1)d$.
-\end{flushleft}
-\begin{theorem}[\emph{Space Complexity}]
-Given a well formed MLTL formula $\phi$, $\emph{\texttt{reg}}(\phi)$ has worst-case space complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
-\end{theorem}
-\begin{proof}
-    To analyze worst-case complexity, it's clear from the analysis above that $\mathcal{U}$ and $\mathcal{R}$ give the largest complexity.
-From the constants in their respective bounds, we can show that $\mathcal{C}_U = ((n+1)d - n)^\delta \cdot \mathcal{C}_R > \mathcal{C}_R$, and so we'll analyze only repeated nesting of the operator $\mathcal{U}$.\\
-    However, notice that the structure of the parse tree is important.
-For example, formulas similar to $(a \mathcal{U} b) \mathcal{U} (c \mathcal{U} d)$ generate a balanced binary parse tree where the maximum depth of recursion is $O(\log \ell)$.
-However if the nesting is only from one side, such as formulas similar to $(((p_0 \mathcal{U} p_1) \mathcal{U} p_2) \mathcal{U} p_3)$, then the maximum depth of recursion is $O(\ell)$.
-Thus we'll focus on the formula $$\phi = (((p_0 \mathcal{U}_{[a_1, b_1]} p_1) \mathcal{U}_{[a_2, b_2]} p_2) \mathcal{U}_{[a_3, b_3]}...
-\mathcal{U}_{[a_{\ell - 1}, b_{\ell - 1}]} p_{\ell - 1}) \mathcal{U}_{[a_\ell, b_\ell]} p_\ell$$ where there are $\ell$ logical connectives $\mathcal{U}$ and $n = \ell + 1$ propositional variables.\\
-    We'll derive the complexity of $S(\texttt{reg}(\phi))$ by defining the recursive sequence $\{s_k\}_{k = 1}^\ell$ such that $s_1 = S(\texttt{reg}(p_0 \mathcal{U}_{[a_1, b_1]} p_1))$, and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot S(\texttt{reg}(p_{k+1}))$.
-The recurrence relation captures an extra nesting of the $\mathcal{U}$ operator, based on the complexity of $\mathcal{U}$ defined above.
-We calculate $S(p_m) = n = \ell + 1$ for all $m$ such that $0 \leq m \leq \ell$, thus $s_1 = \mathcal{C}_U(\ell + 1)^{\delta + 1}$ and $s_{k+1} = \mathcal{C}_U (s_k)^\delta \cdot (\ell + 1)$.
-\\
-    The explicit formula is given by $s_k = \mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}$.
-It's easy to check that the base case $k = 1$ holds, and we prove the claim by induction:
-    \vspace{-0.2cm}
-    \begin{align*}
-        S_{k + 1} &= \mathcal{C}_U (\mathcal{C}_U^{\sum_{i = 0}^{k - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k} \delta^i}) ^ \delta \cdot (\ell + 1) \\
-        &= \mathcal{C}_U^{1 + \sum_{i = 0}^{k - 1} \delta^{i + 1}} \cdot (\ell + 1)^{1 + \sum_{i = 0}^{k} \delta^{i + 1}} \\
-        &= \mathcal{C}_U^{\sum_{i = 0}^k \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{k+1} \delta^i}.
-    \end{align*}
-    Thus we have that $S(\texttt{reg}(\phi)) = \mathcal{C}_U^{\sum_{i = 0}^{\ell - 1} \delta^i} \cdot (\ell + 1)^{\sum_{i = 0}^{\ell} \delta^i} = O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$.
- \end{proof}
-
-For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
-In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, \top, \bot$, as well as that of \texttt{set\_intersect}, \texttt{join}, and the operator $\mathcal{U}$ match their respective space complexities.
-\begin{theorem}[\emph{Time Complexity}]
-Given a well formed MLTL formula $\phi$, $\emph{\texttt{reg}}(\phi)$ has worst-case time complexity that is $O(\mathcal{C}_U^{\delta ^ \ell} \cdot (\ell + 1)^{\delta^{\ell + 1}})$, where $\ell$ is the number of logical connectives ($\land, \lor, \mathcal{F}, \mathcal{G}, \mathcal{R}, \mathcal{U}$) in $\phi$.
-\end{theorem}
-If in the worst case no simplification occurs in any call of \texttt{set\_intersect}, space complexity remains unchanged, but simplifying a set of regular expressions is cubic in input size.
-In practice however, both time and space complexities are much more optimistic than worst-case estimates.
-
-\subsection{Experimental Benchmarking}
-We accompany theoretical space and time complexity with experimental evaluation of these complexities using randomly-generated MLTL formulas.
-We ran these experiments on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
-For each simulation, we generated 1000 MLTL formulas using the parameters \texttt{delta}, \texttt{interval\_max}, number of propositional variables, and number of iterations.
-\texttt{delta} is the maximum length we allow for any interval.
-\texttt{interval\_max} is the largest allowed upper bound for any interval.
-Number of iterations refers to the level of nesting in the generated formulas.
-For example, $\mathcal{G}_{[0,2]}p_0$ is a formula generated with one iteration, while $\mathcal{G}_{[0,2]}(p_0 \land p_1)$ is a formula generated with two iterations.
-We measure the number of characters in the output and the amount of time in milliseconds taken to run the program.
-Note that these simulations run the \texttt{reg} function with the subformula boolean set to false and the simplify boolean set to true.\\
-\noindent\textbf{Simulation 1}
-For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}. We obtain plots \ref{InVsOutputLen} and \ref{InLenVsRunTime}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
+\begin{figure}[h]
     \centering
-    \includegraphics[scale=0.35]{images/Sim1Length_large.png}
-    \captionof{figure}{Input length vs output length.\vspace{3mm}}
-    \label{InVsOutputLen}
-    \end{figure}
-\end{minipage}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim1Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{InLenVsRunTime}
-    \end{figure}
-\end{minipage}\\
-\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both Figures \ref{InVsOutputLen} and \ref{InLenVsRunTime}, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InLenVsRunTime}.
-\\
-\noindent\textbf{Simulation 2}
-For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for \texttt{delta}, and 20 for \texttt{interval\_max}. Here are some examples of generated formulas:
-$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain plots \ref{fig:InVsOutLen2} and \ref{fig:InLenVsRunTime2}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim2Length_large.png}
-    \captionof{figure}{Input length vs output length\vspace{3mm}}
-    \label{fig:InVsOutLen2}
-    \end{figure}
-\end{minipage}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim2Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{fig:InLenVsRunTime2}
-    \end{figure}
-\end{minipage}\\
-\noindent\textbf{Simulation 3}
-For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for \texttt{delta}, and 10 for \texttt{interval\_max}.
-We obtain plots \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim3Length_large.png}
-    \captionof{figure}{Input length vs output length\vspace{3mm}}
-    \label{fig:InLenVsOutLen3}
-    \end{figure}
-\end{minipage}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim3Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{fig:InLenVsRunTime3}
-    \end{figure}
-\end{minipage}\\
-The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both Figures \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}, and Figure \ref{fig:InLenVsOutLen3} had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
-\\
-\noindent\textbf{Simulation 4}
-For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}.
-Some examples of generated formulas are: $\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
-We obtain plots \ref{InLenVsOutLen4} and \ref{InLenVsRunTime4}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim4Length_large.png}
-    \captionof{figure}{Input length vs output length\vspace{3mm}}
-    \label{InLenVsOutLen4}
-    \end{figure}
-\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim4Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{InLenVsRunTime4}
-    \end{figure}
-\end{minipage}
-\noindent What we observe from the simulations is that the worst case complexity, both for space and time, is relatively rare.
-We also observe that these worst cases are extreme outliers and that in nearly every case, are examples of nested binary temporal operators.
-As seen in \cite{HLR21}, \cite{KZJZR20}, \cite{AJR22}, and \cite{HCHJR21}, nested binary temporal operators do not appear in any specifications, and thus are likely rare in practical applications.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Correctness of WEST Tool Implementation} \label{test}
-We accompany our proof of algorithmic correctness with a rigorous evaluation of implementation correctness, showing that our WEST tool correctly implements our WEST algorithm.
-Since our proof of algorithmic correctness is manual and our focus is on usability for validation by humans, we utilize more traditional techniques for robust software engineering with testing-based evaluation.
-An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
-Since the primary purpose of the WEST tool is validation of formulas for humans, we focused on writing a tool with an intuitive human-facing interface and then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.\\
-One na\"ive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
-For WEST, this strategy would generate a very large test suite with significant redundancy. 
-For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program.
-We approach this problem more intelligently: we test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm.
-A control path is a sequence of lines of code that are executed in one calculation of an input formula.
-Differing structures of formulas will lead to different sequences of lines of code to be executed, and a test suite to explore all such paths provides high confidence in the correctness of the WEST tool.
-
-\subsection{Intelligent Fuzzing}
-Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; we employ fuzz testing (also know as fuzzing), a form of negative testing.
-We deviate from traditional black-box fuzzing defined by \cite{Miller}:
-\textit{``If we consider a program to
-be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''}\\
-Instead we utilize intelligent fuzzing (sometimes referred to as whitebox fuzzing), which is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
-Borrowing the words of Miller, our approach to testing the WEST program can be thought of as walking all possible paths up to a certain depth of the state space of our algorithm. 
-We first outline our overall approach to intelligent fuzzing: 
-\begin{enumerate}
-    \item Construct a state diagram of our algorithm, represented as a directed graph. 
-    The edges of the graph capture control flow of our algorithm, and vertices represent the remaining blocks of the code without branching statements.  
-    \item Construct a test suite that explores all possible paths in the digraph up to a certain depth. Run the WEST program on the test suite to produce a set of output files.
-    \item Run a na\"ive brute force generator of satisfying computations on the test suite and verify that both outputs match for all test cases.
-\end{enumerate}
-\subsubsection{State Diagram Construction}
- We can represent the state space of the WEST algorithm as a directed graph with the edges representing the control flow and vertices representing blocks of contiguous code without branching statements.
- The core of the WEST program lies in the recursive routine, \texttt{reg}, which calls the $8$ different subroutines as shown in \ref{fig:abstracted_graph}.
-\begin{figure}[t]
-    \centering
-    \begin{tikzpicture}[ node/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=8mm},
-    bignode/.style={rounded rectangle, draw=black!60, fill=black!5, thick, minimum size=10mm},
-    star/.style={circle, draw=red!60, fill=red!5, thick, minimum size=1mm} ]
+    \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, star/.style={circle, draw=red!60, fill=red!5, very thick, minimum size=1mm}]
 
     %Nodes
-    \node[bignode] (reg) {\textbf{Reg}};
+    \node[bignode](reg){\textbf{Reg}};
+    \node[node](prop_var)[left=2 cm of reg]{Prop\_Var};
+    \node[node](prop_cons)[below=of prop_var]{Prop\_Cons};
+    \node[star](unary_star)[below=2 cm of reg]{};
+    \node[node](reg_f)[below=of unary_star]{Reg\_F};
+    \node[node](reg_g)[left= of reg_f]{Reg\_G};
+    \node[star](temp_binary_star1)[right=2 cm of unary_star]{};
+    \node[star](temp_binary_star2)[below= of temp_binary_star1]{};
+    \node[node](reg_u)[below=of temp_binary_star2]{Reg\_U};
+    \node[node](reg_r)[right=of reg_u]{Reg\_R};
     \node[star](prop_binary_star1)[right= of reg]{};
@@
     \node[node](join)[right=of prop_binary_star2]{Join};
-    \node[node](set_intersect)[below=0.5 cm of join]{Set\_Intersect};
-    \node[node] (prop_var) [left=of reg] {Prop\_Var};
-    \node[node] (prop_cons) [below=0.5 cm of prop_var] {Prop\_Cons};
-    \node[star](unary_star)[below=0.9 cm of reg]{};
-    \node[node](reg_f)[below=0.7 cm of unary_star]{Reg\_F};
-    \node[node](reg_g)[left= of reg_f]{Reg\_G};
-    \node[star](temp_binary_star1)[below=0.5 cm of prop_binary_star1]{};
-    \node[star](temp_binary_star2)[below=0.5 cm of temp_binary_star1]{};
-    \node[node](reg_u)[below=0.7 cm of temp_binary_star2]{Reg\_U};
-    \node[node](reg_r)[right=of reg_u]{Reg\_R};
+    \node[node](set_intersect)[below=of join]{Set\_Intersect};
 
     %Lines
-    \draw[->] (reg.west) -- (prop_var);
-    \draw[->] (reg.south) -- (prop_cons);
-    \draw[->] (reg.south) -- (unary_star);
+    \draw[->] (reg.west) -- (prop_var.east);
+    \draw[->] (reg.south) -- (prop_cons.north);
+    \draw[->] (reg.south) -- (unary_star.north);
     \draw[->] (unary_star.south) -- (reg_f.north);
-    \draw[->] (unary_star.south) -- (reg_g);
-    \draw[->] (reg.south) -- (temp_binary_star1);
+    \draw[->] (unary_star.south) -- (reg_g.north);
+    \draw[->] (reg.south) -- (temp_binary_star1.north);
     \draw[->] (reg.east) -- (prop_binary_star1.west);
     \draw[->] (temp_binary_star1.south) -- (temp_binary_star2.north);
-    \draw[->] (temp_binary_star2.south) -- (reg_r);
+    \draw[->] (temp_binary_star2.south) -- (reg_r.north);
     \draw[->] (temp_binary_star2.south) -- (reg_u.north);
@@
     \draw[->] (prop_binary_star2.east) -- (join.west);
-    \draw[->] (prop_binary_star2.south) -- (set_intersect);
+    \draw[->] (prop_binary_star2.south) -- (set_intersect.north);
     \end{tikzpicture}
 
-    \caption{Abstracted graph of the \texttt{reg} main routine. Red nodes signal recursive calls to \texttt{reg} on sub formulas of the input formula.}
+    \caption{Abstracted Graph}
     \label{fig:abstracted graph}
 \end{figure}
-In order to construct the intelligent fuzzing test suite, we make the design choice to abstract away the eight subroutines in the overall state space diagram, despite the fact that they may have different possible execution paths within them.
-Without this abstraction, attempting to explore all execution paths in this finer graph is infeasible due to the explosion in the number of paths \cite{Pham_2016}, some of which are provably impossible to construct a test input to explore.
-\subsubsection{Creating the Test Suite} %KYR: edited to remove excessive passive voice (active voice is best for research papers!)
-To generate our intelligent fuzzing test suite, we first count the number of formulas $\phi(d)$ to be generated as a function of the exact depth $d$ of recursion desired. 
-For $d = 0$, only the paths leading to \texttt{prop\_var} and \texttt{prop\_cons} can be explored, so $\phi(0) = 2$.
-For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \texttt{reg\_G} and \texttt{reg\_F} is counted in the linear term, and paths to \texttt{reg\_U}, \texttt{reg\_R}, \texttt{set\_intersect}, and \texttt{join} is counted by the quadratic term.
-This gives $\phi(1) = 20$, $\phi(2) = 1640$, and $\phi(3) = 10761680$. 
-$d = 3$ is computationally infeasible, and $d = 1$ doesn't give us assurance about operators interacting with each other through nesting. Thus we select $d = 2$ as a happy medium. 
-We generate the full test suite in a similar recursive manner. 
-Firstly, the $d = 0$ test suite consists of two formulas: a propositional variable or its negation, and a propositional constant. 
-Then for any $d \geq 1$, we iterate through all formulas in the depth $d-1$ test suite for \texttt{reg\_G} and \texttt{reg\_F}, and all pairs of formulas from the $d-1$ test suite for the remaining four recursive paths.
-To ensure wider coverage, we randomly generate each of the propositional variables or their negation and propositional constants.
-\subsubsection{Verifying against Na\"ive Brute Force}
-A relatively straightforward approach to generating the set of all satisfying computations of a MLTL formula $\phi$ over $n$ variables, such that $m = \text{cplen}(\phi)$, is to iterate over all $2^{m \cdot n}$ possible computations, which counts all possible length $m \cdot n$ bit strings.
-An interpreter function takes computation $\pi$ and MLTL formula $\phi$ and determines if $\pi \vDash \phi$ purely based on the semantics that define MLTL.
-Our test program translates every first-order quantifier into a loop; then checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
-The full implementation details are available in the WEST GitHub repository.\footnote{Links have been redacted for blind review.} 
-On an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM, the brute force program took nearly nine hours to execute the depth two test suite of $1640$ formulas. 
-For this test suite, we fixed the number of propositional variables at $n = 4$ and the largest computation length was $m = 5$, from formulas with doubly-nested temporal operators. 
-In comparison, the WEST program executed the same test suite in under thirty minutes on the same machine.
-Note that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the ``$S$'' characters in the regular expressions.
-For instance, the regular expression ``$1SS0SS1$'' yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
-It's important to state that although the full test suite matches between both implementations, absolute correctness on all inputs is not guaranteed for either program.
-However, the successful execution of the test suite gives us a much higher confidence in correctness of both the WEST program and the brute force program.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Regular Expression Simplification Theorem} \label{simpsection}
-As a final result, we provide a regular expression simplification theorem.
-This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all ``$S$'' characters.
-Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of ``$S$'' characters when a formula holds true for every computation.
-We first define some vocabulary.
- We say a regular expression composed entirely of ``$S$'' characters and commas is an \emph{arbitrary computation}.
-For the purposes of the following theorem, we remove all commas from computations.
-We say a ``0'' or a ``1'' in a regular expression is a \emph{fixed truth value}.
-We overload the definition of a matrix and say that a \emph{matrix} is a representation of a union of regular expressions, where each row is a regular expression.
-This aids significantly in the description and proof of the theorem; note, however, that matrix algebra does not apply in this definition.
-\begin{theorem}[\emph{Regular Expression Simplification Theorem}] \label{simp}
-Let $M$ be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length $n$ with commas stripped.
-If each column has one ``$1$,'' one ``$0$,'' and $n-1$ ``$S$'' characters, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.
-\end{theorem}
-Note that this theorem gives us a sufficient but not a necessary condition for simplification to the arbitrary computation.
-One such example is the regular expression $101|S1S|1S0|0SS$, which fails the hypothesis of the  simplification theorem but is still equivalent to $SSS$.
-\subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
-First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
-A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof.
 
-\begin{figure}[h!]
-\begin{minipage}{.62\textwidth}
-\begin{example} \label{example1}
-Consider the MLTL formula:
-$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$.
-The WEST program outputs a union of regular expressions represented by the matrix in \eqref{matrix_ex3}.
-Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation.
-However, we foresee some challenges to the implementation of this algorithm.
-\end{example}
-\end{minipage}
-\begin{minipage}{.38\textwidth}
-%     \noindent \textbf{Example:}
-    % \vspace{-0.05\textwidth}
-\begin{equation} \label{matrix_ex3}
-    \begin{pmatrix}
-    1 & S & S & S\\
-    S & 1 & S & S\\
-    S & S & 1 & S\\
-    S & S & S & 1\\
-    0 & 0 & 0 & 0
-    \end{pmatrix}
-\end{equation}
-\end{minipage}
-\end{figure}
-For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
-Next, it is possible that a regular expression could be appended with a substring of ``$S$'' characters at the beginning or end.
-\begin{figure}[h!]
-\begin{minipage}{.62\textwidth}
-\begin{example} \label{example2}
-Consider the following MLTL formula: $T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$.
-The WEST program generates a union of regular expressions corresponding to the matrix shown in \eqref{matrix_ex4}.
-This is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
-\end{example}
-\end{minipage}
-\begin{minipage}{.38\textwidth}
-\begin{equation} \label{matrix_ex4}
-    \begin{pmatrix}
-      S & S & 1 & S \\
-      S & S & S & 1 \\
-      S & S & 0 & 0
-    \end{pmatrix}
-\end{equation}
-\end{minipage}
-\end{figure}
-
-Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
-Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up'' by common substrings.
-Consider the following modification to the matrix generated by example \ref{example1}:\\
-\begin{minipage}{.5\textwidth}
-The substrings ``$0$,'' ``$1S0$,'' and ``$1$'' are inserted at the beginning, middle, and end, respectively.
-In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
-Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.
-\end{minipage}
-\begin{minipage}{.5\textwidth}
-\begin{center}
-$
-\begin{pmatrix}
-  0 & \mathbf{1} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
-  0 & \mathbf{S} & \mathbf{1} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
-  0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{1} & \mathbf{S} & 1\\
-  0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{1} & 1\\
-  0 & \mathbf{0} & \mathbf{0} & 1 & S & 0 & \mathbf{0} & \mathbf{0} & 1\\
-    \end{pmatrix} 
-    \vspace{2mm}
-    \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
-$
-\end{center}
-\end{minipage}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Closing Remarks}
-\label{Conclusion}
- One goal of this research project is to visually represent MLTL formulas as truth tables, similar to classical truth tables in propositional logic. 
-The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safety-critical systems, and the WEST program can aid in the debugging of such specifications.
-The WEST program accomplishes this: given a MLTL formula $\phi$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
-The tool itself has demonstratively reasonable run time. 
-Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very rare in practice. 
-We have also applied techniques in intelligent fuzzing to explore the state space of the algorithm in a structured way. 
-For a reasonably complex program, a complete walk of the input space is infeasible. 
-However, basing testing on a (manually constructed) graph of the algorithm provides a middle ground where some level of coverage is guaranteed. 
-Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used for algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
-\subsection{Additional Research Directions} The release of the WEST algorithm and open-source tool open many promising avenues for future research, including the following.\\
-\textbf{Describe all satisfying computations to LTL formulas using $\omega$-regular expressions.}
-By definition, $\omega$-regular expressions match only infinite words, and can be used to describe satisfying computations to LTL formulas (which have infinite time steps). 
-Our work on validation for MLTL formulas lays the groundwork for future work on validation of the finite-trace logic LTLf \cite{GV13} as well as LTL formulas.
-For the infinite-trace semantics of LTL, the particular difficulties revolve around the need for the Kleene star operation, which may lead to blow-up due to arithmetic of infinite unions and intersections of regular expressions.
-\\
-\noindent \textbf{Simplifying unions of regular expressions to a minimal representation.}
-Theorem \ref{simp} addresses a non-trivial situation in which a set of regular expressions may be simplified.
-A natural question to ask is what is the minimum number of strings of regular expressions needed to represent a language of computations.
-However, such a minimal representation is not unique.
-For instance, $\mathscr{L}(S1|1S) = \mathscr{L}(S1|10) = \{01, 10, 11\}$.
-There may be other schemes needed to simplify any arbitrary union of regular expressions to their minimal representation.\\
-\noindent \textbf{A more general application of intelligent fuzzing to recursive algorithms.}
-A tool to systematically convert a recursive algorithm (perhaps written in some strictly defined pseudocode syntax) into a directed graph representation of the state space would be a helpful aid for generating test suites.
-Significant efforts were made to construct the graph of the WEST algorithm by hand, and an automated process would be invaluable. 
-Additional care should be put into allowing for varying levels of abstractions of execution due to concerns of the path explosion problem.
-We note that such avenues for code-level verification will still be necessary even upon the completion of potential future work avenues like synthesizing the core implemention of the WEST algorithm from an interactive theorem prover.
-This is because the goal of explainability to humans will require at least some manual code authorship for the forseeable future.
-\\
-\noindent \textbf{Synthesizing verified code from MLTL behavior descriptions.} The truth tables generated by the WEST tool can now serve as input to a recently-published toolchain \cite{dasc-2022}.
-This newly-enabled workflow would produce encodings of the represented MLTL behavior for the interactive theorem prover ACL2, including automatically generating related properties of general interest such as unambiguousness \cite{DBLP:journals/corr/abs-2205-11707,ACL2-Site,ACL2-Doc}.
-Next, a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL.
-By providing a new front-end for this toolchain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system.
-Considering the rising popularity of MLTL for describing such behaviors, we expect this to be a rewarding avenue for future exploration.
-
-% FUTURE WORK:
-% potentially recursive function implementation of Regular Expression Simplification Theorem
-%% \subsubsection{Acknowledgements}
-%% \hspace{\parindent} This work was done as part of Iowa State University's Research Experience for Undergraduates funded by NSF grant DMS-1950583.
-We would like to thank Iowa State University and the NSF for this research opportunity.
-%% The assistance of our mentors Dr.
-Kristin Yvonne Rozier and Laura Gamboa Guzmán was invaluable and greatly appreciated.
-In addition, we thank Dr.
-Steve Butler and Dr.
-Bernard Lidický for their management of this program and organization of its funding.
-%% Finally, we want to thank Brian Kempa for his guidance and suggestions on the intelligent fuzzing portion of our research, and Dr.
-Steve Butler for his intuition on the Regular Expression Simplification Theorem.
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-\newpage
-\bibliographystyle{splncs04}
-\bibliography{Citations}
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section*{Appendix} \label{Appendix}
-\renewcommand{\thesection}{\Roman{section}}
-Content in the appendices will appear online, on the paper's website, but appears here for now due to blind review.
-
- \section{Soundness and Completeness} \label{Appendix-SoundComplete}
-%  \vspace{-0.1in}
- We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
-\begingroup
-\renewcommand\thetheorem{2}
- \begin{theorem}[\emph{Soundness and Completeness}]
- For any well formed MLTL formula $\phi$ in negation normal form, a computation $\pi$ with $|\pi| = \text{cplen}(\phi)$ satisfies $\phi$ and  if and only if $\pi \in \mathscr{L}(\emph{reg}(\phi))$.
-\end{theorem}
-\endgroup
- \begin{proof}
- We proceed by induction on the length of the formula.\\
- \noindent \textbf{Base Cases.}\\
- \noindent\textbf{reg($\top$)}\\
- Any computation $\pi$ satisfies $\top$, and $\mathscr{L}(\text{reg}(\top))$ is the set of all computations of one time step.
-Padding conventions extends this to the set of all computations of any positive number of time steps, so we are done.\\
- \noindent\textbf{reg($\bot$)}\\
- There are no computations that satisfy $\bot$ and $\mathscr{L}(\text{reg}(\bot))$ is the empty string, so we are done.\\
- \noindent\textbf{reg($p_k$)}\\
- For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
- $$S^{k} 1 S^{n-k-1}$$
- which is precisely reg($p_k$).\\
- \noindent\textbf{reg($\neg p_k$)}\\
- If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
- $$S^{k} 0 S^{n-k-1}$$
- which is precisely reg($\neg p_k$).\\
- \noindent\textbf{Inductive Step.}\\
- Suppose the theorem holds for MLTL formulas $\varphi$ and $\psi$.
-We now show that it holds for $\varphi \land \psi$, $\varphi \lor \psi$, $\mathcal{F}_{[a,b]} \varphi$, $\mathcal{G}_{[a,b]} \varphi$, $\varphi \ \mathcal{U}_{[a,b]} \psi$, and $\varphi \mathcal{R}_{[a,b]} \psi$.\\
- \noindent \textbf{reg($\varphi \land \psi$)}\\
- We know that $\pi \vDash \varphi \land \psi \text{ iff } \pi \vDash \varphi \text{ and } \pi \vDash \psi$.\\
- By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
- \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
- $$\pi \vDash \varphi \land \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \land \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \land \psi)).$$
- \noindent \textbf{reg($\varphi \lor \psi$)}\\
- We know that $\pi \vDash \varphi \lor \psi \text{ iff } \pi \vDash \varphi \text{ or } \pi \vDash \psi$.\\
- By the inductive hypothesis, $\pi \vDash \varphi$ iff $\pi \in \mathscr{L}(\text{reg}(\varphi))$ and 
- \\$\pi \vDash \psi$ iff $\pi \in \mathscr{L}(\text{reg}(\psi))$, so
- $$\pi \vDash \varphi \lor \psi \text{ iff } \pi \in (\mathscr{L}(\text{reg}(\varphi)) \lor \mathscr{L}(\text{reg}(\psi))) = \mathscr{L}(\text{reg}(\varphi \lor \psi)).$$
- \noindent \textbf{reg($\mathcal{F}_{[a,b]} \varphi$)}\\
- We know that $\pi \vDash \mathcal{F}_{[a,b]} \varphi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \varphi$.\\
- If $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, $|\pi| > a$.
-Likewise, $\pi \in \mathscr{L}\left(\text{reg}\left(\mathcal{F}_{[a,b]} \varphi \right)\right)$ implies $|\pi| = \text{cplen}(\mathcal{F}_{[a,b]} \varphi)$, so the length condition is satisfied.\\
- By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for some $i \in [a,b]$. Equivalently, 
- $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
- \noindent \textbf{reg($\mathcal{G}_{[a,b]} \varphi$)}\\
- We know that $\pi \vDash \mathcal{G}_{[a,b]}\varphi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \varphi$.\\
- Since $|\pi| = \text{cplen}(\mathcal{G}_{[a,b]} \varphi)$ and $\text{cplen}(\mathcal{G}_{[a,b]} \varphi) > a$, the first option for satisfying the formula never occurs.\\
- By the inductive hypothesis, $\pi_i \vDash \varphi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\varphi))$, so $\pi \in \mathscr{L}((S^n,)^i \text{reg}(\varphi))$ for all $i \in [a,b]$. Equivalently, 
- $$\pi \in \mathscr{L}\left(\bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)(,S^n)^{b-i}\right) = \mathscr{L}(\text{reg}(\mathcal{F}_{[a,b]}\varphi)).$$
- \noindent \textbf{reg($\varphi \ \mathcal{U}_{[a,b]} \psi$)}\\
-  We have that 
-  $$\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } (\pi_i \vDash \psi \text{ and } \forall a \leq j < i, \pi_j \vDash \varphi).$$
-  As argued in the Finally case, the length condition is satisfied.\\
-  By the inductive hypothesis, $\pi_i \vDash \psi$ iff $\pi_i \in \mathscr{L}(\text{reg}(\psi))$, or equivalently, \\
-  $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[i,i]} \psi))$. Also, $\pi_j \vDash \varphi$ if and only if $\pi_j \in \mathscr{L}(\text{reg}(\varphi))$.\\
-  By the argument used in the Global case, we see that $\forall a \leq j < i, \ \pi_j \vDash \varphi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a, i-1]} \varphi))$.\\
-  Thus $\pi \vDash \varphi \ \mathcal{U}_{[a,b]} \psi$ iff $\pi \in \mathscr{L}((\text{reg}(\mathcal{G}_{[i,i]} \psi) \land \text{reg}( \mathcal{G}_{[a, i-1]} \varphi)))$ for some $i \in [a,b]$, or equivalently,
-  $$\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\right) = \mathscr{L}\left(\text{reg}(\varphi \ \mathcal{U}_{[a,b]} \psi)\right).$$
-  \noindent \textbf{reg($\varphi \mathcal{R}_{[a,b]} \psi$)}\\
-  We have that
-  \begin{align*}
-    &\pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \psi \text{ or } \\ 
-    &\exists j\in[a,b] \text{ such that }
-    (\pi_j \vDash \varphi \text{ and } \forall a\leq k \leq j, \pi_k \vDash \psi).
-  \end{align*}
-  As argued in the Global case, the first option for satisfying the formula never occurs.\\
-  By the Global case, the statement $\forall i\in[a,b] \ \pi_i \vDash \psi$ is equivalent to $\pi \in \mathscr{L}(\text{reg}(\mathcal{G}_{[a,b]} \psi))$ and, by the Finally case.
-the statement $\exists j\in[a,b]$ such that ($\pi_j \vDash \varphi$ and $\forall a\leq k \leq j$, $\pi_k \vDash \psi$) is equivalent to $\pi \in \mathscr{L}\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)$.
-Hence
-  \begin{align*}
-    \pi \vDash \varphi \mathcal{R}_{[a,b]} \psi \text{ iff } \pi &\in \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right) \\
-    &= \mathscr{L}\left(\text{reg}(\mathcal{G}_{[a,b]} \psi) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)\right)\\
-    &= \mathscr{L}\left(\text{reg}(\varphi \mathcal{R}_{[a,b]} \psi)\right).
-  \end{align*}
- \noindent This completes the inductive step, and thus the proof. Since this proof addresses all possible MLTL formulas in negation normal form, it shows completeness along with soundness.
- \end{proof}
-% \newpage
-
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Nested Until and Release Rewriting Theorem} \label{Appendix-NestedUR}
-\begingroup
-\renewcommand\thetheorem{3}
- \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}] \label{NestedUR}
-   Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas.
-Let $\mathcal{B} = \mathcal{R} \text{ or } \mathcal{U}$.
-Let $a,b,c \in \mathbb{Z}_{\geq 0} , a \leq b,$ \text{and} $ \phi,   \psi$ \text{be well-formed MLTL formulas in NNF.
-Then,} $ \phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
-That is, $ \phi \ \mathcal{U}_{[a,b+c]} \psi \equiv \phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi)$ and $ \phi \ \mathcal{R}_{[a,b+c]} \psi \equiv \phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi)$.
-\end{theorem}
-\endgroup
-The proof of Theorem \ref{NestedUR} appears below.
-\begin{proof}
-\textbf{Case 1: $\mathbf{\mathcal{B} = \mathcal{U}}$}\\
-\noindent Let $\gamma = \phi \ \mathcal{U}_{[0,c]} \psi$.
-Then,  $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) = \phi \ \mathcal{U}_{[a,b]}\gamma$ and\\ $\text{reg}\left(\gamma\right) = \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi \land \mathcal{G}_{[j, j]}\psi\right).$ Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \mathcal{G}_{[i, i]}\left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right).
-\end{align*}
-$\mathcal{G}_{[i, i]}$ distributes over $\land$ and $\lor$, so
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land  \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\left( \text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[j, j]}\psi\right) \right) \right) \\
-&= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \mathcal{G}_{[i, i]}\text{reg}\left(\mathcal{G}_{[0,j-1]}\phi\right) \land \mathcal{G}_{[i, i]}\text{reg}\left(
-\mathcal{G}_{[j, j]}\psi \right) \right) \right).
-\end{align*}
-Since $\mathcal{G}_{[t_1,t_1]} \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1+t_2,t_1+t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \left( \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right) \right) \right) \\
-&= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi\right) \land  \text{reg}\left(\mathcal{G}_{[i,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi \right).
-\end{align*}
-Since $\mathcal{G}_{[t_1,t_2-1]}\phi \land \mathcal{G}_{[t_2,t_3]} \phi \equiv \mathcal{G}_{[t_1,t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{i=a}^{b}  \bigvee_{j=0}^{c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right)\\
-&= \bigvee_{i+j=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,i+j-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[i+j, i+j]}\psi  \right).
-\end{align*}
-Finally, let $k = i + j$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{U}_{[a,b]}\gamma\right) &= \bigvee_{k=a}^{b+c} \text{reg}\left(\mathcal{G}_{[a,k-1]}\phi\right) \land \text{reg}\left(\mathcal{G}_{[k, k]}\psi  \right) \\
-&= \text{reg}\left(\phi \ \mathcal{U}_{[a,b+c]} \psi\right).
-\end{align*}
-This shows that $\phi \ \mathcal{U}_{[a,b]}(\phi \ \mathcal{U}_{[0,c]} \psi) \equiv \phi \ \mathcal{U}_{[a,b+c]} \psi$.\\
-\noindent \textbf{Case 2: $\mathbf{\mathcal{B} = \mathcal{R}}$} \\
-We begin by rewriting the regex for Release in an equivalent form to better mirror the structure of the Until case. The Release operator is the dual of the Until operator. Thus,
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \text{reg}\left(\neg\left(\neg\phi \ \mathcal{U}_{[a,b]}\neg\psi\right)\right) \\
-&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\neg\phi \land \mathcal{G}_{[i, i]}\neg\psi\right)\right).
-\end{align*}
-Global is the dual of Finally, so
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\psi\right) &= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\mathcal{F}_{[a,i-1]}\phi \land \neg\mathcal{F}_{[i, i]}\psi\right)\right)\\
-&= \neg\left(\bigvee_{i=a}^{b} \text{reg}\left(\neg\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\right)\\
-&= \neg\neg\left(\bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right)\right)\\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\psi\right).
-\end{align*}
-This completes the rewriting of the regex for Release.
-Now let $\gamma = \phi \ \mathcal{R}_{[0,c]} \psi$.
-Then $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) = \phi \ \mathcal{R}_{[a,b]}\gamma$ and
-$\text{reg}\left(\gamma\right) = \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi \lor \mathcal{F}_{[j, j]}\psi\right)$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \mathcal{F}_{[i, i]}\text{reg}\left(\gamma\right)\right)\\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \mathcal{F}_{[i, i]}\left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right).
-\end{align*}
-$\mathcal{F}_{[i, i]} \equiv \mathcal{G}_{[i, i]}$, so this operation distributes over $\land$ and $\lor$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor  \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\left( \text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[j, j]}\psi\right) \right) \right) \\
-&= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[0,j-1]}\phi\right) \lor \mathcal{F}_{[i, i]}\text{reg}\left(\mathcal{F}_{[j, j]}\psi \right) \right) \right).
-\end{align*}
-Since $\mathcal{F}_{[t_1,t_1]}\mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1+t_2,t_1+t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi \lor \left( \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right) \right) \right) \\
-&= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i-1]}\phi\right) \lor  \text{reg}\left(\mathcal{F}_{[i,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi \right).
-\end{align*}
-Since $\mathcal{F}_{[t_1,t_2-1]} \phi \land \mathcal{F}_{[t_2,t_3]} \phi \equiv \mathcal{F}_{[t_1, t_3]} \phi$, we have
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{i=a}^{b}  \bigwedge_{j=0}^{c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right) \\
-&= \bigwedge_{i+j=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,i+j-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[i+j, i+j]}\psi  \right).
-\end{align*}
-Let $k = i + j$. Thus
-\begin{align*}
-\text{reg}\left(\phi \ \mathcal{R}_{[a,b]}\gamma\right) &= \bigwedge_{k=a}^{b+c} \text{reg}\left(\mathcal{F}_{[a,k-1]}\phi\right) \lor \text{reg}\left(\mathcal{F}_{[k, k]}\psi  \right) \\
-&= \text{reg}\left(\phi \ \mathcal{R}_{[a,b+c]} \psi\right).
-\end{align*}
-Thus  $\phi \ \mathcal{R}_{[a,b]}(\phi \ \mathcal{R}_{[0,c]} \psi) \equiv \phi \ \mathcal{R}_{[a,b+c]} \psi$, so $\phi \ \mathcal{B}_{[a,b+c]} \psi \equiv \phi \ \mathcal{B}_{[a,b]}(\phi \ \mathcal{B}_{[0,c]} \psi)$.
-This completes the proof.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
- \section{Until and Release Duality Lemma} \label{duality appendix}
- \begin{lemma}[\emph{Until and Release Duality}]\label{dual_proof}
- The definition of Release is equivalent to the dual of Until: 
- $\phi \mathcal{R} \psi \equiv \neg (\neg \phi \mathcal{U} \neg \psi)$. That is to say,
-$\phi \mathcal{R}_{[a,b]} \psi$ if and only if $|\pi| \le a \text{ or } \forall s \in [a,b] ,(\pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] , \pi_t \vDash \phi)$.
- \end{lemma}
-\begin{proof} $ $\newline
-($\Rightarrow$):\\
-\indent Suppose $\pi \vDash \phi \mathcal{R}_{[a,b]} \psi$, so:
-\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \psi \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \pi_k \vDash \psi \text{)} \]
-We proceed by cases to show that:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)} \tag{A1}
-\]
-\indent Case 0: If $|\pi| \leq a$, then we are immediately done.
-\indent Case 1: Suppose $\forall i \in [a,b] \text{, } \pi_i \vDash \psi$.\\
-\indent Through re-labeling, we have $\forall s \in [a,b] \text{, } \pi_s \vDash \psi$. Then we clearly have:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)} \tag{A1}
-\]
-\indent Case 2: Suppose $\exists i \in [a,b] \text{, } \pi_i \cancel{\vDash} \psi$.\\
-\indent \indent Then we must have that:
-\[ \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{1} \]
-\indent \indent We want to show that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)}$.\\
-\\
-\indent \indent Suppose by contradiction that: 
-\[ \exists s \in [a,b] \text{, (} \forall t \in [a, s-1] \text{, } \pi_t \cancel{\vDash} \phi \text{)} \tag{2} \]
-\indent \indent Since $s \in [a,b] \text{ and }  t \in [a, s-1]$, we have that $t \in [a,b-1]$.\\
-\indent \indent Since $j \in [a,b-1]$ (from Line 1), we have that $\pi_j \cancel{\vDash} \phi$ from Line 2.\\
-\indent \indent However from Line 1 we have that $\pi_j \vDash \phi$ and have thus derived a contradiction.\\
-\indent \indent Thus, we now have that $ \forall s \in [a,b] \text{, (} \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)}$.\\ \indent \indent From this, we clearly have that:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{)} \tag{A1}
-\]
-$ $ \newline
-\indent Since these $3$ cases exhaustively capture all cases fo the assumption, the ($\Rightarrow$) direction is proved.
-$ $ \newline
-\noindent ($\Leftarrow$):\\
-\indent Suppose that $\pi \vDash \neg (\neg \phi \mathcal{U} \neg \psi)$:
-\[
-|\pi| \le a \text{ or } \forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{ or } \exists t \in [a, s-1] \text{, } \pi_t \vDash \phi \text{) \tag{1}}
-\]
-$ $ \newline
-\indent We want to show $\pi \vDash \phi R_{[a,b]} \psi$, that is:
-\[ |\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \psi \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{B1} \]
-\indent Case 0: If $|\pi| \leq a$, again we are immediately done. \\
-\indent Case 1: Suppose $\forall s \in [a,b] \text{, (} \pi_s \vDash \psi \text{)}$.\\ 
-\indent \indent Relabeling $s$ to $i$, we now have that $\forall i \in [a, b] \text{, (}\pi_s \vDash \psi \text{)}$, which implies line B1. \\
-\indent Case 2: Suppose $\exists s \in [a,b], \pi_s \cancel{\vDash} \psi$.\\
-\indent \indent By re-labeling $s$ to $i$, we have that $\exists i \in [a,b], \pi_i \cancel{\vDash} \psi$.\\
-\indent \indent Since $[a,b]$ is a finite-discrete interval, there must exist a first $i_1$ s.t. $\pi_{i_1} \cancel{\vDash} \psi$, that is:
-\[ 
-\exists i_1 \in [a,b]\text{, (}  \pi_{i_1} \cancel{\vDash} \psi  \text{ and }  \forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \psi \text{)}
-\tag{2}\]
-\indent \indent Since (line 2) $\exists i_1 \in [a,b], \pi_{i_1} \cancel{\vDash} \psi$, by Line 1 we have that: $\pi_{i_1} \vDash \psi \text{ or } \exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \phi$.\\
-\indent \indent Thus, we have that: 
-\[
-\exists t \in [a, i_1 - 1] \text{, } \pi_t \vDash \phi \tag{3}
-\]
-\indent \indent Since  $[a, t] \subseteq [a, i_1 - 1]$ and $\forall k \in [a, i_1 - 1] \text{, } \pi_{k} \vDash \psi$, we have that:
-\[ 
-\forall k \in [a, t]\text{, } \pi_{k} \vDash \psi \tag{4}
-\]
-\indent \indent Since $[a,t] \subseteq [a, i_1 - 1] \subseteq [a,b-1]$, we have that $t \in [a,b-1]$, so let $j := t$.
-\indent \indent Then from lines 3 and 4, we have that:
-\[
-\exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{5}
-\]
-\indent \indent From line 5, we now get:
-\[ 
-|\pi| \leq a \text{ or } \forall i \in [a,b] \text{, (} \pi_i \vDash \psi \text{) or } \exists j \in [a,b-1] \text{, (} \pi_j \vDash \phi \text{ and } \forall k \in [a, j] \ \pi_k \vDash \psi \text{)} \tag{B1}
-\]
-\indent Again the 3 cases are exhaustive of all cases in the assumption, this we have the ($\Leftarrow$) direction.\\
-This finishes the proof.
-\end{proof}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Regular Expression Simplification Theorem} \label{simp_appendix}
-\begin{proof}[Theorem \ref{simp}]
-Assume no row is the arbitrary computation, because then the union of the set of regular expressions would trivially simplify to the arbitrary computation.\\
-We begin by showing that there must be at least one row in the matrix $M$ that is composed of one fixed truth value and $n-1$ `$S$'s.
-This will be of use later in the proof.
-Because there are $n$ columns and $2$ fixed truth values in each column, there are $2n$ fixed truth values.
-There are $n+1$ rows, so the average number of fixed truth values per row is strictly less than $2$ since $\frac{2n}{n+1} < \ 2$.
-Thus, there must exist at least one row composed of one fixed truth value and $n-1$ `$S$'s. \\
-\noindent We now proceed by induction on the length of computations, $n$. \\
-\textbf{Base Cases:} $n=1$ and $n=2$. \\
-The $n=1$ case holds by definition:
-    $$\begin{bmatrix}
-    1\\
-    0
-    \end{bmatrix}  \equiv S.$$
-For $n=2$, we can manually verify that each possible matrix indeed satisfies the theorem. Note that because the union of regular expressions is commutative, any permutation of rows is equivalent:
-        $$\begin{bmatrix}
-    1 & S\\
-    S & 1\\
-    0 & 0
-    \end{bmatrix}  \equiv \begin{bmatrix}
-    0 & S\\
-    S & 0\\
-    1 & 1
-    \end{bmatrix} \equiv \begin{bmatrix}
-    1 & S\\
-    S & 0\\
-    0 & 1
-    \end{bmatrix} \equiv \begin{bmatrix}
-    0 & S\\
-    S & 1\\
-    1 & 0
-    \end{bmatrix} \equiv SS.
-        $$
-\noindent \textbf{Inductive Hypothesis:}\\
-Let $n\geq 2$.
-Assume that a matrix of regular expressions, $H$, with the following characteristics is equivalent to the arbitrary computation of length $n-1$: $n$ rows, $n-1$ columns, one `$1$' per column, one `$0$' per column, and $n-2$ `$S$'s per column.\\
-\noindent \textbf{Inductive Step:}\\
-Consider a matrix of regular expressions, $J$, with the following characteristics: $n+1$ rows, $n$ columns, one `$1$' per column, one `$0$' per column, and $n-1$ `$S$'s per column.
-We show $J$ is equivalent to the arbitrary computation of length $n$.\\
-As aforementioned, there must exist at least one row composed of one fixed truth value and $n-1$ `$S$'s, and the union of regular expressions is commutative.
-Thus, WLOG, let the first row of $J$, $r_1$, be a row with one known truth value.
-Suppose this known truth value is in column $k$, $c_k$, where $1 \leq k \leq n$.. Assume WLOG that this value is a 0. Matrix $J$ can be represented as follows:
-\[
-J = \begin{blockarray}{cccccccc}
-\mathbf{c_1} & & \mathbf{c_{k-1}} & \mathbf{c_k} & \mathbf{c_{k+1}} & & \mathbf{c_n} \\
-\begin{block}{(ccccccc)c}
-    S & \hdots & S & 0 & S & \hdots & S & \mathbf{r_1}\\
-     &  &  & S &  &  &  & \mathbf{r_2}\\
-    &  &  & \vdots &  &  &  & \\
-    &  & & S &  &  &  & \\
-    & \vdots &  & 1 &  & \vdots &  & \\
-    & &  & S &  & &  & \\
-    &  &  & \vdots & &  &  & \\
-    &  & & S & &  & & \mathbf{r_{n+1}}\\
-\end{block}
-\end{blockarray}
- \]
-The first row of $J$ represents half of the regular expressions contained in the arbitrary computation.
-The other half would be represented by a regular expression of all `S's, except for a `1' at the $k^{th}$ position.
-Thus, if the rest of $J$, rows $r_2$ through $r_{n+1}$, represents the other half of the arbitrary computation, then the matrix - the union of the set of the regular expressions - represents the arbitrary computation of length $n$.
-We show that this is indeed the case:
-Because the first row represents all the computations with `0' at the $k^{th}$ position, every `$S$' in $c_k$ can be replaced with a `1', to avoid redundancy; the case for which each `$S_k$' is `0' is a subset of $r_1$.
-Thus, matrix $J$ can be represented as follows:
-\[
-J = \begin{blockarray}{cccccccc}
-\mathbf{c_1} & & \mathbf{c_{k-1}} & \mathbf{c_k} & \mathbf{c_{k+1}} & & \mathbf{c_n} \\
-\begin{block}{(ccccccc)c}
-    S & \hdots & S & 0 & S & \hdots & S & \mathbf{r_1}\\
-     &  &  & 1 &  &  &  & \mathbf{r_2}\\
-    &  \vdots &  & \vdots &  &  \vdots &  & \\
-    &  &  &  &  & &  & \\
-    & & & 1 & &  & & \mathbf{r_{n+1}}\\
-\end{block}
-\end{blockarray}
- \]
-The problem reduces to showing that $J - r_1$, that is, $J$ with the row $r_1$ removed, represents the other half of the arbitrary computation. Thus, let $J' = J - r_1$:
-\[
-J' = \begin{blockarray}{cccccc}
-\mathbf{c_1} &  & \mathbf{c_k} & & \mathbf{c_n} \\
-\begin{block}{(ccccc)c}
-     &   & 1 &   &  & \mathbf{r_2}\\
-     \vdots & &  \vdots & & \vdots  & \\
-    &   &   & &  & \\
-    & & 1 &  & & \mathbf{r_{n+1}}\\
-\end{block}
-\end{blockarray}
- \]
-Again, we want to show that $J'$ represents the other half of the arbitrary computation.
-Recall that we specify this to be the union of regular expressions of all $`S'$s except for a $`1'$ at the $k^{th}$ position.
-Because each row indeed contains a $`1'$ at the $k^{th}$ position, the problem reduces to showing that $r_2 - c_k$ through $r_{n+1} - c_k$ represents the arbitrary computation, where $r_j - c_k$ is the row $r_j$ with the $k^{th}$ entry removed.
-Thus, we remove $c_k$ from $J'$ and call this new matrix $J''$:
-\[
- J'' = \begin{pmatrix}
-    r_2 - c_k \\
-    . \\
-    . \\
-    . \\
-    r_{n+1} - c_k \\
-
-  \end{pmatrix}
-\]
-Because $J''$ is the result removing one row and one column from $J$, $J''$ has $n$ rows and $n-1$ columns.
-In each column of $J''$, there remains one `$1$' and one `$0$'.
-Also, there are now $n-2$ `$S$'s in each column, because $r_1$ was removed.
-Thus, $J''$ is equivalent to $H$, and is therefore equivalent to the arbitrary computation by the inductive hypothesis.
-Because $r_1$ is equivalent to half of the arbitrary computation and $J'$ is equivalent to the other half of the arbitrary computation, $J$ is equivalent to the arbitrary computation, as the union of $r_1$ and $J'$ is equivalent to $J$.
-Therefore, by induction, the theorem holds.
-\end{proof}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pseudocode for the WEST Algorithm Functions} \label{pseudocode_appendix}
-To compute the satisfying computations of an MLTL formula, many of the functions in the WEST program require the regular expressions of the satisfying computations of the subformulas as inputs.
-We denote these regexes by $R$ and $T$.
-Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.
-\begin{algorithm}[H]
-\caption{Pad a set to elements of all equal length}
-Input: set of strings that represents a regex, number of propositional variables \\
-Output: set of strings padded to equal length
-\begin{algorithmic}
-\Procedure{Pad}{set $R$, int $n$} 
-    \State max\_Length $\leftarrow$ $\max_{\{r \in R\}}$($r$.length())
-    \For{($r \in R$)}
-        \State diff $\leftarrow$ (max\_length$- r$.length()) / $(n+1)$ 
-        \State  $r \leftarrow r + (,S^n)^{\text{diff}}$
-    \EndFor
-    \State return $R$
-
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Computes regex for propositional constant}
-Input: String that is either ``T" or ``!", number of propositional variables\\
-Output: set of strings that represents the appropriate satisfying computations
-\begin{algorithmic}
-\Procedure{reg\_prop\_cons}{string nnf, int $n$}
-    \If {(nnf $=$ ``T" and $n \neq 0$)} return $\{S^n\}$
-    \Else \hspace{1mm} return $\{\}$ 
-    \EndIf
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Output the set of computation satisfying a propositional variable.}
-Input: String that represents a propositional variable or the negation of one, number of propositional variables \\
-Output: set of strings that represents the appropriate satisfying computations
-\begin{algorithmic}
-\Procedure{reg\_prop\_var}{string nnf, int $n$}
-    \If {(nnf $=$ ``p$k$", where $k$ is a nonnegative integer)} return $\{S^k1S^{n-k-1}\}$
-    \EndIf 
-    \If {(nnf $=$ ``$\scriptstyle{\sim}$p$k$", where $k$ is a nonnegative integer)} return $\{S^k0S^{n-k-1}\}$
-    \EndIf
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Combines two strings that differ only by one character into one}
-Input: Two strings that represent regexes\\
-Output: Single string that represents computations represented by both input strings or FAIL
-\begin{algorithmic}
-\Procedure{simplify\_string}{string $r$, string $t$}   
-    \If{($r$.length() $\neq$ $t$.length())} exit
-        \EndIf
-    \For{($0 \leq i < r$.length())}
-        \State pre\_r $\leftarrow r[0, i-1]$ 
-        \State char\_r $\leftarrow r[i]$ 
-        \State post\_r $\leftarrow r[i+1, r\text{.length()}-1]$ 
-        \State pre\_t $\leftarrow t[0, i-1]$ 
-        \State char\_t $\leftarrow t[i]$ 
-        \State post\_t $\leftarrow t[i+1, t\text{.length()}-1]$
-        \If{(pre\_r $=$ pre\_t and post\_r $=$ post\_t)}
-            \If{(char\_r $\neq$ char\_t)}
-                \State return pre\_r +``$S$" + post\_r 
-            \Else
-                \State return $r$
-            \EndIf
-        \EndIf
-    \EndFor
-    \State return FAIL 
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[H]
-\caption{Simplifies a set of strings using simplify\_string}
-Input: set of strings representing a regex\\
-Output: set of strings representing a regex simplified using simplify\_string
-\begin{algorithmic}
-\Procedure{simplify}{set $R$}    
-    \State Pad all strings in $R$ to the same length
-    \If{($R$.length() $\leq 1$)} return $R$
-        \EndIf
-    \State $i = R\text{.length} - 1$
-    \State $j = i - 1$
-
-    \State START
-    \While{($i \geq 1$)}
-        \While{($j \geq 0$)}
-            \State simplified = simplify\_string($R[i]$, $R[j]$) 
-            \If{(simplified $\neq$ FAIL)}
-                \State replace string at index $j$ with simplified
-                \State remove string at index $i$ from $R$
-                \State $i = R\text{.length()} - 1$
-                \State $j = i - 1$
-                \State goto START
-                \EndIf
-            \State -{}-$j$
-            \EndWhile
-        \State -{}-$i$
-        \State $j = i - 1$
-        \EndWhile
-
-    \State return $R$
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Takes the intersection of two computations}
-Input: Two strings representing regexes\\
-Output: Bitwise AND of the inputted strings
-\begin{algorithmic}
-\Procedure{bit\_wise\_and}{string $r$, string $t$}
-    \State ret $\leftarrow$ ``" 
-    \For {(i $\in [0, \ r\text{.length()}]$)}
-        \If{($r[i] \land$ $t[i] = ``"$)} return ``"
-        \Else \hspace{1mm} ret $\leftarrow$ ret $+$ $r[i] \land t[i]$
-        \EndIf
-    \EndFor
-    \State return ret
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[H]
-\caption{Takes union of two regexes (combines two sets into one)}
-Input: sets of strings that represent regexes, simplify boolean\\
-Output: set of strings that represents union of inputted regexes
-\begin{algorithmic}
-\Procedure{join}{set $R$, set $T$, bool simp}
-    \State ret $\leftarrow \{\}$
-    \For{($r \in R$)} add $r$ to ret
-    \EndFor
-    \For{($t \in T$)} add $t$ to ret
-    \EndFor
-    \If{(simp is true)} return simplify(ret)
-    \Else \hspace{1mm}return ret
-    \EndIf
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
-Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: set of strings that represents the appropriate satisfying computations 
-\begin{algorithmic}
-\Procedure{reg\_F}{set $r_\phi$, int $a$, int $b$, int $n$, bool simp} 
-    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
-    \State comp $\leftarrow$ $r_\phi$
-    \If{$a > b$} return $\{\}$
-    \EndIf
-    \For{($1 \leq i \leq b-a$) }
-        \State temp$_\phi$ $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + $r_\phi$
-        \State comp $\leftarrow$ join(comp, temp$_\phi$, simp)
-    \EndFor
-    \State return pre + comp
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula G[a:b]$\phi$}
-Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: set of strings that represents the appropriate satisfying computations
-\begin{algorithmic}
-\Procedure{reg\_G}{set $r_\phi$, int $a$, int $b$, int $n$, bool simp} 
-    \State pre $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a}$
-    \State comp $\leftarrow$ $r_\phi$ 
-    \If{$a > b$} return $\{S^n\}$
-    \EndIf
-    \For{($1 \leq i \leq b-a$)}
-        \State temp$_\phi$ $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{i}$ + $r_\phi$
-        \State comp $\leftarrow$ set\_intersect(comp, temp$_\phi$, simp)
-    \EndFor
-    \State return pre + comp
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
-Inputs: sets of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
-Output: set of strings that represents the appropriate satisfying computations 
-\begin{algorithmic}
-\Procedure{reg\_R}{set $r_\phi$, set $r_\psi$, int $a$, int $b$, int $n$, bool simp} 
-    \State comp $\leftarrow$ reg\_G($r_\psi$, $a$, $b$, $n$, simp)
-    \If{$a > b$} return $\{S^n\}$
-    \EndIf
-    \For{($a \leq i \leq b-1$) }
-        \State temp\_comp $\leftarrow$ set\_intersect(reg\_G($r_\psi$, $a$, $i$, $n$), reg\_G($r_\phi$, $i$, $i$, $n$), $n$, simp)
-        \State comp $\leftarrow$ join(comp, temp\_comp, simp)
-    \EndFor
-    \State return comp
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\begin{algorithm}[H]
-    \caption{Generates test suite template without propositional constants, propositional variables, or negations of propositional variables filled in}
-    Inputs: Depth of desired test suite template to generate, interval bounds\\
-    Output: set of MLTL formulas (without propositional constants, propositional variables, or negations of propositional variables)
-    \begin{algorithmic}
-        \Procedure{generate\_test\_template}{int depth, int $a$, int $b$}
-        \If{(depth = 0)} return $\{p, q\}$
-        \EndIf
-        \State template $\leftarrow \{\}$
-        \State $V \leftarrow$ generate\_test\_template(depth$- 1$, $a$, $b$)
-        \For{(string $\phi \in V$)}
-            \State add ``G[a:b]" + $\phi$ to template
-            \State add ``F[a:b]" + $\phi$ to template
-            \For{string $\psi \in V$}
-                \State add $\phi$ + ``U[a:b]" + $\psi$ to template
-                \State add  $\phi$ + ``R[a:b]" + $\psi$ to template
-                \State add $\phi$ + ``$\lor$" + $\psi$ to template
-                \State add $\phi$ + ``\&" + $\psi$ to template
-            \EndFor
-        \EndFor
-        \State return template
-    \EndProcedure
-    \end{algorithmic}
-
-\end{algorithm}
-\begin{algorithm}[H]
-    \caption{Generates a complete test suite of MLTL formulas in negation normal form up to a certain depth}
-    Inputs: Depth of desired test suite template to generate, interval bounds, number of propositional variables\\
-    Output: set of MLTL formulas
-    \begin{algorithmic}
-        \Procedure{generate\_test}{int depth, int $a$, int $b$, int $n$}
-        \State tests $\leftarrow$ generate\_test\_template(depth, $a$, $b$) 
-        \For{string $t \in $ tests}
-            \For{char ch $\in t$}
-                \If{ch $ = p$}
-                    \State $k \leftarrow \text{rand()} \% n$ 
-                    \If{rand() $\% 2 = 0$} replace ch with p$k$
-                    \Else \hspace{1mm}replace ch with $\scriptstyle{\sim}$p$k$
-                    \EndIf
-                \ElsIf{ch $= q$}
-                    \If{rand() $\% 2 = 0$} replace ch with T
-                    \Else \hspace{1mm}replace ch with $!$
-                    \EndIf
-                \EndIf
-            \EndFor
-        \EndFor
-    \State return tests
-    \EndProcedure
-    \end{algorithmic}
-\end{algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{State Diagram Graphs} \label{graphs_appendix}
-Below we provide the state diagram graphs of the functions examined in our intelligent fuzzing.
-Nodes in the graph represent portions of the code without control flow statements, so a single node can represent large chunks of code.
-Directed edges represent branching of control flow, such as IF statements and loops.
-Each graph directly corresponds with the pseudocode of their corresponding function, with nodes and edges being labeled accordingly.
-Note that the option to run \texttt{simplify} has been omitted for clarity.\\
-
-\begin{minipage}{0.4\textwidth}
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
-    \resizebox{7cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){set R, \# of propositional variables n};
+    \node[emptynode](inputs){vector R, \# of propositional variables n};
     \node[node](length)[below=of inputs]{Run max\_length on R};
-    \node[node](body)[below=of length]{pad r, update R};
-    \node[emptynode](empty_set)[rotate=-70, left=1cm of body]{R $=\{\}$};
-    \node[emptynode](for_loop)[right=1.1cm of body]{for r in R};
+    \node[node](body)[below=of length]{pad w, update R};
+    \node[emptynode](empty_vector)[rotate=-70, left=1cm of body]{R $=\{\}$};
+    \node[emptynode](for_loop)[right=.75cm of body]{for w in R};
     \node[node](return)[below=of body]{return R};
@@
     \end{tikzpicture}
-    }
+
     \caption{Pad Function}
-    \label{fig:pad_graph}
+    \label{fig:pad graph}
 \end{figure}
-\end{minipage}
-\begin{minipage}{0.5\textwidth}
-\begin{figure}[H]
+
+\begin{figure}[h]
     \centering
-    \resizebox{8.5cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){strings r, t};
+    \node[emptynode](inputs){strings w1, w2};
     \node[node](initialize)[below=of inputs]{Initialize string Ret};
@@
     \node[emptynode](placeholder)[below=0.05cm of loop_entry]{};
-    \node[emptynode](emptytext)[rotate=35, left=.75cm of placeholder]{\small{r$[i] \land$ t$[i] = ``"$}};
+    \node[emptynode](emptytext)[rotate=35, left=.75cm of placeholder]{\small{w1$[i] \land$ w2$[i] = ``"$}};
     \node[emptynode](placeholder2)[below=0.05cm of placeholder]{};
     \node[emptynode](else)[rotate=-23, right=1.9cm of placeholder2]{else};
-    \node[emptynode](updatetext)[right=3cm of loop_entry]{for $0 \leq i \leq$ r.length};
+    \node[emptynode](updatetext)[right=3cm of loop_entry]{for $0 \leq i \leq$ w1.length};
 
@@
     \end{tikzpicture}
-    }
     \caption{Bitwise\_And Function}
-    \label{fig:bitwise_and_graph}
+    \label{fig:bitwise_and graph}
 \end{figure}
-\end{minipage}
 
-\begin{minipage}{0.5\textwidth}
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
-    \resizebox{8cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){sets R, T};
-    \node[node](initialize)[below=of inputs]{Initialize set Ret};
-    \node[node](add_r)[below=of initialize]{Add r to Ret};
-    \node[node](add_t)[below=of add_r]{Add t to Ret};
+    \node[emptynode](inputs){vectors R, T};
+    \node[node](initialize)[below=of inputs]{Initialize vector Ret};
+    \node[node](add_r)[below=of initialize]{Add w to Ret};
+    \node[node](add_t)[below=of add_r]{Add v to Ret};
     \node[node](return)[below=of add_t]{return Ret};
-    \node[emptynode](rtext)[right=1.2cm of add_r]{for string r$\in$R};
-    \node[emptynode](ttext)[left=1.2cm of add_t]{for string t$\in$T};
+    \node[emptynode](rtext)[right=of add_r]{for string w$\in$R};
+    \node[emptynode](ttext)[left=of add_t]{for string v$\in$T};
 
@@
     \end{tikzpicture}
-    }
     \caption{Join Function}
-    \label{fig:join_graph}
+    \label{fig:join graph}
 \end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}{0.5\textwidth}
-\begin{figure}[H]
+
+\begin{figure}[h]
     \centering
-    \resizebox{8cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){sets R,T};
-    \node[node](initialize)[below=of inputs]{Pad R and T, Initialize set Ret=\{\}};
+    \node[emptynode](inputs){vectors R,T};
+    \node[node](initialize)[below=of inputs]{Pad R and T, Initialize vector Ret=\{\}};
     \node[node](outer_loop)[below=of initialize]{Outer Loop Entry};
@@
     \node[node](return)[below=of outer_exit]{return Ret};
-    \node[emptynode](inner_text)[right=1.25cm of inner_loop]{for t$\in$T};
-    \node[emptynode](outer_text)[left=2.25 cm of inner_loop]{for r$\in$R};
+    \node[emptynode](inner_text)[right=1.25cm of inner_loop]{for w$\in$T};
+    \node[emptynode](outer_text)[left=2.25 cm of inner_loop]{for v$\in$R};
 
@@
     \end{tikzpicture}
-    }
     \caption{Set\_Intersect Function}
-    \label{fig:set_intersect_graph}
+    \label{fig:set_intersect graph}
 \end{figure}
-\end{minipage}
 
-\begin{minipage}{0.4\textwidth}
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
-    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){set $r_\phi$, integers a, b, n};
-    \node[node](initialize)[below=of inputs]{Initialize string pre, set Comp};
+    \node[emptynode](inputs){vector reg\_alpha, integers a, b, n};
+    \node[node](initialize)[below=of inputs]{Initialize string pre, vector Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};
@@
     \node[node](return)[below=of loop]{return pre + Comp};
-    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [1, \text{b}-\text{a}]$};
+    \node[emptynode](loop_text)[right= of loop]{for $i \in [1, \text{b}-\text{a}]$};
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
-    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};
+    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};
 
@@
     \end{tikzpicture}
-    }
+
     \caption{Reg\_F Function}
-    \label{fig:reg_f_graph}
+    \label{fig:reg_f graph}
 \end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}{0.4\textwidth}
-\begin{figure}[H]
+
+\begin{figure}[h]
     \centering
-    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     \end{tikzpicture}
-    }
+
     \caption{Reg\_G Function}
-    \label{fig:reg_g_graph}
+    \label{fig:reg_g graph}
 \end{figure}
-\end{minipage}
-\vfill
-\begin{minipage}{0.4\textwidth}
-\begin{figure}[H]
+
+\begin{figure}[h]
     \centering
-    \resizebox{7.25cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){set $r_\phi$, $r_\psi$ and integers a, b, n};
-    \node[node](initialize)[below=of inputs]{Initialize set Comp};
+    \node[emptynode](inputs){vector reg\_alpha, reg\_beta and integers a, b, n};
+    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};
-    \node[node](empty)[left=of loop]{return \{\}};
+    \node[node](empty)[left=of loop]{return \{$S^n$\}};
     \node[node](return)[below=of loop]{return Comp};
-    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
+    \node[emptynode](loop_text)[right= of loop]{for $i \in [\text{a}, \text{b}-1]$};
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
-    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};
+    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};
 
@@
     \end{tikzpicture}
-    }
-    \caption{Reg\_U Function}
-    \label{fig:reg_u_graph}
+
+    \caption{Reg\_R Function}
+    \label{fig:reg_r graph}
 \end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}{0.4\textwidth}
-\begin{figure}[H]
-    \centering
-    \resizebox{7.25cm}{!}{
+
+\begin{figure}[h]
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none, very thick, minimum size=1mm}]
@@
     %Nodes
-    \node[emptynode](inputs){set $r_\phi$, $r_\psi$ and integers a, b, n};
-    \node[node](initialize)[below=of inputs]{Initialize set Comp};
+    \node[emptynode](inputs){vector reg\_alpha, reg\_beta and integers a, b, n};
+    \node[node](initialize)[below=of inputs]{Initialize vector Comp};
     \node[node](loop)[below=2cm of initialize]{Update Comp};
-    \node[node](empty)[left=of loop]{return \{$S^n$\}};
+    \node[node](empty)[left=of loop]{return \{\}};
     \node[node](return)[below=of loop]{return Comp};
-    \node[emptynode](loop_text)[right=1.1cm of loop]{for $i \in [\text{a}, \text{b}-1]$};
+    \node[emptynode](loop_text)[right= of loop]{for $i \in [\text{a}, \text{b}-1]$};
     \node[emptynode](placeholder)[below=0.5cm of initialize]{};
-    \node[emptynode](empty_text)[rotate=36, left=1.3cm of placeholder]{If a$>$b};
+    \node[emptynode](empty_text)[rotate=30, left=1.3cm of placeholder]{If a$>$b};
 
@@
     \end{tikzpicture}
-    }
-    \caption{Reg\_R Function}
-    \label{fig:reg_r_graph}
+
+    \caption{Reg\_U Function}
+    \label{fig:reg_u graph}
 \end{figure}
-\end{minipage}
 
 \begin{landscape}
-
-\begin{figure}[htbp]
+\begin{figure}[h]
     \centering
-    \resizebox{20cm}{!}{
     \begin{tikzpicture}[node/.style={rounded rectangle, draw=black!60, fill=black!5, text width=3cm,text centered, very thick, minimum size=15mm}, bignode/.style={rounded rectangle, draw=black!60, fill=black!5, very thick, minimum size=20mm}, emptynode/.style={draw=none, fill=none,text width=3cm,text centered, very thick, minimum size=1mm}, rednode/.style={rounded rectangle, draw=red!60, fill=red!5, text width=3cm,text centered, very thick, minimum size=15mm}]
@@
 
-    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, $\phi$ and call reg($\phi$, n)};
-    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F($\phi$)};
-    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G($\phi$)};
+    \node[rednode](parse_unary)[below=1cm of prop_cons]{Parse for unary temp conn, a, b, alpha and call reg(alpha, n)};
+    \node[node](reg_f)[below=1cm of parse_unary]{return reg\_F(alpha)};
+    \node[node](reg_g)[left=0.5cm of reg_f]{return reg\_G(alpha)};
 
-    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, $\phi$, $\psi$};
-    \node[rednode](prop_phi)[below=of parse_binary_prop]{$r_\phi$ $\leftarrow$ reg($\phi$,n)};
-    \node[rednode](prop_psi)[below=of prop_phi]{$r_\psi$ $\leftarrow$ reg($\psi$,n)};
-    \node[rednode](equals)[left=0.5cm of prop_psi]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};
-    \node[node](set_intersect)[below=of prop_psi]{return set\_intersect};
+    \node[node](parse_binary_prop)[below=0.5cm of start]{Parse for binary prop conn, alpha, beta};
+    \node[rednode](prop_alpha)[below=of parse_binary_prop]{reg\_alpha $\leftarrow$ reg(alpha,n)};
+    \node[rednode](prop_beta)[below=of prop_alpha]{reg\_beta $\leftarrow$ reg(beta,n)};
+    \node[rednode](equals)[left=0.5cm of prop_beta]{Rewrite as equiv\_formula, return reg(equiv\_formula,n)};
+    \node[node](set_intersect)[below=of prop_beta]{return set\_intersect};
     \node[node](join)[left=of set_intersect]{return join};
@@
 
-    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, $\phi$, $\psi$};
-    \node[rednode](temp_phi)[below=of parse_binary_temp]{$r_\phi$ $\leftarrow$ reg($\phi$,n)};
-    \node[rednode](temp_psi)[below=of temp_phi]{$r_\psi$ $\leftarrow$ reg($\psi$,n)};
-    \node[node](until)[below=of temp_psi]{return reg\_U};
+    \node[node](parse_binary_temp)[right=3cm of start]{Parse for binary temp conn, a, b, alpha, beta};
+    \node[rednode](temp_alpha)[below=of parse_binary_temp]{reg\_alpha $\leftarrow$ reg(alpha,n)};
+    \node[rednode](temp_beta)[below=of temp_alpha]{reg\_beta $\leftarrow$ reg(beta,n)};
+    \node[node](until)[below=of temp_beta]{return reg\_U};
     \node[node](release)[right=of until]{return reg\_R};
@@
     \node[emptynode](prop_cons_text)[left=0.01cm of start]{nnf is T or !$$~$$};
-    \node[emptynode](prop_var_text)[rotate=-43, above=1.1cm of prop_cons_text]{nnf is p or $\scriptstyle{\sim}\textstyle$p};
+    \node[emptynode](prop_var_text)[rotate=-43, above=1.1cm of prop_cons_text]{nnf is p or $\neg$ p};
 
-    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] $\phi$}};
+    \node[emptynode](unary_text)[rotate=45, below=0.3cm of prop_cons_text]{\small{nnf is X[a,b] alpha}};
     \node[emptynode](reg_g_text)[above=0.2cm of reg_g]{X is G};
@@
 
-    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is $\phi$ X[a,b] $\psi$}$$~$$};
+    \node[emptynode](binary_temp_text)[right=0.01cm of start]{\small{nnf is alpha X[a,b] beta}};
     \node[emptynode](release_text)[above=0.2cm of release]{X is R};
@@
     \node[emptynode](assoc_text)[rotate=45, above=1.1cm of binary_temp_text]{\footnotesize{nnf is X[nnf\_array]}};
-    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for $\phi$ in nnf\_array};
+    \node[emptynode](loop_text)[right=1.75cm of parse_assoc]{$$~$$for alpha in nnf\_array};
 
-    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is $\phi$ X $\psi$};
+    \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is alpha X beta};
     \node[emptynode](join_text)[above=0.2cm of join]{X is v};
     \node[emptynode](intersect_text)[right=1.75cm of join_text]{X is \&};
-    \node[emptynode](implies_text)[right=-0.25cm of prop_psi]{X is $>$};
+    \node[emptynode](implies_text)[right=-0.25cm of prop_beta]{X is $>$};
     \node[emptynode](equals_text)[right=-1.2cm of reg_f_text]{X is =};
@@
     \draw[->] (start.south) -- (parse_binary_prop.north);
-    \draw[->] (parse_binary_prop.south) -- (prop_phi.north);
-    \draw[->] (prop_phi.south) -- (prop_psi.north);
-    \draw[->] (prop_psi.south) -- (set_intersect.north);
-    \draw[->] (prop_psi.south) -- (join.north);
+    \draw[->] (parse_binary_prop.south) -- (prop_alpha.north);
+    \draw[->] (prop_alpha.south) -- (prop_beta.north);
+    \draw[->] (prop_beta.south) -- (set_intersect.north);
+    \draw[->] (prop_beta.south) -- (join.north);
     \draw[->] (parse_binary_prop.east) .. controls +(down:2cm) .. (implies.north);
@@
     \draw[->] (start.east) -- (parse_binary_temp.west);
-    \draw[->] (parse_binary_temp.south) -- (temp_phi.north);
-    \draw[->] (temp_phi.south) -- (temp_psi.north);
-    \draw[->] (temp_psi.south) -- (until.north);
-    \draw[->] (temp_psi.south) -- (release.north);
+    \draw[->] (parse_binary_temp.south) -- (temp_alpha.north);
+    \draw[->] (temp_alpha.south) -- (temp_beta.north);
+    \draw[->] (temp_beta.south) -- (until.north);
+    \draw[->] (temp_beta.south) -- (release.north);
     \draw[->] (start.east) -- (parse_assoc.west);
@@
     \end{tikzpicture}
-    }
-    $$~$$
-    \caption{Control Flow of Reg. Red nodes indicate a recursive call to Reg.}
-    \label{fig:big_boy}
+    \caption{Control Flow}
+    \label{fig:big boy}
 \end{figure}
 \end{landscape}
+
 \end{document}

### 2023-01-19 extras/mltl_in_the_wild.tex
formulas in the wild

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsthm, amsmath, amssymb}
\usepackage[letterpaper,width=150mm,top=20mm,bottom=25mm]{geometry}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{ dsfont }
\usepackage{ mathrsfs }
\usepackage{hyperref}
\usepackage{cancel}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

\newcommand{\FF}{\mathcal{F}}
\newcommand{\GG}{\mathcal{G}}
\newcommand{\UU}{\mathcal{U}}
\newcommand{\RR}{\mathcal{R}}

\begin{document}
From \href{https://link.springer.com/chapter/10.1007/978-3-030-76384-8_10}{Integrating Runtime Verification into a Sounding Rocket Control System}:
\begin{itemize}
    \item $\neg \GG_{[0,2]} \neg p_0$
    \item $p_0 \rightarrow \FF_{[0,140]}p_1$
    \item $p_0 \rightarrow \FF_{[0,800]}p_1$
    \item $(p_0 \land p_1) \rightarrow \FF_{[0,10]}p_2$
    \item $p_0 \rightarrow (p_0 \UU_{[0,130]} p_1)$
    \item $p_0 \rightarrow \FF_{[0,5]} p_1$
    \item $(p_0 \land p_1) \rightarrow \FF_{[0, 126]} p_2$
    \item $p_0 \rightarrow (p_0 \UU_{[0,114]} p_1)$
\end{itemize}
$$$$

From \href{https://link.springer.com/chapter/10.1007/978-3-030-57628-8_12}{Embedding Online Runtime Verification for Fault Disambiguation on Robonaut2}:
\begin{itemize}
    \item $\GG_{[0,3]}p_0$
    \item $(p_0 \land \GG_{[0,3]}p_1) \rightarrow p_2$
\end{itemize}
$$$$

From \href{https://link.springer.com/chapter/10.1007/978-3-031-06773-0_45}{
Runtime verification triggers real-time, autonomous fault recovery on the CySat-I}:
\begin{itemize}
    \item $\GG_{[0,360]}(\neg p_0 \land \neg p_1 \land \neg p_2 \land \neg p_3 \land \neg p_4 \land \neg p_5)$
    \item $\GG_{[360, M]}(p_0 \rightarrow p_1)$ ($M$ is end of mission)
    \item $\GG_{[0, M]}(p_0 = p_1)$
\end{itemize}
$$$$

From \href{https://link.springer.com/chapter/10.1007/978-3-030-59155-7_26}{Integrating Runtime Verification into an Automated UAS Traffic Management System}:
\begin{itemize}
    \item $\neg \GG_{[0,3]} \neg (p_0 \land p_1)$
    \item $\GG_{[0,3]} (p_0 \land p_1)$
    \item $(p_0 \land p_1 \land p_2) \rightarrow \neg \GG_{[0,3]}\neg(p_3 \land p_4)$
    \item $\GG_{[0,3]} \neg(p_0 \land p_1)$
    \item $\GG_{[0, M]} (p_0 \lor p_1 \lor p_2 \lor p_3 \lor p_4 \lor p_5 \lor p_6 \lor p_7 \lor p_8)$ ($M$ is end of mission)
    \item $\GG_{[0, M]}(p_0 \rightarrow (p_1 \land p_2))$
    \item $\GG_{[0,M]}((p_0 \lor p_1) \rightarrow (p_2 \land p_3 \land p_4 \land p_5 \land p_6))$
    \item $p_0 \rightarrow \FF_{[0,M]} p_1$
    \item $p_0 \rightarrow \FF_{[0,M]} (p_1 \land p_2 \land p_3)$
    \item $\FF_{[0,M]} (p_1 \land p_2)$
\end{itemize}
$$$$

From \href{https://link.springer.com/chapter/10.1007/978-3-030-25543-5_1}{
Satisfiability Checking for Mission-Time LTL}:\\
\indent Consider random mLTL formula generation for benchmarking\\

\end{document}

### 2023-06-15 paper/TACASPaper.tex
updated paper

--- 2023-01-19 paper/Paper.tex
@@
 \usepackage{caption}
+\usepackage{subcaption}
 \usepackage{mwe}
+
+% Spacing: left, before, after
+\usepackage{titlesec}
+\titlespacing*{\section}{0pt}{10pt}{2pt}
+\titlespacing*{\subsection}{0pt}{5pt}{2pt}
+
 %% \hypersetup{
@@
 \renewcommand\UrlFont{\color{blue}\rmfamily}
-
 %for qed:
@@
 
+% Used in REST experiment section
+\usepackage{wrapfig}
+
 \usepackage{enumitem}
@@
 \addtolength{\belowcaptionskip}{-2mm}
+\addtolength{\abovedisplayskip}{-5pt}
+\addtolength{\belowdisplayskip}{-5pt}
 
@@
 %\title{Contribution Title\thanks{Supported by organization x.}}
-\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}}
+\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by NSF grant DMS-1950583}}
 %
@@
 %
-\vspace{-0.1in}
-%\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-%Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-%Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
-%\author{Jenna Elwing\thanks{University of Michigan, Ann Arbor} \and Laura Gamboa Guzmán\thanks{Iowa State University} \and Jeremy Sorkin\thanks{The Ohio State University} \and Chiara Travesset\thanks{Purdue University} \and Zili Wang\thanks{University of California, Berkeley} \and Kristin Y.
-Rozier\footnotemark[2]}
+
+\author{Jenna Elwing\inst{1}\and
+Laura Gamboa-Guzman\inst{2} \and
+Jeremy Sorkin\inst{3} \and Chiara Travesset\inst{4}\and Zili Wang\inst{2} \and Kristin Y. Rozier\inst{2}}
 %
-%\authorrunning{F. Author et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-%\institute{Princeton University, Princeton NJ 08544, USA \and
-%Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-%\email{lncs@springer.com}\\
-%\url{http://www.springer.com/gp/computer-science/lncs} \and
-%ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-%\email{\{abc,lncs\}@uni-heidelberg.de}}
-%
-\maketitle              % typeset the header of the contribution
-%
-
+\authorrunning{J. Elwing et al.}
+\institute{University of Michigan, Ann Arbor \and
+Iowa State University \and University of Amsterdam \and University of Wisconsin, Madison}
+
+\maketitle
 \vspace{-0.3in}
@@
 
-        \vspace{-0.1in}
-\keywords{Mission-time Linear Temporal Logic (MLTL)  \and MLTL Satisfiability \and Temporal Logic Validation.}
+% \vspace{-0.1in}
+\keywords{Mission-time Linear Temporal Logic (MLTL)  \and MLTL Validation \and Temporal Logic Validation.}
 \end{abstract}
 
-\vspace{-0.4in}
+% \vspace{-0.4in}
 \section{Introduction}
-\vspace{-0.1in}
+% \vspace{-0.1in}
 System specifications, such as aerospace operational concepts, often utilize timelines to express critical requirements.
@@
 
-There are a number of SAT solvers for MLTL \textcolor{red}{CITE SAT SOLVERS IDK THEM}, but there are currently no tools to check for MLTL formula validation, i.e.
-there are no tools available that allow people to \emph{validate} that a proposed MLTL formula is indeed capturing a specification for a system they want to verify.
-%It is necessary to perform validation before even being able to utilize SAT solvers in any meaningful way.
-This is precisely the role of the WEST tool, which is introduced in this paper.
-In this paper we introduce the WEST tool, which takes an MLTL formula and produces a description of the set of all finite time lines (of a fixed length) that satisfy the given formula, similar to filling out a truth table for propositional formulas and looking at the rows on which the formula holds.
-As a consequence, MLTL validation can be done by verifying that the output of the WEST program on a given input indeed matches the behaviour of the specification in question.
-
-We show that our contributions not only fill a critical gap in temporal logic validation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C code from temporal logic behavior descriptions.
+There exists a SAT solver for MLTL, MLTLSAT \cite{LVR22}, but there are currently no tools for MLTL formula validation.
+This paper introduces the WEST tool \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-}{[GitHub]}, which produces a description of the set of all finite time lines (of a fixed length) that satisfy a given MLTL formula, similar to a truth table for propositional formulas.
+MLTL validation can be done by verifying that the output of the WEST program indeed matches the behaviour of the specification in question.
+
+%The WEST program utilizes regular expressions to describe and visualize the finite time lines satisfying an MLTL formula, an approach that differs from the more commonly used ones that rely on finite automata theory.
+Currently, there are no tools that visualize MLTL formulas in the form of a finite automata, but even if such a tool were to exist, it would not fill the same niche for formula validation as the WEST algorithm.
+For example, the WEST algorithm allows validation and visualization for subformulas of any given formula, and allows visualization of the truth value for these at each time step of the satisfying computations, while automata do not necessarily have these capabilities.
+
+We show that our contributions not only fill a critical gap in temporal logic validation but also directly connect to parallel developments to enable better temporal logic formula analysis, benchmark generation, proof generation (e.g., in ACL2), and synthesis of verified C++ code from temporal logic behavior descriptions.
 
@@
 
-We structure the paper around our contributions as follows.
-In Section \ref{prereq}, we build on the semantics of MLTL to define a computation and its bit string representation.
+We structure the paper as follows.
+Section \ref{prereq} builds on the semantics of MLTL to define a computation and its bit string representation.
 % of a computation that is used throughout the paper and the WEST program.
@@
 %
-In Section \ref{regex}, we recursively define regular expressions encapsulating the satisfying computations of MLTL formulas and prove that our new translation algorithm is both sound and complete.
-In addition, we provide a calculation for the minimum computation length required to describe all the satisfying computations of a MLTL formula that slightly improves upon existing calculations in the literature.
-Finally, we show an application of the regular expressions of the satisfying computations by using them to prove an MLTL theorem.
-In particular, we show that $\phi\mathcal{U}_{[a,b]}(\phi\mathcal{U}_{[0,c]}\psi) \equiv \phi\mathcal{U}_{[a,b+c]}\psi$ and $\phi\mathcal{R}_{[a,b]}(\phi\mathcal{R}_{[0,c]}\psi) \equiv \phi\mathcal{R}_{[a,b+c]}\psi$.
+Section \ref{regex}, recursively defines regular expressions encapsulating the satisfying computations of MLTL formulas.
+We provide a calculation for the minimum computation length required to describe all the satisfying computations of a MLTL formula that slightly improves upon existing calculations in the literature.
+Finally, we show an application of the regular expressions by using them to prove an MLTL theorem.
 %
-We introduce a new tool, called WEST (acronym redacted for blind review), that implements automated validation in Section \ref{WESTalg}
+We introduce the WEST tool that implements automated validation in Section \ref{WESTalg}
 and calculate its space and time complexity, both theoretically and experimentally.
-We show that the theoretical worst-case complexity for both space and time is doubly exponential, but that the average case fares far better.
+%We show that the theoretical worst-case complexity for both space and time is doubly exponential, but that the average case fares far better.
 %
-Section \ref{test} proves correctness of the algorithms and provides a test suite to show correctness of implementation with high confidence.
-Intelligent fuzzing techniques contribute to test suite construction from a state diagram representing the control flow of the algorithm.
+Section \ref{test} proves the correctness of WEST and provides a test suite to show correctness of implementation with high confidence.
+Intelligent fuzzing techniques contribute to test suite construction from a state diagram representing the control flow of WEST.
 We also verify the correctness of outputs of the WEST program against a na\"ive brute force implementation.
 %
-Section \ref{simpsection}, provides a combinatorial theorem for simplifying certain outputs of the WEST program.
-Formulas of the form $\phi \equiv \psi$ to check for equivalence between two expressions can lead to outputs that are non-trivial to simplify.
+Section \ref{simpsection} provides a combinatorial theorem for simplifying certain outputs of the WEST program to the trivial computation.
+%Formulas of the form $\phi \equiv \psi$ to check for equivalence between two expressions can lead to outputs that are non-trivial to simplify.
+%
+Section \ref{Using WEST} demonstrates a specific use case of the WEST tool and explores the currently supported features. 
+%
 Section \ref{Conclusion} discusses impacts and future work. 
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-0.1in}
+% \vspace{-0.40in}
 \section{Preliminaries: Mission-time LTL and Bit String Computations} \label{prereq}
-\vspace{-0.1in}
+% \vspace{-0.5in}
 %\subsection{Mission-time Linear Temporal Logic}
 \emph{Mission-time Linear Temporal Logic (MLTL)} \cite{LVR22} is a finite variation of LTL over bounded, closed, discrete intervals of the form $[a,b]$ where $a,b \in \mathbb{N}$ and $0 \leq a \leq b$.
-The syntax of MLTL formulas, $\phi$ and $\psi$, over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar:%
-\vspace{-0.1in}
-$$\phi, \psi := \top \ | \ \bot \ | \ p \ | \ \neg \phi \ | \ \phi \land \psi \ | \ \phi \lor \psi \ | \ \mathcal{F}_{[a,b]} \phi \ | \ \mathcal{G}_{[a,b]} \phi \ | \ \phi \mathcal{U}_{[a,b]} \psi \ | \ \phi \mathcal{R}_{[a,b]} \psi \footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{WESTalg}).
+The syntax of MLTL formulas, $\phi$ and $\psi$, over a set of atomic propositions $\mathcal{AP}$, where $p \in \mathcal{AP}$ is a propositional variable, is given by the following BNF grammar: \\
+% \vspace{-0.1in}
+$$\phi, \psi := \top \ | \ \bot \ | \ p \ | \ \neg \phi \ | \ \phi \land \psi \ | \ \phi \lor \psi \ | \ \mathcal{F}_{[a,b]} \phi \ | \ \mathcal{G}_{[a,b]} \phi \ | \ \phi \mathcal{U}_{[a,b]} \psi \ | \ \phi \mathcal{R}_{[a,b]} \psi.\footnote{For simplicity, we do not include parentheses in the grammar, but the WEST program requires parentheses (see Section \ref{WESTalg}).
 We encode Release directly rather than as the dual of Until \cite{bmc,LVR22}.}$$
+
 MLTL formulas can be interpreted using both finite and infinite ``time lines'' that are called \emph{computations}, which represent a discrete sequence of time instances and the truth values for the propositional variables on each one of these.
@@
 That is, a propositional variable $p$ is true at time step $i$ if and only if $p \in \pi[i]$.
-{\color{blue} What is the semantics for the other logical and temporal operators?
-Where can we find a formal definition for this?
-This is never explicitly said before \texttt{reg} is introduced and it can lead to misinterpretations from the reviewers.} We denote the suffix of $\pi$ starting at $i$ (including $i$) by $\pi_i$.
+We denote the suffix of $\pi$ starting at $i$ (including $i$) by $\pi_i$.
 Note that $\pi_0 = \pi$.
 \end{definition}
+We now provide the semantics for MLTL.
+A computation $\pi$ satisfies a given MLTL formula $\alpha$, written $\pi \vDash \alpha$, in the following cases\footnote{We do not include the Next operator, often denoted by $\chi$, as it can be defined as $\mathcal{G}_{[1,1]}$.}:\\
+\begin{minipage}{0.5\textwidth}
+\begin{flalign*}
+   &\pi \vDash p \text{ iff } p \in \pi[0]&\\
+   &\pi \vDash \alpha \land \beta \text{ iff } \pi \vDash \alpha \text{ and } \pi \vDash \beta&
+\end{flalign*}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+\begin{flalign*}
+    &\pi \vDash \neg \alpha \text{ iff } \pi \nvDash \alpha&\\
+    &\pi \vDash \alpha \lor \beta \text{ iff } \pi \vDash \alpha \text{ or } \pi \vDash \beta&
+\end{flalign*}
+\end{minipage}
+{\setlength{\abovedisplayskip}{0pt}
+\begin{flalign*}
+    &\pi \vDash \mathcal{F}_{[a,b]}\alpha \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \alpha&\\
+    &\pi \vDash \mathcal{G}_{[a,b]}\alpha \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \alpha&\\
+    &\pi \vDash \alpha \ \mathcal{U}_{[a,b]} \beta \text{ iff } |\pi| > a \text{ and } \exists i \in [a,b] \text{ such that } \pi_i \vDash \beta \text{ and }\forall j \in [a, i-1]\ \pi_j \vDash \alpha &\\
+    &\pi \vDash \alpha \ \mathcal{R}_{[a,b]} \beta \text{ iff } |\pi| \leq a \text{ or } \forall i \in [a,b] \ \pi_i \vDash \beta \text{ or }\exists j \in [a,b-1] \text{ such that } \pi_j \vDash \alpha &\\
+    &\indent \text{ and } \forall a \leq k \leq j \ \pi_k \vDash \beta&
+\end{flalign*}}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{-0.1in}
+% \vspace{-0.1in}
 \section{MLTL Regular Expressions} \label{regex}
-\vspace{-0.1in}
+% \vspace{-0.1in}
 We modify the standard definition of Regular Expressions (Regex) to introduce notation that describes the satisfying computations of an MLTL formula.
@@
 \end{definition}
-Note that our regular expressions do not use the Kleene star. This is because are computations are of a fixed, finite length.
+Note that our regular expressions do not use the Kleene star. This is because our computations are of a fixed, finite length.
 %An example of these operations follows.
@@
 To compute $R \land T$ and $R \lor T$, we use Pad($R$,$T$).
-Since $T$ is the longer regex by one time step, we concatenate $(,S^2)$ to the right of $R$.
+Since $T$ is the longer regex by one time step, we extend $R$ by one time-step.
 Thus $T =1S,1S \lor S1,S1$ and $R = S1,SS$.
-Now the regexes are the same length, so we can perform set intersection and alternation:
+Now we can perform set intersection and alternation on the two regular expressions of equal length:
 \begin{itemize}
@@
 We define the regular expression of satisfying computations for a MLTL formula as follows:\\
-
-% ZILI: Left Aligned Version
-\vspace{-7mm}
-\hspace{-8.5mm}
-\begin{minipage}{0.45 \textwidth}
-    \begin{align}
-    &\text{reg}(\top) = S^n\\
-    &\text{reg}(p_k) = S^{k}1S^{n-k-1} \\
-    &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)\\
-    &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)
-    \end{align}
+\begin{minipage}{0.5\textwidth}
+    \begin{flalign*}
+        &\text{reg}(\top) = S^n&\\
+    &\text{reg}(p_k) = S^{k}1S^{n-k-1}&\\
+    &\text{reg}(\phi \lor \psi) =  \text{reg}(\phi) \lor \text{reg}(\psi)&\\
+    &\text{reg}(\mathcal{G}_{[a,b]} \phi) = \bigwedge_{i=a}^{b} (S^n,)^i \text{reg}(\phi)&
+    \end{flalign*}
 \end{minipage}
-\begin{minipage}{0.55\textwidth}
-    \begin{align}
-    &\text{reg}(\bot) = \emptyset \\
-    &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1} \\
-    &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi) \\
-    &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)
-    \end{align}
+\begin{minipage}{0.5\textwidth}
+\begin{flalign*}
+        &\text{reg}(\bot) = \emptyset&\\
+    &\text{reg}(\neg p_k) = S^{k}0S^{n-k-1}&\\
+    &\text{reg}(\phi \land \psi) = \text{reg}(\phi) \land \text{reg}(\psi)&\\
+    &\text{reg}(\mathcal{F}_{[a,b]} \phi) = \bigvee_{i=a}^{b} (S^n,)^i \text{reg}(\phi)&
+\end{flalign*}    
 \end{minipage}
-\vspace{-5mm}\\
-\begin{minipage}{0.99\textwidth}
-\begin{align}
-&\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)\\
-\vspace*{-10mm}&\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \label{release}
-\end{align}
-\end{minipage}
+{\setlength{\abovedisplayskip}{0pt}
+\begin{flalign*}
+    &\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)&\\
+&\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)&
+\end{flalign*}
+}
+
 \begin{definition}[\emph{Computation Length}]
-We define the computation length $\emph{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:\\
-          %\begin{align}
-\indent \qquad   $\emph{cplen}(p_k) = \emph{cplen}(\neg p_k) = 1$\\
-\indent \qquad   $\emph{cplen}(\phi \land \psi) = \emph{cplen}(\phi \lor \psi) = \max(\emph{cplen}(\phi), \emph{cplen}(\psi))$\\
-\indent \qquad   $\emph{cplen}(\mathcal{G}_{[a,b]} \phi) = \emph{cplen}(\mathcal{F}_{[a,b]} \phi) = b + \emph{cplen}(\phi)$\\
-\indent \qquad   $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$
-%\end{align}
+We define the computation length $\emph{cplen}(\phi)$ of an MLTL formula $\phi$ recursively:
+\begin{flalign*}
+    &\emph{cplen}(p_k) = \emph{cplen}(\neg p_k) = 1,&\\
+    &\emph{cplen}(\phi \land \psi) = \emph{cplen}(\phi \lor \psi) = \max(\emph{cplen}(\phi), \emph{cplen}(\psi)),&\\
+    &\emph{cplen}(\mathcal{G}_{[a,b]} \phi) = \emph{cplen}(\mathcal{F}_{[a,b]} \phi) = b + \emph{cplen}(\phi),&\\
+    &\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi)).&
+\end{flalign*}
 \end{definition}
-\vspace{-0.1in}
+% \vspace{-0.1in}
 Intuitively, $\text{cplen}(\phi)$ is the minimum computation length required to ensure that none of the intervals in $\phi$ are out of bounds.
@@
 \end{theorem}
-\vspace{-0.2in}
+% \vspace{-0.2in}
 \begin{proof}
-The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Globally, AND, and OR.\\
- Recall that $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$. Thus
- \begin{align*}
-     \text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \phi \land \mathcal{G}_{[i,i]} \psi) \right)\\
-     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\phi), i + \text{cplen}(\psi))\right)\\
-     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi))\right)\\
-     &= b + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi)).
- \end{align*}
- \vspace{-0.1in}
- Now recall that $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$.
-Thus%
-% \vspace{-0.1in}
- \begin{align*}
-     \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \psi), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)  \right)\\
-     &= \max\left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)\\
-     &= \max \left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\psi), i + \text{cplen}(\phi))\right) \right)\\
-     &= \max \left( b + \text{cplen}(\psi), \max(b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\right)\\
-     &= \max(b + \text{cplen}(\psi), b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\\
-     &= b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi)). 
- \end{align*}
-% This completes the proof.
+The formulas for the minimum computation length follow directly from the regular expressions for the satisfying computations for Until and Release and the minimum computation lengths for Finally, Globally, AND, and OR.
+See Appendix \ref{complen-proof} for details.
  \end{proof}
- \vspace{-0.25in} \hfill $\blacksquare$\\
- \noindent Intuitively, we can reduce the minimum computation length of Until/Release because:
- \begin{itemize}
-     \item At the final time-step for $\phi \mathcal{U}_{[a,b]} \psi$, if $\psi$ has not yet been assigned to be true in the computation, it will be assigned true because $\phi \mathcal{U}_{[a,b]} \psi$ is a strong operator.
-Semantically, the truth value of $\phi$ at this time interval doesn't matter; whether $\phi$ is true or false, the computation for $\phi \mathcal{U}_{[a,b]} \psi$ is satisfied.
-     \item Likewise, in the case for $\phi \mathcal{R}_{[a,b]} \psi$, if $\psi$ is true from the first to the last time-step, the truth value of $\phi$ at the final time-step doesn't matter - the computation satisfies $\phi \mathcal{R}_{[a,b]} \psi$ regardless of whether $\phi$ is true or false.
- \end{itemize} % \vspace{-0.1in} % \subsection{Soundness and Completeness} %  \vspace{-0.1in}
+ \noindent We can reduce the minimum computation length of Until because at the final time step for $\phi \mathcal{U}_{[a,b]} \psi$, $\psi$ must be assigned true if it hasn't been at a prior time step due to Until being a strong operator, and the truth value of $\phi$ at this final time step doesn't matter.
+Likewise, in the case for $\phi \mathcal{R}_{[a,b]} \psi$, if $\psi$ is true from the first to the last time step, the truth value of $\phi$ at the final time step doesn't matter — the computation satisfies the formula regardless.\\
  We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
@@
  \end{theorem}
+ \begin{proof}
+     Straightforward proof by induction on the length of a formula. See Appendix \ref{Appendix-SoundComplete} for details.
+ \end{proof}
+
  We prove the correctness of our formula rewriting algorithm using our regular expressions from Definition \ref{TRE}.
@@
 \end{theorem}
+\begin{proof}
+    Follows directly from the regular expressions for MLTL. See \ref{Appendix-NestedUR} for details.
+\end{proof}
+
+% ZILI: Presenting algorithm vertically instead
+\hspace{-5mm}
+\begin{minipage}[t]{0.52\textwidth} 
+\begin{algorithm}[H] 
+\caption{WEST Algorithm}
+Inputs: $\phi$ - MLTL formula in NNF \\
+$\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
+$n$ - number of propositional variables \\
+Output: set of REGEX satisfying $\phi$
+\begin{algorithmic}[1]
+    \Procedure{reg}{string $\phi$, int $n$}
+        \If{$\phi$ is $\top$ or $\bot$}
+            \State return reg\_prop\_const($\phi$, n)
+        \EndIf
+
+        \If{$\phi$ is $p_k$ or $\neg p_k$}
+            \State return reg\_prop\_var($\phi$, n)
+        \EndIf
+
+        \If{$\phi  = \phi_1 \land \phi_2$}
+            \State \parbox[t]{.82\linewidth}{return set\_intersect(reg($\phi_1$), reg($\phi_2$), \hspace*{5mm}n)}
+        \EndIf
+
+        \If{$\phi  = \phi_1 \lor \phi_2$}
+            \State return join(reg($\phi_1$), reg($\phi_2$), n)
+        \EndIf
+
+        \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$}
+            \State return reg\_F(reg($\phi_1$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$}
+            \State return reg\_G(reg($\phi_1$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$}
+            \State return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
+            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
+        \EndIf
+    \EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\vspace{5.9mm}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.48\textwidth}
+\begin{algorithm}[H]
+\caption{set\_intersect}
+Inputs: $R, T$ - two sets of REGEX\\
+$n$ - number of propositional variables\\
+Output: set of REGEX equal to $R \land T$
+\begin{algorithmic}[1]
+\Procedure{set\_intersect}{$R$, $T$, n}
+    \State Pad($R$, $T$, n), return $\leftarrow \{\}$
+    \For{$(r, t) \in R\times T$}
+            \State add bit\_wise\_and($r, t$) to ret 
+    \EndFor
+    \State return simplify(ret)
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\vspace{-6.5mm}
+\begin{algorithm}[H]
+\caption{reg\_U} 
+Inputs: $r_\phi$, $r_\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
+$a, b$ - integers representing interval bound \\
+$n$ - number of propositional variables\\
+Output: set of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
+\begin{algorithmic}[1]
+\Procedure{reg\_U}{$r_\phi$, $r_\psi$, $a$, $b$, $n$} 
+    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
+    \If{$a > b$} return $\{\}$
+    \EndIf
+    \For{($a \leq i \leq b-1$) }
+        \State G1 $\leftarrow$ reg\_G($r_\phi$, $a$, $i$, $n$)
+        \State \parbox[t]{.8\linewidth}{G2 $\leftarrow$ reg\_G($r_\psi$, $i+1$, $i+1$, $n$)}
+        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect(G1,  \hspace*{5mm}G2, n)}
+        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
+        % , \hspace*{5mm}simp)}
+    \EndFor
+    \State return comp
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+
 %The proof of Theorem \ref{NestedUR} appears in Appendix \ref{Appendix-NestedUR}.
@@
 \section{WEST Algorithm and Analysis} \label{WESTalg}
-We now present the  full WEST algorithm, which recursively computes all satisfying temporal regular expressions to a given MLTL formula (in NNF). 
-For convenience, we use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_0, ..., t_{n-1}\} = \bigcup_{i=0}^{n-1} t_i$. 
+Algorithm 1 recursively computes all satisfying temporal regular expressions to an input formula $\phi$.
+We use sets to represent alternation of regular expressions; for $n$ regular expressions $t_0, ..., t_{n-1}$, we'll write $\{t_0, ..., t_{n-1}\} = \bigcup_{i=0}^{n-1} t_i$. 
 Additionally, we provide details for performing set intersection of temporal regular expressions, and the algorithm for the temporal operator $\mathcal{U}$.
-Note how \texttt{reg\_U} parallels the regular expression defined for $\mathcal{U}$, and the algorithms for the other three temporal operators follow an identical structure.
-
-One major detail that drastically improves running time is applying a simplifying function to the output of set intersection. 
-This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
-Although repeated set intersection blows up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
-We simplify alternation by using the fact that for regular expressions $w_0$ and $w_1$, $\mathscr{L}(w_0 1 w_1 \lor w_0 0 w_1) = \mathscr{L}(w_0 s w_1)$, and check if the reduction applies at every index between every pair of strings in a given set.
+Note how \texttt{reg\_U} parallels the regular expression defined for $\mathcal{U}$, and the algorithms (see appendix \ref{pseudocode_appendix}) for the other three temporal operators follow an identical structure.
+
+For for regular expressions $w_0$ and $w_1$, a useful reduction is that $\{w_0 1 w_1, w_0 0 w_1\} = \{w_0 s w_1\}$.
+Each time set intersection is performed, we greedily apply this reduction to all appropriate pairs of regular expressions in the set.
+This prevents repeated set intersection operations from blowing up exponentially most of the time, and drastically improves running time.
+
+% Applying a simplifying function to the output of set intersection drastically improves running time. 
+% This is because the set intersection operation is repeatedly used to compute the temporal operators $\mathcal{G}, \mathcal{U}, \mathcal{R}$. 
+% Although repeated set intersection blows up exponentially in space in the worse case, it rarely does in practice; thus why we frequently simplify outputs. 
+% We simplify alternation by using the fact that for regular expressions $w_0$ and $w_1$, $\mathscr{L}(w_0 1 w_1 \lor w_0 0 w_1) = \mathscr{L}(w_0 s w_1)$, and check if the reduction applies at every index between every pair of strings in a given set.
 
@@
 
-% ZILI: Presenting algorithm vertically instead
-\hspace{-5mm}
-\begin{minipage}{0.52\textwidth} 
-\begin{algorithm}[H] 
-\caption{WEST Algorithm}
-Inputs: $\phi$ - MLTL formula in NNF \\
-$\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
-$n$ - number of propositional variables \\
-Output: set of REGEX satisfying $\phi$
-\begin{algorithmic}[1]
-    \Procedure{reg}{string $\phi$, int $n$}
-        \If{$\phi$ is $\top$ or $\bot$}
-            \State return reg\_prop\_const($\phi$, n)
-        \EndIf
-
-        \If{$\phi$ is $p_k$ or $\neg p_k$}
-            \State return reg\_prop\_var($\phi$, n)
-        \EndIf
-
-        \If{$\phi  = \phi_1 \land \phi_2$}
-            \State \parbox[t]{.82\linewidth}{return set\_intersect(reg($\phi_1$), reg($\phi_2$), \hspace*{5mm}n)}
-        \EndIf
-
-        \If{$\phi  = \phi_1 \lor \phi_2$}
-            \State return join(reg($\phi_1$), reg($\phi_2$), n)
-        \EndIf
-
-        \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$}
-            \State return reg\_F(reg($\phi_1$), a, b, n)
-        \EndIf
-
-        \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$}
-            \State return reg\_G(reg($\phi_1$), a, b, n)
-        \EndIf
-
-        \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$}
-            \State return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
-        \EndIf
-
-        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
-            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
-        \EndIf
-    \EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\vspace{5.9mm}
-\end{minipage}
-\hfill
-\begin{minipage}{0.48\textwidth}
-\begin{algorithm}[H]
-\caption{set\_intersect}
-Inputs: $R, T$ - two sets of REGEX\\
-$n$ - number of propositional variables\\
-Output: set of REGEX equal to $R \land T$
-\begin{algorithmic}[1]
-\Procedure{set\_intersect}{$R$, $T$, n}
-    \State Pad($R$, $T$, n), return $\leftarrow \{\}$
-    \For{$(r, t) \in R\times T$}
-            \State add bit\_wise\_and($r, t$) to ret 
-    \EndFor
-    \State return simplify(ret)
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\vspace{-6.5mm}
-\begin{algorithm}[H]
-\caption{reg\_U} 
-Inputs: $r_\phi$, $r_\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
-$a, b$ - integers representing interval bound \\
-$n$ - number of propositional variables\\
-Output: set of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
-\begin{algorithmic}[1]
-\Procedure{reg\_U}{$r_\phi$, $r_\psi$, $a$, $b$, $n$} 
-    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
-    \If{$a > b$} return $\{\}$
-    \EndIf
-    \For{($a \leq i \leq b-1$) }
-        \State G1 $\leftarrow$ reg\_G($r_\phi$, $a$, $i$, $n$)
-        \State \parbox[t]{.8\linewidth}{G2 $\leftarrow$ reg\_G($r_\psi$, $i+1$, $i+1$, $n$)}
-        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect(G1,  \hspace*{5mm}G2, n)}
-        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
-        % , \hspace*{5mm}simp)}
-    \EndFor
-    \State return comp
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-\end{minipage}
+% % ZILI: Presenting algorithm vertically instead
+% \hspace{-5mm}
+% \begin{minipage}[t]{0.52\textwidth} 
+% \begin{algorithm}[H] 
+% \caption{WEST Algorithm}
+% Inputs: $\phi$ - MLTL formula in NNF \\
+% $\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
+% $n$ - number of propositional variables \\
+% Output: set of REGEX satisfying $\phi$
+% \begin{algorithmic}[1]
+%     \Procedure{reg}{string $\phi$, int $n$}
+%         \If{$\phi$ is $\top$ or $\bot$}
+%             \State return reg\_prop\_const($\phi$, n)
+%         \EndIf
+
+%         \If{$\phi$ is $p_k$ or $\neg p_k$}
+%             \State return reg\_prop\_var($\phi$, n)
+%         \EndIf
+
+%         \If{$\phi  = \phi_1 \land \phi_2$}
+%             \State \parbox[t]{.82\linewidth}{return set\_intersect(reg($\phi_1$), reg($\phi_2$), \hspace*{5mm}n)}
+%         \EndIf
+
+%         \If{$\phi  = \phi_1 \lor \phi_2$}
+%             \State return join(reg($\phi_1$), reg($\phi_2$), n)
+%         \EndIf
+
+%         \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$}
+%             \State return reg\_F(reg($\phi_1$), a, b, n)
+%         \EndIf
+
+%         \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$}
+%             \State return reg\_G(reg($\phi_1$), a, b, n)
+%         \EndIf
+
+%         \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$}
+%             \State return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
+%         \EndIf
+
+%         \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
+%             \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
+%         \EndIf
+%     \EndProcedure
+% \end{algorithmic}
+% \end{algorithm}
+% \vspace{5.9mm}
+% \end{minipage}
+% \hfill
+% \begin{minipage}[t]{0.48\textwidth}
+% \begin{algorithm}[H]
+% \caption{set\_intersect}
+% Inputs: $R, T$ - two sets of REGEX\\
+% $n$ - number of propositional variables\\
+% Output: set of REGEX equal to $R \land T$
+% \begin{algorithmic}[1]
+% \Procedure{set\_intersect}{$R$, $T$, n}
+%     \State Pad($R$, $T$, n), return $\leftarrow \{\}$
+%     \For{$(r, t) \in R\times T$}
+%             \State add bit\_wise\_and($r, t$) to ret 
+%     \EndFor
+%     \State return simplify(ret)
+% \EndProcedure
+% \end{algorithmic}
+% \end{algorithm}
+% \vspace{-6.5mm}
+% \begin{algorithm}[H]
+% \caption{reg\_U} 
+% Inputs: $r_\phi$, $r_\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
+% $a, b$ - integers representing interval bound \\
+% $n$ - number of propositional variables\\
+% Output: set of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
+% \begin{algorithmic}[1]
+% \Procedure{reg\_U}{$r_\phi$, $r_\psi$, $a$, $b$, $n$} 
+%     \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
+%     \If{$a > b$} return $\{\}$
+%     \EndIf
+%     \For{($a \leq i \leq b-1$) }
+%         \State G1 $\leftarrow$ reg\_G($r_\phi$, $a$, $i$, $n$)
+%         \State \parbox[t]{.8\linewidth}{G2 $\leftarrow$ reg\_G($r_\psi$, $i+1$, $i+1$, $n$)}
+%         \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect(G1,  \hspace*{5mm}G2, n)}
+%         \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
+%         % , \hspace*{5mm}simp)}
+%     \EndFor
+%     \State return comp
+% \EndProcedure
+% \end{algorithmic}
+% \end{algorithm}
+% \end{minipage}
 
@@
 We show that $\mathscr{L}(\texttt{set\_intersect}(R, T)) = \mathscr{L}(R) \cap \mathscr{L}(T)$:
-\vspace{-3mm}$$\mathscr{L}(R) \cap \mathscr{L}(T) = \left(\bigcup_{i = 0}^{a-1} \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^{b-1} \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^{a-1} \bigcup_{j = 0}^{b-1} \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).$$
+%\vspace{-3mm}
+$$\mathscr{L}(R) \cap \mathscr{L}(T) = \left(\bigcup_{i = 0}^{a-1} \mathscr{L}(r_i) \right)\cap \left( \bigcup_{j = 0}^{b-1} \mathscr{L}(t_j)\right) = \bigcup_{i = 0}^{a-1} \bigcup_{j = 0}^{b-1} \left(\mathscr{L}(r_i) \cap \mathscr{L}(t_j)\right).$$
 The loop in line 3 of \texttt{set\_intersect} computes the union of \texttt{bit\_wise\_and}$(r_i, t_j)$ over all such pairs, and so it suffices to show $\mathscr{L}(\texttt{bit\_wise\_and}(r_i, t_j)) = \mathscr{L}(r_i) \cap \mathscr{L}(t_j)$.
@@
     Thus using our previous results for the $\mathcal{G}$, $\land$ and $\lor$ operators, we have that:
-    \vspace{-.4cm}
+    {\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
     \begin{align*}
@@
         &= \mathcal{C}_U \cdot S(\texttt{reg}(\phi_1))^\delta \cdot S(\texttt{reg}(\phi_2))
-    \end{align*}
-    where $\mathcal{C}_U = \delta ((n+1)(b-1) + 1)^\delta \cdot (n+1) \cdot d$.\\
+    \end{align*}}
+    where $\mathcal{C}_U = \delta ((n+1)(d-1) + 1)^\delta \cdot (n+1) \cdot d$.\\
 \hspace{3mm} If $\phi$ = $``\phi_1 \mathcal{R}_{[a, b]} \phi_2"$:
@@
 It's easy to check that the base case $k = 1$ holds, and we prove the claim by induction:
-    \vspace{-0.2cm}
+    % \vspace{-0.2cm}
     \begin{align*}
@@
  \end{proof}
-
-For time complexity, through a similar analysis, we've found that the time-complexity of all of the above functions is the same as their space complexity.
-In particular, the time complexities of $\phi = p_k, \scriptstyle{\sim}\textstyle p_k, \top, \bot$, as well as that of \texttt{set\_intersect}, \texttt{join}, and the operator $\mathcal{U}$ match their respective space complexities.
+Through a similar analysis we've found that the time complexity of all of the above functions is the same as their space complexity.
 \begin{theorem}[\emph{Time Complexity}]
@@
 
-\subsection{Experimental Benchmarking}
+\subsection{Experimental Benchmarking} \label{WESTexp}
 We accompany theoretical space and time complexity with experimental evaluation of these complexities using randomly-generated MLTL formulas.
@@
 
-We ran these experiments on an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM.
+We ran these experiments on an Intel(R) Xeon(R) Gold 6140 CPU @ 2.30GHz with 376 GB RAM.
 For each simulation, we generated 1000 MLTL formulas using the parameters \texttt{delta}, \texttt{interval\_max}, number of propositional variables, and number of iterations.
@@
 \noindent\textbf{Simulation 1}
-For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}. We obtain plots \ref{InVsOutputLen} and \ref{InLenVsRunTime}:\\
-\begin{minipage}{0.5 \textwidth}
+For the first simulation, we consider 2 iterations, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}. We obtain plots \ref{InVsOutputLen1} and \ref{InLenVsRunTime1}.
 \begin{figure}[H]
+\captionsetup[subfigure]{aboveskip=-1pt,belowskip=-1pt}
     \centering
-    \includegraphics[scale=0.35]{images/Sim1Length_large.png}
-    \captionof{figure}{Input length vs output length.\vspace{3mm}}
-    \label{InVsOutputLen}
+    \begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTspace1.png}
+    \caption{}
+    \label{InVsOutputLen1}
+    \end{subfigure}
+    \begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTtime1.png}
+    \caption{}
+    \label{InLenVsRunTime1}
+    \end{subfigure}
+    \caption{$(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ is an outlier in both. $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and
+    $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ are outliers only in \subref{InLenVsRunTime1}.}
 \end{figure}
-\end{minipage}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
+
+\noindent\textbf{Simulation 2}
+For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for \texttt{delta}, and 20 for \texttt{interval\_max}.
+We obtain plots \ref{fig:InVsOutLen2} and \ref{fig:InLenVsRunTime2}.
+\begin{figure}[h]
+\captionsetup[subfigure]{aboveskip=-1pt,belowskip=-1pt}
     \centering
-    \includegraphics[scale=0.35]{images/Sim1Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{InLenVsRunTime}
+    \begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTspace2.png}
+    \caption{}
+    \label{fig:InVsOutLen2}
+    \end{subfigure}
+\begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTtime2.png}
+    \caption{}
+    \label{fig:InLenVsRunTime2}
+    \end{subfigure}
+    \caption{We observe no outliers.}
 \end{figure}
-\end{minipage}\\
-\noindent The formula $(p_0 = p_1) \mathcal{U}_{[2,9]} (p_1 \mathcal{U}_{[7,9]} p_3)$ was an outlier for both Figures \ref{InVsOutputLen} and \ref{InLenVsRunTime}, and the formulas $(p_4 \rightarrow p_2) \mathcal{R}_{[1,8]} (p_3 \mathcal{U}_{[3,4]} p_0)$ and $(p_3 \mathcal{R}_{[2,7]} p_4) \mathcal{R}_{[1,9]} (p_4 \mathcal{R}_{[4,9]} p_3)$ were outliers for Figure \ref{InLenVsRunTime}.
-\\
-\noindent\textbf{Simulation 2}
-For the second simulation, we consider 1 iteration, 10 propositional variables, 20 for \texttt{delta}, and 20 for \texttt{interval\_max}. Here are some examples of generated formulas:
-$\mathcal{F}_{[10,17]} p_4$, $\neg p_6$, $p_6 \mathcal{U}_{[6,14]} p_8$. We obtain plots \ref{fig:InVsOutLen2} and \ref{fig:InLenVsRunTime2}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim2Length_large.png}
-    \captionof{figure}{Input length vs output length\vspace{3mm}}
-    \label{fig:InVsOutLen2}
-    \end{figure}
-\end{minipage}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim2Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{fig:InLenVsRunTime2}
-    \end{figure}
-\end{minipage}\\
+
 \noindent\textbf{Simulation 3}
 For the third simulation, we consider 2 iterations, 10 propositional variables, 5 for \texttt{delta}, and 10 for \texttt{interval\_max}.
-We obtain plots \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
+We obtain plots \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}.
+\begin{figure}[h]
+\captionsetup[subfigure]{aboveskip=-1pt,belowskip=-1pt}
     \centering
-    \includegraphics[scale=0.35]{images/Sim3Length_large.png}
-    \captionof{figure}{Input length vs output length\vspace{3mm}}
+    \begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTspace3.png}
+    \caption{}
     \label{fig:InLenVsOutLen3}
+    \end{subfigure}
+    \begin{subfigure}[h]{0.49 \textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTtime3.png}
+    \caption{}
+    \label{fig:InLenVsRunTime3}
+    \end{subfigure}
+    \caption{$(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and
+    $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ are outliers in both. $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ is an outlier in \ref{fig:InLenVsOutLen3} only.}
 \end{figure}
-\end{minipage}
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
+
+\noindent\textbf{Simulation 4}
+For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}. We obtain plots \ref{InLenVsOutLen4} and \ref{InLenVsRunTime4}.
+\begin{figure}[h]
+\captionsetup[subfigure]{aboveskip=-1pt,belowskip=-1pt}
     \centering
-    \includegraphics[scale=0.35]{images/Sim3Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{fig:InLenVsRunTime3}
+    \begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTspace4.png}
+    \caption{}
+    \label{InLenVsOutLen4}
+    \end{subfigure}
+    \begin{subfigure}[h]{0.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/WESTtime4.png}
+    \caption{}
+    \label{InLenVsRunTime4}
+    \end{subfigure}
+    \caption{We observe no outliers.}
 \end{figure}
-\end{minipage}\\
-The formulas $(p_7 \mathcal{U}_{[5,7]} p_9) \mathcal{U}_{[3,7]} (\mathcal{F}_{[1,4]} p_4)$ and $\mathcal{G}_{[3,7]} (p_9 \mathcal{U}_{[0,4]} p_0)$ were outliers in both Figures \ref{fig:InLenVsOutLen3} and \ref{fig:InLenVsRunTime3}, and Figure \ref{fig:InLenVsOutLen3} had one more outlier from the formula $(\neg p_9) \mathcal{R}_{[5,9]} (p_5 \mathcal{U}_{[2,4]} p_3)$.
-\\
-\noindent\textbf{Simulation 4}
-For the fourth simulation, we consider 1 iteration, 5 propositional variables, 10 for \texttt{delta}, and 10 for \texttt{interval\_max}.
-Some examples of generated formulas are: $\neg p_1$, $p_1 \mathcal{R}_{[6,7]} p_3$, $\mathcal{F}_{[5,5]} p_3$.
-We obtain plots \ref{InLenVsOutLen4} and \ref{InLenVsRunTime4}:\\
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim4Length_large.png}
-    \captionof{figure}{Input length vs output length\vspace{3mm}}
-    \label{InLenVsOutLen4}
-    \end{figure}
-\end{minipage}%
-\begin{minipage}{0.5 \textwidth}
-    \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.35]{images/Sim4Time_large.png}
-    \captionof{figure}{Input length vs run time.\vspace{3mm}}
-    \label{InLenVsRunTime4}
-    \end{figure}
-\end{minipage}
+
 What we conclude from the simulations is that for most practical purposes, the WEST algorithm demonstrates good space and time complexity.
@@
 Since our proof of algorithmic correctness is manual and our focus is on usability for validation by humans, we utilize more traditional techniques for robust software engineering with testing-based evaluation.
-An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
-Since the primary purpose of the WEST tool is validation of formulas for humans, we focused on writing a tool with an intuitive human-facing interface and then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.\\
-One na\"ive approach involves testing every possible input up to a certain size to verify the output or behaviors of the program.
-For WEST, this strategy would generate a very large test suite with significant redundancy. 
+% An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
+% Since the primary purpose of the WEST tool is validation of formulas for humans, we focused on writing a tool with an intuitive human-facing interface and then verifying that implementation rather than wrestling with verified code generated by a tool made to optimize for different objectives.\\
+The na\"ive approach is to test all inputs up to a certain size and verify the outputs, but this strategy would generate an unnecessarily large and redundant test suite. 
 For instance, there is little sense in testing all MLTL formulas of the form $p_0 \mathcal{U}_{[0,t]} p_1$ for all $t$ such that $0 \leq t \leq 99$; verification of a few should give sufficient confidence of correctness of the program.
-We approach this problem more intelligently: we test our implementation with a test suite that explores all control paths (up to a certain depth) of the algorithm.
+Instead, we test our implementation with a test suite that explores all possible sequences of lines of code that are executed (up to a certain depth).
+% control paths (up to a certain depth) of the algorithm.
 A control path is a sequence of lines of code that are executed in one calculation of an input formula.
@@
 \subsection{Intelligent Fuzzing}
-Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; we employ fuzz testing (also know as fuzzing), a form of negative testing.
-We deviate from traditional black-box fuzzing defined by \cite{Miller}:
+% Negative testing is the process of checking that a program is able to handle unexpected inputs without crashing; we employ fuzz testing (also know as fuzzing), a form of negative testing.
+We deviate from
+Traditional black-box fuzzing is defined by Miller \cite{Miller}:
 \textit{``If we consider a program to
 be a complex finite state machine, then our testing strategy can be thought of as a random walk through the state space, searching for undefined states.''}\\
-Instead we utilize intelligent fuzzing (sometimes referred to as whitebox fuzzing), which is an alternate approach to fuzz testing that leverages knowledge about program structure to generate valid inputs and increase coverage.
+Instead we utilize intelligent fuzzing, an alternate approach that leverages knowledge about program structure to generate valid inputs and increase coverage. 
 Borrowing the words of Miller, our approach to testing the WEST program can be thought of as walking all possible paths up to a certain depth of the state space of our algorithm. 
@@
 \begin{enumerate}
-    \item Construct a state diagram of our algorithm, represented as a directed graph. 
-    The edges of the graph capture control flow of our algorithm, and vertices represent the remaining blocks of the code without branching statements.  
+    \item Construct a directed graph representation of our algorithm.
+    The edges capture control flow of our algorithm, and vertices represent non-branching blocks of code.
     \item Construct a test suite that explores all possible paths in the digraph up to a certain depth. Run the WEST program on the test suite to produce a set of output files.
@@
  The core of the WEST program lies in the recursive routine, \texttt{reg}, which calls the $8$ different subroutines as shown in \ref{fig:abstracted_graph}.
-\begin{figure}[t]
+\begin{figure}[h]
     \centering
@@
 For $d = 0$, only the paths leading to \texttt{prop\_var} and \texttt{prop\_cons} can be explored, so $\phi(0) = 2$.
-For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \texttt{reg\_G} and \texttt{reg\_F} is counted in the linear term, and paths to \texttt{reg\_U}, \texttt{reg\_R}, \texttt{set\_intersect}, and \texttt{join} is counted by the quadratic term.
+For $d \geq 1$, we recursively calculate $\phi(d + 1) = 2\phi(d) + 4\phi(d)^2$; paths to \texttt{reg\_G} and \texttt{reg\_F} is counted by the linear term, and paths to \texttt{reg\_U}, \texttt{reg\_R}, \texttt{set\_intersect}, and \texttt{join} is counted by the quadratic term.
 This gives $\phi(1) = 20$, $\phi(2) = 1640$, and $\phi(3) = 10761680$. 
@@
 Our test program translates every first-order quantifier into a loop; then checking for satisfying conditions of the suffix of a computation naturally lends itself to recursion.
-The full implementation details are available in the WEST GitHub repository.\footnote{Links have been redacted for blind review.} 
+The full implementation details are available in the WEST GitHub repository \href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-}{[Link]}.
 On an Intel(R) Core(TM) i7-4770S CPU at 3.10GHz with 32gb RAM, the brute force program took nearly nine hours to execute the depth two test suite of $1640$ formulas. 
@@
 Note that the brute force program outputs only computations of zeros and ones, and thus comparing the outputs of the WEST program requires expanding out the ``$S$'' characters in the regular expressions.
-For instance, the regular expression ``$1SS0SS1$'' yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
+%For instance, the regular expression ``$1SS0SS1$'' yields $2^{\text{\# of `$S$'s}} = 2^4 = 16$ computations after expansion.
 It's important to state that although the full test suite matches between both implementations, absolute correctness on all inputs is not guaranteed for either program.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Regular Expression Simplification Theorem} \label{simpsection}
 As a final result, we provide a regular expression simplification theorem.
-This theorem describes a form of a set of computations that are guaranteed to simplify down to a string of all ``$S$'' characters.
-Although not implemented in the WEST program, this theorem may help users identify tautologies, as the WEST program does not always output a single string of ``$S$'' characters when a formula holds true for every computation.
+This theorem describes the form of a set of computations that simplify down to all ``$S$'' characters.
+This theorem may help users identify tautologies, as the WEST program does not always output a single string of ``$S$'' characters when a formula holds true for every computation.
 We first define some vocabulary.
@@
 This aids significantly in the description and proof of the theorem; note, however, that matrix algebra does not apply in this definition.
+
 \begin{theorem}[\emph{Regular Expression Simplification Theorem}] \label{simp}
@@
 \end{theorem}
-Note that this theorem gives us a sufficient but not a necessary condition for simplification to the arbitrary computation.
-One such example is the regular expression $101|S1S|1S0|0SS$, which fails the hypothesis of the  simplification theorem but is still equivalent to $SSS$.
-\subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
-First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
+\begin{proof}
+    Follows from induction and the pigeon hole principle. See Appendix \ref{simp_appendix} for details.
+\end{proof}
+This theorem gives us a sufficient but not a necessary condition for simplification to the arbitrary computation.
+One such example is the regular expression $101 \lor S1S \lor 1S0 \lor 0SS$, which fails the hypothesis of the  simplification theorem but is still equivalent to $SSS$.
+\subsection{Theoretical and Experimental Analysis of REST}
+We present an algorithm based on Theorem \ref{simp} for simplifying disjunctions of regular expressions and provide theoretical analysis as well as experimental benchmarking.
+We determine that REST runs exponentially with respect to the length of the inputted regular expressions, both in the worst case and average case.
+Since REST does not apply for many inputted MLTL formulas, however, and WEST demonstrates good time and space complexity in the average case without REST (see section \ref{WESTexp}), this is not of much concern.
+\begin{algorithm}[h]
+\caption{Regular Expression Simplification Algorithm (REST)}
+Inputs: vector $v$ of $m$ regular expressions each of length $n$\\
+Output: simplified set of equivalent regular expressions using Theorem \ref{simp}
+    \begin{algorithmic}
+    \Procedure{rest}{set $v$} 
+        \For{$r \in [3, \min(m, n+1)]$}
+            \For{all vectors of regular expression $w \subseteq v$ s.t. $|v| = r$}
+                \State {diff\_cols $\leftarrow $ indices of all columns of $w$ that aren't uniformly the same character}
+                \If{$|\text{diff\_cols}| = r-1$}
+                    \State $w' \leftarrow w$ containing only columns $\in \text{diff\_cols}$
+                    \If{$w'$ satisfies Theorem \ref{simp}}
+                        \State In $w$, replace all columns $\in$ diff\_cols with $s$ 
+                        \State $v \leftarrow $ remove\_duplicates($v$)
+                    \EndIf
+                \EndIf
+            \EndFor
+        \EndFor
+        \State return $v$
+    \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+%
+\begin{theorem}
+    On input vector of regular expressions $v$ of $m$ strings each of length $n$, REST has a worst case runtime of $O(n^2 2^m)$.
+\end{theorem}
+\begin{proof}
+    We'll first analyze statements in the innermost loop. In line $4$, constructing diff\_cols can be done in $O(nr)$ by iteratively scanning the columns of $w$. 
+    In line $7$ checking if $w'$ satisfies the conditions of Theorem \ref{simp} is done in $O(r^2)$ time by keeping a count of the number of $0, 1, S$ in each column.
+Thus, the innermost portion of the loop has run time $= O(nr +r^2) = O(n^2)$.
+The total run time is bounded as follows:
+    {\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}\begin{flalign*}
+        \text{runtime}(\text{REST}(v)) &= \sum_{r=3}^{min(m, n+1)} \binom{m}{r} O(n^2) 
+        % \\
+        % &= O(n^2) \sum_{r=0}^{m} \binom{m}{r} 
+        = O(n^2 2^m).
+    \end{flalign*}}
+\end{proof}
+
+\begin{wrapfigure}[13]{r}{0.5\textwidth}
+  \centering
+        \includegraphics[width=0.5\textwidth]{images/RESTtime.png}
+        \caption{\small For most inputs, REST's run time is exponential with respect to the input length.}
+        \label{fig:RESTexp}  
+\end{wrapfigure}
+We provide an experimental evaluation of run time using randomly-generated sets of regular expressions satisfying the conditions of REST.
+Unfortunately, results suggest that the average case time complexity of is the worst case.\\
+We generated 100 sets of regular expressions satisfying the REST conditions, with $n$ between $10$ and $25$. 
+We measured the amount of time in seconds taken to run the program.
+We ran these experiments on an Intel(R) Xeon(R) Gold 6140 CPU @ 2.30GHz with 376 GB RAM, taking over one hour.
+We conclude that REST is not advisable to use as a part of the WEST program because it is often too computationally expensive.
+
+% \subsection{Implementation Challenges of the Regular Expression Simplification Theorem}
+% First, the proof of our algorithm relies on a set of $n+1$ regular expressions, yet it is obvious that the inclusion of redundant regular expressions of the same computation length in the union wouldn't alter this equivalence.
 A program implementation of this theorem would require an algorithm to parse through and identify which of these regular expressions are redundant and don't match the format of those described in our proof.
-
-\begin{figure}[h!]
-\begin{minipage}{.62\textwidth}
-\begin{example} \label{example1}
-Consider the MLTL formula:
-$T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$.
-The WEST program outputs a union of regular expressions represented by the matrix in \eqref{matrix_ex3}.
+% \begin{figure}[h!]
+% \begin{minipage}{.62\textwidth}
+% \begin{example} \label{example1}
+% Consider the MLTL formula:
+% $T \ \mathcal{U_{[\text{0,3}]}} p_0 = \mathcal{F_{[\text{0,3}]}}p_0$.
+% The WEST program outputs a union of regular expressions represented by the matrix in \eqref{matrix_ex3}.
 Instances like this demonstrate the utility of the regular expression simplification theorem; a recursive function implementation of this theorem would simplify output to the arbitrary computation.
 However, we foresee some challenges to the implementation of this algorithm.
-\end{example}
-\end{minipage}
-\begin{minipage}{.38\textwidth}
-%     \noindent \textbf{Example:}
-    % \vspace{-0.05\textwidth}
-\begin{equation} \label{matrix_ex3}
-    \begin{pmatrix}
-    1 & S & S & S\\
-    S & 1 & S & S\\
-    S & S & 1 & S\\
-    S & S & S & 1\\
-    0 & 0 & 0 & 0
-    \end{pmatrix}
-\end{equation}
-\end{minipage}
-\end{figure}
-For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
+% \end{example}
+% \end{minipage}
+% \begin{minipage}{.38\textwidth}
+% %     \noindent \textbf{Example:}
+%     % \vspace{-0.05\textwidth}
+% \begin{equation} \label{matrix_ex3}
+%     \begin{pmatrix}
+%     1 & S & S & S\\
+%     S & 1 & S & S\\
+%     S & S & 1 & S\\
+%     S & S & S & 1\\
+%     0 & 0 & 0 & 0
+%     \end{pmatrix}
+% \end{equation}
+% \end{minipage}
+% \end{figure}
+% For example, adding the row ``$1,1,1,1$" to the matrix generated by example \ref{example1} would change the matrix to not match the specifications of the theorem, but the union would still simplify to the arbitrary computation.
 Next, it is possible that a regular expression could be appended with a substring of ``$S$'' characters at the beginning or end.
-\begin{figure}[h!]
-\begin{minipage}{.62\textwidth}
-\begin{example} \label{example2}
-Consider the following MLTL formula: $T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$.
+% \begin{figure}[h!]
+% \begin{minipage}{.62\textwidth}
+% \begin{example} \label{example2}
+% Consider the following MLTL formula: $T \ \mathcal{U_{[\text{2,3}]}} p_0 \equiv \mathcal{F_{[\text{2,3}]}}p_0$.
 The WEST program generates a union of regular expressions corresponding to the matrix shown in \eqref{matrix_ex4}.
 This is equivalent to the arbitrary computation, as one can remove the first two columns and apply the simplification theorem to the remaining columns.
-\end{example}
-\end{minipage}
-\begin{minipage}{.38\textwidth}
-\begin{equation} \label{matrix_ex4}
-    \begin{pmatrix}
-      S & S & 1 & S \\
-      S & S & S & 1 \\
-      S & S & 0 & 0
-    \end{pmatrix}
-\end{equation}
-\end{minipage}
-\end{figure}
-
-Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
+% \end{example}
+% \end{minipage}
+% \begin{minipage}{.38\textwidth}
+% \begin{equation} \label{matrix_ex4}
+%     \begin{pmatrix}
+%       S & S & 1 & S \\
+%       S & S & S & 1 \\
+%       S & S & 0 & 0
+%     \end{pmatrix}
+% \end{equation}
+% \end{minipage}
+% \end{figure}
+% Furthermore, identical substrings may be interspersed throughout the set of regular expressions.
 Then, the union of them won't simplify to the arbitrary computation, but rather, the arbitrary computation ``broken up'' by common substrings.
 Consider the following modification to the matrix generated by example \ref{example1}:\\
-\begin{minipage}{.5\textwidth}
-The substrings ``$0$,'' ``$1S0$,'' and ``$1$'' are inserted at the beginning, middle, and end, respectively.
+% \begin{minipage}{.5\textwidth}
+% The substrings ``$0$,'' ``$1S0$,'' and ``$1$'' are inserted at the beginning, middle, and end, respectively.
 In general, a vector of length $m$ strings seeking to apply the theorem to $n$ of its columns has $m \choose n$ combinations of columns to check for.
 Implementation of this algorithm can drastically increase run-time while proving its utility in only a small number of circumstances.
-\end{minipage}
-\begin{minipage}{.5\textwidth}
-\begin{center}
-$
-\begin{pmatrix}
-  0 & \mathbf{1} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
-  0 & \mathbf{S} & \mathbf{1} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
-  0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{1} & \mathbf{S} & 1\\
-  0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{1} & 1\\
-  0 & \mathbf{0} & \mathbf{0} & 1 & S & 0 & \mathbf{0} & \mathbf{0} & 1\\
-    \end{pmatrix} 
-    \vspace{2mm}
-    \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
-$
-\end{center}
-\end{minipage}
+% \end{minipage}
+% \begin{minipage}{.5\textwidth}
+% \begin{center}
+% $
+% \begin{pmatrix}
+%   0 & \mathbf{1} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
+%   0 & \mathbf{S} & \mathbf{1} & 1 & S & 0 & \mathbf{S} & \mathbf{S} & 1\\
+%   0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{1} & \mathbf{S} & 1\\
+%   0 & \mathbf{S} & \mathbf{S} & 1 & S & 0 & \mathbf{S} & \mathbf{1} & 1\\
+%   0 & \mathbf{0} & \mathbf{0} & 1 & S & 0 & \mathbf{0} & \mathbf{0} & 1\\
+%     \end{pmatrix} 
+%     \vspace{2mm}
+%     \equiv  0\mathbf{S}\mathbf{S}1S0  \mathbf{S}\mathbf{S}1
+% $
+% \end{center}
+% \end{minipage}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Using WEST: An Example}\label{Using WEST}
+In this section we include a \href{https://youtu.be/HoBJwdCq42c}{[Video]} tutorial to show how a user can use the WEST program to explore specifications.
+The video uses the example formula $(p_0 \land \mathcal{G}_{[0,3]}p_1) \rightarrow p_2$ from \cite{KZJZR20}.
+The WEST program interface can aid a user in the process of validation by allowing them to explore the behavior of the formula and its subformulas.
+The user can input specific computations and confirm whether or not they satisfy the given formula.
+
+% \begin{minipage}[t]{0.48\textwidth}
+% \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.45]{images/initial.png}
+%     \caption{\small When the user types in a well-formed MLTL formula, they have the option to use \texttt{simplify} or REST.
+We choose only the former.The user can now explore the satisfying computations of either the specification in its entirety or its subformulas.
+Clicking on the last subformula in the list gives \ref{fig:SS2}.}
+%     \label{fig:SS1}
+% \end{figure}
+% \end{minipage} \hfill
+% \begin{minipage}[t]{0.48\textwidth}
+%     \begin{figure}[H]
+%         \centering
+%         \includegraphics[scale=0.35]{images/subformula.png}
+%         \caption{\small The computation demonstrated by the check boxes both satisfies the green regular expressions and the formula itself.
+Here the user can toggle the truth value of each variable at every time step or choose a random satisfying computation.
+Clicking any of the regular expressions will generate a random computation of that form, while clicking \texttt{Rand Comp} gives a random satisfying computation of any form.}
+%         \label{fig:SS2}
+%     \end{figure}
+% \end{minipage}
+
+% \begin{minipage}{0.48\textwidth}
+%    \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.35]{images/unsat.png}
+%     \caption{\small If the user toggles a computation that doesn't satisfy the formula, none of the regular expressions turn green and the formula itself turns red.}
+%     \label{fig:SS3}
+% \end{figure} 
+% \end{minipage} \hfill
+% \begin{minipage}{0.48\textwidth}
+%     \begin{figure}[H]
+%     \centering
+%     \includegraphics[scale=0.35]{images/backbone.png}
+%     \caption{\small The Backbone Analysis tab describes which propositional variables must hold true or false at which time steps in order for a computation to satisfy or not satisfy the given formula.}
+%     \label{fig:SS4}
+% \end{figure}  
+% \end{minipage}
+
 \section{Closing Remarks}
 \label{Conclusion}
- One goal of this research project is to visually represent MLTL formulas as truth tables, similar to classical truth tables in propositional logic. 
-The goal is motivated by the fact that MLTL is widely used in industry by engineers and scientists to write specifications for safety-critical systems, and the WEST program can aid in the debugging of such specifications.
-The WEST program accomplishes this: given a MLTL formula $\phi$, we compute a way to capture all satisfying formulas $\pi$ in a relatively readable format that additionally captures structural patterns in such regular expressions.
-The tool itself has demonstratively reasonable run time. 
-Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very rare in practice. 
-We have also applied techniques in intelligent fuzzing to explore the state space of the algorithm in a structured way. 
-For a reasonably complex program, a complete walk of the input space is infeasible. 
-However, basing testing on a (manually constructed) graph of the algorithm provides a middle ground where some level of coverage is guaranteed. 
-Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used for algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
-\subsection{Additional Research Directions} The release of the WEST algorithm and open-source tool open many promising avenues for future research, including the following.\\
-\textbf{Describe all satisfying computations to LTL formulas using $\omega$-regular expressions.}
-By definition, $\omega$-regular expressions match only infinite words, and can be used to describe satisfying computations to LTL formulas (which have infinite time steps). 
+%  One goal of this research project is to visually represent MLTL formulas as truth tables, similar to classical truth tables in propositional logic.
+MLTL is widely used in industry by engineers and scientists to write specifications for safety-critical systems, and the WEST program can aid in the debugging of such specifications.
+% The WEST program accomplishes this: given a MLTL formula $\phi$, we use regular expressions to capture all satisfying computations $\pi$ in a readable format that additionally captures structural patterns.
+The tool itself has demonstratively reasonable run time for most inputs.
+The primary goal of this work is to visually represent MLTL formulas as truth tables to aide in debugging of MLTL specifications in industrial domains.
+We have accomplished this with our regular expressions framework, which captures many structural patterns of satisfying computations for a given MLTL formula.
+The tool itself has demonstratively reasonable run time for most inputs, and the correctness of outputs has been verified to a high degree of confidence through intelligent fuzzing.
+%Although worst case theoretical complexity is doubly exponential, our benchmarking shows that the most severe case is very rare in practice. 
+% We have also applied techniques in intelligent fuzzing to explore the state space of the algorithm in a structured way. 
+% For a reasonably complex program, a complete walk of the input space is infeasible. 
+% However, basing testing on a (manually constructed) graph of the algorithm provides a middle ground where some level of coverage is guaranteed. 
+% Although this isn't a magic box that generates test cases for arbitrary algorithms, the methods used for algorithmic analysis and test suite construction are easily adaptable to similar recursive algorithms.
+\subsection{Additional Research Directions} The WEST algorithm and release of our open-source tool open many promising avenues for future research. \\
+\textbf{Similar Analysis of LTL and LTLf.}
+$\omega$-regular expressions match only infinite words, and can be used to describe satisfying computations of LTL formulas.% (which have infinite time steps).
 Our work on validation for MLTL formulas lays the groundwork for future work on validation of the finite-trace logic LTLf \cite{GV13} as well as LTL formulas.
-For the infinite-trace semantics of LTL, the particular difficulties revolve around the need for the Kleene star operation, which may lead to blow-up due to arithmetic of infinite unions and intersections of regular expressions.
-\\
+For the infinite-trace semantics of LTL, the particular difficulties revolve around the Kleene star operation, which behave poorly due to computing infinite unions and intersections of regular expressions.\\
 \noindent \textbf{Simplifying unions of regular expressions to a minimal representation.}
 Theorem \ref{simp} addresses a non-trivial situation in which a set of regular expressions may be simplified.
-A natural question to ask is what is the minimum number of strings of regular expressions needed to represent a language of computations.
+A natural question to ask is what is the minimum number of regular expressions needed to represent a language of computations.
 However, such a minimal representation is not unique.
-For instance, $\mathscr{L}(S1|1S) = \mathscr{L}(S1|10) = \{01, 10, 11\}$.
-There may be other schemes needed to simplify any arbitrary union of regular expressions to their minimal representation.\\
-\noindent \textbf{A more general application of intelligent fuzzing to recursive algorithms.}
-A tool to systematically convert a recursive algorithm (perhaps written in some strictly defined pseudocode syntax) into a directed graph representation of the state space would be a helpful aid for generating test suites.
-Significant efforts were made to construct the graph of the WEST algorithm by hand, and an automated process would be invaluable. 
+For instance, $\{S1, 1S\} = \{S1, 10\} = \{01, 10, 11\}$.
+Other schemes may needed to simplify any arbitrary union of regular expressions to a minimal representation.\\
+\noindent \textbf{Intelligent Fuzzing to General Recursive Algorithms.}
+A tool to systematically convert a recursive algorithm
+% (perhaps written in some strictly defined pseudocode syntax) 
+into a directed graph representation of the state space would be a helpful aid for generating test suites. 
+% Significant efforts were made to construct the graph of the WEST algorithm by hand, and an automated process would be invaluable. 
 Additional care should be put into allowing for varying levels of abstractions of execution due to concerns of the path explosion problem.
-We note that such avenues for code-level verification will still be necessary even upon the completion of potential future work avenues like synthesizing the core implemention of the WEST algorithm from an interactive theorem prover.
-This is because the goal of explainability to humans will require at least some manual code authorship for the forseeable future.
+We note that such avenues for code-level verification will still be necessary even upon the completion of potential future work avenues like synthesizing the core implementation of the WEST algorithm from an interactive theorem prover.
+This is because the goal of explainability to humans will require at least some manual code authorship for the foreseeable future.
 \\
@@
 %a proof-generating C code synthesizer \cite{DBLP:journals/corr/abs-2205-11708} based on the Axe tool \cite{DBLP:phd/us/Smith11} generates verified software implementing the behaviors originally described in MLTL.
-By providing a new front-end for this toolchain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system.
+By providing a new front-end for this tool chain, we have now enabled a path to generating provably correct software from validated MLTL formulas describing the desired behaviors of a system.
 Considering the rising popularity of MLTL for describing such behaviors, we expect this to be a rewarding avenue for future exploration.
+
+% An attractive alternative for future work involves encoding our proofs in an interactive theorem prover and utilizing a verified code generator like PVS2C\cite{Sha17} or the Isabelle/HOL code generator \cite{HB21}.
 
@@
 \renewcommand{\thesection}{\Roman{section}}
-Content in the appendices will appear online, on the paper's website, but appears here for now due to blind review.
+\section{Minimum Computation Length}
+\label{complen-proof}
+\renewcommand\thetheorem{1}
+\begin{theorem}[\emph{Minimum Computation Length of Until and Release}]
+    Let $0 \leq a\leq b \in \mathbb{N}$ and let $\phi, \psi$ be well-formed MLTL formulas in NNF.
+The minimum computation length of \emph{Until} and \emph{Release} is given by $\emph{cplen}(\phi \mathcal{U}_{[a,b]} \psi) = \emph{cplen}(\phi \mathcal{R}_{[a,b]} \psi) = b + \max(\emph{cplen}(\phi)-1, \emph{cplen}(\psi))$.
+\end{theorem}
+
+\begin{proof}
+ Recall that $\text{reg}(\phi \ \mathcal{U}_{[a,b]} \psi) =  \bigvee_{i=a}^{b} \text{reg}\left(\mathcal{G}_{[a,i-1]}\phi \land \mathcal{G}_{[i, i]} \psi\right)$. Thus
+ \begin{align*}
+     \text{cplen}(\phi \mathcal{U}_{[a,b]} \psi) &= \max_{a \leq i \leq b} \left( \text{cplen}(\mathcal{G}_{[a, i-1]} \phi \land \mathcal{G}_{[i,i]} \psi) \right)\\
+     &= \max_{a \leq i \leq b} \left( \max(i-1 + \text{cplen}(\phi), i + \text{cplen}(\psi))\right)\\
+     &= \max_{a \leq i \leq b} \left(i + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi))\right)\\
+     &= b + \max(\text{cplen}(\phi) - 1, \text{cplen}(\psi)).
+ \end{align*}
+ % \vspace{-0.1in}
+ Now recall that $\text{reg}(\phi \mathcal{R}_{[a,b]} \psi) =  \text{reg}\left(\mathcal{G}_{[a,b]}\psi\right) \lor \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right)$.
+Thus%
+% \vspace{-0.1in}
+ \begin{align*}
+     \text{cplen}(\phi \mathcal{R}_{[a,b]} \psi) &= \max \left( \text{cplen}(\mathcal{G}_{[a,b]} \psi), \text{cplen}\left( \bigvee_{i=a}^{b-1} \text{reg}\left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)  \right)\\
+     &= \max\left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\mathcal{G}_{[a,i]}\psi \land \mathcal{G}_{[i, i]} \phi\right) \right)\\
+     &= \max \left( b + \text{cplen}(\psi), \max_{a \leq i \leq b-1} \left(\max(i + \text{cplen}(\psi), i + \text{cplen}(\phi))\right) \right)\\
+     &= \max \left( b + \text{cplen}(\psi), \max(b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\right)\\
+     &= \max(b + \text{cplen}(\psi), b-1+\text{cplen}(\phi), b-1+\text{cplen}(\psi))\\
+     &= b + \max(\text{cplen}(\phi)-1, \text{cplen}(\psi)). 
+ \end{align*}
+% This completes the proof.
+ \end{proof}
 
  \section{Soundness and Completeness} \label{Appendix-SoundComplete}
-%  \vspace{-0.1in}
- We write $\mathscr{L}(\text{reg}(\phi))$ to denote the language of reg($\phi$). That is, the set of computations represented by the regular expression $\text{reg}(\phi)$.
-\begingroup
 \renewcommand\thetheorem{2}
@@
 \end{theorem}
-\endgroup
  \begin{proof}
@@
 \renewcommand\thetheorem{3}
- \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}] \label{NestedUR}
+ \begin{theorem}[\emph{Nested Until and Release Rewriting Theorem}]
    Any MLTL formula using the Until or Release operator can be rewritten with right-nested subformulas.
@@
 \section{Regular Expression Simplification Theorem} \label{simp_appendix}
-\begin{proof}[Theorem \ref{simp}]
+\renewcommand\thetheorem{7}
+\begin{theorem}[\emph{Regular Expression Simplification Theorem}]
+Let $M$ be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length $n$ with commas stripped.
+If each column has one ``$1$,'' one ``$0$,'' and $n-1$ ``$S$'' characters, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.
+\end{theorem}
+\begin{proof}
 Assume no row is the arbitrary computation, because then the union of the set of regular expressions would trivially simplify to the arbitrary computation.\\
@@
 We denote these regexes by $R$ and $T$.
-Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.
+Additionally, $n$ will always refer to the number of propositional variables, and nnf refers to an input formula in negation normal form.\\
+
+\begin{algorithm}[H] 
+\caption{WEST Algorithm}
+Inputs: $\phi$ - MLTL formula in NNF \\
+$\phi_1$ and $\phi_2$ below are subformulas of $\phi$\\
+$n$ - number of propositional variables \\
+Output: set of REGEX satisfying $\phi$
+\begin{algorithmic}
+    \Procedure{reg}{string $\phi$, int $n$}
+        \If{$\phi$ is $\top$ or $\bot$}
+            \State return reg\_prop\_const($\phi$, n)
+        \EndIf
+
+        \If{$\phi$ is $p_k$ or $\neg p_k$}
+            \State return reg\_prop\_var($\phi$, n)
+        \EndIf
+
+        \If{$\phi  = \phi_1 \land \phi_2$}
+            \State \parbox[t]{.82\linewidth}{return set\_intersect(reg($\phi_1$), reg($\phi_2$), \hspace*{5mm}n)}
+        \EndIf
+
+        \If{$\phi  = \phi_1 \lor \phi_2$}
+            \State return join(reg($\phi_1$), reg($\phi_2$), n)
+        \EndIf
+
+        \If{$\phi = \mathcal{F}_{[a, b]}\phi_1$}
+            \State return reg\_F(reg($\phi_1$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \mathcal{G}_{[a, b]}\phi_1$}
+            \State return reg\_G(reg($\phi_1$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \phi_1 \mathcal{U}_{[a, b]} \phi_2$}
+            \State return reg\_U(reg($\phi_1$), reg($\phi_2$), a, b, n)
+        \EndIf
+
+        \If{$\phi = \phi_1 \mathcal{R}_{[a, b]} \phi_2$}
+            \State return reg\_R(reg($\phi_1$), reg($\phi_2$), a, b, n)
+        \EndIf
+    \EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
 \begin{algorithm}[H]
@@
 \end{algorithm}
+
 \begin{algorithm}[H]
 \caption{Computes regex for propositional constant}
-Input: String that is either ``T" or ``!", number of propositional variables\\
+Input: String that is either ``true" or ``false", number of propositional variables\\
 Output: set of strings that represents the appropriate satisfying computations
@@
 \Procedure{reg\_prop\_cons}{string nnf, int $n$}
-    \If {(nnf $=$ ``T" and $n \neq 0$)} return $\{S^n\}$
+    \If {(nnf $=$ ``true" and $n \neq 0$)} return $\{S^n\}$
     \Else \hspace{1mm} return $\{\}$ 
@@
 \end{algorithm}
+
 \begin{algorithm}[H]
@@
 \end{algorithm}
-\begin{algorithm}[H]
-\caption{Combines two strings that differ only by one character into one}
-Input: Two strings that represent regexes\\
-Output: Single string that represents computations represented by both input strings or FAIL
-\begin{algorithmic}
-\Procedure{simplify\_string}{string $r$, string $t$}   
-    \If{($r$.length() $\neq$ $t$.length())} exit
-        \EndIf
-    \For{($0 \leq i < r$.length())}
-        \State pre\_r $\leftarrow r[0, i-1]$ 
-        \State char\_r $\leftarrow r[i]$ 
-        \State post\_r $\leftarrow r[i+1, r\text{.length()}-1]$ 
-        \State pre\_t $\leftarrow t[0, i-1]$ 
-        \State char\_t $\leftarrow t[i]$ 
-        \State post\_t $\leftarrow t[i+1, t\text{.length()}-1]$
-        \If{(pre\_r $=$ pre\_t and post\_r $=$ post\_t)}
-            \If{(char\_r $\neq$ char\_t)}
-                \State return pre\_r +``$S$" + post\_r 
-            \Else
-                \State return $r$
-            \EndIf
-        \EndIf
-    \EndFor
-    \State return FAIL 
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[H]
-\caption{Simplifies a set of strings using simplify\_string}
-Input: set of strings representing a regex\\
-Output: set of strings representing a regex simplified using simplify\_string
-\begin{algorithmic}
-\Procedure{simplify}{set $R$}    
-    \State Pad all strings in $R$ to the same length
-    \If{($R$.length() $\leq 1$)} return $R$
-        \EndIf
-    \State $i = R\text{.length} - 1$
-    \State $j = i - 1$
-
-    \State START
-    \While{($i \geq 1$)}
-        \While{($j \geq 0$)}
-            \State simplified = simplify\_string($R[i]$, $R[j]$) 
-            \If{(simplified $\neq$ FAIL)}
-                \State replace string at index $j$ with simplified
-                \State remove string at index $i$ from $R$
-                \State $i = R\text{.length()} - 1$
-                \State $j = i - 1$
-                \State goto START
-                \EndIf
-            \State -{}-$j$
-            \EndWhile
-        \State -{}-$i$
-        \State $j = i - 1$
-        \EndWhile
-
-    \State return $R$
-\EndProcedure
-\end{algorithmic}
-\end{algorithm}
+
 \begin{algorithm}[H]
@@
     \State return ret
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{set\_intersect}
+Inputs: $R, T$ - two sets of REGEX\\
+$n$ - number of propositional variables\\
+Output: set of REGEX equal to $R \land T$
+\begin{algorithmic}
+\Procedure{set\_intersect}{$R$, $T$, n}
+    \State Pad($R$, $T$, n), return $\leftarrow \{\}$
+    \For{$(r, t) \in R\times T$}
+            \State add bit\_wise\_and($r, t$) to ret 
+    \EndFor
+    \State return simplify(ret)
 \EndProcedure
@@
 \end{algorithm}
+
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula F[a:b]$\phi$}
+\caption{Computes the regex for a MLTL formula F[a,b]$\phi$}
 Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
@@
 \end{algorithm}
+
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula G[a:b]$\phi$}
+\caption{Computes the regex for a MLTL formula G[a,b]$\phi$}
 Inputs: set of strings representing the regex for $\phi$, interval bounds, number of propositional variables, simplify boolean\\
@@
 \end{algorithm}
+
 \begin{algorithm}[H]
-\caption{Computes the regex for a MLTL formula $\phi$R[a:b]$\psi$}
+\caption{Computes the regex for a MLTL formula $\phi$U[a,b]$\psi$} 
+Inputs: $r_\phi$, $r_\psi$ - sets of REGEX for MLTL formulas $\phi$ and $\psi$ (after calling reg)\\
+$a, b$ - integers representing interval bound \\
+$n$ - number of propositional variables\\
+Output: set of REGEX for $\phi \mathcal{U}_{[a, b]} \psi$
+\begin{algorithmic}
+\Procedure{reg\_U}{$r_\phi$, $r_\psi$, $a$, $b$, $n$} 
+    \State comp $\leftarrow$ ((`$S$')$^{n}$ + `,')$^{a} + $ r\_$\psi$
+    \If{$a > b$} return $\{\}$
+    \EndIf
+    \For{($a \leq i \leq b-1$) }
+        \State G1 $\leftarrow$ reg\_G($r_\phi$, $a$, $i$, $n$)
+        \State \parbox[t]{.8\linewidth}{G2 $\leftarrow$ reg\_G($r_\psi$, $i+1$, $i+1$, $n$)}
+        \State \parbox[t]{.8\linewidth}{temp\_comp $\leftarrow$ set\_intersect(G1,  \hspace*{5mm}G2, n)}
+        \State \parbox[t]{.8\linewidth}{comp $\leftarrow$ join( comp, temp\_comp)}
+        % , \hspace*{5mm}simp)}
+    \EndFor
+    \State return comp
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{Computes the regex for a MLTL formula $\phi$R[a,b]$\psi$}
 Inputs: sets of strings representing the regexes for $\phi$ and $\psi$, interval bounds, number of propositional variables, simplify boolean\\
@@
 \end{algorithm}
+
+\begin{algorithm}[H]
+\caption{Combines two strings that differ only by one character into one}
+Input: Two strings that represent regexes\\
+Output: Single string that represents computations represented by both input strings or FAIL
+\begin{algorithmic}
+\Procedure{simplify\_string}{string $r$, string $t$}   
+    \If{($r$.length() $\neq$ $t$.length())} exit
+        \EndIf
+    \For{($0 \leq i < r$.length())}
+        \State pre\_r $\leftarrow r[0, i-1]$ 
+        \State char\_r $\leftarrow r[i]$ 
+        \State post\_r $\leftarrow r[i+1, r\text{.length()}-1]$ 
+        \State pre\_t $\leftarrow t[0, i-1]$ 
+        \State char\_t $\leftarrow t[i]$ 
+        \State post\_t $\leftarrow t[i+1, t\text{.length()}-1]$
+        \If{(pre\_r $=$ pre\_t and post\_r $=$ post\_t)}
+            \If{(char\_r $\neq$ char\_t)}
+                \State return pre\_r +``$S$" + post\_r 
+            \Else
+                \State return $r$
+            \EndIf
+        \EndIf
+    \EndFor
+    \State return FAIL 
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{Simplifies a set of strings using simplify\_string}
+Input: set of strings representing a regex\\
+Output: set of strings representing a regex simplified using simplify\_string
+\begin{algorithmic}
+\Procedure{simplify}{set $R$}    
+    \State Pad all strings in $R$ to the same length
+    \If{($R$.length() $\leq 1$)} return $R$
+        \EndIf
+    \State $i = R\text{.length} - 1$
+    \State $j = i - 1$
+
+    \State START
+    \While{($i \geq 1$)}
+        \While{($j \geq 0$)}
+            \State simplified = simplify\_string($R[i]$, $R[j]$) 
+            \If{(simplified $\neq$ FAIL)}
+                \State replace string at index $j$ with simplified
+                \State remove string at index $i$ from $R$
+                \State $i = R\text{.length()} - 1$
+                \State $j = i - 1$
+                \State goto START
+                \EndIf
+            \State -{}-$j$
+            \EndWhile
+        \State -{}-$i$
+        \State $j = i - 1$
+        \EndWhile
+
+    \State return $R$
+\EndProcedure
+\end{algorithmic}
+\end{algorithm}
+
 \begin{algorithm}[H]
@@
 
-    \node[emptynode](prop_cons_text)[left=0.01cm of start]{nnf is T or !$$~$$};
+    \node[emptynode](prop_cons_text)[left=0.01cm of start]{nnf is true or false$$~$$};
     \node[emptynode](prop_var_text)[rotate=-43, above=1.1cm of prop_cons_text]{nnf is p or $\scriptstyle{\sim}\textstyle$p};
@@
     \node[emptynode](binary_prop_text)[right=1.4cm of unary_text]{$$~$$$$~$$$$~$$nnf is $\phi$ X $\psi$};
-    \node[emptynode](join_text)[above=0.2cm of join]{X is v};
+    \node[emptynode](join_text)[above=0.2cm of join]{X is $|$};
     \node[emptynode](intersect_text)[right=1.75cm of join_text]{X is \&};
-    \node[emptynode](implies_text)[right=-0.25cm of prop_psi]{X is $>$};
+    \node[emptynode](implies_text)[right=-0.25cm of prop_psi]{X is -$>$};
     \node[emptynode](equals_text)[right=-1.2cm of reg_f_text]{X is =};

### 2023-06-16 paper/Paper.tex
updated paper
minor fixes: passive voice, grammar, typos

@@
 
+%% Save the class definition of \subparagraph
+\let\llncssubparagraph\subparagraph
+%% Provide a definition to \subparagraph to keep titlesec happy
+\let\subparagraph\paragraph
+%% Load titlesec
+\usepackage[compact]{titlesec}
+%% Revert \subparagraph to the llncs definition
+\let\subparagraph\llncssubparagraph
+
 % Spacing: left, before, after
@@
 %\title{Contribution Title\thanks{Supported by organization x.}}
-\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by NSF grant DMS-1950583}}
+\title{Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by NSF grant DMS-1950583 and NSF CAREER Award CNS-1552934.}}
 %
@@
 NASA, for example, has developed several tools that operate over temporal logic requirements, such as FRET\cite{GMRPSS20}, R2U2\cite{RS17}, and a PVS library \cite{CTGPD22} for the logic MLTL (Mission-time Linear Temporal Logic) \cite{RRS14,LVR22}.
-MLTL was the logic used recently in NASA's Robonaut2 verification project \cite{KZJZR20} and is being used currently for both design-time and runtime verification of the NASA Lunar Gateway Vehicle System Manager \cite{DBR21}.
+MLTL was the specification logic for NASA's Robonaut2 verification project \cite{KZJZR20} and is currently the specification logic for both design-time and runtime verification of the NASA Lunar Gateway Vehicle System Manager \cite{DBR21}.
 Other recent verification %verification-for-certification
@@
 % \vspace{-0.1in}
-We modify the standard definition of Regular Expressions (Regex) to introduce notation that describes the satisfying computations of an MLTL formula.
+We modify the standard definition of Regular Expressions (regex) to introduce notation that describes the satisfying computations of an MLTL formula.
 We begin by quoting the parts of the standard definition of a regex from \cite{sipser} that we use to describe our computations:
@@
 For for regular expressions $w_0$ and $w_1$, a useful reduction is that $\{w_0 1 w_1, w_0 0 w_1\} = \{w_0 s w_1\}$.
-Each time set intersection is performed, we greedily apply this reduction to all appropriate pairs of regular expressions in the set.
+Each time we perform set intersection, we greedily apply this reduction to all appropriate pairs of regular expressions in the set.
 This prevents repeated set intersection operations from blowing up exponentially most of the time, and drastically improves running time.
@@
  For $0\leq k \leq n-1$, consider the propositional variable $p_k$. If $\pi$ satisfies $p_k$, then $p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
- $$S^{k} 1 S^{n-k-1}$$
+ $$S^{k} 1 S^{n-k-1}$$,
  which is precisely reg($p_k$).\\
@@
  If $\pi$ satisfies $\neg p_k$, then $\neg p_k$ evaluates to true at $\pi[0]$. This is equivalent to writing that $\pi[0]$ is of the form 
- $$S^{k} 0 S^{n-k-1}$$
+ $$S^{k} 0 S^{n-k-1}$$,
  which is precisely reg($\neg p_k$).\\
